### 2017-07-24 paper/ms.tex
Skeletal paper repo for studying explosions from the Brooks, et al hybrid model.

%\documentclass[12pt,preprint]{aastex}
\documentclass[iop,apj]{emulateapj}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{ulem}
%\usepackage[monochrome]{color}
\usepackage{color}
\usepackage{lipsum}
\usepackage{amsmath}
%\usepackage{hyperref}

\newcommand{\eqqref}[1]{Equation (\ref{#1})}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\appref}[1]{Appendix~\ref{#1}}

\newcommand{\SNeIa}{SNe~Ia}
\newcommand{\SNIa}{SN~Ia}
\newcommand{\C}[1]{\ensuremath{{}^{#1}{\rm C}}}
\newcommand{\Ox}[1]{\ensuremath{{}^{#1}{\rm O}}}
\newcommand{\Ne}[1]{\ensuremath{{}^{#1}{\rm Ne}}}
\newcommand{\Na}[1]{\ensuremath{{}^{#1}{\rm Na}}}
\newcommand{\Mg}[1]{\ensuremath{{}^{#1}{\rm Mg}}}
\newcommand{\Ni}[1]{\ensuremath{{}^{#1}{\rm Ni}}}
\newcommand{\Co}[1]{\ensuremath{{}^{#1}{\rm Co}}}
\newcommand{\Si}[1]{\ensuremath{{}^{#1}{\rm Si}}}
\newcommand{\Fe}[1]{\ensuremath{{}^{#1}{\rm Fe}}}
\newcommand{\code}[1]{\textsc{#1}}
\newcommand{\FLASH}{\code{FLASH}}
\newcommand{\CASTRO}{\code{CASTRO}}
\newcommand{\MESA}{\code{MESA}}
\newcommand{\PARAMESH}{\code{PARAMESH}}
\newcommand{\pv}{\ensuremath{\phi}}
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}} %boldface vector style
\newcommand{\grad}{\bvec{\nabla}} %gradient
\newcommand{\curl}{\bvec{\nabla \times}} %curl
\newcommand{\Atwood}{\ensuremath{\mathrm{At}}}
\newcommand{\adndt}{At.~Data~Nucl.~Data~Tables}
\newcommand{\At}{{\rm At}}
\newcommand{\ee}[1]{\ensuremath{\times 10^{#1}}}
\newcommand{\cdens}{\rho_{c}}

% basic unit typesetteing
\newcommand{\unitspace}{\ensuremath{\,}}
\newcommand{\usp}{\unitspace}
\newcommand{\numberspace}{\ensuremath{\;}}
\newcommand{\nsp}{\numberspace}
\newcommand{\unitstyle}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\power}[2]{\ensuremath{{#1}^{#2}}}

% prefixes
\newcommand{\nano}{\unitstyle{n}}
\newcommand{\milli}{\unitstyle{m}}
\newcommand{\centi}{\unitstyle{c}}
\newcommand{\kilo}{\unitstyle{k}}
\newcommand{\Mega}{\unitstyle{M}}
\newcommand{\Giga}{\unitstyle{G}}

% base units, mks
\newcommand{\meter}{\unitstyle{m}}
\newcommand{\kilogram}{\kilo\gram}
\newcommand{\second}{\unitstyle{s}}

\newcommand{\Kelvin}{\unitstyle{K}}
\newcommand{\K}{\Kelvin}  %degrees Kelvin

% base units, cgs
\newcommand{\cm}{\centi\meter}
\newcommand{\gram}{\unitstyle{g}}

% derived units
\newcommand{\grampercc}{\gram\usp\power{\cm}{-3}} %mass density
\newcommand{\grampersquarecm}{\gram\usp\power{\cm}{-2}} %column depth
\newcommand{\GramPerCc}{\grampercc}
\newcommand{\GramPerSc}{\grampersquarecm}
\newcommand{\columnunit}{\grampersquarecm}
\newcommand{\dyne}{\unitstyle{dyn}} %dyne
\newcommand{\erg}{\unitstyle{ergs}} %ergs
\newcommand{\ergs}{\erg}
\newcommand{\gauss}{\unitstyle{G}} %gauss
\newcommand{\ergspersecond}{\erg\unitspace\power{\second}{-1}}
\newcommand{\ergspergram}{\erg\unitspace\power{\gram}{-1}}
\newcommand{\cgsflux}{\erg\unitspace\power{\cm}{-2}\usp\power{\second}{-1}}
\newcommand{\kms}{\kilo\meter\unitspace\power{\second}{-1}}

% Nuclear and atomic units
\newcommand{\amu}{\unitstyle{u}} %atomic mass unit
\newcommand{\angstrom}{\mbox{\AA}} %Angstrom
\newcommand{\fermi}{\unitstyle{fm}} %fermi
\newcommand{\eV}{\unitstyle{eV}}        %eV
\newcommand{\keV}{\kilo\eV} %Kev
\newcommand{\MeV}{\Mega\eV} %MeV

% solar and astronomical units
\newcommand{\Msun}{\ensuremath{M_\odot}}
\newcommand{\Myr}{\Mega\yr}
\newcommand{\Gyr}{\Giga\yr}
\newcommand{\parsec}{\unitstyle{pc}}
\newcommand{\kpc}{\kilo\parsec} %kiloparsec
\newcommand{\mJy}{\unitstyle{\mu Jy}} %micro Jansky

% misc. units
\newcommand{\minute}{\unitstyle{min}} %minute
\newcommand{\hour}{\unitstyle{hr}} %hour
\newcommand{\yr}{\unitstyle{yr}}        %year
\newcommand{\km}{\kilo\meter}   %kilometers
\newcommand{\Hz}{\unitstyle{Hz}}        %Hertz
\newcommand{\ksec}{\kilo\second} %kilosecond

\newcommand{\tDDT}{\ensuremath{t_{\rm DDT}}}
\newcommand{\rhoDDT}{\ensuremath{\rho_{\rm DDT}}}
\newcommand{\COreac}{\ensuremath{\C{12}\left(\alpha,\gamma\right)\Ox{16}}}

\bibliographystyle{apj}

\shorttitle{Short Paper Title}

\begin{document}

\title{Paper Title}

\author{
Some Awesome People\altaffilmark{1,2,3,4}
}

\altaffiltext{1}{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
  \href{mailto:somebody@someplace}{somebody@someplace}
}
\altaffiltext{2}{
  Department of Physics and Astronomy,
  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
}
\altaffiltext{3}{
  Department of Physics and Astronomy,
  Stony Brook University, Stony Brook, NY, 11794-3800, USA
}
\altaffiltext{4}{
  Institute for Advanced Computational Sciences,
  Stony Brook University, Stony Brook, NY, 11794-5250, USA
}

\begin{abstract}
Awesome Abstract
\end{abstract}

\keywords{hydrodynamics --- nuclear reactions, nucleosynthesis, abundances
--- supernovae: general --- white dwarfs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Introduction with a pretty plot in \figref{fig:progenitor_abundances}.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{figures/samples/cf_wdb_mesa_comp_vs_mass.pdf}
	\caption{\label{fig:progenitor_abundances} Abundance profile
          of \MESA\ progenitor (\MESA) and its reconstruction on a
          uniform grid at $4$~km spatial resolution with the hydrostatic equilibrium condition of
          \eqqref{eq:hse_pressure} enforced (\FLASH). The reduced set
          of nuclides are shown, where $\mathrm{X_{\Ox{16}} = 1 -
            X_{\C{12}} - X_{\Ne{20}} - X_{\Ne{22}}}$ for the
          abundances labeled \FLASH. Solid lines and circles denote
          the abundances used in \FLASH\ whereas plain solid lines
          denote the abundances used in \MESA.}
\end{figure}

\section{Methodology}

Methodology goes here.

A handy example of a vertical multi-plot figure is \figref{fig:znd_abundances}.

\begin{figure}[t]
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_0_XC-50.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.5} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.50$, $X_{^{20}Ne} = 0.00$}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_20_XC-30.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.3} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.30$, $X_{^{20}Ne} = 0.20$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_35_XC-15.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.15} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, $X_{^{20}Ne} = 0.35$}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\textwidth}
		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_45_XC-05.pdf}
		%\caption{\label{fig:znd_abundances_xc12_0.05} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.05$, $X_{^{20}Ne} = 0.45$}
	\end{minipage}
        \caption{\label{fig:znd_abundances} Mass Fraction Evolution for ZND Detonations with varying initial \C{12} and \Ne{20} mass fractions, calculated for an initial density of $10^7~\grampercc$.}
\end{figure}

Here's a text citation \citet{timmes92,Chametal08}, and here's a parenthetical citation ~\citep{timmes.swesty:accuracy,castro1}.

Here's an ordinary equation in \eqref{eq:hse_pressure}.

\begin{equation}\label{eq:hse_pressure}
  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
  \rho_{i-1})\ .
\end{equation}

Here's a multi-line equation.

\begin{subequations}
\begin{align}
X_{\C{12}}^{FLASH} &= X_{\C{12}}^{MESA} \\
X_{\Ne{22}}^{FLASH} &= 22 \cdot \left(\dfrac{1}{2}-Y_e^{MESA}\right) \\
R &= X_{\Ne{20}}^{MESA}/X_{\Ox{16}}^{MESA} \\
X_{\Ox{16}}^{FLASH} &= \frac{1 - X_{\C{12}}^{FLASH} - X_{\Ne{22}}^{FLASH}}{R + 1} \\
X_{\Ne{20}}^{FLASH} &= R \cdot X_{\Ox{16}}^{FLASH}.
\end{align}
\end{subequations}

\section{Simulations and Results}

Simulations and results go here.

Example of multi-figure plot that spans the columns is given by \figref{fig:cone_delayed_core}.

\begin{figure*}[!ht]
  \begin{minipage}{0.24\textwidth}
    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0000"}
  \end{minipage} \hfill
  \begin{minipage}{0.24\textwidth}
    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0190"}
  \end{minipage} \hfill 
  \begin{minipage}{0.24\textwidth}
    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0200"}
  \end{minipage} \hfill 
  \begin{minipage}{0.24\textwidth}
    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0210"}
  \end{minipage} \caption{\label{fig:cone_delayed_core} Progress of the burning front into the stellar core for one hybrid C-O-Ne realization, delayed relative to complete burning throughout the rest of the star. For reference, the initially burned geometry is shown at left. Material is shaded based on the reaction progress variables so that \textbf{White} denotes unburned fuel (\C{12}, \Ox{16} \& \Ne{20}) and \textbf{Red} denotes ash from \C{12} and \Ne{20}-burning. \textbf{Green} then denotes material in quasi-nuclear statistical equilibrium (primarily intermediate-mass silicon-group elements), and \textbf{Black} denotes material in nuclear statistical equilibrium (IGEs and $\alpha$-particles). From left to right, the burning is shown at 0.0~\second, 1.9~\second, 2.0~\second, and 2.1~\second. The DDT time for this realization is $\approx \mathrm{1.4}~\second$.}
\end{figure*}

Example of a table with data, units, etc is at \tabref{YieldSummaryTable}.

\begin{table}[htbp]
  \caption{Average Yields and Kinetic Energy}
  \begin{center}
    \begin{tabular}{llll}
      \vspace{-0.75cm} \\ \hline \hline
      Progenitor & \Ni{56} & IGE & Kinetic Energy \\
      Type & (\Msun) & (\Msun) & $\left(\times 10^{51} ~\erg\right)$ \\ \hline
      C-O & $0.97 \pm 0.06$ & $1.12 \pm 0.07$ & $1.39 \pm 0.05$ \\
      C-O-Ne & $0.86 \pm 0.10$ & $0.98 \pm 0.11$ & $1.06 \pm 0.10$ \\ \hline
    \end{tabular}
  \end{center}
  \label{YieldSummaryTable}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}

Conclusive conclusions go here.

\section{Appendix}

If there's material for an appendix, it can go here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgements

We'd like to acknowledge helpful discussions with Cab Ernet.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SOFTWARE
%% \software{
%%   FLASH \citep{Fryxetal00},
%%   CASTRO \citep{castro1},
%%   MESA \citep{mesa1},
%%   Matplotlib \citep{http://dx.doi.org/10.5281/zenodo.44579}
%% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{master}

\end{document}

### 2017-07-24 paper/figures/eps2pdfall.py

@@ -1,0 +1,8 @@
+import glob
+import os
+
+fl = glob.glob('*.eps')
+
+for f in fl:
+        fb = f[:-4]
+        os.system('ps2pdf -dEPSCrop ' + f + ' ' + fb + '.pdf')

### 2017-07-24 paper/figures/eps2png.py

@@ -1,0 +1,15 @@
+import sys
+import os
+
+# Converts all eps files passed on the command line to png
+
+if len(sys.argv)==1:
+	exit()
+
+fl = sys.argv[1:]
+
+for f in fl:
+	fb = f[:-4]
+	os.system('ps2pdf -dEPSCrop ' + f + ' ' + fb + '.pdf')
+	os.system('gs -o ' + fb + '.png -sDEVICE=png16m  ' + 
+			'-dLastPage=1  -r300 ' + fb + '.pdf')

### 2017-07-24 paper/figures/epsprep.sh

@@ -1,0 +1,14 @@
+for var in "$@"
+do
+	cat $var | sed 's+Times-Bold+NimbusSanL-Bold+g' |\
+	sed 's+Times-Roman+NimbusSanL-Regu+g' |\
+	sed 's+Times+NimbusSanL-Regu+g' |\
+	sed 's+Helvetica-BoldOblique+NimbusSanL-BoldItal+g' |\
+	sed 's+Helvetica-Oblique+NimbusSanL-ReguItal+g' |\
+	sed 's+Helvetica-Bold+NimbusSanL-Bold+g' |\
+	sed 's+Helvetica-Bold-iso+NimbusSanL-Bold+g' |\
+	sed 's+Helvetica+NimbusSanL-Regu+g' |\
+	sed 's+Helvetica-iso+NimbusSanL-Regu+g' |\
+	sed 's+Symbol+StandardSymL+g' |\
+	sed 's+/BackgroundColor {-1.000 -1.000 -1.000} def+/BackgroundColor {1.000 1.000 1.000} def+g' > $var
+done

### 2017-07-24 paper/figures/prep.py

@@ -1,0 +1,7 @@
+import glob
+import os
+
+fl = glob.glob('*.eps')
+
+for f in fl:
+	os.system('./epsprep.sh ' + f)

### 2018-03-29 paper/ms.tex
Added Rough Outline

@@
 
-\shorttitle{Short Paper Title}
+\shorttitle{Hybrid Ia Progenitors}
 
@@
 
-\title{Paper Title}
+\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors}
 
 \author{
-Some Awesome People\altaffilmark{1,2,3,4}
+Carlyn N.\ Augustine\altaffilmark{1},
+Donald E.\ Willcox\altaffilmark{2},
+Dean M.\ Townsley\altaffilmark{3},
+and Alan C.\ Calder\altaffilmark{2,4}
 }
@@
   Department of Physics and Astronomy,
-  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
-  \href{mailto:somebody@someplace}{somebody@someplace}
+  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
 }
@@
   Department of Physics and Astronomy,
-  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
+  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
+  \href{mailto:donald.willcox@stonybrook.edu}{donald.willcox@stonybrook.edu}
 }
 \altaffiltext{3}{
-  Department of Physics and Astronomy,
-  Stony Brook University, Stony Brook, NY, 11794-3800, USA
-}
-\altaffiltext{4}{
   Institute for Advanced Computational Sciences,
@@
 \begin{abstract}
-Awesome Abstract
+We present simulations of thermonuclear (type Ia) supernovae
+from hybrid C/O/Ne progenitor white dwarfs. These progenitors 
+were evolved though accretion with the \MESA\ stellar evolution code 
+and include blah blah about the new hybridocity....
+For comparison, we performed a set of supernova simulations from
+traditional C/O progenitors....
+We find ....
 \end{abstract}
@@
 \label{sec:intro}
+Type Ia supernovae (\SNeIa) are bright stellar explosions....
 
-Introduction with a pretty plot in \figref{fig:progenitor_abundances}.
+Phillips relation
+~\citep{phillips:absolute}.
+
+Cosmology
+due to dark energy \citep{riess.filippenko.ea:observational,
+perlmutter.aldering.ea:measurements,leibundgut2001}.
+
+Brief discussion of progentors...
+ancient history~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis}. The
+Single degenerate 
+\citep{hoylefowler60,trucam71,whelaniben73,Nomo84}. Alternately, in
+
+Other models
+\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
+
+Hybrid models 
+old 
+\citep{denissenkovetal2015}
+\citet{Wangetal2014} and \citet{Mengetal2014} presented binary
+
+Recent results from stellar evolution
+The models we are exploding \citep{brooksetal2017}
+
+If we refer to the work by name, it should appear ``The hybrid models
+of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
+
+Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
+Give a read to see!
+
+\subsection{The Chandrasekhar-mass Single Degenerate Scenario}
+
+Explain the Single Degenerate scenario
+\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
+expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born.
+
+Explain DDT
+
+Go through below and cite some of these as you tell the story
+
+d~\citep{arnett.truran.ea:nucleosynthesis}.
+~\citep{mazzalietal2008}.
+
+\citep{khokhlov1993,bychovliberman1995,
+SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
+cholazarianvishniac2003,
+roepkehn2003,roepkehn2004,
+Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
+Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
+jacketal2014,poludnenko2015,hicks2015}.
+
+A deflagration alone will not produce a event of normal brightness and
+expansion velocity~\citep{roepkeetal07}. Instead, the initial
+deflagration must transition to a detonation after the star has
+expanded some in order to produce abundances and a stratified ejecta
+in keeping with
+observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
+The physics of this ``deflagration-to-detonation transition'' (DDT)
+are not completely understood, but there has been considerable study
+based on mechanisms involving flame fronts in highly turbulent
+conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
+  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
+  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
+These models generally reproduce the observations under certain
+assumptions about the ignition~\citep{townetal2009}, but research has
+shown that the results are very sensitive to the details of the
+ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
+  roepkeetal07,Jordan2008Three-Dimension}.
+
+Summarize what we do a la:
+In our simulations, we initialize a detonation once the 
+deflagration front reaches a
+characteristic DDT fuel density, which controls the degree of
+expansion the star undergoes during the deflagration stage.
+
+The comparison study of tradition C/O progentor WDs used the same
+initial conditions for the realizations within the suite. Make the
+point that the traditional models are simalted with the same code
+and the same set if perturbations on the initial match head (that is
+what we mean by a realization). The only difference is the different
+nuclear buring to include the other Ne and the initial profile of
+the 1-d model.
+
+For much of the methodology to be described below, just say a few
+words about what was done and cite \citet{willcoxetal2016}.
+
+\section{Methods}
+\section{Inital Models}
+\section{Results}
+\section{Discussion and Conclusion}
+\section{Below here from Dons paper}
+\subsection{Systematic Effects}
+
+Contemporary observational campaigns typically investigate how
+the brightness and rates of supernovae correlate to 
+properties of the host galaxy such as mass and star formation
+rate~\citep[c.f.][]{graurmaoz2013,graurbiancomodjaz2015}. Of
+particular interest is the delay time distribution (DTD), the
+supernovae rate as a function of time elapsed from 
+early, rapid
+star formation in the host galaxy, and how it may be used
+to constrain progenitor models~\citep{hachisu:2008,
+conleyetal2011,howell2011,grauretal2011,biancoetal2011,maozmannuccibrandt2012}.
+See also the review by~\citet{maozmannucci2012}.
+Very recent results indicate evolution of the UV spectrum with 
+redshift, providing evidence for systematic effects with
+cosmological time \citep{milneandfoley2015}.
+
+Motivated by this interest in correlations between properties of the
+host galaxy and the brightness and rate of events, earlier incarnations of  
+our group performed suites of simulations in the DDT scenario
+with a modified version the \FLASH\ code (described below) to explore
+systematic effects on the brightness of an event measured by the yield of
+$^{56}$Ni~\citep{Krueger2010On-Variations-o,jacketal2010,kruegetal12}. The
+study we present here explores how explosions following from a new class
+of ``hybrid" 
+progenitors~\citep{denissenkovetal2013,chenetal2014,denissenkovetal2015} 
+compares to these previous results.
+
+\section{Hybrid Progenitor Models}\label{section:hybrid_progenitor_models}
+Rumors that the structure and evolution of stars is a solved
+problem~\citep{HansenEtAl04} are greatly exaggerated. Recent
+developments obtained with the modern software instrument
+\MESA~\citep{mesa1,mesa2,mesa3,mesa3e} indicate that convective boundary
+mixing (CBM) in the cores of super asymptotic giant branch stars
+(super-AGB) plays a more critical role than previously thought.  There
+are several examples in which the inclusion of CBM improves agreement
+between models and observations, including that
+of~\citet{denissenkovetal2013}, which studied WD interior shell
+convection, and~\citet{herwig2005, werner.herwig.2006}, which treated
+He-shell burning in AGB stars.
+\citet{denissenkovetal2013,chenetal2014} found that in some super-AGB
+stars, CBM halts the progression of carbon burning into the stellar
+core, leaving an unburned C-rich core as large as $0.2~\Msun$
+surrounded by an O-Ne-rich intershell region extending out to the
+accretion layer at the end of hydrostatic carbon burning. This effect
+of C-flame quenching via CBM is also confirmed by the extensive
+parameter study on C-burning in super-AGB stars
+in~\citet{farmeretal2015}. Nevertheless, the true test of
+  whether or not CBM is effective enough to quench the carbon flame
+  awaits sufficiently resolved hydrodynamic simulations or further
+  evidence via observational consequences.
+
+Accounting for CBM, ~\citet{denissenkovetal2015} explored
+the stellar evolution of a super-AGB star with initial mass of
+$6.9~\Msun$ and obtained the hybrid white dwarf that is the focus of
+the present work. After hydrostatic carbon burning has ceased, the
+white dwarf accretes carbon-rich material at its surface, leading to
+the rise of temperature near its center. This results in carbon
+burning in the upper layer of the small carbon-rich core, which,
+together with the thermal effects of the $\Ne{23}/\Na{23}$ Urca process,
+provides off-center heating~\citep{denissenkovetal2015} that drives
+convection throughout the entire white dwarf except the carbon-rich
+core.
+
+Convection subsequently mixes the carbon-poor material in the
+O-Ne intershell region with carbon-rich material on the accreted layer
+and also partially mixes carbon-rich material from the core with the
+carbon-poor material in the O-Ne intershell. This proceeds along with
+accretion and carbon burning, until the latter yields peak
+temperatures near $10^9$~\K, around which the local heating time is
+shorter than the eddy turnover time so as to ignite thermonuclear
+runaway~\citep{wunschwoosley2004}. At this point, the carbon-rich core
+has been significantly depleted of carbon and consists mostly of
+\Ox{16} and \Ne{20}, while the O-Ne intershell region has been
+enriched to a \C{12} abundance of $\approx 0.14$ due to convective
+mixing. This scenario, immediately preceding the \SNIa-like explosion,
+is shown in \figref{fig:progenitor_abundances} and
+\figref{fig:progenitor_temperatures}.  The process of mapping this
+\MESA\ progenitor into hydrostatic equilibrium in \FLASH\ is described
+in~\secref{subsec:mesa_flash_mapping}.
+
+This hybrid WD has the interesting property that its mass before the
+onset of accretion is $1.06~\Msun$, naturally closer to the
+Chandrasekhar limit than a traditional C-O WD. Such
+hybrid WD progenitors thus require less mass accretion to approach
+the Chandrasekhar limit, which helps to resolve one of the
+difficulties with the SD progenitor
+system~\citep{denissenkovetal2015,chenetal2014,kromeretal2015}. The
+mass of this hybrid WD following accretion is $1.36~\Msun$.
+
+We note that these models include the influence of the URCA process on the 
+convective phase of the pre-explosion progenitor. Our progenitor profiles are
+taken directly from \MESA\ models presented in ~\citet{denissenkovetal2015}. 
+These include contributions to the energy from thermal energy produced
+by the URCA process, but the underlying mixing length theory was not 
+modified correspondingly. Thus the effect on the convection is only
+due to the energy loss/generation rate. Our progenitor profiles are
+shown in Figures \ref{fig:progenitor_abundances} and \ref{fig:progenitor_temperatures}
+and correspond to the models in Figure 9a of~\citet{denissenkovetal2015}.
+In this regard, this progenitor differs from the carbon-core
+models of~\citet{kromeretal2015} in that it includes the pre-explosion convective
+burning phase that spreads the carbon enrichment throughout the star before
+ignition of the flame front.
+% They also differ in that they are a DDT
+% Also discuss Marquadt 2015.
+While the progenitor we study consists mostly of \Ox{16}
+  and \Ne{20}, having the average composition of (\C{12} = 0.17,
+  \Ox{16} = 0.42, \Ne{20} = 0.32), it differs from the O-Ne white
+  dwarf of~\citet{marquardtetal2015} by having a much higher abundance
+  of \C{12} due to accumulation and mixing of \C{12} material during
+  the accretion phase, as described above. As discussed below in
+  \secref{subsec:one_burning_mods} and
+  \secref{subsec:hybrid_ignition_parameters}, given the temperature
+  profile of \figref{fig:progenitor_temperatures}, this available
+  \C{12} is sufficient to drive both a subsonic deflagration and
+  subsequently a supersonic detonation front as in previous work that
+  applied the same DDT approach to C-O white dwarf
+  progenitors~\citep{kruegetal12}.
 
 \begin{figure}[t]
-	\includegraphics[width=\linewidth]{figures/samples/cf_wdb_mesa_comp_vs_mass.pdf}
+	\includegraphics[width=\linewidth]{figures/progenitor_400k/Dr-400k/cf_wdb_mesa_comp_vs_mass.pdf}
 	\caption{\label{fig:progenitor_abundances} Abundance profile
@@
 
+\begin{figure}[t]
+	\includegraphics[width=0.9\linewidth]{figures/progenitor_400k/Dr-400k/cf_wdb_mesa_temp.pdf}
+	\caption{\label{fig:progenitor_temperatures} Temperature
+          profile of \MESA\ progenitor (\MESA) shown with a solid red
+          line and its reconstruction on a uniform grid at $4$~km spatial resolution (\FLASH) with
+          grid zones shown in blue circles.}
+\end{figure}
+
 \section{Methodology}
+A few significant new developments in our computational methods were
+necessary to simulate the explosion of the hybrid C-O-Ne WD. In
+\secref{subsec:one_burning_mods}, we obtain the steady-state
+detonation structure for the hybrid C-O-Ne fuel and compare its
+detonation characteristics with those of C-O fuel to analyze the
+suitability of our combustion model in \FLASH. Then in
+\secref{subsec:mesa_flash_mapping} we map the hybrid C-O-Ne WD into a
+uniform spatial grid to initialize \FLASH\ while taking care to
+preserve hydrostatic equilibrium. We comment in
+\secref{subsec:flash_flame} on our \FLASH\ combustion model and in
+\secref{subsec:ddt_details} on the deflagration to detonation
+transition (DDT) scheme. Finally, we describe the simulation geometry
+and the adaptive mesh refinement used in
+\secref{subsec:flash_geometry}.
 
-Methodology goes here.
+\subsection{Modifications for C-O-Ne Burning} 
+\label{subsec:one_burning_mods}
 
-A handy example of a vertical multi-plot figure is \figref{fig:znd_abundances}.
+The combustion model in \FLASH\ that we use for Type Ia supernovae
+simulations \citep{Caldetal07, townsley.calder.ea:flame,
+  SeitTownetal09, townetal2009, jacketal2014, townetal15} separates
+the burning into four states: unburned fuel, C-fusion ash, a
+silicon-group-dominated nuclear statistical quasi-equilibrium (NSQE)
+state, and a full nuclear statistical equilibrium (NSE) state
+dominated by iron-group elements (IGEs). The progress of combustion
+from one of these states to the next is tracked by three scalar
+progress variables whose dynamics is calibrated to reproduce the
+timescales of reactions that convert material among these
+states. Previous work has focused on fuel mixtures composed
+principally of $^{12}$C, $^{16}$O, and $^{22}$Ne.  Simulation of the
+hybrid models required extension of this burning model to account for
+the presence of \Ne{20} as a large abundance in the fuel. Here we
+describe both how $^{20}$Ne is processed during combustion, and the
+modifications made to the burning model that accommodate it.
+
+The burning stages above are determined by the hierarchy of timescales
+for the consecutive consumption of C and O via fusion and Si via
+photo-disintegration and alpha capture. Investigation of the inclusion
+of \Ne{20} focused on whether an additional Ne-consumption stage would
+be required, and, if not, what stage should include Ne consumption. In
+order to characterize the physical burning sequence that we want to
+model, we performed a series of simulations of detonations propagating
+through WD material with the TORCH nuclear reaction network
+software~\citep{timmes1999,torch}.\footnote{TORCH is available from
+  \url{http://cococubed.asu.edu}, and the modified version used for
+  this study is available from
+  \url{http://astronomy.ua.edu/townsley/code}.} TORCH is a general
+reaction network package capable of solving networks with up to
+thousands of nuclides. A mode is implemented that computes the
+one-dimensional spatial thermodynamic and composition structure of a
+steady-state planar detonation using the the Zel'dovich, von Neumann,
+and D\"{o}ring (ZND) model \citep{FickDavi79,townetal15}. We use a
+reaction network composed of 225 nuclides consisting of the 200
+nuclides in \citet{Woosley1995The-Evolution-a} in addition to the 25
+neutron-rich nuclides added by \citet{Caldetal07} to improve coverage
+of electron capture processes in the Fe group.
+
+For the multi-species fuel and ash relevant to typical white dwarf material, the ZND detonation exhibits the stages that motivate the combustion model.
+Figure \ref{fig:co_znd_stages} shows these stages as they appear in a
+ZND detonation calculation in fuel with the fractional composition
+(\C{12} = 0.50, \Ox{16} = 0.48, \Ne{22} = 0.02) corresponding to
+the composition found in the interior of a C-O WD, and a fuel density of $10^7$~g~cm$^{-3}$.
+The evolution of the mass fractions in time following the passage of the shock through 
+the zone of material is plotted below the density structure in Figure \ref{fig:co_znd_stages}.
+The time range of the four states representing the burning stages are indicated by colors in the upper panel of Figure \ref{fig:co_znd_stages}, with the consecutive states separated by the
+\C{12}-\Si{28}, \Ox{16}-\Si{28}, and \Si{28}-\Fe{54} crossing times.
+It can be seen that the times of the density plateaus are directly comparable to the times at which the primary energy release transitions from one fuel source to another, 
+as, e.g., when the \C{12} fraction has fallen
+to $\approx1\%$ of its initial value just before $10^{-8}$~s.
+
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{figures/detonation_plotfiles/Composition_Density_vs_Time.pdf}
+	\caption{\label{fig:co_znd_stages} Density (upper) and
+          abundance (lower) structure in the post-shock flow of a ZND
+          detonation calculation of C-O WD material. The upper panel is shaded to show
+          the fuel (red), ash (blue), NSQE (green), and NSE (gray) burning stages, demarcated by the \C{12}-\Si{28}, \Ox{16}-\Si{28}, and
+          \Si{28}-\Fe{54} crossing times. The initial composition is
+          $X_{^{16}\rm O} = 0.48$, $X_{^{22}\rm Ne} = 0.02$,
+          $X_{^{12}\rm C} = 0.50$, and $X_{^{20}\rm Ne} = 0.00$, and
+          the pre-shock density is $10^7$~g~cm$^{-3}$.}
+\end{figure}
+
+In our combustion models for C-O progenitors, consumption of the
+initial fuel is modeled as a two-step process. The two stages
+represent the consumption first of \C{12}, then of \Ox{16}, mimicking
+the sequence seen in the detonation structure shown in
+Figure~\ref{fig:co_znd_stages} for ``Fuel'' and ``Ash'' stages. At the
+end of this second stage the material is in a \Si{28}-dominated NSQE
+state~\citep{Caldetal07,townsley.calder.ea:flame}. To determine how
+the burning stages change with the inclusion of \Ne{20}, as is the
+case in the hybrid C-O-Ne progenitor, we perform ZND calculations with
+an admixture of \Ne{20} ranging from $0.01$ to $0.45$, at the expense
+of \C{12} content. For each composition we find the minimally
+overdriven solution, as was done in the C-O case. Out to the minimum
+in density, this solution is the same as the eigenvalue ZND solution,
+which corresponds to a self-supported detonation \citep{FickDavi79,townetal15}.
+This computation gives the resolved detonation structure in C-O-Ne Hybrid WD matter.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{figures/detonation_plotfiles/Vdet_vs_xc12_w_fit_includebump.pdf}
+	\caption{\label{fig:detonation_velocity_wfit} Self-supported detonation speed plotted versus carbon fraction in fuel with initial (pre-shock) density of $10^7$~\grampercc and initial composition of $X_{^{16}\rm O} = 0.48$ and $X_{^{22}\rm Ne} = 0.02$.
+The sum $X_{^{12}\rm C} + X_{^{20}\rm Ne}$ is kept constant.\\}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=0.95\linewidth]{figures/detonation_plotfiles/dens_multi_new.pdf}
+        \caption{\label{fig:co_znd_multi_den}} Density structures shaded with varying $^{12}$C mass fraction, keeping constant the sum $X_{^{12}\rm C} + X_{^{20}\rm Ne}$.
+The rest of the composition is $X_{^{16}\rm O} = 0.48$ and $X_{^{22}\rm Ne} = 0.02$.
+\end{figure}
+
+The eigenvalue detonation speeds from ZND calculations in material with \C{12} fraction varying from 0.05 to 0.5 are shown in Figure \ref{fig:detonation_velocity_wfit}, demonstrating that self-supported detonations in this progenitor are feasible with only small variation in speed across this range of \C{12} fractions.
+Figure \ref{fig:co_znd_multi_den} shows
+the effect of simultaneously adding \Ne{20} and reducing \C{12} on the density profile.
+Lowering the \C{12} fraction weakens the shock and
+lengthens the timescales of the step features, corresponding to more slowly
+burning fuel and ash, as might be expected from the lower energy release
+afforded by the \Ne{20}. However, it is noteworthy that no qualitatively
+new features arise from the change in fuel source that would suggest
+that more than 4 representative burning stages are needed.
 
@@
 	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_0_XC-50.pdf}
+		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_0_XC-50.pdf}
 		%\caption{\label{fig:znd_abundances_xc12_0.5} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.50$, $X_{^{20}Ne} = 0.00$}
@@
 	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_20_XC-30.pdf}
+		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_20_XC-30.pdf}
 		%\caption{\label{fig:znd_abundances_xc12_0.3} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.30$, $X_{^{20}Ne} = 0.20$}
@@
 	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_35_XC-15.pdf}
+		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_35_XC-15.pdf}
 		%\caption{\label{fig:znd_abundances_xc12_0.15} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, $X_{^{20}Ne} = 0.35$}
@@
 	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_45_XC-05.pdf}
+		\includegraphics[width=0.86\textwidth]{figures/detonation_plotfiles/XvsT_wn_45_XC-05.pdf}
 		%\caption{\label{fig:znd_abundances_xc12_0.05} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.05$, $X_{^{20}Ne} = 0.45$}
@@
         \caption{\label{fig:znd_abundances} Mass Fraction Evolution for ZND Detonations with varying initial \C{12} and \Ne{20} mass fractions, calculated for an initial density of $10^7~\grampercc$.}
+
 \end{figure}
 
-Here's a text citation \citet{timmes92,Chametal08}, and here's a parenthetical citation ~\citep{timmes.swesty:accuracy,castro1}.
+Qualitative similarity between C-O and C-O-Ne detonation structures
+are visible in the mass fractions as well.
+To demonstrate this, the abundance structures with initial \C{12} abundances of 0.5, 0.3,
+0.15, and 0.05 are shown in \figref{fig:znd_abundances}. 
+We find that the \Ne{20} burns simultaneously with whatever \C{12} is present,
+producing primarily \Si{28}.  The Ne-C burning stage is then followed by \Ox{16}
+burning to silicon-group NSQE elements and then on to NSE,
+just as in a model with no initial \Ne{20}, except for the progressively
+later \Ox{16} burning time.
 
-Here's an ordinary equation in \eqref{eq:hse_pressure}.
+\begin{figure}[t]
+	\includegraphics[width=1\linewidth]{figures/detonation_plotfiles/nuclides_xmax_xc12_15.pdf}
+	\caption{\label{fig:nuclides_xmax} Our reaction network of 225 nuclides is shown, with nuclides shaded by their maximum abundance and categorized based on whether they were maximally abundant before the earliest of the following crossing times: \C{12}-\Si{28} (purple), \Ox{16}-\Si{28} (blue), \Si{28}-\Fe{54} (green).
+Nuclides maximally abundant after the \Si{28}-\Fe{54} crossing time are shown in orange.
+		The initial composition used 
+		is $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, and $X_{^{20}Ne} = 0.35$.
+	}
+\end{figure}
 
-\begin{equation}\label{eq:hse_pressure}
-  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
-  \rho_{i-1})\ .
-\end{equation}
+A graphic representation of the most significant nuclides by mass
+fraction and the stage in which they are important is shown in
+\figref{fig:nuclides_xmax} for an initial \C{12} fraction of 0.15,
+representative of the majority of the hybrid stellar profile
+(cf. \figref{fig:progenitor_abundances}). Nuclides are categorized
+based on the time at which they were maximally abundant in the network
+and shaded by their maximum abundance.  Nuclides within the purple
+color palette were maximally abundant during the initial
+``fuel-burning'' stage after the beginning of fusion and before the
+\Si{28} becomes equally abundant with \C{12}, the \C{12}-\Si{28}
+crossing time $t_{\rm fa}$.  Blue nuclides were maximally abundant
+after $t_{\rm fa}$ but prior to the \Ox{16}-\Si{28} crossing time
+$t_{\rm aq}$, and nuclides maximally abundant after $t_{\rm aq}$ but
+before the \Si{28}-\Fe{54} crossing time $t_{\rm qn}$ are plotted in
+green. Nuclides maximally abundant following $t_{\rm qn}$ are IGEs
+together with protons and alpha particles and are shaded in
+orange. Note that for the time scales we adopt the notation of
+\citep{townetal15}, which describes the burning stages in detail.
 
-Here's a multi-line equation.
+The burning model we are using computes the rates for progression
+through the burning stages from the local temperature and the energy
+release from a set of major fuel abundances, previously including
+\C{12}, \Ox{16}, and \Ne{22}. We have found here that any \Ne{20} is
+consumed along with \C{12} and that otherwise the burning is quite
+similar to that with just \C{12} and \Ox{16} as principal
+constituents. In consequence, the only necessary modification to our
+burning model is to include \Ne{20} in the abundances of the initial
+state in the burning model. This accounts for the difference in
+binding energy of \Ne{20} compared to \C{12} and gives lower burning
+temperatures. Additionally, throughout the majority of the progenitor
+outside the core ignition region, due to prior convective mixing, the
+\C{12} content is high enough that we will extrapolate the laminar flame speeds of
+\citet{timmes92,Chametal08}. We consider this a reasonable
+approximation since much of the flame propagation is dominated by
+Rayleigh-Taylor overturn and turbulence.
+
+\subsection{Mapping a \MESA\ Profile to \FLASH\ While Preserving Hydrostatic Equilibrium}
+\label{subsec:mesa_flash_mapping}
+The temperature and composition at the base of the convective zone in
+the hybrid C-O-Ne white dwarf provides a natural flame initialization
+region for simulation of thermonuclear runaway in the DDT scenario, so
+we map the \MESA\ profile into the \FLASH\ domain preserving its
+features at $4$~km spatial resolution. We do this by first converting
+the \MESA\ model to a uniform grid by mass-weighted averaging of
+quantities in \MESA\ zones with spacing less than $4$~km and using
+quadratic interpolation to estimate quantities where \MESA\ zones have
+spacing greater than $4$~km. Although our combustion model in
+\FLASH\ does not evolve nuclide abundances, it uses the initial
+abundances of \C{12}, \Ne{20} and \Ne{22} (assuming the rest is \Ox{16}) to compute the
+initial mean nuclear binding energy and electron fraction.
+%properties\footnote{The
+%  initial abundances determine the following properties of fuel and
+%  ash, assuming that \C{12} and \Ne{20} burning produces only \Mg{24}:
+%  $Y_e$, $Y_i$, and the average binding energy per baryon
+%  $\overline{Q}$} used to evolve the fuel-to-ash progress variable.
+Therefore, we also represent the full set of nuclides in the
+\MESA\ profile by this reduced set of four nuclides in the uniformly
+gridded profile, requiring the carbon mass fractions to be identical
+because there is still sufficient \C{12} in the star to sustain a
+detonation front. In addition, we use \Ne{22} in the reduced set to
+account for the $Y_e$ of the full set of nuclides, and we constrain
+\Ne{20} and \Ox{16} to be in the same ratio $R$ in both sets of
+abundances. These constraints provide the following definitions for
+the reduced abundances used for \FLASH:
+
+%% \begin{subequations}
+%% \begin{align}
+%% \mathrm{X_{\C{12}}^{FLASH}} &= \mathrm{X_{\C{12}}^{MESA}} \\
+%% \mathrm{X_{\Ne{22}}^{FLASH}} &= \mathrm{22 \cdot \left(\dfrac{1}{2}-Y_e^{MESA}\right)} \\
+%% \mathrm{R} &= \mathrm{X_{\Ne{20}}^{MESA}/X_{\Ox{16}}^{MESA}} \\
+%% \mathrm{X_{\Ox{16}}^{FLASH}} &= \mathrm{\frac{1 - X_{\C{12}}^{FLASH} - X_{\Ne{22}}^{FLASH}}{R + 1}} \\
+%% \mathrm{X_{\Ne{20}}^{FLASH}} &= \mathrm{R \cdot X_{\Ox{16}}^{FLASH}}
+%% \end{align}
+%% \end{subequations}
 
@@
 
+Nothing constrains the resulting uniformly gridded profile to be in
+hydrostatic equilibrium (HSE), however, so we next construct an
+equilibrium profile by applying the HSE pressure
+constraint
+\begin{equation}\label{eq:hse_pressure}
+  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
+  \rho_{i-1})\ .
+\end{equation}
+Starting at the uniformly gridded profile's central density and using
+its temperature and composition in each zone together with the HELM
+equation of state (EOS) of~\citet{castro1}, we solve
+\eqqref{eq:hse_pressure} for the density in each zone. In
+\eqqref{eq:hse_pressure}, $\Delta r$ indicates the zone width, $T_i$
+is the temperature in zone $i$, $X_i$ is the composition in zone $i$,
+and $g$ is the gravitational acceleration at the boundary of zone $i$
+and $i-1$ due to the mass enclosed by zone $i-1$ and below. The
+resulting uniformly gridded, equilibrium profile (\FLASH) and the
+original profile (\MESA) are shown for comparison in Figures
+\ref{fig:progenitor_abundances} and \ref{fig:progenitor_temperatures}.
+The values of the total mass before and after this procedure differ by
+$6 \times 10^{-3}\ \mathrm{M_\odot}$.  This procedure produced a
+structure that was stable in \FLASH, with fluctuations in central
+density less than $3\%$, for at least $5$ seconds with no energy
+deposition. Finally, we replaced the EOS routine in the public
+\FLASH\ distribution with that from
+\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1} to obtain a more
+consistent tabulation.\footnote{The Helmholtz EOS table used in
+  \CASTRO\ is in the public BoxLib Microphysics repository at
+  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit hash
+  $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).}
+
+%\begin{equation}\label{eq:hse_pressure} P_{EOS}(\rho_i,T_i,X_i)
+%= \frac{g \Delta r}{2} (\rho_i + \rho_{i-1}) \end{equation}
+%DON: This equation should have dPeos on the left, I'll check it!
+%DON: Also, what's the right citation for the HELM EOS? We used the one from Castro, but it's being phased out...
+
+\subsection{Combustion and Explosion Mechanisms In The \FLASH\ Code} 
+\label{subsec:flash_flame}
+To simulate the explosion from either hybrid or traditional
+progenitor models, we use a modified version of \FLASH 
+\footnote{\FLASH\ is available from
+  \url{http://flash.uchicago.edu}. Our modifications for C-O WDs are
+  available from \url{http://astronomy.ua.edu/townsley/code}.}, an
+Eulerian adaptive-mesh compressible hydrodynamics code developed by
+the ASC/Alliances Center for Astrophysical Thermonuclear Flashes at
+the University of Chicago~\citep{Fryxetal00, calder.fryxell.ea:on}.
+While \FLASH\ is capable of evolving thermonuclear reaction networks
+coupled to the hydrodynamics, in order to treat a $ \le 1$ \cm\ flame
+front in full-star simulations of Type Ia supernovae, we use a
+coarsened flame model that uses an advection-diffusion-reaction (ADR)
+scheme to evolve a scalar variable representing the progression of
+burning from fuel to ash compositions as detailed
+in~\citet{Caldetal07, townsley.calder.ea:flame,townetal2009}. An
+additional scalar represents the burning progress from ash to
+intermediate-mass silicon-group elements in nuclear statistical
+quasi-equilibrium (NSQE). A final scalar represents the burning of
+silicon-group elements to IGEs in nuclear statistical equilibrium
+(NSE). The timescales for evolving these scalars are density and
+temperature-dependent and are determined from self-heating and
+steady-state detonation calculations with a $200+$ species nuclear
+reaction network~\citep{Caldetal07,townetal15}. For our evaluation of
+the suitability of this burning scheme for fuel with an admixture of
+\Ne{20}, see \secref{subsec:one_burning_mods}.
+
+The two-dimensional models we present do not utilize a subgrid-scale
+model for the turbulence-flame interaction (TFI). Earlier work
+produced subgrid-scale TFI models by extending terrestrial combustion
+models to consider astrophysical flames~\citep{Schmetal06a,
+  Schmetal06b, jacketal2014}, however the resulting subgrid-scale
+models only capture TFI in three-dimensional
+simulations. Two-dimensional models inherently lack true turbulence,
+so instead we use the mimimal enhancement based on the Rayleigh-Taylor
+strength introduced by~\citet{townsley.calder.ea:flame}. This assumes
+that the TFI will self-regulate on resolved scales so that results are
+insensitive to the detailed treatment of the TFI. We believe this to
+be sufficient for two-dimensional comparative studies like that
+undertaken here.
+
+\subsection{Deflagration-to-Detonation Transition}
+\label{subsec:ddt_details}
+This study presents simulations of the thermonuclear explosions of
+both a hybrid C-O-Ne white dwarf
+progenitor~\citep{denissenkovetal2015} and a C-O white dwarf
+progenitor similar to that used in previously published suites of
+\SNIa\ simulations~\citep{kruegetal12}. In both cases, we initialize
+the simulations with a ``matchhead'' consisting of a region near or at
+the white dwarf's center that is fully burned to nuclear statistical
+equilibrium (NSE). The energy release from this initial burn ignites a
+subsonic thermonuclear flame front that buoyantly rises and partially
+consumes the star while the star expands in response. As detailed
+in~\citet{townetal2009, jacketal2010}, in order to effect a
+deflagration-to-detonation transition, we suppose the DDT point to be
+parameterizable by a fuel density $\rho_{\mathrm{DDT}}$ at which the
+subsonic flame reaches the distributed burning regime where the flame
+region has become sufficiently turbulent that a supersonic detonation
+front may arise, self-supported by the energy release from the nuclear
+burning proceeding behind the detonation shock front.
+
+We thus use a similar DDT parameterization for our C-O and hybrid
+C-O-Ne simulations as in the C-O WD \SNIa\ simulations
+of~\citet{Krueger2010On-Variations-o, kruegetal12} for
+consistency. Our choice is to ignite the detonation when a rising
+plume reaches the threshold density, but reality may be quite
+different. For example, the turbulent intensity may be greatest at the
+underside of a rising plume, which would imply igniting a detonation
+deeper in the core and possibly later, both of which would affect the
+yield. For purposes of this paper, which was to compare the yield from
+a hybrid model to a traditional C-O model, we prefer to use a simply
+consistent condition across cases.~\citet{jacketal2010} addresses the
+dependence of the DDT density on composition separately.
+
+Consequently, when the deflagration reaches a point where it is at
+$\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$, we place a region with
+its fuel stage (representing \C{12} and \Ne{20}, if present) fully
+burned $32$~\km\ radially outwards from this point that is of size
+$12$~\km\ in radius. Multiple DDT points may arise, but they are
+constrained to be at least $200$~\km\ apart. Our choice of DDT
+  density is slightly high in order to ensure robust ignition of a
+  detonation shock in all cases. We note that this choice strongly
+  influences the \Ni{56} yield because it determines the amount of
+  expansion of the star prior to the detonation, which determines the
+  overall density profile \citep{jacketal2010}.
+
+\subsection{Mesh Geometry And Refinement}
+\label{subsec:flash_geometry}
+We performed our calculations in two-dimensional $\mathrm{z-r}$
+cylindrical coordinates, extending radially from 0 to
+$65,536$~\km\ and along the axis of symmetry from $-65,536$~\km\ to
+$65,536$~\km. We selected a maximum refinement level corresponding to
+$4$~\km\ resolution using the PARAMESH adaptive mesh refinement scheme
+described in~\citet{Fryxetal00}. This resolution permitted efficiency
+in performing many repeated simulations with different initial
+conditions. The $4$~\km\ resolution was also informed by previous
+resolution studies in~\citet{townsley.calder.ea:flame,townetal2009},
+that found that in 2-D DDT simulations of C-O white dwarf explosions,
+the trends with resolution of total mass above the DDT density
+threshold at the DDT time are fairly robust. The amount of high
+density mass at the DDT is important because it reflects the extent of
+neutronization during the deflagration and thus correlates with the
+IGE yield of the explosion. In addition, we wish to compare the hybrid
+IGE yields and other explosion characteristics with those of
+explosions from C-O white dwarf progenitors previously explored
+in~\citet{kruegetal12}, which used $4$~\km\ resolution in \FLASH\ with
+the same $\mathrm{z-r}$ geometry we describe above. We can thus make
+our comparison robust by controlling for resolution and geometry
+factors.
+
 \section{Simulations and Results}
+\subsection{Reference C-O WD Model}\label{refcomodel}
+To compare the resulting features of Type Ia supernovae produced by
+the hybrid model to those of previous studies of centrally ignited C-O
+white dwarfs in the DDT
+paradigm~\citep{Krueger2010On-Variations-o,kruegetal12}, we generate a
+reference C-O model. The reference model has the same central density
+as the hybrid model with a central temperature of $7 \times 10^8$~K, a
+core composition of (\C{12} = 0.4, \Ne{20} = 0.03, \Ox{16} = 0.57) and
+envelope composition of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} =
+0.48). For comparison, \figref{fig:co_vs_cone_density} and
+\figref{fig:co_vs_cone_temp} show the density and temperature profiles of
+the C-O and C-O-Ne hybrid WD.
 
-Simulations and results go here.
+We use the deflagration initialization of~\citet{kruegetal12}, which
+followed the method of~\citet{townetal2009}. \citet{townetal2009}
+reported that the scatter in \Ni{56} yield from \SNeIa\ could be
+produced in a theoretical sample of \SNIa\ simulations from C-O WD
+progenitors in the DDT scenario if the evolution of the flame surface
+shortly following the start of deflagration is described by a deformed
+spherical burned region within the progenitor core. This deformation
+consists of a perturbation of the sphere's surface by a set of
+spherical harmonic functions with randomly chosen amplitudes. The
+theoretical \SNIa\ sample is formed by thus constructing a set of
+randomized burned geometries and then using each as the initial
+condition for a DDT simulation of the explosion.
 
-Example of multi-figure plot that spans the columns is given by \figref{fig:cone_delayed_core}.
+We adopt this procedure to burn a spherical ignition region extending
+to a nominal radius of $150$~km before applying a set of 35 randomly
+seeded amplitude perturbations, including those
+of~\citet{kruegetal12}, to ignite a suite of 35 C-O WD
+explosions. Finally, previous work has made the point that the
+explosion yield from simulations such as these may be sensitive to the
+initial conditions, motivating us to perform suites of two-dimensional
+simulations instead of a modest number of three-dimensional
+simulations~\citep{scidac}. Although this kind of ``vigorous''
+ignition is disfavored by convection zone ignition
+simulations~\citep{nonakaetal2012}, it appears necessary for DDT
+simulations to reproduce observed supernovae,
+e.g.,~\citep{seitenzahletal13, Simetal2013}.
+
+\subsection{Ignition Conditions for the C-O-Ne Hybrid WD}
+\label{subsec:hybrid_ignition_parameters}
+Given the temperature and composition profile of the hybrid model, if
+it is to undergo thermonuclear runaway, \C{12} ignition will begin at
+the base of the convective zone where temperatures are highest. This
+coincides with a \C{12} abundance of $\approx 0.14$ at a stellar
+radius of $350$~km. Because the hybrid progenitor model was produced
+by the one-dimensional \MESA\ code and has only radial dependence, a
+shell-like ignition region naturally results when mapping the model to
+a multi-dimensional grid. Because this scheme cannot adequately
+capture the effects of any low-mode, large-scale convection present in
+such a star, it is not clear what is the correct choice of ignition
+geometry for this hybrid WD model.
+
+Lacking constraints on the exact geometry of the ignition region, we
+modify the ignition scheme described in \secref{refcomodel} minimally
+for the hybrid progenitor by replacing the burned sphere with a thin
+burned shell modulated by a spherical harmonic function with variable
+amplitude and harmonic number, as shown in
+\figref{fig:init_mpole_comparison} for different choices of the
+harmonic number.  With this parameterization, the harmonic number
+controls the spatial localization and the amplitude controls the
+amount of initially burned mass.  We therefore use our ignition
+parameterization to generate a suite of 35 hybrid realizations
+corresponding to a range of initially burned masses from $3.0\times
+10^{-3}~\Msun$ to $1.3\times 10^{-2}~\Msun$ and a number of initial
+burned regions from 1 to 10. We note that our implementation of 
+the initial conditions produced a slight asymmetry in the initially burned
+regions as a function of angle as may be observed in \figref{fig:init_mpole_comparison}.
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/compare/CO_vs_CONe_Density.pdf}
+	\caption{\label{fig:co_vs_cone_density} Density profiles of the hybrid C-O-Ne white dwarf (red) and the reference C-O white dwarf (blue), prepared at the same central density.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/compare/CO_vs_CONe_Temperature.pdf}
+	\caption{\label{fig:co_vs_cone_temp} Temperature profiles of the hybrid C-O-Ne white dwarf (red) and the reference C-O white dwarf (blue).}
+\end{figure}
+
+\begin{figure*}[ht]
+  \begin{minipage}{0.24\textwidth}
+    \includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/profile75_mpole-2_r-35e6_a-24e5_init.pdf}
+  \end{minipage} \hfill
+  \begin{minipage}{0.24\textwidth}
+    \includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/profile75_mpole-4_r-35e6_a-24e5_init.pdf}
+  \end{minipage} \hfill 
+  \begin{minipage}{0.24\textwidth}
+    \includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/profile75_mpole-12_r-35e6_a-24e5_init.pdf}
+  \end{minipage} \hfill 
+  \begin{minipage}{0.24\textwidth}
+    \includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/profile75_mpole-20_r-35e6_a-24e5_init.pdf}
+  \end{minipage} \caption{\label{fig:init_mpole_comparison}
+    Distribution of initially burned mass for different choices of the
+    harmonic number controlling the angular sinusoidal function. From
+    left to right, the number of initially burned regions is 1, 2, 6,
+    10. The harmonic number parameter is twice the number of ignition
+    points. \textbf{White} denotes unburned fuel (\C{12}, \Ox{16} \&
+    \Ne{20}), and \textbf{Black} denotes material in nuclear
+    statistical equilibrium (IGEs and $\alpha$-particles). The burned
+    mass is located at a radial distance of $350$~km consistent with
+    the location of maximum temperature at the base of the convective
+    zone in the \MESA\ profile used to initialize the
+    \FLASH\ simulations. For these four initial configurations, the
+    average initially burned mass is $(6.67 \pm 0.02) \times
+    10^{-3}\ \Msun$.}
+\end{figure*}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/ni56_initial-burned-mass_scatter.pdf}
+	\caption{\label{fig:co_vs_cone_ignition_bm} Dependence of the
+          final \Ni{56} yield on the initially burned mass at ignition
+          for the 35 C-O (red) and 35 C-O-Ne realizations (green).}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_initcond_rhoddt-7.2/ni56_mpoles_scatter.pdf}
+	\caption{\label{fig:cone_ignition_mp} Dependence of the final
+          \Ni{56} yield on the distribution of the initially burned
+          mass at ignition for the 35 C-O-Ne realizations.}
+\end{figure}
+
+We demonstrate the influence of the number-and-amplitude parameters
+using the final \Ni{56} yield as a proxy for the explosion results in
+\figref{fig:co_vs_cone_ignition_bm} and \figref{fig:cone_ignition_mp}.
+Because we use the same ignition geometry and conditions for the C-O
+realizations as were used in~\citet{kruegetal12}, the general size of
+the initially burned region for the C-O realizations remains very near
+$0.0084~\Msun$. However, because the nature of the ignition in the
+C-O-Ne hybrid progenitor is unknown, we chose to sample the
+number-and-amplitude parameter space to provide a range of initially
+burned masses for comparison. In spite of the scatter in
+\figref{fig:co_vs_cone_ignition_bm}, we performed a linear fit between
+the \Ni{56} yield and initially burned mass for the C-O-Ne
+realizations, obtaining a slope indistinguishable from zero within
+uncertainties and an intercept that matches the average \Ni{56} yield
+for the C-O-Ne realizations (\tabref{YieldSummaryTable}). We also show
+in \figref{fig:cone_ignition_mp} that most of the variation in \Ni{56}
+yield from the C-O-Ne realizations originates from the interplay
+between the number of ignition regions and their size. The more
+ignition regions that are used, the greater effect the variation on
+their size has on the spread in \Ni{56} yields.
+
+Using these parameters to vary the initial burned mass and its
+distribution within the progenitor, we evaluate the effect of this
+parameterization on the estimated \Ni{56} yield, IGE yield, binding
+energy, and other explosion properties in the following section.
+
+\subsection{Characteristics of Explosions from C-O and C-O-Ne WD Models}
+We simulate the explosions of the hybrid and C-O realizations through
+the end of the detonation phase and compare their features in Figures
+\ref{fig:est_ni_mass}, \ref{fig:e_binding},
+\ref{fig:mass_dens_lt_2e7}, \ref{fig:ige_vs_highrho_ddt},
+\ref{fig:ni56_vs_nse_mass}, \ref{fig:ni56_nse_mass_ratio}, and
+\ref{fig:nse_burn_mass} below. We compare the \Ni{56} yields in the
+C-O and hybrid models, estimated from $Y_e$ and the NSE progress
+variable, by assuming the composition in NSE is \Ni{56} plus equal
+parts \Fe{54} and \Ni{58}, as described in
+\citet{townetal2009,Meaketal09}.
+
+\begin{figure}[!ht]
+\includegraphics[width=\linewidth]{figures/cf_shaded/estimated_Ni56_mass.pdf}
+\caption{\label{fig:est_ni_mass} Evolution of the estimated $^{56}$Ni yields for C-O and Hybrid C-O-Ne WD Realizations.
+The time-averaged value among C-O realizations is shown in yellow, with the full range of values at any point in time for the C-O realizations shown in red.
+Likewise, the time-averaged value among C-O-Ne realizations is shown in blue and their range of values shown in green.}
+\end{figure}
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_shaded/E_binding.pdf}
+	\caption{\label{fig:e_binding} Evolution of the binding energy for C-O and Hybrid C-O-Ne WD Realizations.
+The time-averaged value among C-O realizations is shown in yellow, with the full range of values at any point in time for the C-O realizations shown in red.
+Likewise, the time-averaged value among C-O-Ne realizations is shown in blue and their range of values shown in green.}
+\end{figure}
 
@@
   \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0000"}
+    \includegraphics[width=\linewidth]{"figures/flash_simulations/delayed-core/mpole-16_amp-12/cone_400k_m16_a12_0000"}
   \end{minipage} \hfill
   \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0190"}
+    \includegraphics[width=\linewidth]{"figures/flash_simulations/delayed-core/mpole-16_amp-12/cone_400k_m16_a12_0190"}
   \end{minipage} \hfill 
   \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0200"}
+    \includegraphics[width=\linewidth]{"figures/flash_simulations/delayed-core/mpole-16_amp-12/cone_400k_m16_a12_0200"}
   \end{minipage} \hfill 
   \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0210"}
+    \includegraphics[width=\linewidth]{"figures/flash_simulations/delayed-core/mpole-16_amp-12/cone_400k_m16_a12_0210"}
   \end{minipage} \caption{\label{fig:cone_delayed_core} Progress of the burning front into the stellar core for one hybrid C-O-Ne realization, delayed relative to complete burning throughout the rest of the star.
@@
 
-Example of a table with data, units, etc is at \tabref{YieldSummaryTable}.
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_shaded/mass_with_dens_gt_2e7.pdf}
+	\caption{\label{fig:mass_dens_lt_2e7} Evolution of the total mass having density greater than $2 \times 10^7~\grampercc$ for C-O and Hybrid C-O-Ne WD Realizations.
+The time-averaged value among C-O realizations is shown in yellow, with the full range of values at any point in time for the C-O realizations shown in red.
+Likewise, the time-averaged value among C-O-Ne realizations is shown in blue and their range of values shown in green.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/compare/final_nse_mass_vs_high_density_mass_at_ddt.pdf}
+	\caption{\label{fig:ige_vs_highrho_ddt} Final IGE yields for a range of deflagration expansion, where the degree of expansion is characterized by the mass denser than $2\times 10^7~\grampercc$ at the DDT time.
+Individual C-O (red) and C-O-Ne (green) realizations are shown, together with a rectangular area centered at their average values with size extending $\pm 1 \sigma$ along each axis for C-O (yellow) and C-O-Ne (blue) groups.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/compare/ni56_vs_nse_mass.pdf}
+	\caption{\label{fig:ni56_vs_nse_mass} Production of $^{56}$Ni and Mass Burned to IGE for C-O (red) and Hybrid C-O-Ne (green) WD Realizations.
+To estimate the overall fraction for each case, a linear fit is shown for C-O (yellow) and C-O-Ne (blue) realizations.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_shaded/ni56_nse_ratio.pdf}
+	\caption{\label{fig:ni56_nse_mass_ratio} Estimated fraction by mass of IGE material producing $^{56}$Ni evolving in time for C-O and Hybrid C-O-Ne WD Realizations.
+The time-averaged value among C-O realizations is shown in yellow, with the full range of values at any point in time for the C-O realizations shown in red.
+Likewise, the time-averaged value among C-O-Ne realizations is shown in blue and their range of values shown in green.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\linewidth]{figures/cf_shaded/mass_burned_to_NSE.pdf}
+	\caption{\label{fig:nse_burn_mass} Mass burned to IGE for C-O and Hybrid C-O-Ne WD Realizations evolving in time.
+The time-averaged value among C-O realizations is shown in yellow, with the full range of values at any point in time for the C-O realizations shown in red.
+Likewise, the time-averaged value among C-O-Ne realizations is shown in blue and their range of values shown in green.}
+\end{figure}
+
+Production of \Ni{56} is comparable between the C-O and hybrid cases
+(\figref{fig:est_ni_mass}), with the full range of values from each
+suite of simulations shown in the shaded regions and the mean values
+shown by solid curves. The DDT event can be distinguished in the
+\Ni{56} evolution by the sharp increase in the rate of \Ni{56}
+production around $1.5~\second$ that rapidly yields over $0.5~\Msun$ of
+\Ni{56}. While the C-O cases show a wider variation in the time at
+which the DDT occurs, these also have a narrower spread in final
+\Ni{56} mass relative to the hybrid models. The hybrid models also
+tend to produce more \Ni{56} in the deflagration phase and some of
+them show a temporary plateau in \Ni{56} production between $1.5$~s
+and $2$~s. The same feature is also evident in the binding energy
+curves of \figref{fig:e_binding}, computed by summing the
+realization's gravitational potential, internal, and kinetic energies.
+
+This feature is a peculiarity of the off-center ignition in the hybrid models that is 
+absent in the C-O cases and results from the relatively \C{12}-poor,
+cooler core region burning about $0.25$~s after the detonation front has
+swept through the rest of the star. This delayed burning is shown in
+Figure \ref{fig:cone_delayed_core}, which demonstrates the progression of
+the detonation front into the core. Although a feature evolving over so
+short a time this early in the explosion will likely not be visible in
+the supernova light curves, the delayed contribution
+of the core to \Ni{56} production may modify the \Ni{56} distribution in
+space and velocity, potentially yielding spectral differences compared to non-delayed
+hybrid as well as C-O white dwarf explosions.
+
+The dynamical qualities of the explosion shown in the binding energy
+curves of Figure \ref{fig:e_binding} indicate that the time
+distribution of unbinding is more narrow for the hybrid models than
+for the C-O models, though the hybrid models have a wider distribution
+of final binding energies in all cases lower than the binding energies
+of the C-O models within $1$~s of becoming unbound. This should
+correlate to a lower expansion velocity of the ejecta, thus slower
+cooling and delayed transparency relative to ejecta from C-O models.
+The binding energy curves also explain the differences in expansion
+the models undergo during deflagration and detonation, shown by the
+mass above the density threshold $2 \times 10^7$~\grampercc\ in Figure
+\ref{fig:mass_dens_lt_2e7}. For times prior to $\approx 1.2$~\second,
+the C-O mass curves lie slightly lower than the average hybrid mass
+curve, indicative of a greater degree of expansion on average for the
+C-O models. However, the hybrid mass curve range encompasses that of
+the C-O mass curves until $\approx 1.4$~\second, reflective of the
+fact that until then, some hybrid realizations
+are more tightly bound than all the C-O
+realizations due to burning less mass and thus expanding less. 
+During the detonation phase, however, the
+C-O models show a much wider variation in expansion than do the hybrid
+models in spite of having a smaller range of kinetic energies and
+mass burned to IGE (Figures \ref{fig:e_binding} and
+\ref{fig:nse_burn_mass} below) once unbound. This is due to the C-O
+models demonstrating a much wider range of DDT times than the hybrid
+models.
+
+% Need to massage the following into the preceding section:
+Figure \ref{fig:ige_vs_highrho_ddt} compares the final IGE yield of
+the C-O and C-O-Ne models with the degree by which the models expand
+during the deflagration phase. The latter is characterized by the mass
+above $2 \times 10^7$~\grampercc\ at the DDT time, with more high-density mass
+indicating less expansion during deflagration. The averages of both
+the C-O and C-O-Ne suites along both axes are indicated by the shaded
+regions with $\pm1\sigma$ widths. The trend for both C-O and C-O-Ne
+models is that less expansion during the deflagration phase results in
+greater IGE yields, expected because low expansion results in there
+being more high density fuel for the detonation to consume. In
+addition, both the C-O and C-O-Ne models expand over similar ranges
+during deflagration on average, showing they are dynamically comparable in spite of
+having qualitatively different deflagration ignition
+geometries. Furthermore, for similar deflagration expansion, the C-O
+models tend to yield consistently greater IGE mass, suggesting that
+the lower IGE yields from C-O-Ne models is not a result of these
+models expanding differently than the C-O models. Rather, we interpret
+this disparity as indicating that the lower IGE yield in C-O-Ne models
+results from their lower \C{12} abundance and the fact that given
+similar fuel density, their \Ne{20}-rich fuel will burn to cooler
+temperatures than fuel in the C-O models. This in turn will result in
+slower burning to IGE and thus a lower IGE yield.
+
+The estimated \Ni{56} yields are shown in
+\figref{fig:ni56_vs_nse_mass} across the range of masses burned to IGE
+for all C-O and C-O-Ne realizations at $4.0$~\second\ simulation time,
+at which point the total mass burned to \Ni{56} had become constant,
+c.f.\ \figref{fig:est_ni_mass}. For comparable masses burned to IGE,
+the hybrid models tend to consistently produce slightly more \Ni{56}
+than the C-O models, although the ratio of IGE mass producing \Ni{56}
+given by the slope is the same in both cases, within the fit error.
+The reason for this trend is evident from Figure
+\ref{fig:ni56_nse_mass_ratio}, which shows the fraction by mass of IGE
+material producing \Ni{56} evolving in time, and Figure
+\ref{fig:nse_burn_mass}, which shows the concurrent evolution of mass
+burned to IGE. During the deflagration phase, the C-O-Ne models on
+average burn more material to IGE and also had a significantly higher
+fraction of IGE material producing \Ni{56}, yielding more \Ni{56} than
+the C-O models. This may be due to greater neutronization in the early
+deflagration of the C-O models, which are ignited closer to the center
+and thus at slightly higher density than the initial deflagration of
+the C-O-Ne models. However, during the subsequent detonation phase,
+the C-O models on average burn more mass to IGE while maintaining a
+\Ni{56}/IGE fraction very similar to that of the C-O-Ne models,
+yielding significantly more \Ni{56} by the end of the detonation
+phase.  For reference, \tabref{YieldSummaryTable} summarizes the
+average values of \Ni{56} yield, IGE yield, and final kinetic energy
+for the 35 C-O and 35 C-O-Ne realizations with one standard deviation
+uncertainties.
+%% \begin{table}[htbp]
+%%   \begin{center}
+%%     \begin{tabular}{|c|c|c|}
+%%       \hline
+%%        & C-O & C-O-Ne \\ \hline
+%%       \Ni{56} $(\Msun)$ & $0.97 \pm 0.06$ & $0.86 \pm 0.10$ \\ \hline
+%%       IGE $(\Msun)$ & $1.12 \pm 0.07$ & $0.98 \pm 0.11$ \\ \hline
+%%       Kinetic Energy $\left(\times 10^{51} \erg \right)$ & $1.39 \pm 0.05$ & $1.06 \pm 0.10$ \\ \hline
+%%     \end{tabular}
+%%   \end{center}
+%%   \caption{Summary of Final Yields for the 35 C-O and 35 C-O-Ne Realizations, showing average values with one standard deviation uncertainties.}
+%%   \label{YieldSummaryTable}
+%% \end{table}
 
@@
 \label{sec:conclusions}
+Our simulations of thermonuclear (Type Ia) supernovae from both hybrid
+C-O-Ne and reference C-O white dwarf progenitors using the deflagration
+to detonation transition paradigm have shown that on average the
+hybrid progenitors yield $0.1~\Msun$ less \Ni{56} than the C-O white
+dwarfs. While this indicates that Type Ia supernovae from C-O-Ne
+hybrids will be dimmer on average than those from C-O white dwarfs, we
+also find sufficient variance in burning efficiency with the geometry
+of the ignition region precipitating thermonuclear runaway such that
+there are some hybrid progenitors that yield more \Ni{56} than some
+C-O progenitors. Furthermore, we have found that not only do hybrid
+C-O-Ne progenitors deposit an average of 24\% less kinetic energy in
+their ejecta than C-O progenitors but also this trend of more weakly
+expelled ejecta from hybrids is robust across all ignition geometries.
+The consistency of this result suggests it is a consequence of the
+lower energy release from Ne burning compared to C burning in spite of
+the fact that using \Ne{20} as an alternate fuel can still yield
+comparable \Ni{56} production in some cases.
 
-Conclusive conclusions go here.
+As we noted above, we found considerable variation in the \Ni{56}
+production for both hybrid and traditional C-O models, and in
+particular, we found a much wider range of DDT times in the C-O models
+than the hybrid models. While in the realm of speculation, this result
+could follow from a greater degree of randomization in the geometry of
+the initially burned region for the C-O models than in the hybrids. The
+C-O models are initialized with an amplitude perturbation of the
+initially burned region comprised of several angular modes, whereas the
+thickness of the initially burned region in each of the hybrid models
+is controlled by a single angular mode.
 
-\section{Appendix}
+We also found that for some ignition geometries in the hybrid
+progenitor, a combination of off-center ignition, flame buoyancy, and
+composition permits their cooler core region to delay burning until
+nearly 0.25~\second\ after the detonation front has consumed the rest
+of the star. This result is unique to the hybrid progenitors that rely
+on the Urca process to provide a lower bound on the convective zone
+outside the core of the white dwarf. Delayed core burning in these
+white dwarfs may result in a modified \Ni{56} distribution in their
+ejecta compared to ejecta from C-O white dwarfs or even other hybrids
+with prompt core burning. Exploration of such effects is the subject
+of future work.
 
-If there's material for an appendix, it can go here.
+As our explosions from hybrid progenitors have a lower \Ni{56} yield
+and hence lower brightness than traditional C-O models, the question
+of these events as the source of observed subluminous events, e.g.
+type Iax supernovae~\citep{foleyetal2013} arises. Our finding of an
+average \Ni{56} yield of $0.1~\Msun$ less than the C-O, (and the
+larger range of yields) indicates that explosions from these
+progenitors in the DDT paradigm are not subluminous and cannot on
+their own explain subluminous events like type Iax supernovae.
+
+A recent study by \citet{kromeretal2015} addressed pure deflagrations
+in near-Chandrasekhar-mass hybrid WDs as the possible progenitor
+systems of these faint events. The study found that most of the mass
+stays bound and that early epoch light curves and spectra calculated
+from the explosion models are consistent with observations of SN
+2008ha~\citep{foleyetal2009}. We note that comparison between our
+results and these is difficult for reasons besides the obvious
+difference of the detonation phase in our simulations. The
+near-Chandrasekhar-mass progenitor model of \citet{kromeretal2015} is
+substantially different in that it is parameterized and it does not
+include the effects of late-time convection, or the URCA process.
+Also, the ignition of the deflagration is substantially different. For
+these reasons, there is limited utility in a direct comparison between
+results.
+
+Another recent study by \citet{bravoetal2016} investigated explosions
+from two classes of hybrid WDs, those with relatively large central
+C-O regions that follow from off-center C burning that stops prior
+to consuming the core due to neutrino cooling and those with 
+somewhat smaller C-O cores that follow from convective boundary mixing
+inhibiting burning. These latter ``medium-sized" cores are most similar
+to our models as they assume similar stellar evolution.
+
+The group performed suites of one-dimensional simulations evoking
+explosions via both pure detonations and DDTs and including
+``homogeneous" models that include the effect of mixing during C
+simmering prior to the ignition of the explosion. Some of the DDT
+models produce \Ni{56}~yields consistent with our results, but the
+model closest to ours (number 28) produces a yield substantially lower
+than our average result. This difference follows from the choice of
+\rhoDDT~and its very different role in one dimension compared to two
+dimensions. DDT in two dimensions occurs at the tops of plumes, so
+that the degree of pre-expansion for a particular \rhoDDT~is
+significantly less in two dimensions than in one dimension.  Thus
+two-dimensional simulations produce significantly higher $^{56}$Ni
+yields than one-dimensional simulations for a similar \rhoDDT.  For
+similar reasons, one-dimensional simulations with a higher
+\rhoDDT~give comparable yields to two-dimensional simulations with
+lower \rhoDDT, leading to some cases with comparable yields.
+
+%\section{Appendix}
 
@@
 
-We'd like to acknowledge helpful discussions with Cab Ernet.
+This work was supported in part by the Department of Energy under
+grant DE-FG02-87ER40317. The software used in this work was in part
+developed by the DOE-supported ASC/Alliances Center for Astrophysical
+Thermonuclear Flashes at the University of Chicago. Results in this
+paper were obtained using the high-performance computing system at the
+Institute for Advanced Computational Science at Stony Brook
+University. The authors thank Sam Jones and Ivo Seitenzahl for
+fruitful discussions at the Fifty One Ergs conference, June 1-6, 2015.
 

### 2018-05-11 paper/ms.tex
Drop in text and figures from Carlyn's report
This removes all the old stuff just sitting there from Don's paper
and puts in text and figures from the end-of-semester report Carlyn turned in
at the end of Spring 2018.

--- 2017-07-24 paper/ms.tex
@@
 \documentclass[iop,apj]{emulateapj}
-\usepackage{multirow}
+%\usepackage{multirow}
 \usepackage{longtable}
@@
 \usepackage{color}
-\usepackage{lipsum}
+%\usepackage{lipsum}
 \usepackage{amsmath}
@@
 \begin{abstract}
-Awesome Abstract
+Type Ia Supernovae are thermonuclear explosions of white dwarf (WD) stars.
+Past studies predict the existence of "hybrid" white dwarfs, made of a C/O/Ne
+core with a O/Ne shell, and that these are viable progenitors for supernovae.
+More recent work found that the C/O core is mixed with the surrounding O/Ne
+while the WD cools. Inspired by this scenario, we performed simulations of
+thermonuclear supernovae in the single degenerate paradigm from these hybrid
+progenitors. A hybrid white dwarf model constructed with the one-dimensional
+stellar evolution code MESA[5] was provided (Brooks et al. 2017) for our
+simulations.  This model had been run through the phase of unstable interior
+mixing followed by accretion until central ignition of carbon burning. The
+MESA model was then mapped to a two-dimensional initial condition and an
+explosion simulated from that with FLASH[4]. For comparison, a similar
+simulation of an explosion was performed from a traditional C/O progenitor
+WD. Comparing the yields produced by explosion simulations allows us to
+determine which model produces more 56Ni, and therefore brighter events, and
+how explosions from these models differ from explosions from previous models
+without the mixing during the WD cooling.
 \end{abstract}
@@
 \label{sec:intro}
+Type Ia supernovae (\SNeIa) are bright stellar explosions....
 
-Introduction with a pretty plot in \figref{fig:progenitor_abundances}.
+Carlyn's starter text: (to end starter)
 
-\begin{figure}[t]
-	\includegraphics[width=\linewidth]{figures/samples/cf_wdb_mesa_comp_vs_mass.pdf}
-	\caption{\label{fig:progenitor_abundances} Abundance profile
-          of \MESA\ progenitor (\MESA) and its reconstruction on a
-          uniform grid at $4$~km spatial resolution with the hydrostatic equilibrium condition of
-          \eqqref{eq:hse_pressure} enforced (\FLASH). The reduced set
-          of nuclides are shown, where $\mathrm{X_{\Ox{16}} = 1 -
-            X_{\C{12}} - X_{\Ne{20}} - X_{\Ne{22}}}$ for the
-          abundances labeled \FLASH. Solid lines and circles denote
-          the abundances used in \FLASH\ whereas plain solid lines
-          denote the abundances used in \MESA.}
+When a main sequence star runs out of fuel, it dies off to become a dense
+remnant of the MS, known as a white dwarf. Type Ia Supernova are bright
+explosions produced from radioactive Ni-56 determined by the white dwarf
+(WD). Astronomers use the fact that they give off a known amount of light and
+the inverse square law to determine distances of far objects. They were also
+used to find Hubble’s expansion of the universe.
+
+There has been debate over what triggers a WD explosion. One of the primary
+ideas is the single degenerate process. During this process the white dwarf
+accretes material from a giant companion. Once the white dwarf reaches the
+Chandrasekhar limit, the star is consumed by thermonuclear runaway and
+explodes.
+
+In our study, we use the single degenerate process to ignite a flame. The
+flame in the core starts out in the deflagration process, sub sonically
+burning C/O/Ne in its path. Once it reaches a certain density, the wave moves
+into the detonation front and sweeps through the rest of the star.  This
+process is the deflagration to detonation process (DDT): when a wave moves
+from being subsonic to supersonic.
+
+(end starter)
+
+Phillips relation
+~\citep{phillips:absolute}.
+
+Cosmology
+due to dark energy \citep{riess.filippenko.ea:observational,
+perlmutter.aldering.ea:measurements,leibundgut2001}.
+
+Brief discussion of progentors...
+ancient history~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis}. The
+Single degenerate 
+\citep{hoylefowler60,trucam71,whelaniben73,Nomo84}. Alternately, in
+
+Other models
+\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
+
+Hybrid models 
+old 
+\citep{denissenkovetal2015}
+\citet{Wangetal2014} and \citet{Mengetal2014} presented binary
+
+Recent results from stellar evolution
+The models we are exploding \citep{brooksetal2017}
+
+If we refer to the work by name, it should appear ``The hybrid models
+of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
+
+Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
+Give a read to see!
+
+\subsection{The Chandrasekhar-mass Single Degenerate Scenario}
+
+Explain the Single Degenerate scenario
+\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
+expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born.
+
+Explain DDT
+
+Go through below and cite some of these as you tell the story
+
+d~\citep{arnett.truran.ea:nucleosynthesis}.
+~\citep{mazzalietal2008}.
+
+\citep{khokhlov1993,bychovliberman1995,
+SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
+cholazarianvishniac2003,
+roepkehn2003,roepkehn2004,
+Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
+Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
+jacketal2014,poludnenko2015,hicks2015}.
+
+A deflagration alone will not produce a event of normal brightness and
+expansion velocity~\citep{roepkeetal07}. Instead, the initial
+deflagration must transition to a detonation after the star has
+expanded some in order to produce abundances and a stratified ejecta
+in keeping with
+observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
+The physics of this ``deflagration-to-detonation transition'' (DDT)
+are not completely understood, but there has been considerable study
+based on mechanisms involving flame fronts in highly turbulent
+conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
+  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
+  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
+These models generally reproduce the observations under certain
+assumptions about the ignition~\citep{townetal2009}, but research has
+shown that the results are very sensitive to the details of the
+ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
+  roepkeetal07,Jordan2008Three-Dimension}.
+
+Summarize what we do a la:
+In our simulations, we initialize a detonation once the 
+deflagration front reaches a
+characteristic DDT fuel density, which controls the degree of
+expansion the star undergoes during the deflagration stage.
+
+The comparison study of tradition C/O progentor WDs used the same
+initial conditions for the realizations within the suite. Make the
+point that the traditional models are simalted with the same code
+and the same set if perturbations on the initial match head (that is
+what we mean by a realization). The only difference is the different
+nuclear buring to include the other Ne and the initial profile of
+the 1-d model.
+
+For much of the methodology to be described below, just say a few
+words about what was done and cite \citet{willcoxetal2016}.
+
+\section{Methods}
+\section{Initial Conditions}
+
+We used MESA, a 1-D stellar evolution code, to create the hybrid model.
+
+We found that the most abundant isotopes in the model were C12, O16, Ne20.
+There were a few other isotopes that were added to form Ne22 later. We saw
+that  ...
+
+Plotting the density verses solar radii, we found that the densest part of
+the star is in the center slowly decreasing until it hits 0 at the outer
+edge of the star.
+
+In order to see where we should ignite the flame, we plotted the temperature
+profile. It was found that the peak temperature is at the center of the
+star, therefore, it was obvious to ignite the flame in the core.
+
+\subsection{Created 2D model from 1-D model}
+
+We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
+MESA model into FLASH, which is a 2-D code, we needed the ratio of neutrons
+to protons in the nuclei to be the same ratio as in the mesa profile. This is
+because the amount of extra neutrons around is important when burning the
+star because that determines how much neutron rich isotopes the burring
+produces.
+
+\subsection{DDT Process and Suits of Explosions}
+
+The fuel starts off cold. The elections in the plasma conduct heat and the
+fuel begins to heat up. Once the fuel reaches a certain temperature, the
+reaction starts. The fuel abundance begins to decline because it is consuming
+fuel. Energy is produced which makes the fuel hot. Eventually, all that’s
+left is ash. As surface area grows, conducted energy increases and density
+decreases. At low densities Rayleigh-Taylor instability causes the flame to
+get more tangled and unstable. Eventually, the star will get a large enough
+surface area in this volume that the net burning effect is supersonic.
+Therefore, the transition from deflagration to detonation is made.
+
+Using the FLASH code from University of Chicago, simulations of
+explosions were preformed. For each simulation we varied the central
+ignition seed.
+
+\section{Results}
+
+A plot of the estimated Ni56 yield as a function of the final, burned mass
+for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
+model is shown in blue. As it is shown, the CO model has a higher final mass
+then the Hybrid model.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
+\caption{\label{fig:cumdist}
+A plot of the estimated Ni56 yield as a function of the final, burned mass
+for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
+model is shown in blue. As it is shown, the CO model has a higher final mass
+then the Hybrid model. 
+}
 \end{figure}
 
-\section{Methodology}
-
-Methodology goes here.
-
-A handy example of a vertical multi-plot figure is \figref{fig:znd_abundances}.
-
-\begin{figure}[t]
-	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_0_XC-50.pdf}
-		%\caption{\label{fig:znd_abundances_xc12_0.5} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.50$, $X_{^{20}Ne} = 0.00$}
-	\end{minipage}	
-	\hfill
-	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_20_XC-30.pdf}
-		%\caption{\label{fig:znd_abundances_xc12_0.3} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.30$, $X_{^{20}Ne} = 0.20$}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_35_XC-15.pdf}
-		%\caption{\label{fig:znd_abundances_xc12_0.15} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.15$, $X_{^{20}Ne} = 0.35$}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.5\textwidth}
-		\includegraphics[width=0.86\textwidth]{figures/samples/XvsT_wn_45_XC-05.pdf}
-		%\caption{\label{fig:znd_abundances_xc12_0.05} Initial composition: $X_{^{16}O} = 0.48$, $X_{^{22}Ne} = 0.02$, $X_{^{12}C} = 0.05$, $X_{^{20}Ne} = 0.45$}
-	\end{minipage}
-        \caption{\label{fig:znd_abundances} Mass Fraction Evolution for ZND Detonations with varying initial \C{12} and \Ne{20} mass fractions, calculated for an initial density of $10^7~\grampercc$.}
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
+\caption{\label{fig:nithybrid}
+Estimated Ni56 mass for Hybrid Model
+}
 \end{figure}
 
-Here's a text citation \citet{timmes92,Chametal08}, and here's a parenthetical citation ~\citep{timmes.swesty:accuracy,castro1}.
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
+\caption{\label{fig:nitco}
+Estimated Ni56 mass for CO Model
+}
+\end{figure}
 
-Here's an ordinary equation in \eqref{eq:hse_pressure}.
+The figures show that the final Estimated Ni56 for the CO model is slightly
+larger then the Hybrid model. Therefore, the CO produces more Ni56. The
+Hybrid model has a larger range then the CO model. Also, on average, the CO
+model reaches the DDT phase sooner then the Hybrid model.
 
-\begin{equation}\label{eq:hse_pressure}
-  P_{EOS}(\rho_i,T_i,X_i) = \frac{g \Delta r}{2} (\rho_i +
-  \rho_{i-1})\ .
-\end{equation}
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.png}
+\caption{\label{fig:masshighdens}
+...
+}
+\end{figure}
 
-Here's a multi-line equation.
+\section{Discussion and Conclusion}
 
-\begin{subequations}
-\begin{align}
-X_{\C{12}}^{FLASH} &= X_{\C{12}}^{MESA} \\
-X_{\Ne{22}}^{FLASH} &= 22 \cdot \left(\dfrac{1}{2}-Y_e^{MESA}\right) \\
-R &= X_{\Ne{20}}^{MESA}/X_{\Ox{16}}^{MESA} \\
-X_{\Ox{16}}^{FLASH} &= \frac{1 - X_{\C{12}}^{FLASH} - X_{\Ne{22}}^{FLASH}}{R + 1} \\
-X_{\Ne{20}}^{FLASH} &= R \cdot X_{\Ox{16}}^{FLASH}.
-\end{align}
-\end{subequations}
-
-\section{Simulations and Results}
-
-Simulations and results go here.
-
-Example of multi-figure plot that spans the columns is given by \figref{fig:cone_delayed_core}.
-
-\begin{figure*}[!ht]
-  \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0000"}
-  \end{minipage} \hfill
-  \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0190"}
-  \end{minipage} \hfill 
-  \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0200"}
-  \end{minipage} \hfill 
-  \begin{minipage}{0.24\textwidth}
-    \includegraphics[width=\linewidth]{"figures/samples/cone_400k_m16_a12_0210"}
-  \end{minipage} \caption{\label{fig:cone_delayed_core} Progress of the burning front into the stellar core for one hybrid C-O-Ne realization, delayed relative to complete burning throughout the rest of the star.
-For reference, the initially burned geometry is shown at left.
-Material is shaded based on the reaction progress variables so that \textbf{White} denotes unburned fuel (\C{12}, \Ox{16} \& \Ne{20}) and \textbf{Red} denotes ash from \C{12} and \Ne{20}-burning.
-\textbf{Green} then denotes material in quasi-nuclear statistical equilibrium (primarily intermediate-mass silicon-group elements), and \textbf{Black} denotes material in nuclear statistical equilibrium (IGEs and $\alpha$-particles).
-From left to right, the burning is shown at 0.0~\second, 1.9~\second, 2.0~\second, and 2.1~\second.
-The DDT time for this realization is $\approx \mathrm{1.4}~\second$.}
-\end{figure*}
-
-Example of a table with data, units, etc is at \tabref{YieldSummaryTable}.
-
-\begin{table}[htbp]
-  \caption{Average Yields and Kinetic Energy}
-  \begin{center}
-    \begin{tabular}{llll}
-      \vspace{-0.75cm} \\ \hline \hline
-      Progenitor & \Ni{56} & IGE & Kinetic Energy \\
-      Type & (\Msun) & (\Msun) & $\left(\times 10^{51} ~\erg\right)$ \\ \hline
-      C-O & $0.97 \pm 0.06$ & $1.12 \pm 0.07$ & $1.39 \pm 0.05$ \\
-      C-O-Ne & $0.86 \pm 0.10$ & $0.98 \pm 0.11$ & $1.06 \pm 0.10$ \\ \hline
-    \end{tabular}
-  \end{center}
-  \label{YieldSummaryTable}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-\label{sec:conclusions}
-
-Conclusive conclusions go here.
-
-\section{Appendix}
-
-If there's material for an appendix, it can go here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgements
-
-We'd like to acknowledge helpful discussions with Cab Ernet.
+This work was supported in part by the Department of Energy under
+grant DE-FG02-87ER40317. The software used in this work was in part
+developed by the DOE-supported ASC/Alliances Center for Astrophysical
+Thermonuclear Flashes at the University of Chicago. Results in this
+paper were obtained using the high-performance computing system at the
+Institute for Advanced Computational Science at Stony Brook
+University.  other grants...
 

### 2018-08-14 paper/ms.tex
Updated the text with text from Carlyn.

@@
 explosions produced from radioactive Ni-56 determined by the white dwarf
-(WD). Astronomers use the fact that they give off a known amount of light and
-the inverse square law to determine distances of far objects. They were also
-used to find Hubble’s expansion of the universe.
+(WD). Astronomers use the fact that they give off a known amount of light
+and the inverse square law to determine distances of far objects. They
+were also used to find Hubble’s expansion of the universe.
 
-There has been debate over what triggers a WD explosion. One of the primary
-ideas is the single degenerate process. During this process the white dwarf
-accretes material from a giant companion. Once the white dwarf reaches the
-Chandrasekhar limit, the star is consumed by thermonuclear runaway and
-explodes.
+ There has been debate over what triggers a WD explosion. One of the
+ primary ideas is the single degenerate process. During this process
+ the white dwarf accretes material from a giant companion. Once the
+ white dwarf reaches the Chandrasekhar limit, the star is consumed
+ by thermonuclear runaway and explodes. Another idea is the double
+ degenerate process: two white dwarfs merge to exceed the Chandrasekhar
+ limit. Hydrogen is not expected to be observed since both stars exhausted
+ their hydrogen long ago.
 
@@
 flame in the core starts out in the deflagration process, sub sonically
-burning C/O/Ne in its path. Once it reaches a certain density, the wave moves
-into the detonation front and sweeps through the rest of the star.  This
-process is the deflagration to detonation process (DDT): when a wave moves
-from being subsonic to supersonic.
+burning C/O/Ne in its path. Once it reaches a certain density, the
+wave moves into the detonation front and sweeps through the rest of
+the star. This process is the deflagration to detonation process (DDT):
+when a wave moves from being subsonic to supersonic.
 
@@
 \subsection{The Chandrasekhar-mass Single Degenerate Scenario}
+
+Carlyn's starter text: (to end starter)
+
+The fuel starts off cold. The elections in the plasma conduct heat
+and the fuel begins to heat up. Once the fuel reaches a certain
+temperature, the reaction starts. The fuel abundance begins to
+decline because it is consuming fuel. Energy is produced which
+makes the fuel hot. Eventually, all that’s left is ash. As
+surface area grows, conducted energy increases and density
+decreases. At low densities Rayleigh-Taylor instability causes
+the flame to get more tangled and unstable. Eventually, the
+star will get a large enough surface area in this volume that
+the net burning effect is supersonic. Therefore, the transition
+from deflagration to detonation is made.
+
+A deflagration alone will not produce an event of normal
+brightness and expansion velocity. Instead, the initial
+deflagration must transition to a detonation after the star has
+expanded some in order to produce abundances and a stratified
+ejecta in keeping with observations. The physics of this
+“deflagration-to- detonation transition” (DDT) are not
+completely understood, but there has been considerable study
+based on mechanisms involving flame fronts in highly turbulent
+conditions. These models generally reproduce the observations
+under certain assumptions about the ignition, but research has
+shown that the results are very sensitive to the details of the
+ignition. In our simulations, we initialize a detonation once
+the deflagration front reaches a characteristic DDT fuel density,
+which controls the degree of expansion the star undergoes during
+the deflagration stage.
+
+The comparison study of tradition C/O progenitor WDs used the same initial
+conditions for the realizations within the suite. The traditional models
+are simulated with the same code and the same set of perturbations on the
+initial match head (realization). The only difference is the different
+nuclear burning to include the other Ne and the initial profile of the
+1-d model.
+
+(end starter)
 
@@
 
-We used MESA, a 1-D stellar evolution code, to create the hybrid model.
+We used MESA, a 1-D stellar evolution code, to create the hybrid
+model. We made the hybrid model have the same central temperature
+and density as the classic model.
 
-We found that the most abundant isotopes in the model were C12, O16, Ne20.
-There were a few other isotopes that were added to form Ne22 later. We saw
-that  ...
+We found that the most abundant isotopes in the model were C12, O16,
+Ne20. There were a few other isotopes that were added to form Ne22
+later. We saw that  ….
 
-Plotting the density verses solar radii, we found that the densest part of
-the star is in the center slowly decreasing until it hits 0 at the outer
-edge of the star.
+Plotting the density verses solar radii, we found that the densest part
+of the star is in the center slowly decreasing until it hits 0 at the
+outer edge of the star.
 
-In order to see where we should ignite the flame, we plotted the temperature
-profile. It was found that the peak temperature is at the center of the
-star, therefore, it was obvious to ignite the flame in the core.
+In order to see where we should ignite the flame, we plotted the
+temperature profile. It was found that the peak temperature is at the
+center of the star, therefore, it was obvious to ignite the flame in
+the core. (PUT IN TEMP PROFILE)
 
@@
 We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
-MESA model into FLASH, which is a 2-D code, we needed the ratio of neutrons
-to protons in the nuclei to be the same ratio as in the mesa profile. This is
-because the amount of extra neutrons around is important when burning the
-star because that determines how much neutron rich isotopes the burring
-produces.
+MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
+matter. This means that the ratio of neutrons to protons in the nuclei
+must be the same ratio as in the mesa profile. This is because the amount
+of extra neutrons around is important when burning the star because that
+determines how much neutron rich isotopes the burning produces.
 
@@
 ignition seed.
+
+----updated text-----
+
+DDT Process:
+The fuel starts off cold. The elections in the plasma conduct heat
+and the fuel begins to heat up. Once the fuel reaches a certain
+temperature, the reaction starts. The fuel abundance begins to
+decline because it is consuming fuel. Energy is produced which
+makes the fuel hot. Eventually, all that’s left is ash. As
+surface area grows, conducted energy increases and density
+decreases. At low densities Rayleigh-Taylor instability causes
+the flame to get more tangled and unstable. Eventually, the
+star will get a large enough surface area in this volume that
+the net burning effect is supersonic. Therefore, the transition
+from deflagration to detonation is made.
+
+A deflagration alone will not produce an event of normal
+brightness and expansion velocity. Instead, the initial
+deflagration must transition to a detonation after the star has
+expanded some in order to produce abundances and a stratified
+ejecta in keeping with observations. The physics of this
+“deflagration-to- detonation transition” (DDT) are not
+completely understood, but there has been considerable study
+based on mechanisms involving flame fronts in highly turbulent
+conditions. These models generally reproduce the observations
+under certain assumptions about the ignition, but research has
+shown that the results are very sensitive to the details of the
+ignition. In our simulations, we initialize a detonation once
+the deflagration front reaches a characteristic DDT fuel density,
+which controls the degree of expansion the star undergoes during
+the deflagration stage.
+
+The comparison study of tradition C/O progenitor WDs used the same initial
+conditions for the realizations within the suite. The traditional models
+are simulated with the same code and the same set of perturbations on the
+initial match head (realization). The only difference is the different
+nuclear burning to include the other Ne and the initial profile of the
+1-d model.
+
+----above updated text-----
 
@@
 
-The figures show that the final Estimated Ni56 for the CO model is slightly
-larger then the Hybrid model. Therefore, the CO produces more Ni56. The
-Hybrid model has a larger range then the CO model. Also, on average, the CO
-model reaches the DDT phase sooner then the Hybrid model.
+The figures show that the final Estimated Ni56 for the CO model is
+slightly larger then the Hybrid model. Therefore, the CO produces more
+Ni56. The Hybrid model has a larger range then the CO model. Also, on
+average, the CO model reaches the DDT phase sooner then the Hybrid model.
+
+This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at
+the time of the DDT.
+
+The degree of expansion was found using the time at which the first
+detonation point occurred, and the mass at density less then 2e7 g/cc. The
+estimated Ni56 Yield is the final estimated mass of the model.
 
@@
 \section{Discussion and Conclusion}
+
+The conversion of Ni56 to Iron group elements are more pronounced in my
+case. There are two assumptions as to why figure 6 is more pronounced
+in my paper then in Dons.  First is that higher critical density leads
+to higher electron capture resulting in less Ni56 produced. The second
+is that the central ignition leads to early burning at higher density.
+
+As the star burns mass, the surface area grows, resulting in a decrease
+in density. The results show that the models that burned less mass during
+the deflagration phase, expand less, produce more Ni-56. This is because
+the density rich mass the model has at the DDT point is the ‘fuel’
+it needs to produce Ni-56. Therefore, the more mass, the more Ni-56. On
+average, the CO model, shown in figure 4, reaches the DDT faster then
+the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
+range of estimated Ni-56 mass suggesting a greater range of burned mass
+and expansion during the deflagration phase.
 

### 2018-11-16 paper/ms.tex
Working on the Brooks et al hybrid model manuscript.

@@
 \begin{abstract}
-Type Ia Supernovae are thermonuclear explosions of white dwarf (WD) stars.
-Past studies predict the existence of "hybrid" white dwarfs, made of a C/O/Ne
-core with a O/Ne shell, and that these are viable progenitors for supernovae.
+Recent studies of stellar evolution predict the existence of "hybrid" white 
+dwarfs, made of a C/O/Ne
+core within a O/Ne shell, and that these are viable progenitors for supernovae.
 More recent work found that the C/O core is mixed with the surrounding O/Ne
 while the WD cools. Inspired by this scenario, we performed simulations of
-thermonuclear supernovae in the single degenerate paradigm from these hybrid
-progenitors. A hybrid white dwarf model constructed with the one-dimensional
-stellar evolution code MESA[5] was provided (Brooks et al. 2017) for our
-simulations.  This model had been run through the phase of unstable interior
-mixing followed by accretion until central ignition of carbon burning. The
-MESA model was then mapped to a two-dimensional initial condition and an
-explosion simulated from that with FLASH[4]. For comparison, a similar
+thermonuclear supernovae from these hybrid progenitors. The progenitor model 
+was constructed with the one-dimensional stellar evolution code MESA and
+represented a star evolved through the phase of unstable interior mixing 
+followed by accretion until it reached conditions for the ignition of 
+carbon burning. The MESA model was then mapped to a two-dimensional initial 
+condition and an explosion simulated with FLASH. For comparison, a similar
 simulation of an explosion was performed from a traditional C/O progenitor
-WD. Comparing the yields produced by explosion simulations allows us to
-determine which model produces more 56Ni, and therefore brighter events, and
+WD. By comparing the yields of the explosions, we found....
 how explosions from these models differ from explosions from previous models
@@
 \label{sec:intro}
-Type Ia supernovae (\SNeIa) are bright stellar explosions....
+Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
+thought to occur when approximately 1.5 \Msun of material composed principally 
+of C and O burns under degenerate conditions. This class of supernovae is
+know to synthesize much of the Fe-group elements found in the galaxy and
+the light curves of these events have a spectial property that allows
+their use as distance indicators for cosmological studies~\citep{phillips:absolute}
+resulting in the discovery of the acceleration of the expansion of
+the Universe and thus the inference of Dark 
+Energy~\citep{riess.filippenko.ea:observational,
+perlmutter.aldering.ea:measurements,leibundgut2001}.
 
-Carlyn's starter text: (to end starter)
+Supernovae are observationally classified 
+by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
+wheelerharkness1990conf,Fili97}, with the type Ia designation following from
+the absence of H in the spectrum and the presence of a specific Si 
+line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
+have been associated with C burning under degenerate conditions
+for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
+but discerning the setting of these events is proving difficult
+and remains the subject of active research. At present there are three
+widely-accpeted scenarios, the {\em double detonation} or {\em sub-Chandrasekhar}
+scenario, the {\em white dwarf merger} scenario, and  
+the {\em single degenerate} scenario.
 
@@
 
-Phillips relation
-~\citep{phillips:absolute}.
-
-Cosmology
-due to dark energy \citep{riess.filippenko.ea:observational,
-perlmutter.aldering.ea:measurements,leibundgut2001}.
-
 Brief discussion of progentors...
@@
 \citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
+
+\citet{woosleyweavertaam80,taam80a,taam80b, nomoto80,nomoto82b} subchandra
 
@@
 
-Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
+Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
 Give a read to see!

### 2018-11-19 paper/ms.tex
More wordsmithing on Carlyn's paper.

@@
 More recent work found that the C/O core is mixed with the surrounding O/Ne
-while the WD cools. Inspired by this scenario, we performed simulations of
+while the white dwarf cools. Inspired by this scenario, we performed simulations of
 thermonuclear supernovae from these hybrid progenitors. The progenitor model 
@@
 simulation of an explosion was performed from a traditional C/O progenitor
-WD. By comparing the yields of the explosions, we found....
+white dwarf. By comparing the yields of the explosions, we found....
 how explosions from these models differ from explosions from previous models
-without the mixing during the WD cooling.
+without the mixing during the white dwarf cooling.
 \end{abstract}
@@
 perlmutter.aldering.ea:measurements,leibundgut2001}. 
+This special property of the light curve is thought to follow
+from the fact that the source of luminosity, the radioactive decay
+of \Ni{56}, synthesized by the thermonuclear burning, is also the
+principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.
 
-Supernovae are observationally classified 
+Supernovae are classified observationally 
 by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
@@
 for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
-but discerning the setting of these events is proving difficult
+but discerning the setting(s) of these events is proving difficult
 and remains the subject of active research. At present there are three
-widely-accpeted scenarios, the {\em double detonation} or {\em sub-Chandrasekhar}
-scenario, the {\em white dwarf merger} scenario, and  
-the {\em single degenerate} scenario.
+widely-accpeted scenarios: the {\em single degenerate} scenario,
+the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
+the {\em white dwarf merger} or {\em double degenerate} scenario.
 
-When a main sequence star runs out of fuel, it dies off to become a dense
-remnant of the MS, known as a white dwarf. Type Ia Supernova are bright
-explosions produced from radioactive Ni-56 determined by the white dwarf
-(WD). Astronomers use the fact that they give off a known amount of light
-and the inverse square law to determine distances of far objects. They
-were also used to find Hubble’s expansion of the universe.
+The single degenerate picture posits a white dwarf gaining mass
+from a main-sequence companion. The process relies on a long
+period of accretion combined with either steady burning or a 
+series of nova explosions to allow the WD to gain
+~0.6 CHECK THIS \Msun needed for it to approach the
+limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
+the Chandrasekhar limit, conditions in the compressed core are right
+to ignite the thermonuclear buring that will incinerate the star. Within this
+progenitor setting, the models that best reproduce the observed
+stratified ejecta are those in which the burning begins as a 
+subsonic deflagration, which allows the star to react and expand
+thus lowering the density, that is followed by a 
+detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
+We adopt this setting for the explosion simulations we present and 
+describe our approach in detail below.
+
+The white dwarf merger progentor picture has two white dwarfs 
+coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
+
+. This scenario 
+provides an abundance of degenerate fuel, which may explain some 
+The other main class of models is the DD progenitor,
+\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
+This scenario includes inspiraling pairs, collisions, violent mergers,
+and also the ``core-degenerate'' model where the merger takes place in
+a common envelope
+\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
+Also
+see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
+for additional discussion.
 
@@
 
-\subsection{The Chandrasekhar-mass Single Degenerate Scenario}
+\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
 

### 2018-12-03 paper/ms.tex
Added a new version of Carlyn's figure.
Wee update of Carlyn's paper.

@@
 Supernovae are classified observationally 
-by their light curves and spectra~~\citet{minkowski41,bertola64,porterfilippenko87,
+by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
 wheelerharkness1990conf,Fili97}, with the type Ia designation following from
@@
 coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
+This scenario provides an abundance of degenerate fuel, which may explain some 
+bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers  scenario
 
-. This scenario 
-provides an abundance of degenerate fuel, which may explain some 
 The other main class of models is the DD progenitor,
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.png}
+\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
 \caption{\label{fig:masshighdens}

### 2018-12-05 paper/ms.tex
More work on Carlyn's paper.

@@
 Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
-thought to occur when approximately 1.5 \Msun of material composed principally 
-of C and O burns under degenerate conditions. This class of supernovae is
+thought to occur when approximately 1.X \Msun of material composed principally 
+of C and O burns under degenerate conditions (SETTLE ON X). This class of supernovae is
 know to synthesize much of the Fe-group elements found in the galaxy and
@@
 This scenario provides an abundance of degenerate fuel, which may explain some 
-bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers  scenario
+bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers include
+variations on the interaction and include
 
-The other main class of models is the DD progenitor,
-\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
-This scenario includes inspiraling pairs, collisions, violent mergers,
-and also the ``core-degenerate'' model where the merger takes place in
+inspiraling pairs, collisions, violent mergers,
+and the ``core-degenerate'' model where the merger takes place in
 a common envelope

### 2018-12-05 paper/ms.tex
More work on Carlyn's paper

@@
 the {\em white dwarf merger} or {\em double degenerate} scenario.
+We briefly describe these in the subsection that follows. `
+Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
+for additional discussion.
+
+\subsection{Proposed Progenitor Settings}
 
@@
 
-The white dwarf merger progentor picture has two white dwarfs 
-coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
-This scenario provides an abundance of degenerate fuel, which may explain some 
-bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers include
-variations on the interaction and include
+The double detionation picture is a variation of the single degenerate picture.
+In this case, a white dwarf accretes material from a companion, but rather
+than gaining enough mass to approach the Chandrasekhar limit, a detonation
+occurs in the accreted layer that subsequently triggers a detonation
+in the underlying white dwarf \citet{woosleyweavertaam80,taam80a,taam80b,
+nomoto80,nomoto82b}. Early studies indicated that a detonation in an 
+accreted He
+layer could produce an inwardly propagating
+shock that would ignite a detonation in the C-O core and found
+that this scenario could work for a wide range of white dwarf
+masses, not just the near-Chandrasekhar case \citep{livne90}, hence the
+moniker ``sub-Chandrasekhar'' \citep{ww94}. Multidimensional supported the
+efficacy of this picture~\citep{livneglasner91, livnearnett95,HoefKhok96,
+hoeflichetal96, wigginsfalle97,wigginsetal98,garciasenzbravowoosley99} 
+but indicated that uncertainties 
+like the initial conditions were found to play a significant role.
+on the explosion outcome.
 
+A particular problem was that most models 
+included a massive He layer, which leads to 
+the unobserved result intermediate and heavy elements synthesized in 
+the He detonation in the outer parts of the ejecta~\citep{HoefKhok96, 
+hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.
+\citet{bildstenetal2007}, however, found that fairly thin He layers
+could flash on sub-Chandrasekhar
+mass white dwarfs, partially resolving the issue and encouraging
+further research~\citep{simetal2012,brooksetal2015, shenetal2018,
+glasneretal2018}.
+
+The white dwarf merger progentor picture has two white dwarfs coming 
+together and subsequently exploding~\citep{tutukovyungelson76,tutukovyungelson79,
+webbink84,ibentutukov84}. This scenario provides an abundance of degenerate fuel, 
+which may explain some bright events~\citep{scalzo:2010,Yuan:2010}. 
+An early concern about this model came from studies finding that
+the white dwarf will ignite at the edge and the coalesced object, 
+and a flame will burn inward, converting the C-O white dwarf into 
+an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004}, with
+further accretion leading to the collapse of the white dwarf
+into a neutron star, a scenario termed ``accretion-induced collapse''
+\citep{nomotokondo1991}.
+
+Subsequent work allayed this concern~\citep{yoonetal2007,lorenaguilaretal2009,
+Shenetal12, pakmoretal2012b} and motivated by the need to expain briht events
+and the estimated population WD pairs, active research continues. Contemporary
+research focuses on variations on the merger idea, including 
 inspiraling pairs, collisions, violent mergers,
-and the ``core-degenerate'' model where the merger takes place in
-a common envelope
-\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
-Also
-see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
-for additional discussion.
+and the ``core-degenerate'' model in which the merger takes place in
+a common envelope \citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12,katzetal2016}.
 
-There has been debate over what triggers a WD explosion. One of the
-primary ideas is the single degenerate process. During this process
-the white dwarf accretes material from a giant companion. Once the
-white dwarf reaches the Chandrasekhar limit, the star is consumed
-by thermonuclear runaway and explodes. Another idea is the double
-degenerate process: two white dwarfs merge to exceed the Chandrasekhar
-limit. Hydrogen is not expected to be observed since both stars exhausted
-their hydrogen long ago.
+\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
 
@@
 when a wave moves from being subsonic to supersonic.
-
-(end starter)
-
-Brief discussion of progentors...
-ancient history~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis}. The
-Single degenerate 
-\citep{hoylefowler60,trucam71,whelaniben73,Nomo84}. Alternately, in
-
-Other models
-\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.
-
-\citet{woosleyweavertaam80,taam80a,taam80b, nomoto80,nomoto82b} subchandra
-
-Hybrid models 
-old 
-\citep{denissenkovetal2015}
-\citet{Wangetal2014} and \citet{Mengetal2014} presented binary
-
-Recent results from stellar evolution
-The models we are exploding \citep{brooksetal2017}
-
-If we refer to the work by name, it should appear ``The hybrid models
-of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
-
-Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
-Give a read to see!
-
-\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
 
@@
 
+\subsection{A Recent Advance in Stellar Evolution: Hybrid White Dwarfs}
+
+Hybrid models 
+old 
+\citep{denissenkovetal2015}
+\citet{Wangetal2014} and \citet{Mengetal2014} presented binary
+
+Recent results from stellar evolution
+The models we are exploding \citep{brooksetal2017}
+
+If we refer to the work by name, it should appear ``The hybrid models
+of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
+
+Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
+Give a read to see!
+
+\section{Methods}
+
 Summarize what we do a la:
@@
 
-\section{Methods}
-\section{Initial Conditions}
+\subsection{Initial Conditions}
 

### 2018-12-07 paper/ms.tex
More on Carlyn's paper

@@
 the Chandrasekhar limit, conditions in the compressed core are right
-to ignite the thermonuclear buring that will incinerate the star. Within this
-progenitor setting, the models that best reproduce the observed
+to ignite the thermonuclear buring that will incinerate the star.
+
+Within this progenitor setting, many mechanisms for the explosion have 
+been studied with the result being that the outcome is sensitive to
+the ignition conditions and the nature of the thermonuclear buring.
+Studies indicate that neither a pure deflagration (subsonic flame front)
+nor a pure detonation (supersonic burning front) produce ejecta conisitent
+with observations \citep{arnett69,roepkeetal07}.
+Instead, the models that best reproduce the observed
 stratified ejecta are those in which the burning begins as a 
@@
 detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
-We adopt this setting for the explosion simulations we present and 
-describe our approach in detail below.
+The classic delayed detonation model is that of 
+Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
+and many variations have been 
+explored \cite[and references therein]{hillebrandtetal2013,calderetal2013}.
+The approach we employ for this study is a variation, the deflagration-to-detonation
+transition (DDT).
 
@@
 
-\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
+\subsection{The Deflagraiton to Detonation Transition Mechanism Within the Single Degenerate Scenario}
+
+Our models are within the DDT explosion paradigm \cite{1986SvAL,
+Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004, fishjump2015}. 
+Thermonuclear burning begins as a deflagration in the core of the WD.
+The flame is unstable, and as the deflagration propagates toward the surface
+of the WD, it is subject to the Rayleigh-Taylor instability that generates
+turbulence and boosts buring.  
+Burning proceeds as a deflagration
+
+and we 
+adopt a variation of the latter case, a deflagration-to-detonation transition
+that occurs at the top of a rising plume of hot, burned material when it
+reaches a threshold density.
+
+Because the two extremes of pure deflagrations or pure detonations cannot
+robustly reproduce events with characteristics consistent with the observations,
+researchers have investigated models evoking a combination of the two. These models
+may be broadly described as delayed detonation, and a variety of scenarios have
+been proposed. The classic delayed detonation model was introduced by
+Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
+and variations include pulsational
+detonations \cite{ivanovaetal1974,Khokhlov1991Delayed-detonat,
+arnettlivne94a, arnettlivne94b, bravogarcia-senz2006},
+gravitationally confined detonation \cite{PlewCaldLamb04,Jordan2008Three-Dimension,
+jordanetal2012}, and deflagration-to-detonation
+transitions (DDTs) \cite{1986SvAL,Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,
+fishjump2015}. We adopt a variation of the latter case, a deflagration-to-detonation transition
+that occurs at the top of a rising plume of hot, burned material when it
+reaches a threshold density.
+
+The physics by which a DDT may occur are not completely understood, but
+ideas have been proposed. One idea is that at low densities the flame
+enters a regime of distributed burning in which it is no longer
+well-defined but the net burning rate is high enough that it is
+effectively supersonic \cite{NiemWoos97}. Similarly, others argue
+that when the flame reaches a certain fractal dimension, it is
+effectively supersonic \cite{woosley90}. The Zel'dovich mechanism
+posits that composition and temperature gradients may ``prepare" the
+fuel in just the right way that it will detonate
+\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}. Our approach
+is to assume that when the top of a rising, Rayleigh-Taylor unstable
+plume reaches a particular density, conditions are favorable and the
+transition occurs \cite{townsley.calder.ea:flame}.
 
@@
 Give a read to see!
+
+Recent population synthesis work indicating a substantial contribution
+to the Ia population rate from mergers where one member is a 
+hybrid~\citep{yungelsonkuranov2017}.
 

### 2018-12-10 paper/ms.tex
More on Carlyn's paper

--- 2018-12-05 paper/ms.tex
@@
 Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
-thought to occur when approximately 1.X \Msun of material composed principally 
+thought to occur when approximately 1.X \Msun\ of material composed principally 
 of C and O burns under degenerate conditions (SETTLE ON X). This class of supernovae is
@@
 series of nova explosions to allow the WD to gain
-~0.6 CHECK THIS \Msun needed for it to approach the
+~0.6 CHECK THIS \Msun\ needed for it to approach the
 limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
 the Chandrasekhar limit, conditions in the compressed core are right
-to ignite the thermonuclear buring that will incinerate the star. Within this
-progenitor setting, the models that best reproduce the observed
+to ignite the thermonuclear buring that will incinerate the star.
+
+Within this progenitor setting, many mechanisms for the explosion have 
+been studied with the result being that the outcome is sensitive to
+the ignition conditions and the nature of the thermonuclear buring.
+Studies indicate that neither a pure deflagration (subsonic flame front)
+nor a pure detonation (supersonic burning front) produce ejecta conisitent
+with observations \citep{arnett69,roepkeetal07}.
+Instead, the models that best reproduce the observed
 stratified ejecta are those in which the burning begins as a 
@@
 detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
-We adopt this setting for the explosion simulations we present and 
-describe our approach in detail below.
+The ``classic'' delayed detonation model is that of 
+Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
+and many variations have been 
+explored \cite[and references therein]{hillebrandtetal2013,calderetal2013}.
+The approach we employ for this study is a variation, the 
+deflagration-to-detonation transition (DDT), in which the transition
+occurs at the top of a rising Rayleigh-Taylor unstable plume of hot, burned 
+material when it reaches a threshold density.
+Which we describe this approach and our methodology  in detail below.
 
@@
 
-\subsection{The near-Chandrasekhar-mass Single Degenerate Scenario}
+\subsection{The Deflagraiton to Detonation Transition Mechanism Within the Single Degenerate Scenario}
 
-In our study, we use the single degenerate process to ignite a flame. The
-flame in the core starts out in the deflagration process, sub sonically
-burning C/O/Ne in its path. Once it reaches a certain density, the
-wave moves into the detonation front and sweeps through the rest of
-the star. This process is the deflagration to detonation process (DDT):
-when a wave moves from being subsonic to supersonic.
+Our models are within the DDT explosion paradigm \cite{1986SvAL,
+Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}. 
+Thermonuclear burning begins as a deflagration in the core of the WD.
+The flame is unstable, and as the deflagration propagates toward the surface
+of the WD, it is subject to the Rayleigh-Taylor instability that generates
+turbulence and boosts buring.  
+Burning proceeds as a deflagration for about one second, and then 
+the flame transitions to a detonation.
 
-Carlyn's starter text: (to end starter)
+%Maybe add some of below?
+%and variations include pulsational
+%detonations \cite{ivanovaetal1974,Khokhlov1991Delayed-detonat,
+%arnettlivne94a, arnettlivne94b, bravogarcia-senz2006},
+%gravitationally confined detonation \cite{PlewCaldLamb04,Jordan2008Three-Dimension,
+%jordanetal2012}, and deflagration-to-detonation
+%transitions (DDTs) \cite{1986SvAL,Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,
+%fishjump2015}. We adopt a variation of the latter case, a deflagration-to-detonation transition
+%that occurs at the top of a rising plume of hot, burned material when it
+%reaches a threshold density.
 
-The fuel starts off cold. The elections in the plasma conduct heat
-and the fuel begins to heat up. Once the fuel reaches a certain
-temperature, the reaction starts. The fuel abundance begins to
-decline because it is consuming fuel. Energy is produced which
-makes the fuel hot. Eventually, all that’s left is ash. As
-surface area grows, conducted energy increases and density
-decreases. At low densities Rayleigh-Taylor instability causes
-the flame to get more tangled and unstable. Eventually, the
-star will get a large enough surface area in this volume that
-the net burning effect is supersonic. Therefore, the transition
-from deflagration to detonation is made.
-
-A deflagration alone will not produce an event of normal
-brightness and expansion velocity. Instead, the initial
-deflagration must transition to a detonation after the star has
-expanded some in order to produce abundances and a stratified
-ejecta in keeping with observations. The physics of this
-“deflagration-to- detonation transition” (DDT) are not
-completely understood, but there has been considerable study
-based on mechanisms involving flame fronts in highly turbulent
-conditions. These models generally reproduce the observations
-under certain assumptions about the ignition, but research has
-shown that the results are very sensitive to the details of the
-ignition. In our simulations, we initialize a detonation once
-the deflagration front reaches a characteristic DDT fuel density,
-which controls the degree of expansion the star undergoes during
-the deflagration stage.
+The mechanism by which the deflagration transistions to a detonation
+is imcompletely understood, but the development of fluid instabilities
+at the deflagration front, particuarly the Rayleigh-Taylor 
+instability~\cite{}, is an accepted part of the process.
+Many ideas have been proposed, including the deflagration front
+entering a regime of distributed burning and the net
+rate becoming supersonic \cite{NiemWoos97}, the unstable
+flame reaching a certian fractal dimension~\cite{woosley90},
+and the Zel'dovich mechanism in which condtions are right for
+a pocket of fuel to 
+detonate~\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
+Our simulations assume that the transition occurs when the top of a 
+rising, Rayleigh-Taylor unstable plume reaches a characteristic low
+density \cite{townsley.calder.ea:flame}.
 
@@
 
-Explain the Single Degenerate scenario
-\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
-expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born.
-
-Explain DDT
-
-Go through below and cite some of these as you tell the story
-
-d~\citep{arnett.truran.ea:nucleosynthesis}.
-~\citep{mazzalietal2008}.
-
-\citep{khokhlov1993,bychovliberman1995,
-SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
-cholazarianvishniac2003,
-roepkehn2003,roepkehn2004,
-Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
-Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
-jacketal2014,poludnenko2015,hicks2015}.
-
-A deflagration alone will not produce a event of normal brightness and
-expansion velocity~\citep{roepkeetal07}. Instead, the initial
-deflagration must transition to a detonation after the star has
-expanded some in order to produce abundances and a stratified ejecta
-in keeping with
-observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
-The physics of this ``deflagration-to-detonation transition'' (DDT)
-are not completely understood, but there has been considerable study
-based on mechanisms involving flame fronts in highly turbulent
-conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
-  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
-  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
-These models generally reproduce the observations under certain
-assumptions about the ignition~\citep{townetal2009}, but research has
-shown that the results are very sensitive to the details of the
-ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
-  roepkeetal07,Jordan2008Three-Dimension}.
+%
+%
+%Explain the Single Degenerate scenario
+%\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
+%expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born. 
+%
+%Explain DDT
+%
+%Go through below and cite some of these as you tell the story
+%
+%d~\citep{arnett.truran.ea:nucleosynthesis}.
+%~\citep{mazzalietal2008}.  
+%
+%
+%\citep{khokhlov1993,bychovliberman1995,
+%SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
+%cholazarianvishniac2003,
+%roepkehn2003,roepkehn2004,
+%Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
+%Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
+%jacketal2014,poludnenko2015,hicks2015}.
+%
+%
+%A deflagration alone will not produce a event of normal brightness and
+%expansion velocity~\citep{roepkeetal07}. Instead, the initial
+%deflagration must transition to a detonation after the star has
+%expanded some in order to produce abundances and a stratified ejecta
+%in keeping with
+%observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
+%The physics of this ``deflagration-to-detonation transition'' (DDT)
+%are not completely understood, but there has been considerable study
+%based on mechanisms involving flame fronts in highly turbulent
+%conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
+%  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
+%  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
+%These models generally reproduce the observations under certain
+%assumptions about the ignition~\citep{townetal2009}, but research has
+%shown that the results are very sensitive to the details of the
+%ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
+%  roepkeetal07,Jordan2008Three-Dimension}.
 

### 2018-12-10 paper/ms.tex
More work on Caryn's paper. And, responding to criticism that these messages are not helpful, I'll add blaming @bkkrueger as a way of craking out more specific text.

@@
 series of nova explosions to allow the WD to gain
-~0.6 CHECK THIS \Msun\ needed for it to approach the
+$\sim 0.6$ CHECK THIS \Msun\ needed for it to approach the
 limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
@@
 Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}. 
-Thermonuclear burning begins as a deflagration in the core of the WD.
-The flame is unstable, and as the deflagration propagates toward the surface
+In this scenario, the accretion of mass on the white dwarf compresses and 
+heats the core, igniting carbon fusion and driving a period of convection
+\citep{WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
+At some point, the fusion rate becomes fast enough due to the rising
+temperature that energy production exceeds convective cooling and
+the deflagration phase begins in the core~\citep{Nomo84,WoosWunsKuhl04}.
+This flame is unstable, and as the deflagration propagates toward the surface
 of the WD, it is subject to the Rayleigh-Taylor instability that generates
@@
 Burning proceeds as a deflagration for about one second, and then 
-the flame transitions to a detonation.
+the flame transitions to a detonation~\citep{hoflich.khokhlov.ea:delayed}.
 
@@
 at the deflagration front, particuarly the Rayleigh-Taylor 
-instability~\cite{}, is an accepted part of the process.
+instability~\cite{taylor+50,chandra+81}, is an accepted part of the process.
 Many ideas have been proposed, including the deflagration front
@@
 density \cite{townsley.calder.ea:flame}.
-
-The comparison study of tradition C/O progenitor WDs used the same initial
-conditions for the realizations within the suite. The traditional models
-are simulated with the same code and the same set of perturbations on the
-initial match head (realization). The only difference is the different
-nuclear burning to include the other Ne and the initial profile of the
-1-d model.
-
-(end starter)
 
@@
 
+Modern computing resources now enable simulations with unprecedented 
+realism, allowing both one-dimensional simulations with a vast
+amount of included physics and full three-dimensional simulations
+albeit with less included physics~\cite{caldertownsley2018}.
+In the area of stellar evolution, recent investigations revisiting 
+late-time evolution of ????-mass stars indicate the existance of
+``hybrid" white dwarfs that
+
 Hybrid models 
@@
 \citet{Wangetal2014} and \citet{Mengetal2014} presented binary
+
+see however~\cite{lecoanetetal16}
 
@@
 
-Recent population synthesis work indicating a substantial contribution
+Also, recent population synthesis work indicating a substantial contribution
 to the Ia population rate from mergers where one member is a 
@@
 expansion the star undergoes during the deflagration stage.
+
+The comparison study of tradition C/O progenitor WDs used the same initial
+conditions for the realizations within the suite. The traditional models
+are simulated with the same code and the same set of perturbations on the
+initial match head (realization). The only difference is the different
+nuclear burning to include the other Ne and the initial profile of the
+1-d model.
 
@@
 
-A plot of the estimated Ni56 yield as a function of the final, burned mass
+A plot of the estimated \Ni{56} yield as a function of the final, burned mass
 for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
@@
 \caption{\label{fig:cumdist}
-A plot of the estimated Ni56 yield as a function of the final, burned mass
+A plot of the estimated \Ni{56} yield as a function of the final, burned mass
 for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
@@
 \caption{\label{fig:nithybrid}
-Estimated Ni56 mass for Hybrid Model
+Estimated \Ni{56} mass for Hybrid Model
 }
@@
 \caption{\label{fig:nitco}
-Estimated Ni56 mass for CO Model
+Estimated \Ni{56} mass for CO Model
 }
@@
 
-The figures show that the final Estimated Ni56 for the CO model is
+The figures show that the final Estimated \Ni{56} for the CO model is
 slightly larger then the Hybrid model. Therefore, the CO produces more
-Ni56. The Hybrid model has a larger range then the CO model. Also, on
+\Ni{56}. The Hybrid model has a larger range then the CO model. Also, on
 average, the CO model reaches the DDT phase sooner then the Hybrid model.
 
-This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at
+This is a plot of the estimated \Ni{56} yield vs. mass below 2e7 g/cc at
 the time of the DDT.
@@
 detonation point occurred, and the mass at density less then 2e7 g/cc. The
-estimated Ni56 Yield is the final estimated mass of the model.
+estimated \Ni{56} Yield is the final estimated mass of the model.
 
@@
 
-The conversion of Ni56 to Iron group elements are more pronounced in my
+The conversion of \Ni{56} to Iron group elements are more pronounced in my
 case. There are two assumptions as to why figure 6 is more pronounced
 in my paper then in Dons.  First is that higher critical density leads
-to higher electron capture resulting in less Ni56 produced. The second
+to higher electron capture resulting in less \Ni{56} produced. The second
 is that the central ignition leads to early burning at higher density.
@@
 in density. The results show that the models that burned less mass during
-the deflagration phase, expand less, produce more Ni-56. This is because
+the deflagration phase, expand less, produce more \Ni{56}. This is because
 the density rich mass the model has at the DDT point is the ‘fuel’
-it needs to produce Ni-56. Therefore, the more mass, the more Ni-56. On
+it needs to produce \Ni{56}. Therefore, the more mass, the more Ni-56. On
 average, the CO model, shown in figure 4, reaches the DDT faster then
 the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
-range of estimated Ni-56 mass suggesting a greater range of burned mass
+range of estimated \Ni{56} mass suggesting a greater range of burned mass
 and expansion during the deflagration phase.

### 2018-12-26 paper/ms.tex
Bunch of changes and additions from a session sitting with Carlyn. Added new figures for the initial conditions of the simulations and the comparison between the estimated yields between the C/O and hybrid models. Also atted the poster document for future reference.

@@
 We briefly describe these in the subsection that follows. `
-Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
+Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
 for additional discussion.
@@
 
+Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}
+
 \section{Methods}
@@
 
-We used MESA, a 1-D stellar evolution code, to create the hybrid
-model. We made the hybrid model have the same central temperature
-and density as the classic model.
+A hybrid white dwarf model constructed with the one-dimensional stellar 
+evolution code MESA~\citep{mesa1,mesa2,mesa3,mesa3e} served as the 
+initial conditions for the simulations of supernova explosions presented
+in this work~\citep{brooksetal2017}.
+The hybrid model was constructed to have conditions as similar a possible
+to a ``classic" C/O model and the two shared the same central temperature
+and density.  Figure~\ref{fig:init_conds} shows the density and temperature
+profiles of the two initial one-dimensional models. 
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/initial_conds.png}
+\caption{\label{fig:init_conds}
+	We used MESA, a 1-D stellar evolution code, to create the hybrid model. We made the hybrid model have the same central temperature and density as the classic model. 
+ We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
+Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
+In order to see where we should ignite the flame, we plotted the temperature profile.
+It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core.
+(PUT IN TEMP PROFILE)
+}
+\end{figure}
+In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
+temperature was the highest at the center of the star and accordingly the simulations 
+began with central initions.
 
-We found that the most abundant isotopes in the model were C12, O16,
-Ne20. There were a few other isotopes that were added to form Ne22
-later. We saw that  ….
+\subsection{Created two-dimensional models from one-dimensional models}
 
-Plotting the density verses solar radii, we found that the densest part
-of the star is in the center slowly decreasing until it hits 0 at the
-outer edge of the star.
+The two-dimensional simulations were performed with a modified version
+of the FLASH code developed at the University of Chicago. CITE
+The initial one-dimensional MESA models were mapped to the two-dimensional 
+FLASH grid. MORE HERE.
 
-In order to see where we should ignite the flame, we plotted the
-temperature profile. It was found that the peak temperature is at the
-center of the star, therefore, it was obvious to ignite the flame in
-the core. (PUT IN TEMP PROFILE)
-
-\subsection{Created 2D model from 1-D model}
-
-We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
+An additional step in constructing the two-dimensional initial conditions
+was aggregating nuclides representing neutron-rich metals. 
+The most abundant isotopes in the model were C12, O16,
+Ne20 CHECK NE@) IS SYMMETRIC, which are symmetric (the number of neutrons 
+equals the number of protons). Similarly to~\citet{willcoxetal2016}, other 
+neutron-rich isotopes in
+the initial model were to form Ne22, which serves as a proxy for metallicty. 
 MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
@@
 
+The cumulative distribution of the \Ni{56} yield for the C/O and hybrid
+simulations is presented in \ref{fig:cumdist}. 
+The figure presents the estimated \Ni{56} yield as a function of the final burned 
+mass. The results show that the C/O models have a higher burned mass than the
+hybrid models for a given estimated mass of \Ni{56}. CHECK THIS.
+
 \begin{figure}
@@
 A plot of the estimated \Ni{56} yield as a function of the final, burned mass
-for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
-model is shown in blue. As it is shown, the CO model has a higher final mass
+for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
+models are shown in blue. As it is shown, the CO model has a higher final mass
 then the Hybrid model. 
@@
 \caption{\label{fig:nithybrid}
-Estimated \Ni{56} mass for Hybrid Model
+Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
+Shown are realizations 21-30. 
 }
@@
 \caption{\label{fig:nitco}
-Estimated \Ni{56} mass for CO Model
+Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
+Shown are realizations 21-30. 
 }
@@
 \caption{\label{fig:masshighdens}
-...
+This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
+The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc.
+The estimated Ni56 Yield is the final estimated mass of the model.
+Hybrid- Red
+CO- Blue
+For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
+The rectangular regions show one stanadard deviation from the average for both the C/O and hybrid 
+models (SEE DON'S PAPER)
+}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/compare.png}
+\caption{\label{fig:compare}
+The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
+First is that higher critical density leads to higher electron capture resulting in less Ni56 produced.
+Figure 4 shows that CO model has a stronger electron capture then the hybrid model.
+The second is that the central ignition leads to early burning at higher density.
+Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
+NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
+hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
+}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/compare_burned_mass.png}
+\caption{\label{fig:compare}
+SAME AS DON'S FIGURE 19.
+C/O blue hybrid red.
+Note that one of the C/O simulations presented did not complete.
+}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/compare_ratio.png}
+\caption{\label{fig:compare_ratio}
+Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
+SAME AS DON'S FIGURE 20.
 }

### 2018-12-28 paper/ms.tex
More work on Carlyn's paper. Going through the literature of forming hybrid WDs and the subsequent evolution of these.

@@
 In the area of stellar evolution, recent investigations revisiting 
-late-time evolution of ????-mass stars indicate the existance of
-``hybrid" white dwarfs that
+late-time evolution of roughly 8 \Msun stars indicate that under
+the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne 
+mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
+white dwarf are thought to form when mixing at the lower convective boundary quenches
+C burning in an asymptotic giant branch (AGB) star, leaving unburned C
+in the core. The situation is at best uncertain, however, and the 
+results depending on assumptions about convective
+overshoot that have been questioned \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.
+
+Assuming a hybrid WD forms, there is subsequent evolution that will occur.
+
+\citep{schwabgaraud2018}
 
@@
 Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
-Give a read to see!
+Give a read to see! Reading says no, but confirm.
 

### 2018-12-29 paper/ms.tex
Even more on Carlyn's paper.

@@
 
-Assuming a hybrid WD forms, there is subsequent evolution that will occur.
+Assuming a hybrid WD forms, there is subsequent evolution that will occur. There
+are two ways in which a hybrid WD can become a progenitor of a thermonuclear supernova.
+First, the hybrid could be part of a binary system in which the companion star becomes
+another white dwarf and the two merge. Recent population synthesis work supports
+this pathway by indicating a substantial contribution to the Ia population rate from 
+mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. The second way
+occurs if the hybrid WD is part of a binary with a main sequence or giant companion
+and gains enough mass to approach the Chandrasekhar mass and ignite C fusion (i.e.
+the single degenerate picture)~\citep{}.
 
-\citep{schwabgaraud2018}
+In either case, the hybrid WD will experience a period of cooling, which will
+make the core-mantle interface subject to convective 
+instability \citep{brooksetal2017,schwabgaraud2018}. In the case of the 
+hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
+heat the core and start C fusion, leading to a period of ``simmering" prior
+to the explosion \citep{who?}. The upshot is that is likely to be considerable
+mixing after the hybrid forms that may homegenize the compostion 
+\citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.
 
-Hybrid models 
-old 
-\citep{denissenkovetal2015}
-\citet{Wangetal2014} and \citet{Mengetal2014} presented binary
+Hybrid WDs have more mass than traditional C/O WDs, with some studies indicating the
+mass can approach 1.3 \Msun \citep{chenetal2014}. This increased mass
+minimizes one of the problems associated with the single-degenerate picture,
+the need to accrete enough mass for the WD to approach the Chandrasekhar
+mass~\citep{chenetal2014,denissenkovetal2015,kromeretal2015}.
+Accordingly, there has been considerable interest in viability of explosions from 
+these progenitors.
 
-see however~\cite{lecoanetetal16}
+From population synthesis, \citet{mengpods2014} found that these
+%meng received may 5 accepted may 16
+progenitors may substantially contribue to the population of SNeIa (1-8\%) and have
+relatively short delay times. They also suggested that these 
+may produce part of the Iax class of events. \citet{Wangetal2014} also with population
+synthesis studied the case
+%received august 28 accepted sept 26
+of a hybrid progenitor accreting from a nondegenerate He star and found
+birth rates indicating that up to 18\% of SNe Ia may follow from this chanel
+and very short delay times. \citet{Wangetal2014} also suggested that explosions 
+from hybrid progenitors may provide an explanation for type Iax events.
+\citet{mengpods2018}, from the common-envelope-wind model developed in 
+\citep{mengpods2014}, propose that both Ia-CSM and Iax events 
+are caused by the explosion of hybrid progenitors, with Ia-CSM occuring in systems with 
+a massive common envelope and Iax events occuring in systems where most of the common envelope
+has been lost.
 
-Recent results from stellar evolution
-The models we are exploding \citep{brooksetal2017}
+Other groups have simulated explosions from hybrid progenitors. 
+\citet{kromeretal2015} performed pure deflagration simulations from models 
+with a C core. They found that their models may explain some faint events 
+such as SN 2008ha~\citep{foleyetal2009}.
+\citet{bravoetal2016} performed one-dimensional simulations of explosions from 
+a variety of progenitor models assuming both pure deflagration and the DDT 
+explosion mechanism. 
+Some of their models are similar to those of \citep{denissenkovetal2015} and 
+they report that many models produce less synthesized
+\Ni{56}, indicating dimmer events. They also note that some of their
+models may explain Iax events.
+
+\citet{willcoxetal2016} simulated explosions from the progenitors of 
+\citep{denissenkovetal2015} and
+
+Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}
 
@@
 of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
-
-Here's the other Books paper \citep{brooksetal2016}. Do we need to mention it?
-Give a read to see! Reading says no, but confirm.
-
-Also, recent population synthesis work indicating a substantial contribution
-to the Ia population rate from mergers where one member is a 
-hybrid~\citep{yungelsonkuranov2017}.
-
-Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}
 

### 2019-01-08 paper/ms.tex
Even more on Carlyn's paper.
Added a revised figure from Carlyn

@@
 models may explain Iax events.
-
 \citet{willcoxetal2016} simulated explosions from the progenitors of 
-\citep{denissenkovetal2015} and
-
-Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}
+\citep{denissenkovetal2015} and found a trend of lower energy and lower
+\Ni{56} yield when compared to explosions from traditional C/O progenitors.
 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_burned_mass.png}
+\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
 \caption{\label{fig:compare}

### 2019-02-05 paper/ms.tex
Updated a couple of figures for Carlyn's paper.
figure touch-ups 1
Prettied up figures from Carlyn round 1.  A few more to do.

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
+\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
 \caption{\label{fig:cumdist}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
+\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
 \caption{\label{fig:masshighdens}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare.png}
+\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
 \caption{\label{fig:compare}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_ratio.png}
+\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
 \caption{\label{fig:compare_ratio}

### 2019-02-06 paper/ms.tex
Few quick fixes to Carlyn's manuscript. In looking at the new versions of the figures that she and Dean pushed, I realized that the order and text of a couple were swapped. Also fixed a few text things.

@@
 Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
-thought to occur when approximately 1.X \Msun\ of material composed principally 
-of C and O burns under degenerate conditions (SETTLE ON X). This class of supernovae is
+thought to occur when approximately 1.0 \Msun\ of material composed principally 
+of C and O burns under degenerate conditions. This class of supernovae is
 know to synthesize much of the Fe-group elements found in the galaxy and
@@
 period of accretion combined with either steady burning or a 
-series of nova explosions to allow the WD to gain
-$\sim 0.6$ CHECK THIS \Msun\ needed for it to approach the
+series of nova explosions to allow the WD to gain at least
+$\sim 0.4$ \Msun\ as needed for it to approach the
 limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
@@
 \includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
-\caption{\label{fig:compare}
+\caption{\label{fig:conversion}
 The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
-\caption{\label{fig:compare}
+\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
+\caption{\label{fig:compare_ratio}
+Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
 SAME AS DON'S FIGURE 19.
-C/O blue hybrid red.
-Note that one of the C/O simulations presented did not complete.
 }
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
-\caption{\label{fig:compare_ratio}
-Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
+\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
+\caption{\label{fig:compare_burned}
 SAME AS DON'S FIGURE 20.
+C/O blue hybrid red.
+Note that one of the C/O simulations presented did not complete.
 }

### 2019-02-07 paper/ms.tex
Work on intro in Carlyn's paper.

@@
 \begin{abstract}
-Recent studies of stellar evolution predict the existence of "hybrid" white 
-dwarfs, made of a C/O/Ne
-core within a O/Ne shell, and that these are viable progenitors for supernovae.
-More recent work found that the C/O core is mixed with the surrounding O/Ne
-while the white dwarf cools. Inspired by this scenario, we performed simulations of
-thermonuclear supernovae from these hybrid progenitors. The progenitor model 
+The existence of "hybrid" white dwarfs, made of a C/O
+core within a O/Ne shell is accepted, and studies indicate that these are 
+viable progenitors for thermonuclear (type Ia) supernovae.
+Recent work found that the C/O core is mixed with the surrounding O/Ne
+while the white dwarf cools. To further investigate the efficacy
+of these white dwarfs as progenitors of thermonuclear supernovae, we performed 
+simulations of thermonuclear supernovae from a new series of hybrid progenitors
+that include the effects of cooling. The progenitor white dwarf model
 was constructed with the one-dimensional stellar evolution code MESA and
@@
 followed by accretion until it reached conditions for the ignition of 
-carbon burning. The MESA model was then mapped to a two-dimensional initial 
+carbon burning. This MESA model was then mapped to a two-dimensional initial 
 condition and an explosion simulated with FLASH. For comparison, a similar
 simulation of an explosion was performed from a traditional C/O progenitor
-white dwarf. By comparing the yields of the explosions, we found....
-how explosions from these models differ from explosions from previous models
-without the mixing during the white dwarf cooling.
+white dwarf. By comparing the yields of the explosions, we found that as
+with earlier studies, these hybrid models are viable supernova progenitors.
+We contrast explosions from these models with explosions 
+from previous models {\color{red} without the mixing during the white dwarf cooling.}
 \end{abstract}
@@
 of C and O burns under degenerate conditions. This class of supernovae is
-know to synthesize much of the Fe-group elements found in the galaxy and
-the light curves of these events have a spectial property that allows
-their use as distance indicators for cosmological studies~\citep{phillips:absolute}
-resulting in the discovery of the acceleration of the expansion of
+know to synthesize much of the Fe-group elements found in the galaxy, and
+the light curves of these events have a special property that allows
+standardization of their light curves and thus use
+as distance indicators for cosmological studies~\citep{phillips:absolute}.
+This use resulted in the discovery of the acceleration of the expansion of
 the Universe and thus the inference of Dark 
 Energy~\citep{riess.filippenko.ea:observational,
-perlmutter.aldering.ea:measurements,leibundgut2001}. 
-This special property of the light curve is thought to follow
+perlmutter.aldering.ea:measurements,leibundgut2001}, and these events
+remain the premier distance indicators for cosmological studies {\color{red} REF?}. 
+The special property of the light curve is thought to follow
 from the fact that the source of luminosity, the radioactive decay
 of \Ni{56}, synthesized by the thermonuclear burning, is also the
-principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.
+principle source of opacity~\citep{Pinto2001The-type-Ia-sup}, giving
+the Phillips relation between the brightness of an event and the
+rate of decline of the B-band magnitude from maximum~\citep{phillips:absolute}.
 
@@
 the {\em white dwarf merger} or {\em double degenerate} scenario.
-We briefly describe these in the subsection that follows. `
+We briefly describe these in the subsection that follows.
 Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
@@
 nor a pure detonation (supersonic burning front) produce ejecta conisitent
-with observations \citep{arnett69,roepkeetal07}.
-Instead, the models that best reproduce the observed
-stratified ejecta are those in which the burning begins as a 
-subsonic deflagration, which allows the star to react and expand
-thus lowering the density, that is followed by a 
-detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
+with observations \citep{arnett69,roepkeetal07}.  Instead, the models 
+that best reproduce the observed stratified ejecta are those in which 
+the burning begins as a subsonic deflagration, which allows the star 
+to react and expand thus lowering the density, and is then followed by a 
+supersonic detonation that incinerates the 
+star~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
 The ``classic'' delayed detonation model is that of 
-Khokhlov \cite{Khokhlov1991Delayed-detonat,hoflich.khokhlov.ea:delayed,GameKhokOran05},
+\citet{Khokhlov1991Delayed-detonat} \citep[See also][]{hoflich.khokhlov.ea:delayed,GameKhokOran05},
 and many variations have been 
-explored \cite[and references therein]{hillebrandtetal2013,calderetal2013}.
+explored \citep[and references therein]{hillebrandtetal2013,calderetal2013}.
 The approach we employ for this study is a variation, the 
@@
 material when it reaches a threshold density.
-Which we describe this approach and our methodology  in detail below.
+We describe this approach and our methodology in detail below.
 
@@
 efficacy of this picture~\citep{livneglasner91, livnearnett95,HoefKhok96,
-hoeflichetal96, wigginsfalle97,wigginsetal98,garciasenzbravowoosley99} 
-but indicated that uncertainties 
-like the initial conditions were found to play a significant role.
-on the explosion outcome.
+hoeflichetal96, wigginsfalle97,wigginsetal98,garciasenzbravowoosley99}. 
+These studies indicated that uncertainties in the initial conditions, 
+however, were found to play a significant role on the explosion outcome.
 
-A particular problem was that most models 
-included a massive He layer, which leads to 
-the unobserved result intermediate and heavy elements synthesized in 
-the He detonation in the outer parts of the ejecta~\citep{HoefKhok96, 
-hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.
-\citet{bildstenetal2007}, however, found that fairly thin He layers
-could flash on sub-Chandrasekhar
+A particular problem was that most models included a massive He layer on 
+the white dwarf. Such a configuration leads to the unobserved result 
+intermediate and heavy elements synthesized in the He detonation appear in 
+the outer parts of the ejecta, which does not match obesrvation~\citep{HoefKhok96,
+hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007}, 
+however, found that fairly thin He layers could flash on sub-Chandrasekhar
 mass white dwarfs, partially resolving the issue and encouraging
@@
 An early concern about this model came from studies finding that 
-the white dwarf will ignite at the edge and the coalesced object, 
-and a flame will burn inward, converting the C-O white dwarf into 
-an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004}, with
-further accretion leading to the collapse of the white dwarf
+the as the stars merge, the more massive white dwarf can ignite near
+its edge and a flame will burn inward, converting the C-O white dwarf into 
+an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004}.  Further accretion 
+leads to the collapse of the white dwarf
 into a neutron star, a scenario termed ``accretion-induced collapse''
@@
 Subsequent work allayed this concern~\citep{yoonetal2007,lorenaguilaretal2009,
-Shenetal12, pakmoretal2012b} and motivated by the need to expain briht events
+Shenetal12, pakmoretal2012b} and motivated by the need to expain bright events
 and the estimated population WD pairs, active research continues. Contemporary
-research focuses on variations on the merger idea, including 
-inspiraling pairs, collisions, violent mergers,
-and the ``core-degenerate'' model in which the merger takes place in
-a common envelope \citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12,katzetal2016}.
+research focuses on variations on the merger idea, including inspiraling pairs, 
+collisions, violent mergers, and the ``core-degenerate'' model in which the merger 
+takes place in a common envelope \citep{raskinetal2009,pakmoretal2011,kashi:2011,
+pakmoretal2012a,Shenetal12,katzetal2016}.
 
@@
 
-Our models are within the DDT explosion paradigm \cite{1986SvAL,
+Our single-degenerate models are within the DDT explosion paradigm \cite{1986SvAL,
 Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}. 
-In this scenario, the accretion of mass on the white dwarf compresses and 
+In this case, the accretion of mass on the white dwarf compresses and 
 heats the core, igniting carbon fusion and driving a period of convection
@@
 at the deflagration front, particuarly the Rayleigh-Taylor 
-instability~\cite{taylor+50,chandra+81}, is an accepted part of the process.
+instability~\citep{taylor+50,chandra+81}, is an accepted part of the process.
 Many ideas have been proposed, including the deflagration front
 entering a regime of distributed burning and the net
-rate becoming supersonic \cite{NiemWoos97}, the unstable
-flame reaching a certian fractal dimension~\cite{woosley90},
+rate becoming supersonic \citep{NiemWoos97}, the unstable
+flame reaching a certian fractal dimension~\citep{woosley90},
 and the Zel'dovich mechanism in which condtions are right for
 a pocket of fuel to 
-detonate~\cite{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
+detonate~\citep{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
+We note that regardless of
+the mechanism, the amount of expansion of the star prior to the bulk of burning
+is critical to the composition of material synthesized in the explosion. Also,
+early burning during the deflagtation phase is at high enough densites that
+the effects of electron capture are significant and similarly influence the 
+compositon the material synthesised in the explosion~\citep{hoeflichetal2004,
+hoeflich2006,fesenetal2007,diamondetal2018}.
 Our simulations assume that the transition occurs when the top of a 
 rising, Rayleigh-Taylor unstable plume reaches a characteristic low
-density \cite{townsley.calder.ea:flame}.
+density~\citep{townsley.calder.ea:flame}. 
+Variations on the choice of this density allowed earlier studies to explore
+the effects of physics influencing the transition 
+density~\citep{jacketal2010,Krueger2010On-Variations-o,kruegetal12}.
 
@@
 amount of included physics and full three-dimensional simulations
-albeit with less included physics~\cite{caldertownsley2018}.
+albeit with less included physics~\citep{caldertownsley2018}.
 In the area of stellar evolution, recent investigations revisiting 
@@
 
-Assuming a hybrid WD forms, there is subsequent evolution that will occur. There
-are two ways in which a hybrid WD can become a progenitor of a thermonuclear supernova.
+A hybrid WD can become a progenitor of a thermonuclear supernova via two 
+of the progenitor system. 
 First, the hybrid could be part of a binary system in which the companion star becomes
@@
 this pathway by indicating a substantial contribution to the Ia population rate from 
-mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. The second way
-occurs if the hybrid WD is part of a binary with a main sequence or giant companion
-and gains enough mass to approach the Chandrasekhar mass and ignite C fusion (i.e.
-the single degenerate picture)~\citep{}.
+mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. Second, if the hybrid 
+WD is part of a binary with a main sequence or giant companion, it can gain mass and 
+approach the Chandrasekhar mass, i.e.\  the single degenerate picture~\citep{willcoxetal2016}. 
+{\color{red} COULD NOT FIND ANY EVIDENCE OF HYBRIDS IN THE SUBCHANDRA PATH. SAY 
+SOMETHING?}
 
-In either case, the hybrid WD will experience a period of cooling, which will
+In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, which will
 make the core-mantle interface subject to convective 
@@
 heat the core and start C fusion, leading to a period of ``simmering" prior
-to the explosion \citep{who?}. The upshot is that is likely to be considerable
+to the explosion \citep{PiroBild08}. The upshot is that is likely to be considerable
 mixing after the hybrid forms that may homegenize the compostion 
@@
 
-If we refer to the work by name, it should appear ``The hybrid models
-of~\citet{brooksetal2017}." Or, we can just cite it~\citep{brooksetal2017}.
-
 \section{Methods}
 
+The methodology of our study follows the approach of \citet{willcoxetal2016}. 
+We per
 Summarize what we do a la:

### 2019-02-07 paper/ms.tex
Added a description of the flame model to Carlyn's paper

@@
 
-\section{Methods}
+\section{Methodology}
 
 The methodology of our study follows the approach of \citet{willcoxetal2016}. 
-We per
-Summarize what we do a la:
-In our simulations, we initialize a detonation once the 
-deflagration front reaches a
-characteristic DDT fuel density, which controls the degree of
-expansion the star undergoes during the deflagration stage.
+We performed a suite of two-dimensional simulations of supernova explosions
+from hybrid progenitors and compared the results to a suite of simulations
+of explosions from traditional C/O progenitor models performed with the
+same simulation code and from similar initial conditions. The simulations assumed
+the deflagration to detonation transition explosion paradigm, and the
+transition densities were the same in both suites. We briefly our methodoly
+here, and refer to the reader to previous work for additional details.
+In particular, we use the same simulation instrument, a modified version
+of the Flash Code, as \citet{willcoxetal2016} and we refer the reader there 
+for a description of modifications for C-O-Ne burning and verification tests
+of the burning module.
 
-The comparison study of tradition C/O progenitor WDs used the same initial
-conditions for the realizations within the suite. The traditional models
-are simulated with the same code and the same set of perturbations on the
-initial match head (realization). The only difference is the different
-nuclear burning to include the other Ne and the initial profile of the
-1-d model.
+\subsection{Simulation Instrument}
 
-The comparison study of tradition C/O progentor WDs used the same
-initial conditions for the realizations within the suite. Make the
-point that the traditional models are simalted with the same code
-and the same set if perturbations on the initial match head (that is
-what we mean by a realization). The only difference is the different
-nuclear buring to include the other Ne and the initial profile of
-the 1-d model.
+The simulations of supernova explosions presented here were performed
+with a customized version of the Flash code, originally developed
+at the University of Chicago.
+Flash is a parallel, adaptive mesh, multi-physics simulation code
+developed first for nuclear astrophysics applications and subsequently
+for high-energy-density applications~\cite{Fryxetal00,calder.curtis.ea:high-performance,
+calder.fryxell.ea:on,flash_pragmatic,flash_evolution}. 
+Flash has been applied to a variety of astropysical problems by a host
+of researchers, and the version we apply differs from other versions
+principally in the modules describing thermonuclear burning. 
+specifically routines to describe
+thermonuclear burning during both the deflagration and detonation
+phases, as well as routines to describe the evolution of
+the dynamic ash.
 
-For much of the methodology to be described below, just say a few
-words about what was done and cite \citet{willcoxetal2016}.
+The need for a model flame in simulating thermonuclear supernovae
+follows from the scales of the problem. At high densities, the
+width of a laminar nuclear flame is $< 1\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$
+while the radius of the white dwarf 
+$\sim 10^9\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$.
+Even with adaptive mesh refinement, whole-star simulations cannot simultaneousely
+directly simulate the nuclear flame, thus requiring use of a model to
+describe the burning on unresovable scales. For the deflagration phase,
+our burning model propagates an artificially
+broadened flame with an advection-diffusion-reaction (ADR)
+scheme~\cite{Khok95,VladWeirRyzh06} via evolution of
+a reaction progress variable to describe the consumption of C
+and additional variables to describe the evolution of intermediate-mass
+elements into the stastical quasi-equilibruim of the 
+Si-group~\cite{ifk1981,khok1981,khok1983} and then into iron-group elements
+(IGEs) in full nuclear statistical equilibrium (NSE).
+
+The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
+unburned fuel and $\phi=1$ for burned ash. $\phi$ is evolved
+via an advection-diffusion-reaction equation,
+\begin{equation}
+  \label{eq:ard}
+  \partial_t \pv + \vec{u}\cdot\nabla \pv = \kappa \nabla^2 \pv +
+\frac{1}{\tau} R\left(\phi\right) ,
+\end{equation}
+where $\vec{u}$ is the velocity of the fluid, $\kappa$ is the
+diffusion coefficient, $\tau$ is the reaction timescale, and $R(\phi)$ is
+a non-dimensional function describing the reaction. The parameters
+$\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
+front at a prescribed speed.  Our model uses the ``sharpened KPP
+ described by~\cite{VladWeirRyzh06}, 
+with $R\propto(\phi-\epsilon)(1-\phi+\epsilon)$, where
+$\epsilon \simeq 10^{-3}$.  This scheme has been shown to be
+acoustically quiet, stable, and to give a unique flame speed
+\cite{townsley.calder.ea:flame}. The input flame speeds come from
+tabulated results obtained by direct numerical simulations of
+thermonuclear burning~\cite{timmes92,Chamulak2007The-Laminar-Fla},
+these are boosted to account for speed-up of burning due to
+unresolved buoyancy and background
+turbulence~\cite{Khok95,gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
+
+The ADR scheme describes the consumption of C and the subsequent stages
+are described by separate progress variables and
+separate relaxation times derived from full nuclear network calculations
+\cite{Caldetal07,townetal2016}. In both the quasi-equilibrium and full equilibrium, 
+the creation of light elements by photodisintegration balances the creation of heavy 
+elements by fusion, maintaining the equilibrium. The relative balance depends on
+thermodynamic conditions, e.g.\ density and temperature, and hydrodynamic motion
+during the explosion changes the thermodynamic conditions and thus the
+balance. Electron capture also influences the evolution by shifting the binding 
+energy of the material and thereby changing the temperature due to released energy, 
+by changing the Fermi energy and thus the pressure, and by emitting neutrinos that 
+escape and remove energy. Electron captures also neutronize the material, which 
+produces more neutron rich iron-group material at the expense of \Ni. Like the 
+input flame speed, the burning model includes tabulated rates for these effects 
+from detailed NSE calculations ~\cite{SeitTownetal09}. Accordingly, the burning
+model is able to describe dynamic evolution of the ash in addition to the 
+stages of C-O-Ne burning.
+
+The burning model also describes the detonation phase with progress variables.  
+In this case, the model evolves thermally-activated burning with the actual
+temperature-dependent rate for C consumption, which allow a propagating shock to
+trigger burning, i.e.\ to propagate a detonation front. The propagating detonation 
+is able to describe the same stages of C burning as the deflagration case, including 
+the relaxation into NSE~\cite[and references therein]{townetal2016}. Finally,
+we again note that the burning model was adapted for the case of burning in
+hybrid white dwarfs. Direct numerical simulations of burning that guided 
+the modifications, details of the modifications to the burning model, and
+verification tests may be found in \citet{willcoxetal2016}.
 
@@
 
-This work was supported in part by the Department of Energy under
-grant DE-FG02-87ER40317. The software used in this work was in part
-developed by the DOE-supported ASC/Alliances Center for Astrophysical
-Thermonuclear Flashes at the University of Chicago. Results in this
+This work was supported in part by the U.S.\ Department of Energy under
+grant DE-FG02-87ER40317 and in part by the U.S.\ National Science Foundation
+via a supplement to grant AST-1211563. 
+Support also came from the Data + Computing = Discovery summer program at
+the Institute for Advanced Computational Science at Stony Brook University.
+The software used in this work was developed in part by the DOE-supported 
+ASC/Alliances Center for Astrophysical Thermonuclear Flashes at the 
+University of Chicago. 
+The source code used for
+these studies is available as a package compatible with the
+current Flash code from \url{http://astronomy.ua.edu/townsley/code.}
+Results in this
 paper were obtained using the high-performance computing system at the
 Institute for Advanced Computational Science at Stony Brook
-University.  other grants...
+University.
 

### 2019-02-09 paper/ms.tex
Even more on Carlyn's paper.

@@
 of researchers, and the version we apply differs from other versions
-principally in the modules describing thermonuclear burning. 
-specifically routines to describe
-thermonuclear burning during both the deflagration and detonation
-phases, as well as routines to describe the evolution of
-the dynamic ash.
+principally in the modules describing thermonuclear burning via a 
+flame capturing model.
 
-The need for a model flame in simulating thermonuclear supernovae
-follows from the scales of the problem. At high densities, the
-width of a laminar nuclear flame is $< 1\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$
-while the radius of the white dwarf 
-$\sim 10^9\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$.
-Even with adaptive mesh refinement, whole-star simulations cannot simultaneousely
-directly simulate the nuclear flame, thus requiring use of a model to
-describe the burning on unresovable scales. For the deflagration phase,
-our burning model propagates an artificially
-broadened flame with an advection-diffusion-reaction (ADR)
+The need for a model flame in simulating thermonuclear supernovae follows 
+from the scales of the problem. At high densities, the width of a laminar 
+nuclear flame is $< 1\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$ while the 
+radius of the white dwarf $\sim 10^9\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$.
+Even with adaptive mesh refinement, whole-star simulations cannot 
+simultaneousely resolve the nuclear flame, so simulations require a model to 
+describe the burning on unresovable scales.  The model we apply is a flame 
+capturing scheme and thermally-activated burning module to describe
+thermonuclear burning during both the deflagration and detonation phases, 
+as well as routines to describe the evolution of the dynamic ash. 
+This description of the burning was developed during the course of research in 
+thermonuclear supernovae and has been presented in a series of 
+papers \citep[See][and references therein]{chandlery}. For completeness, 
+we briefly review the flame capturing scheme here.
+
+For the deflagration phase, the flame capturing scheme propagates an 
+artificially broadened flame with an advection-diffusion-reaction (ADR)
 scheme~\cite{Khok95,VladWeirRyzh06} via evolution of
@@
 thermonuclear burning~\cite{timmes92,Chamulak2007The-Laminar-Fla},
-these are boosted to account for speed-up of burning due to
-unresolved buoyancy and background
-turbulence~\cite{Khok95,gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
+these are boosted to account for speed-up of burning due to unresolved 
+buoyancy and background turbulence~\cite{Khok95,
+gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
 

### 2019-02-09 paper/ms.tex
Even more on Carlyn's paper.

@@
 Recent work found that the C/O core is mixed with the surrounding O/Ne
-while the white dwarf cools. To further investigate the efficacy
-of these white dwarfs as progenitors of thermonuclear supernovae, we performed 
-simulations of thermonuclear supernovae from a new series of hybrid progenitors
-that include the effects of cooling. The progenitor white dwarf model
+as the white dwarf cools prior to accretion, which results in lower central 
+C fractions in the massive progenitor than previously assumed. To further 
+investigate the efficacy of hybrid white dwarfs as progenitors of 
+thermonuclear supernovae, we performed simulations of thermonuclear 
+supernovae from a new series of hybrid progenitors that include the 
+effects of cooling. The progenitor white dwarf model
 was constructed with the one-dimensional stellar evolution code MESA and
@@
 We contrast explosions from these models with explosions 
-from previous models {\color{red} without the mixing during the white dwarf cooling.}
+from previous hybrid models 
+{\color{red} without the mixing during the white dwarf cooling}
+and traditional C/O progenitors.
 \end{abstract}
@@
 
-\subsection{The Deflagraiton to Detonation Transition Mechanism Within the Single Degenerate Scenario}
+\subsection{The Deflagraiton to Detonation Transition Mechanism Within 
+the Single Degenerate Scenario}
 
@@
 The simulations of supernova explosions presented here were performed
-with a customized version of the Flash code, originally developed
+with a customized version of the \FLASH code, originally developed
 at the University of Chicago.
@@
 
-\subsection{Initial Conditions}
+\subsection{One-dimensional Hybrid Model}
 
-A hybrid white dwarf model constructed with the one-dimensional stellar 
-evolution code MESA~\citep{mesa1,mesa2,mesa3,mesa3e} served as the 
-initial conditions for the simulations of supernova explosions presented
-in this work~\citep{brooksetal2017}.
+The hybrid white dwarf model that served as the initial conditions 
+for the simulations of supernova explosions presented in this work
+was constructed with the one-dimensional stellar evolution code 
+MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model 
+included thermohalene mixing during the cooling phase and thus
+had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
 The hybrid model was constructed to have conditions as similar a possible
@@
 \caption{\label{fig:init_conds}
-	We used MESA, a 1-D stellar evolution code, to create the hybrid model. We made the hybrid model have the same central temperature and density as the classic model. 
+Temperature, density, and  composition profiles of the one-dimensional hybrid 
+progenitor WD. The central temperature and density were the same as
+the tradtional C/O progenitor model. 
  We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
@@
 
-\subsection{Created two-dimensional models from one-dimensional models}
+\subsection{Ttwo-dimensional Models from One-dimensional Models}
 
-The two-dimensional simulations were performed with a modified version
-of the FLASH code developed at the University of Chicago. CITE
-The initial one-dimensional MESA models were mapped to the two-dimensional 
-FLASH grid. MORE HERE.
+The initial progenitor models for the two-dimensional simulations were
+created from the one-dimensional \MESA models by mapping the one-dimensional
+models onto the two-dimensional domain while 
+preserving hydrostatic equilibrium.
+As described above, the flame capturing scheme with progress
+variables describing the evolution as the material burns. The \MESA
+models, however, relied on a detailed reaction network that included
+many species. Accordingly, the process of creating the two-dimensional
+models for \FLASH required aggregating some of the species abundances.
+As with much of this study, we applied the 
+techniques of ~\citet{willcoxetal2016}.
+
+The process of mapping the \MESA models began by converting 
+the \MESA\ model to a uniform grid of $4$~km resolution. \MESA 
+quantities in zones with spacing less than $4$~km 
+were mass-weighted averaged and a quadratic interpolation
+was used to calculate quantities for the case of \MESA zones having
+a spacing greater than $4$~km. At this point, 
+abundances of nuclides from the \MESA models were aggregated
+into abundances of
+
+representing neutron-rich metals were aggregated into
+
+a variable representing
 

### 2019-02-09 paper/ms.tex
Even more on Carlyn's paper. Getting thorough the methodology

@@
 the tradtional C/O progenitor model. 
- We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
-Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
-In order to see where we should ignite the flame, we plotted the temperature profile.
-It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core.
-(PUT IN TEMP PROFILE)
+The peak temperature of the hybrid model is at the center of the star, 
+so both the hybrid and traditional models could share the same 
+	central ignition initial conditions.
 }
@@
 temperature was the highest at the center of the star and accordingly the simulations 
-began with central initions.
+began with central ignitions.
 
@@
 The initial progenitor models for the two-dimensional simulations were
-created from the one-dimensional \MESA models by mapping the one-dimensional
+created from the one-dimensional \MESA\ models by mapping the one-dimensional
 models onto the two-dimensional domain while 
@@
 As described above, the flame capturing scheme with progress
-variables describing the evolution as the material burns. The \MESA
+variables describing the evolution as the material burns. The \MESA\
 models, however, relied on a detailed reaction network that included
 many species. Accordingly, the process of creating the two-dimensional
-models for \FLASH required aggregating some of the species abundances.
+models for \FLASH\ required aggregating some of the species abundances.
 As with much of this study, we applied the 
@@
 
-The process of mapping the \MESA models began by converting 
-the \MESA\ model to a uniform grid of $4$~km resolution. \MESA 
+The process of mapping the \MESA\ models began by converting 
+the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\ 
 quantities in zones with spacing less than $4$~km 
 were mass-weighted averaged and a quadratic interpolation
-was used to calculate quantities for the case of \MESA zones having
+was used to calculate quantities for the case of \MESA\ zones having
 a spacing greater than $4$~km. At this point, 
-abundances of nuclides from the \MESA models were aggregated
-into abundances of
+abundances of nuclides from the \MESA\ models were aggregated
+into the abundances tracked by the flame capturing scheme in
+\FLASH.
+The most abundant isotopes in the model were \C{12}, \Ox{16},
+and \Ne{20}, which are symmetric (the number of neutrons 
+equals the number of protons). Similarly to~\citet{willcoxetal2016}, 
+other neutron-rich isotopes in the initial model were combined into 
+\Ne{22}, which serves as a proxy for metallicty. The aggregation
+account for the $Y_e$ of the full set of nuclides, \Ne{20} 
+and \Ox{16} were constrained to be in the same ratio $R$ in both 
+sets of abundances.
 
-representing neutron-rich metals were aggregated into
-
-a variable representing
-
-An additional step in constructing the two-dimensional initial conditions
-was aggregating nuclides representing neutron-rich metals. 
-The most abundant isotopes in the model were C12, O16,
-Ne20 CHECK NE@) IS SYMMETRIC, which are symmetric (the number of neutrons 
-equals the number of protons). Similarly to~\citet{willcoxetal2016}, other 
-neutron-rich isotopes in
-the initial model were to form Ne22, which serves as a proxy for metallicty. 
 MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear

### 2019-02-10 paper/ms.tex
Picked off another subsection in the methodology section of Carlyn's paper.

@@
 account for the $Y_e$ of the full set of nuclides, \Ne{20} 
-and \Ox{16} were constrained to be in the same ratio $R$ in both 
+and \Ox{16} were constrained to be in the same ratio in both 
 sets of abundances.
 
-MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
-matter. This means that the ratio of neutrons to protons in the nuclei
-must be the same ratio as in the mesa profile. This is because the amount
-of extra neutrons around is important when burning the star because that
-determines how much neutron rich isotopes the burning produces.
+The original \MESA\ model was in equilibrium, but to ensure
+the uniformly gridded model was in hydrostatic equilibrium we 
+constructed the appropriate pressure profile. This was done by
+integrating for the pressure in each zone from the central point up, 
+accounting for the local acceleration of gravity, temperature,
+composition, and the mass below and enclosed by the zone. As
+with \citet{willcoxetal2016} we used
+EOS routine from 
+\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The 
+Helmholtz EOS table used in \CASTRO\ is in the public BoxLib 
+Microphysics repository at
+  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit 
+  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As 
+ with the models in \citet{willcoxetal2016},this procedure produced 
+ a structure that was stable in \FLASH, with fluctuations in central
+density less than $3\%$, for at least $5$ seconds with no energy
+deposition.
 

### 2019-02-11 paper/ms.tex
Finished the methodology section of Carlyn's paper. On to discussion of the results.

@@
 deflagration-to-detonation transition (DDT), in which the transition
-occurs at the top of a rising Rayleigh-Taylor unstable plume of hot, burned 
+occurs at the top of a rising Rayleigh-Taylor~\citep{taylor+50,chandra+81} 
+unstable plume of hot, burned 
 material when it reaches a threshold density.
@@
 at the deflagration front, particuarly the Rayleigh-Taylor 
-instability~\citep{taylor+50,chandra+81}, is an accepted part of the process.
+instability, is an accepted part of the process.
 Many ideas have been proposed, including the deflagration front
@@
 %meng received may 5 accepted may 16
-progenitors may substantially contribue to the population of SNeIa (1-8\%) and have
+progenitors may substantially contribue to the population of \SNeIa (1-8\%) and have
 relatively short delay times. They also suggested that these 
@@
 thermonuclear burning~\cite{timmes92,Chamulak2007The-Laminar-Fla},
+and 
 these are boosted to account for speed-up of burning due to unresolved 
@@
 gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
+
+The two-dimensional models in this study do not utilize a subgrid-scale
+model for the turbulence-flame 
+interaction~\citep[See][for examples]{Schmetal06a,Schmetal06b,jacketal2014},
+The models only apply in three-dimensional
+simulations beacuse two-dimensional hydrodynamics cannot
+correctly describe turbulence. The simulations we present
+use the mimimal enhancement based on the Rayleigh-Taylor
+strength introduced by~\citet{townsley.calder.ea:flame}. The
+assumption here is that the burning self-regulate on resolved 
+scales so that results are insensitive to the detailed treatment 
+of the interaction with turbulence, and previous experience
+indicates this assumption is reasonable for comparisons
+like the one presented in this work~\citet{townsley.calder.ea:flame,
+willcoxetal2016}.
 
@@
 
-\subsection{Ttwo-dimensional Models from One-dimensional Models}
+\subsection{Two-dimensional Initial Conditions From One-dimensional Models}
 
@@
 As with much of this study, we applied the 
-techniques of ~\citet{willcoxetal2016}.
+techniques of~\citet{willcoxetal2016}.
 
@@
 and \Ox{16} were constrained to be in the same ratio in both 
-sets of abundances.
+sets of abundances. \figref{fig:init_conds} shows the initial
+profile of the one-dimensional models.
 
@@
 
-The fuel starts off cold. The elections in the plasma conduct heat and the
-fuel begins to heat up. Once the fuel reaches a certain temperature, the
-reaction starts. The fuel abundance begins to decline because it is consuming
-fuel. Energy is produced which makes the fuel hot. Eventually, all that’s
-left is ash. As surface area grows, conducted energy increases and density
-decreases. At low densities Rayleigh-Taylor instability causes the flame to
-get more tangled and unstable. Eventually, the star will get a large enough
-surface area in this volume that the net burning effect is supersonic.
-Therefore, the transition from deflagration to detonation is made.
+The simulations performed for this study consisted to a suite of
+{\color{red} 35 CHECK THIS! 40?} two-dimensional simulations of 
+thermonuclear supernova
+explosions from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These 
+were compared to a suite of supernova simulations from traditional
+C-O progenitors. In both suites, the simulation
+begins with a progenitor model mapped to the two-dimensional 
+\FLASH\ grid. The burning is initiated with a ``matchhead,'' a region 
+in the white dwarf's center that is fully burned to nuclear statistical
+equilibrium (NSE). 
+This initially burned regeion ignites a deflagration, a subsonic
+flame, and because the mathhead was perturbed it is unstable to
+the Rayleigh-Taylor instability with the result that buoyant plumes 
+rise. The star is partially consumed during this deflagration phase,
+and the star responds by expanding.
+When a plume reaches a specified density,
+a detonation is initiated, and the simulation continues until 
+the expanding star reaches low densities at which point burning
+effectively ends. The paragraphs in this section provide details
+of the implementation of this method.
 
-Using the FLASH code from University of Chicago, simulations of
-explosions were preformed. For each simulation we varied the central
-ignition seed.
+{\color{red} ARE THE BELOW NUMBERS CORRECT?}
+The C-O and C-O-Ne models have the same central density
+and temperature $7 \times 10^8$~K, respectively.
+The C-O model had core composition of (\C{12} = 0.4, 
+\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition 
+of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
+The C-O-Ne model had core composition of (\C{12} = 0.X, 
+\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition 
+of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
+\figref{fig:co_vs_cone_temp} show the density and temperature 
+profiles of the C-O and C-O-Ne hybrid WD.
 
-----updated text-----
+The simulations were performed in two-dimensional $\mathrm{z-r}$
+cylindrical coordinates, extending radially from 0 to
+$65,536$~\km\ and along the axis of symmetry from $-65,536$~\km\ to
+$65,536$~\km. The maximimum refinement level of the adaptive mesh 
+corresponded to $4$~\km\ resolution, which previous study has shown is
+is a good balance between efficiency and 
+accuracy~\citep{townsley.calder.ea:flame,townetal2009}.
+This resolution and geometry was used in previous studies
+allowing direct comparison to previous results~\citep{kruegetal12}.
 
-DDT Process:
-The fuel starts off cold. The elections in the plasma conduct heat
-and the fuel begins to heat up. Once the fuel reaches a certain
-temperature, the reaction starts. The fuel abundance begins to
-decline because it is consuming fuel. Energy is produced which
-makes the fuel hot. Eventually, all that’s left is ash. As
-surface area grows, conducted energy increases and density
-decreases. At low densities Rayleigh-Taylor instability causes
-the flame to get more tangled and unstable. Eventually, the
-star will get a large enough surface area in this volume that
-the net burning effect is supersonic. Therefore, the transition
-from deflagration to detonation is made.
+The ignition of the deflagration via a matchhead followed the 
+initialization described in~\citet{kruegetal12}, which
+followed the method of~\citet{townetal2009}.
+In both the hybrid and traditional cases, the matchhead had a 
+nominal radius of $150$~km before 
+a different randomly-seeded perturbation was applied to the 
+matchhead for each of the 35 simulations in both suites. {\color{red}
+IS THIS RIGHT- BOTH USED THE SAME REALIZATIONS?}
+The perturbation to the sphere's surface is a set of
+spherical harmonic functions with randomly chosen amplitudes, and
+each set of perturbations is referred to as a ``realization." 
+These perturbations have been shown to reproduce 
+the scatter in \Ni{56} 
+yield from \SNeIa\ \citet{townetal2009}.
 
-A deflagration alone will not produce an event of normal
-brightness and expansion velocity. Instead, the initial
-deflagration must transition to a detonation after the star has
-expanded some in order to produce abundances and a stratified
-ejecta in keeping with observations. The physics of this
-“deflagration-to- detonation transition” (DDT) are not
-completely understood, but there has been considerable study
-based on mechanisms involving flame fronts in highly turbulent
-conditions. These models generally reproduce the observations
-under certain assumptions about the ignition, but research has
-shown that the results are very sensitive to the details of the
-ignition. In our simulations, we initialize a detonation once
-the deflagration front reaches a characteristic DDT fuel density,
-which controls the degree of expansion the star undergoes during
-the deflagration stage.
+The transition from deflagration to detonation again follows
+the previous studies, which assumed the transition location
+is parameterized by the fuel density $\rho_{\mathrm{DDT}}$.
+When a rising
+plume reaches the threshold density, in this case
+$\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$, 
+a $12$~\km\ a region of fuel, (\C{12} and \Ne{20}, if present) is
+fully burned $32$~\km\ radially outwards from the flame. This
+instantaneous burning in the region of this size provides conditions
+to generate the shock and support the detonation at the chosen
+threshold density.  Multiple DDT points may arise, but they are
+constrained to be at least $200$~\km\ apart. The choice of DDT
+in the suite has been shown to be high enough to ensure 
+the robust ignition of a detonation shock.
 
-The comparison study of tradition C/O progenitor WDs used the same initial
-conditions for the realizations within the suite. The traditional models
-are simulated with the same code and the same set of perturbations on the
-initial match head (realization). The only difference is the different
-nuclear burning to include the other Ne and the initial profile of the
-1-d model.
-
-----above updated text-----
+Once the detonation starts, the remaining fuel at densities
+high enough for the detonation to propagate is quickly consumed.
+The simulations were run to 4.0 s, at which time burning 
+has effectively ceased.
 

### 2019-02-11 paper/ms.tex
More on Carlyn's paper

@@
 \begin{abstract}
-The existence of "hybrid" white dwarfs, made of a C/O
+The existence of ``hybrid" white dwarfs, made of a C/O
 core within a O/Ne shell is accepted, and studies indicate that these are 
@@
 and remains the subject of active research. At present there are three
-widely-accpeted scenarios: the {\em single degenerate} scenario,
+widely-accepted scenarios: the {\em single degenerate} scenario,
 the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
@@
 the Chandrasekhar limit, conditions in the compressed core are right
-to ignite the thermonuclear buring that will incinerate the star.
+to ignite the thermonuclear burning that will incinerate the star.
 
@@
 been studied with the result being that the outcome is sensitive to
-the ignition conditions and the nature of the thermonuclear buring.
+the ignition conditions and the nature of the thermonuclear burning.
 Studies indicate that neither a pure deflagration (subsonic flame front)
-nor a pure detonation (supersonic burning front) produce ejecta conisitent
+nor a pure detonation (supersonic burning front) produce ejecta consistent
 with observations \citep{arnett69,roepkeetal07}.  Instead, the models 
@@
 
-The double detionation picture is a variation of the single degenerate picture.
+The double detonation picture is a variation of the single degenerate picture.
 In this case, a white dwarf accretes material from a companion, but rather
@@
 intermediate and heavy elements synthesized in the He detonation appear in 
-the outer parts of the ejecta, which does not match obesrvation~\citep{HoefKhok96,
+the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
 hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007}, 
@@
 
-The white dwarf merger progentor picture has two white dwarfs coming 
+The white dwarf merger progenitor picture has two white dwarfs coming 
 together and subsequently exploding~\citep{tutukovyungelson76,tutukovyungelson79,
@@
 Subsequent work allayed this concern~\citep{yoonetal2007,lorenaguilaretal2009,
-Shenetal12, pakmoretal2012b} and motivated by the need to expain bright events
+Shenetal12, pakmoretal2012b} and motivated by the need to explain bright events
 and the estimated population WD pairs, active research continues. Contemporary
@@
 
-\subsection{The Deflagraiton to Detonation Transition Mechanism Within 
+\subsection{The Deflagration to Detonation Transition Mechanism Within 
 the Single Degenerate Scenario}
@@
 of the WD, it is subject to the Rayleigh-Taylor instability that generates
-turbulence and boosts buring.  
+turbulence and boosts burning.  
 Burning proceeds as a deflagration for about one second, and then 
@@
 
-The mechanism by which the deflagration transistions to a detonation
-is imcompletely understood, but the development of fluid instabilities
-at the deflagration front, particuarly the Rayleigh-Taylor 
+The mechanism by which the deflagration transitions to a detonation
+is incompletely understood, but the development of fluid instabilities
+at the deflagration front, particularly the Rayleigh-Taylor 
 instability, is an accepted part of the process.
@@
 rate becoming supersonic \citep{NiemWoos97}, the unstable
-flame reaching a certian fractal dimension~\citep{woosley90},
-and the Zel'dovich mechanism in which condtions are right for
+flame reaching a certain fractal dimension~\citep{woosley90},
+and the Zel'dovich mechanism in which conditions are right for
 a pocket of fuel to 
@@
 is critical to the composition of material synthesized in the explosion. Also,
-early burning during the deflagtation phase is at high enough densites that
+early burning during the deflagration phase is at high enough densities that
 the effects of electron capture are significant and similarly influence the 
-compositon the material synthesised in the explosion~\citep{hoeflichetal2004,
+composition the material synthesized in the explosion~\citep{hoeflichetal2004,
 hoeflich2006,fesenetal2007,diamondetal2018}.
@@
 to the explosion \citep{PiroBild08}. The upshot is that is likely to be considerable
-mixing after the hybrid forms that may homegenize the compostion 
+mixing after the hybrid forms that may homogenize the composition 
 \citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.
@@
 %meng received may 5 accepted may 16
-progenitors may substantially contribue to the population of \SNeIa (1-8\%) and have
+progenitors may substantially contribute to the population of \SNeIa (1-8\%) and have
 relatively short delay times. They also suggested that these 
@@
 %received august 28 accepted sept 26
-of a hybrid progenitor accreting from a nondegenerate He star and found
-birth rates indicating that up to 18\% of SNe Ia may follow from this chanel
+of a hybrid progenitor accreting from a non-degenerate He star and found
+birth rates indicating that up to 18\% of SNe Ia may follow from this channel
 and very short delay times. \citet{Wangetal2014} also suggested that explosions 
@@
 \citep{mengpods2014}, propose that both Ia-CSM and Iax events 
-are caused by the explosion of hybrid progenitors, with Ia-CSM occuring in systems with 
-a massive common envelope and Iax events occuring in systems where most of the common envelope
+are caused by the explosion of hybrid progenitors, with Ia-CSM occurring in systems with 
+a massive common envelope and Iax events occurring in systems where most of the common envelope
 has been lost.
@@
 the deflagration to detonation transition explosion paradigm, and the
-transition densities were the same in both suites. We briefly our methodoly
+transition densities were the same in both suites. We briefly our methodology
 here, and refer to the reader to previous work for additional details.
@@
 calder.fryxell.ea:on,flash_pragmatic,flash_evolution}. 
-Flash has been applied to a variety of astropysical problems by a host
+Flash has been applied to a variety of astrophysical problems by a host
 of researchers, and the version we apply differs from other versions
@@
 Even with adaptive mesh refinement, whole-star simulations cannot 
-simultaneousely resolve the nuclear flame, so simulations require a model to 
+simultaneously resolve the nuclear flame, so simulations require a model to 
 describe the burning on unresovable scales.  The model we apply is a flame 
@@
 and additional variables to describe the evolution of intermediate-mass
-elements into the stastical quasi-equilibruim of the 
+elements into the statistical quasi-equilibrium of the 
 Si-group~\cite{ifk1981,khok1981,khok1983} and then into iron-group elements
@@
 
-The two-dimensional models in this study do not utilize a subgrid-scale
+The two-dimensional models in this study do not utilize a sub-grid-scale
 model for the turbulence-flame 
@@
 The models only apply in three-dimensional
-simulations beacuse two-dimensional hydrodynamics cannot
+simulations because two-dimensional hydrodynamics cannot
 correctly describe turbulence. The simulations we present
-use the mimimal enhancement based on the Rayleigh-Taylor
+use the minimal enhancement based on the Rayleigh-Taylor
 strength introduced by~\citet{townsley.calder.ea:flame}. The
@@
 progenitor WD. The central temperature and density were the same as
-the tradtional C/O progenitor model. 
+the traditional C/O progenitor model. 
 The peak temperature of the hybrid model is at the center of the star, 
@@
 other neutron-rich isotopes in the initial model were combined into 
-\Ne{22}, which serves as a proxy for metallicty. The aggregation
+\Ne{22}, which serves as a proxy for metallicity. The aggregation
 account for the $Y_e$ of the full set of nuclides, \Ne{20} 
@@
 The original \MESA\ model was in equilibrium, but to ensure
-the uniformly gridded model was in hydrostatic equilibrium we 
+the uniformly-gridded model was in hydrostatic equilibrium we 
 constructed the appropriate pressure profile. This was done by
@@
 begins with a progenitor model mapped to the two-dimensional 
-\FLASH\ grid. The burning is initiated with a ``matchhead,'' a region 
+\FLASH\ grid. The burning is initiated with a ``match head,'' a region 
 in the white dwarf's center that is fully burned to nuclear statistical
 equilibrium (NSE). 
-This initially burned regeion ignites a deflagration, a subsonic
-flame, and because the mathhead was perturbed it is unstable to
+This initially burned region ignites a deflagration, a subsonic
+flame, and because the match head was perturbed it is unstable to
 the Rayleigh-Taylor instability with the result that buoyant plumes 
@@
 $65,536$~\km\ and along the axis of symmetry from $-65,536$~\km\ to
-$65,536$~\km. The maximimum refinement level of the adaptive mesh 
+$65,536$~\km. The maximum refinement level of the adaptive mesh 
 corresponded to $4$~\km\ resolution, which previous study has shown is
@@
 
-The ignition of the deflagration via a matchhead followed the 
+The ignition of the deflagration via a match head followed the 
 initialization described in~\citet{kruegetal12}, which
 followed the method of~\citet{townetal2009}.
-In both the hybrid and traditional cases, the matchhead had a 
+In both the hybrid and traditional cases, the match head had a 
 nominal radius of $150$~km before 
 a different randomly-seeded perturbation was applied to the 
-matchhead for each of the 35 simulations in both suites. {\color{red}
+match head for each of the 35 simulations in both suites. {\color{red}
 IS THIS RIGHT- BOTH USED THE SAME REALIZATIONS?}
@@
 For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
-The rectangular regions show one stanadard deviation from the average for both the C/O and hybrid 
+The rectangular regions show one standard deviation from the average for both the C/O and hybrid 
 models (SEE DON'S PAPER)

### 2019-02-11 paper/ms.tex
Progress on results section of Carlyn's paper.

@@
 of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
-\figref{fig:co_vs_cone_temp} show the density and temperature 
-profiles of the C-O and C-O-Ne hybrid WD.
+The profiles of the two-dimensional models match those of
+the one-dimensional models (shown in \figref{fig:init_conds})
+up to very slight errors from the mapping process. {\color{red}
+OMIT THIS LAST SENTENCE? DONT HAVE A FIGURE}
 
@@
 
-A plot of the estimated \Ni{56} yield as a function of the final, burned mass
-for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
-model is shown in blue. As it is shown, the CO model has a higher final mass
-then the Hybrid model.
-
-The cumulative distribution of the \Ni{56} yield for the C/O and hybrid
-simulations is presented in \ref{fig:cumdist}. 
-The figure presents the estimated \Ni{56} yield as a function of the final burned 
-mass. The results show that the C/O models have a higher burned mass than the
-hybrid models for a given estimated mass of \Ni{56}. CHECK THIS.
+We frame the presention of the results of the suites of simulations 
+principally in terms of the yield of \Ni{56}, the source of 
+the light curve of an event. \Ni{56} thus serves as a proxy
+for the brightness of an explosion and comparison of the yields
+is equivalent to comparing the brightness events. The
+yields estimated from $Y_e$ and the NSE progress
+variable, by assuming the composition in NSE is \Ni{56} plus equal
+parts \Fe{54} and \Ni{58}, as described in
+\citet{townetal2009,Meaketal09}.
 
@@
 \caption{\label{fig:cumdist}
-A plot of the estimated \Ni{56} yield as a function of the final, burned mass
-for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
-models are shown in blue. As it is shown, the CO model has a higher final mass
-then the Hybrid model. 
+The cumulative distribution of the \Ni{56} yield for explosions from
+C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
+results are shown in blue. The curve for the hybrid models is shifted 
+to the left, indicating that explosions from hybrid progenitors produce
+less \Ni{56} than explosions from traditional C-O models. 
 }
 \end{figure}
+The cumulative distribution of the \Ni{56} yield for explosions from
+C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}. 
+The figure shows that the hybrid models consistenly have a higher
+cumulative fraction at a given mass of \Ni{56}, which indicates
+that the yields of \Ni{56} are consistenly lower in explosions 
+from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}
 
@@
 \end{figure}
-
 \begin{figure}
@@
 \end{figure}
-
-The figures show that the final Estimated \Ni{56} for the CO model is
-slightly larger then the Hybrid model. Therefore, the CO produces more
-\Ni{56}. The Hybrid model has a larger range then the CO model. Also, on
-average, the CO model reaches the DDT phase sooner then the Hybrid model.
+The estimated production of \Ni{56} as a function of simulation time
+for 10 simulations of explosions from the hybrid progenitor is shown
+in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
+shown in Figure \ref{fig:nitco}.
+The figures show that the final Estimated \Ni{56} for the C-O model is
+slightly larger then the hybrid model. Therefore, the C-O produces more
+\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
+average, the CO model reaches the DDT phase sooner then the hybrid model.
 

### 2019-02-12 paper/ms.tex
Can you guess which paper?

@@
 \caption{\label{fig:nitco}
-Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
+Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
 Shown are realizations 21-30. 
@@
 \end{figure}
+
 The estimated production of \Ni{56} as a function of simulation time
@@
 shown in Figure \ref{fig:nitco}.
-The figures show that the final Estimated \Ni{56} for the C-O model is
+The figures show that the final estimated \Ni{56} for the C-O model is
 slightly larger then the hybrid model. Therefore, the C-O produces more
@@
 average, the CO model reaches the DDT phase sooner then the hybrid model.
-
-This is a plot of the estimated \Ni{56} yield vs. mass below 2e7 g/cc at
-the time of the DDT.
+Both figures show that production of \Ni{56} effectively ceases (the
+curves flatten out) well before the end of the simulations at 
+$4.0$~\second. Also, the figures show that a few simulations
+did not complete. {\color{red} OFFER A WHY?}
 
@@
 \caption{\label{fig:masshighdens}
-This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
-The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc.
-The estimated Ni56 Yield is the final estimated mass of the model.
-Hybrid- Red
-CO- Blue
-For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
-The rectangular regions show one standard deviation from the average for both the C/O and hybrid 
-models (SEE DON'S PAPER)
+Final estimated IGE {\color{red} 
+TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield 
+vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
+at the time of the first DDT in a simulation.  Individual 
+realizations are shown (C-O-NE
+progenitors in red, C-O in blue) along with rectangles of length
+$\pm 1 \sigma$ along each axis and centered at their average values 
+for C-O and C-O-Ne.
 }
 \end{figure}
+
+Figure \ref{fig:masshighdens} compares the final yield of IGE elemets
+for the C-O and C-O-Ne simulation suites with the amount of expansion of the
+WD during the deflagration phase. The amount of expansion is 
+characterized by the mass above $2 \times 10^7~\grampercc$ at the 
+time of the DDT, with more high-density mass
+indicating less expansion during deflagration. The averages of both
+the C-O and C-O-Ne suites along both axes are indicated by the shaded
+regions with $\pm1\sigma$ widths.
+
+As expected from previous studies, the trend for both C-O and C-O-Ne
+models is that less expansion during the deflagration phase results in
+greater IGE yields, because less expansion gives more high
+density fuel to be consumed in the detonation.
+being more high density fuel for the detonation to consume. 
+As the amount of expansion increases (the less
+mass above $2 \times 10^7 \grampercc$), 
+for a similar amount of expansion, the C-O
+models tend to yield greater IGE mass. Following 
+\citet{willcoxetal2016}, we interpret
+the lower IGE yield in C-O-Ne models as resulting 
+from the lower \C{12} abundance and the fact that given
+similar fuel density, the \Ne{20}-rich fuel will burn to cooler
+temperatures than fuel in the C-O models. The result is
+slower burning to IGE and thus a lower IGE yield.
 
@@
 \caption{\label{fig:conversion}
-The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
+	The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
 First is that higher critical density leads to higher electron capture resulting in less Ni56 produced.
@@
 \end{figure}
+Figure \ref{fig:conversion} shows the estimated \Ni{56} yields 
+across the range of masses burned to IGE
+for all C-O and C-O-Ne realizations at the end 
+of the simulaitons ($4.0$~\second),
+at which point the total mass burned to \Ni{56} had become constant.
 

### 2019-02-12 paper/ms.tex
Declaring this commit a first draft of Carlyn's paper.

@@
 
-{\color{red} ARE THE BELOW NUMBERS CORRECT?}
-The C-O and C-O-Ne models have the same central density
-and temperature $7 \times 10^8$~K, respectively.
+{\color{red} THE BELOW NUMBERS NEED SORTING OUT!}
+The C-O and C-O-Ne models has the same central temperature
+and density ????
+The C-O models had a central density and 
+temperature of $4.62 \times 10^{9}$ $4.27 \times 10^{9}$ ???
+and $7 \times 10^8$~K, respectively.
 The C-O model had core composition of (\C{12} = 0.4, 
@@
 of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
+The C-O models had a central density and 
+temperature of $4.62 \times 10^{9}$ 
+and $8.07 \times 10^8$~K, respectively.
 The C-O-Ne model had core composition of (\C{12} = 0.X, 
@@
 
-We frame the presention of the results of the suites of simulations 
+We frame the presentation of the results of the suites of simulations 
 principally in terms of the yield of \Ni{56}, the source of 
@@
 C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}. 
-The figure shows that the hybrid models consistenly have a higher
+The figure shows that the hybrid models consistently have a higher
 cumulative fraction at a given mass of \Ni{56}, which indicates
-that the yields of \Ni{56} are consistenly lower in explosions 
+that the yields of \Ni{56} are consistently lower in explosions 
 from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}
@@
 at the time of the first DDT in a simulation.  Individual 
-realizations are shown (C-O-NE
+realizations are shown (C-O-Ne
 progenitors in red, C-O in blue) along with rectangles of length
@@
 
-Figure \ref{fig:masshighdens} compares the final yield of IGE elemets
+Figure \ref{fig:masshighdens} compares the final yield of IGE elements
 for the C-O and C-O-Ne simulation suites with the amount of expansion of the
@@
 \caption{\label{fig:conversion}
-	The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
-First is that higher critical density leads to higher electron capture resulting in less Ni56 produced.
-Figure 4 shows that CO model has a stronger electron capture then the hybrid model.
-The second is that the central ignition leads to early burning at higher density.
-Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
-NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
-hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
+Estimated yield of \Ni{56} as a function of final mass burned to IGE
+for C-O-Ne progenitors (red) and C-O progenitors (blue) at
+$t = 4.0 \second$.
 }
@@
 for all C-O and C-O-Ne realizations at the end 
-of the simulaitons ($4.0$~\second),
+of the simulations ($4.0 \second$),
 at which point the total mass burned to \Ni{56} had become constant.
+The difference between the two sets of results is more pronounced
+than the difference between hybrid and tradition models
+found by \citet{willcoxetal2016}. This difference follows from
+differences in the electron capture rates, which follow from
+{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
+MORE METALLICIY? HELP!}
+%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
+%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced.
+Figure 4 shows that CO model has a stronger electron capture then the hybrid model.
+The second is that the central ignition leads to early burning at higher density.
+Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
+%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
+%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
 
@@
 \caption{\label{fig:compare_ratio}
-Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
-SAME AS DON'S FIGURE 19.
+Plot of estimated \Ni{56} mass vs.\ time showing the evolution
+for both suites of simulations. Results from 
+C-O-Ne progenitors are in red and C-O progenitors blue. 
+{\color{red} SAME AS DON'S FIGURE 19}.
+%SAME AS DON'S FIGURE 19
+}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
+\caption{\label{fig:compare_burned}
+Plot of estimated mass burned to IGEs vs.\ time showing the evolution
+for both suites of simulations. Results from C-O-Ne progenitors are 
+in red and C-O progenitors blue.  
+Note that one of the C/O simulations presented did not complete.
+%SAME AS DON'S FIGURE 20
+{\color{red} SAME AS DON'S FIGURE 20.} 
 }
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
-\caption{\label{fig:compare_burned}
-SAME AS DON'S FIGURE 20.
-C/O blue hybrid red.
-Note that one of the C/O simulations presented did not complete.
-}
-\end{figure}
+Figure \ref{fig:compare_ratio} shows the fraction by mass of IGE
+material producing \Ni{56} as it evolves in time and Figure
+\ref{fig:compare_burned} shows the concurrent evolution of mass
+burned to IGE for both suites. While there is considerable
+scatter in the results, differences are obvious.
+
+During the deflagration phase, the C-O models
+on average burn more material to IGE and also had a significantly higher
+fraction of IGE material that is \Ni{56}, yielding more \Ni{56} than
+the C-O-Ne models. This result is counter to that observed in
+\citet{willcoxetal2016}. During the detonation phase, the differences
+are not as obvious and the final mass of IGEs are comparable. The
+fraction of IGE material that is \Ni{56} at the end of the evolution,
+however, is significantly higher. This result differs from 
+the results of \citet{willcoxetal2016} as well.
+
+We attribute these differences as following from the different
+compositions of the progenitors. The C-O-Ne hybrid progenitors
+had more more neutron-rich material (a lower $Y_e$) than the
+traditional C-O models. As expected, when this material burns
+to IGEs, the proportion of neutron-rich material only gets
+higher, as the results demonstrate.
+
+The difference between these results and those of \citet{willcoxetal2016}
+follows from the hybrid C-O-Ne progenitors having a different
+temperature structure that led to ignition of the explosion at lower
+densities. The C-O models in the \citet{willcoxetal2016} study
+thus had more material burning at high densities and thus more
+neutronization and a lower relative \Ni{56} yield than the
+hybrid C-O-Ne models. In the case of the comparison here, the
+C-O and hybrid C-O-Ne models {\color{red} the same central 
+temperature and density and very similar temperature and density 
+profiles at high densities, so the simulations in both cases 
+began with central ignitions. Differences in the explosion outcome 
+accordingly follow from differences in the composition.}
 
@@
 
-The conversion of \Ni{56} to Iron group elements are more pronounced in my
-case. There are two assumptions as to why figure 6 is more pronounced
-in my paper then in Dons.  First is that higher critical density leads
-to higher electron capture resulting in less \Ni{56} produced. The second
-is that the central ignition leads to early burning at higher density.
+Below Rough:
 
-As the star burns mass, the surface area grows, resulting in a decrease
-in density. The results show that the models that burned less mass during
-the deflagration phase, expand less, produce more \Ni{56}. This is because
-the density rich mass the model has at the DDT point is the ‘fuel’
-it needs to produce \Ni{56}. Therefore, the more mass, the more Ni-56. On
-average, the CO model, shown in figure 4, reaches the DDT faster then
-the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
-range of estimated \Ni{56} mass suggesting a greater range of burned mass
-and expansion during the deflagration phase.
+The new generation of C-O-Ne hybrid progenitor models explode similarly to
+traditional C-O models. We conclude they are viable progenitors.
+
+The new generation of C-O-Ne hybrid progenitor models yield
+slightly less \Ni{56}, which is actually in keeping with how
+the C-O models compare to observations. Our C-O models tend
+to produce enough \Ni{56} to imply bright events.
+
+More.....
 

### 2019-02-13 paper/ms.tex
put in Carlyn's cleaned figs and add plotscripts

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
+\includegraphics[width=\columnwidth]{figures/Hybrid_Ni56mass_v_time_plot.pdf}
 \caption{\label{fig:nithybrid}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
+\includegraphics[width=\columnwidth]{figures/CO_Ni56mass_v_time_plot.pdf}
 \caption{\label{fig:nitco}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
+\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
 \caption{\label{fig:compare_ratio}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
+\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
 \caption{\label{fig:compare_burned}

### 2019-02-13 plotscripts/21_30_plot_CO_withparms.py

@@ -1,0 +1,62 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy
+
+# from Rich Townsend for mesa3
+params = {'backend': 'pdf',
+          'figure.figsize': [3.38, 3.38],
+          'font.family':'serif',
+          'font.size':10,
+#          'font.serif': 'Times Roman',
+          'axes.titlesize': 'medium',
+          'axes.labelsize': 'medium',
+          'legend.fontsize': 8,
+          'legend.frameon' : False,
+#          'text.usetex': True,
+#          'figure.dpi': 600,
+          'lines.markersize': 4,
+          'lines.linewidth': 1,
+          'lines.antialiased': False,
+          'path.simplify': False }
+
+matplotlib.rcParams.update(params)
+
+ORANGE     = (0.90,0.60,0.00)
+SKY_BLUE   = (0.35,0.70,0.90)
+BLUE_GREEN = (0.00,0.60,0.50)
+YELLOW     = (0.95,0.90,0.25)
+BLUE       = (0.00,0.45,0.70)
+VERMILLION = (0.80,0.40,0.00)
+RED_PURPLE = (0.80,0.60,0.70)
+
+
+data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_21/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_22/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data23 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_23/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data24 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_24/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
[…]

### 2019-02-13 plotscripts/21_30_plot_Hybrid_withparms.py

@@ -1,0 +1,59 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy
+
+params = {'backend': 'pdf',
+          'figure.figsize': [3.38, 3.38],
+          'font.family':'serif',
+          'font.size':10,
+#          'font.serif': 'Times Roman',
+          'axes.titlesize': 'medium',
+          'axes.labelsize': 'medium',
+          'legend.fontsize': 8,
+          'legend.frameon' : False,
+#          'text.usetex': True,
+#          'figure.dpi': 600,
+          'lines.markersize': 4,
+          'lines.linewidth': 1,
+          'lines.antialiased': False,
+          'path.simplify': False }
+
+matplotlib.rcParams.update(params)
+
+ORANGE     = (0.90,0.60,0.00)
+SKY_BLUE   = (0.35,0.70,0.90)
+BLUE_GREEN = (0.00,0.60,0.50)
+YELLOW     = (0.95,0.90,0.25)
+BLUE       = (0.00,0.45,0.70)
+VERMILLION = (0.80,0.40,0.00)
+RED_PURPLE = (0.80,0.60,0.70)
+
+data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_21_hybrid2/profile21_flash_h201.dat', unpack=True )
+data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_22_hybrid2/profile21_flash_h201.dat', unpack=True )
+data23 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_23_hybrid2/profile21_flash_h201.dat', unpack=True )
+data24 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_24_hybrid2/profile21_flash_h201.dat', unpack=True )
+data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_25_hybrid2/profile21_flash_h201.dat', unpack=True )
+data26 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_26_hybrid2/profile21_flash_h201.dat', unpack=True )
[…]

### 2019-03-13 paper/ms.tex
Fixed affiliations, fixed/suggested text on page 1.

@@
 
+% editing
+\newcommand\redst{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
+
 \bibliographystyle{apj}
@@
 Donald E.\ Willcox\altaffilmark{2},
-Dean M.\ Townsley\altaffilmark{3},
-and Alan C.\ Calder\altaffilmark{2,4}
+Dean M.\ Townsley\altaffilmark{1},
+and Alan C.\ Calder\altaffilmark{3,4}
 }
@@
 \altaffiltext{2}{
-  Department of Physics and Astronomy,
-  Stony Brook University, Stony Brook, NY, 11794-3800, USA; \\
-  \href{mailto:donald.willcox@stonybrook.edu}{donald.willcox@stonybrook.edu}
+  Center for Computational Sciences and Engineering,
+  Lawrence Berkeley National Lab, Berkeley, CA 94720, USA; \\
+  \href{mailto:dewillcox@lbl.gov}{dewillcox@lbl.gov}
 }
 \altaffiltext{3}{
+  Department of Physics and Astronomy,
+  Stony Brook University, Stony Brook, NY, 11794-3800, USA
+}
+\altaffiltext{4}{
   Institute for Advanced Computational Sciences,
@@
 of C and O burns under degenerate conditions. This class of supernovae is
-know to synthesize much of the Fe-group elements found in the galaxy, and
+known to synthesize much of the Fe-group elements found in the galaxy, and
 the light curves of these events have a special property that allows
-standardization of their light curves and thus use
+standardization \redst{of their light curves and thus use}
 as distance indicators for cosmological studies~\citep{phillips:absolute}.
@@
 of \Ni{56}, synthesized by the thermonuclear burning, is also the
-principle source of opacity~\citep{Pinto2001The-type-Ia-sup}, giving
+principal source of opacity~\citep{Pinto2001The-type-Ia-sup}, giving
 the Phillips relation between the brightness of an event and the
@@
 widely-accepted scenarios: the {\em single degenerate} scenario,
-the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
+the {\em double detonation} or {\em sub-Chandrasekhar} scenario, and
 the {\em white dwarf merger} or {\em double degenerate} scenario.
@@
 period of accretion combined with either steady burning or a 
-series of nova explosions to allow the WD to gain at least
+series of nova explosions. \color{{blue} During this accretion phase, the WD must} gain at least
 $\sim 0.4$ \Msun\ as needed for it to approach the

### 2019-03-13 paper/ms.tex
Add modifications to sections 1.1-1.2. Also delete trailing whitespaces on lines.

@@
 %\usepackage[monochrome]{color}
-\usepackage{color}
+\usepackage{xcolor}
 %\usepackage{lipsum}
@@
 % editing
-\newcommand\redst{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
+\newcommand\blust{\bgroup\markoverwith{\textcolor{blue}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
 
@@
 the light curves of these events have a special property that allows
-standardization \redst{of their light curves and thus use}
+standardization \blust{of their light curves and thus use}
 as distance indicators for cosmological studies~\citep{phillips:absolute}.
@@
 period of accretion combined with either steady burning or a
-series of nova explosions. \color{{blue} During this accretion phase, the WD must} gain at least
+series of nova explosions. {\color{blue} During this accretion phase, the WD must} gain at least
 $\sim 0.4$ \Msun\ as needed for it to approach the
@@
 that best reproduce the observed stratified ejecta are those in which
-the burning begins as a subsonic deflagration, which allows the star 
-to react and expand thus lowering the density, and is then followed by a 
+the burning begins as a subsonic deflagration, {\color{blue} allowing the star
+to expand to lower densities in response, followed} by a
 supersonic detonation that incinerates the
@@
 than gaining enough mass to approach the Chandrasekhar limit, a detonation
-occurs in the accreted layer that subsequently triggers a detonation
-in the underlying white dwarf \citet{woosleyweavertaam80,taam80a,taam80b,
+occurs in the accreted layer that subsequently triggers another detonation
+in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
 nomoto80,nomoto82b}. Early studies indicated that a detonation in an
@@
 masses, not just the near-Chandrasekhar case \citep{livne90}, hence the
-moniker ``sub-Chandrasekhar'' \citep{ww94}. Multidimensional supported the
+moniker ``sub-Chandrasekhar'' \citep{ww94}.
+{\color{blue} Follow-up multidimensional calculations}
+supported the
 efficacy of this picture~\citep{livneglasner91, livnearnett95,HoefKhok96,
@@
 A particular problem was that most models included a massive He layer on
-the white dwarf. Such a configuration leads to the unobserved result 
+the white dwarf. Such a configuration leads to the unobserved result that
 intermediate and heavy elements synthesized in the He detonation appear in
@@
 
-Subsequent work allayed this concern~\citep{yoonetal2007,lorenaguilaretal2009,
-Shenetal12, pakmoretal2012b} and motivated by the need to explain bright events
-and the estimated population WD pairs, active research continues. Contemporary
+Subsequent work allayed this concern {\color{blue} [we should probably mention how]}
+~\citep{yoonetal2007,lorenaguilaretal2009, Shenetal12, pakmoretal2012b}
+and active research continues, motivated by the need to explain bright events
+and the estimated population of WD pairs. Contemporary
 research focuses on variations on the merger idea, including inspiraling pairs,
 collisions, violent mergers, and the ``core-degenerate'' model in which the merger
-takes place in a common envelope \citep{raskinetal2009,pakmoretal2011,kashi:2011,
+takes place in a common envelope~\citep{raskinetal2009,pakmoretal2011,kashi:2011,
 pakmoretal2012a,Shenetal12,katzetal2016}.
@@
 
-Our single-degenerate models are within the DDT explosion paradigm \cite{1986SvAL,
+Our single-degenerate models are within the DDT explosion paradigm~\citep{1986SvAL,
 Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}.

### 2019-03-13 paper/ms.tex
Finished adding updates to section 1.

@@
 
-\subsection{Proposed Progenitor Settings}
+\subsection{Proposed Progenitor Settings}\label{sec:progenitors}
 
@@
 In the area of stellar evolution, recent investigations revisiting
-late-time evolution of roughly 8 \Msun stars indicate that under
+late-time evolution of roughly 8 \Msun~stars indicate that under
 the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne
 mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
-white dwarf are thought to form when mixing at the lower convective boundary quenches
+white dwarfs are thought to form when mixing at the lower convective boundary quenches
 C burning in an asymptotic giant branch (AGB) star, leaving unburned C
 in the core. The situation is at best uncertain, however, and the
-results depending on assumptions about convective
-overshoot that have been questioned \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.
+results depend on assumptions about convective
+overshoot that have been questioned {\color{blue} [questioned for what reasons?]} \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.
 
 A hybrid WD can become a progenitor of a thermonuclear supernova via two
-of the progenitor system.
+of the progenitor scenarios discussed in Section \ref{sec:progenitors}.
 First, the hybrid could be part of a binary system in which the companion star becomes
@@
 make the core-mantle interface subject to convective
-instability \citep{brooksetal2017,schwabgaraud2018}. In the case of the
+instability \citep{brooksetal2017,schwabgaraud2018}.
+{\color{blue} [can we say a bit more about how this cooling-caused instability works?]}
+In the case of the
 hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
 heat the core and start C fusion, leading to a period of ``simmering" prior
-to the explosion \citep{PiroBild08}. The upshot is that is likely to be considerable
+to the explosion \citep{PiroBild08}. The upshot is that there is likely to be considerable
 mixing after the hybrid forms that may homogenize the composition
@@
 %meng received may 5 accepted may 16
-progenitors may substantially contribute to the population of \SNeIa (1-8\%) and have
+progenitors may substantially contribute to the population of \SNeIa\ (1-8\%) and have
 relatively short delay times. They also suggested that these
@@
 \citet{mengpods2018}, from the common-envelope-wind model developed in
-\citep{mengpods2014}, propose that both Ia-CSM and Iax events
+\citet{mengpods2014}, propose that both Ia-CSM and Iax events
 are caused by the explosion of hybrid progenitors, with Ia-CSM occurring in systems with
@@
 \citet{willcoxetal2016} simulated explosions from the progenitors of
-\citep{denissenkovetal2015} and found a trend of lower energy and lower
-\Ni{56} yield when compared to explosions from traditional C/O progenitors.
+\citet{denissenkovetal2015} and found lower
+\Ni{56} yields on average and a trend of lower ejecta kinetic energy
+when compared to explosions from traditional C/O progenitors.
 

### 2019-03-15 paper/ms.tex
Couple o' quick things from discussing the manuscript at group meeting.

@@
 the {\em double detonation} or {\em sub-Chandrasekhar} scenario, and
-the {\em white dwarf merger} or {\em double degenerate} scenario.
+the {\em white dwarf merger} scenario.
 We briefly describe these in the subsection that follows.
@@
 
-Figure \ref{fig:masshighdens} compares the final yield of IGE elements
+Figure \ref{fig:masshighdens} compares the final yield of IGEs
 for the C-O and C-O-Ne simulation suites with the amount of expansion of the

### 2019-03-21 paper/ms.tex
Updated lots of text, added some questions, marked text for removal.

@@
 the deflagration to detonation transition explosion paradigm, and the
-transition densities were the same in both suites. We briefly our methodology
-here, and refer to the reader to previous work for additional details.
+transition densities were the same in both suites. We briefly review our methodology
+here, and refer the reader to previous work for additional details.
 In particular, we use the same simulation instrument, a modified version
@@
 The simulations of supernova explosions presented here were performed
-with a customized version of the \FLASH code, originally developed
+with a customized version of the \FLASH\ code, originally developed
 at the University of Chicago.
@@
 developed first for nuclear astrophysics applications and subsequently
-for high-energy-density applications~\cite{Fryxetal00,calder.curtis.ea:high-performance,
+for high-energy-density applications~\citep{Fryxetal00,calder.curtis.ea:high-performance,
 calder.fryxell.ea:on,flash_pragmatic,flash_evolution}.
@@
 artificially broadened flame with an advection-diffusion-reaction (ADR)
-scheme~\cite{Khok95,VladWeirRyzh06} via evolution of
+scheme~\citep{Khok95,VladWeirRyzh06} via evolution of
 a reaction progress variable to describe the consumption of C
@@
 elements into the statistical quasi-equilibrium of the
-Si-group~\cite{ifk1981,khok1981,khok1983} and then into iron-group elements
+Si-group~\citep{ifk1981,khok1981,khok1983} and then into iron-group elements
 (IGEs) in full nuclear statistical equilibrium (NSE).
@@
 The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
-unburned fuel and $\phi=1$ for burned ash. $\phi$ is evolved
+unburned fuel to $\phi=1$ for burned ash. $\phi$ is evolved
 via an advection-diffusion-reaction equation,
@@
 $\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
-front at a prescribed speed.  Our model uses the ``sharpened KPP
+front at a prescribed speed.  Our model uses the ``sharpened KPP''
  described by~\cite{VladWeirRyzh06},
@@
 acoustically quiet, stable, and to give a unique flame speed
-\cite{townsley.calder.ea:flame}. The input flame speeds come from
+\citep{townsley.calder.ea:flame}. The input flame speeds come from
 tabulated results obtained by direct numerical simulations of
-thermonuclear burning~\cite{timmes92,Chamulak2007The-Laminar-Fla},
+thermonuclear burning~\citep{timmes92,Chamulak2007The-Laminar-Fla},
 and
 these are boosted to account for speed-up of burning due to unresolved
-buoyancy and background turbulence~\cite{Khok95,
+buoyancy and background turbulence~\citep{Khok95,
 gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
@@
 model for the turbulence-flame
-interaction~\citep[See][for examples]{Schmetal06a,Schmetal06b,jacketal2014},
-The models only apply in three-dimensional
+interaction~\citep[See][for examples]{Schmetal06a,Schmetal06b,jacketal2014}.
+Those sub-grid-scale models only apply in three-dimensional
 simulations because two-dimensional hydrodynamics cannot
@@
 strength introduced by~\citet{townsley.calder.ea:flame}. The
-assumption here is that the burning self-regulate on resolved
+assumption here is that the burning self-regulates on resolved
 scales so that results are insensitive to the detailed treatment
@@
 indicates this assumption is reasonable for comparisons
-like the one presented in this work~\citet{townsley.calder.ea:flame,
+like the one presented in this work~\citep{townsley.calder.ea:flame,
 willcoxetal2016}.
@@
 during the explosion changes the thermodynamic conditions and thus the
-balance. Electron capture also influences the evolution by shifting the binding
-energy of the material and thereby changing the temperature due to released energy,
-by changing the Fermi energy and thus the pressure, and by emitting neutrinos that
-escape and remove energy. Electron captures also neutronize the material, which
-produces more neutron rich iron-group material at the expense of \Ni. Like the
-input flame speed, the burning model includes tabulated rates for these effects
-from detailed NSE calculations ~\cite{SeitTownetal09}. Accordingly, the burning
+balance.
+{\color{blue} Electron capture also influences the evolution in several ways by
+neutronizing the material, which produces more neutron rich iron-group
+material at the expense of \Ni. Neutronization also shifts the binding
+energy of the material and the Fermi energy of electrons, respectively
+changing the temperature (due to released energy) and the pressure.
+Finally, individual electron capture reactions emit neutrinos that
+escape and remove energy from the system.}
+Like the input flame speed, the burning model includes tabulated rates for these effects
+from detailed NSE calculations ~\citep{SeitTownetal09}. Accordingly, the burning
 model is able to describe dynamic evolution of the ash in addition to the
@@
 In this case, the model evolves thermally-activated burning with the actual
-temperature-dependent rate for C consumption, which allow a propagating shock to
+temperature-dependent rate for C consumption, which allows a propagating shock to
 trigger burning, i.e.\ to propagate a detonation front. The propagating detonation
@@
 
-The hybrid white dwarf model that served as the initial conditions
+The hybrid white dwarf model that served as the initial condition
 for the simulations of supernova explosions presented in this work
@@
 The hybrid model was constructed to have conditions as similar a possible
-to a ``classic" C/O model and the two shared the same central temperature
+to a ``classic'' C/O model and the two shared the same central temperature
 and density.  Figure~\ref{fig:init_conds} shows the density and temperature
@@
 \end{figure} 
-In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
-temperature was the highest at the center of the star and accordingly the simulations
-began with central ignitions.
+{\color{blue} We centrally ignite our explosion simulations for both
+  C/O and hybrid models to coincide with the peak temperature at the
+  center of the WDs, unlike the hybrid models
+  of~\citet{willcoxetal2016}.}
 
@@
 As described above, the flame capturing scheme with progress
-variables describing the evolution as the material burns. The \MESA\
+variables describes the evolution as the material burns. The \MESA\
 models, however, relied on a detailed reaction network that included
@@
 The process of mapping the \MESA\ models began by converting
-the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\
-quantities in zones with spacing less than $4$~km
-were mass-weighted averaged and a quadratic interpolation
-was used to calculate quantities for the case of \MESA\ zones having
-a spacing greater than $4$~km. At this point,
+the \MESA\ model to a uniform grid of $4$~km resolution. 
+{\color{blue}We mass-weighted and averaged quantities in \MESA\ zones with spacing less than $4$~km
+and quadratically interpolated quantities in \MESA\ zones with spacing greater than $4$~km.}
+At this point,
 abundances of nuclides from the \MESA\ models were aggregated
@@
 \Ne{22}, which serves as a proxy for metallicity. The aggregation
-account for the $Y_e$ of the full set of nuclides, \Ne{20}
+accounts for the $Y_e$ of the full set of nuclides, and \Ne{20}
 and \Ox{16} were constrained to be in the same ratio in both
@@
 composition, and the mass below and enclosed by the zone. As
-with \citet{willcoxetal2016} we used
-EOS routine from
+with \citet{willcoxetal2016} we used the EOS routine from
 \CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
@@
   hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As
- with the models in \citet{willcoxetal2016},this procedure produced
+ with the models in \citet{willcoxetal2016}, this procedure produced
  a structure that was stable in \FLASH, with fluctuations in central
@@
 
-\subsection{DDT Process and Suits of Explosions}
+\subsection{DDT Process and Suites of Explosions}
 
-The simulations performed for this study consisted to a suite of
+The simulations performed for this study consisted of a suite of
 {\color{red} 35 CHECK THIS! 40?} two-dimensional simulations of
@@
 $65,536$~\km. The maximum refinement level of the adaptive mesh
-corresponded to $4$~\km\ resolution, which previous study has shown is
+corresponded to $4$~\km\ resolution, which previous study has shown
 is a good balance between efficiency and
@@
 $\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$,
-a $12$~\km\ a region of fuel, (\C{12} and \Ne{20}, if present) is
+a $12$~\km\ region {\color{blue} [radius or diameter?]} of fuel, (\C{12} and \Ne{20}, if present) is
 fully burned $32$~\km\ radially outwards from the flame. This
@@
 We frame the presentation of the results of the suites of simulations
-principally in terms of the yield of \Ni{56}, the source of
+principally in terms of the yield of \Ni{56}, the energy source of
 the light curve of an event. \Ni{56} thus serves as a proxy
 for the brightness of an explosion and comparison of the yields
-is equivalent to comparing the brightness events. The
-yields estimated from $Y_e$ and the NSE progress
+is equivalent to comparing the brightness of events. The
+yields were estimated from $Y_e$ and the NSE progress
 variable, by assuming the composition in NSE is \Ni{56} plus equal
@@
 \caption{\label{fig:cumdist}
-The cumulative distribution of the \Ni{56} yield for explosions from
+The cumulative distribution of the final \Ni{56} yield for explosions from
 C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
@@
 The cumulative distribution of the \Ni{56} yield for explosions from
-C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}.
+C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
 The figure shows that the hybrid models consistently have a higher
@@
 shown in Figure \ref{fig:nitco}.
-The figures show that the final estimated \Ni{56} for the C-O model is
-slightly larger then the hybrid model. Therefore, the C-O produces more
-\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
-average, the CO model reaches the DDT phase sooner then the hybrid model.
-Both figures show that production of \Ni{56} effectively ceases (the
-curves flatten out) well before the end of the simulations at
-$4.0$~\second. Also, the figures show that a few simulations
-did not complete. {\color{red} OFFER A WHY?}
+{\color{blue} The figures show that the final estimated \Ni{56} for
+  the C-O model is slightly larger than the hybrid model. Therefore,
+  the C-O produces more \Ni{56}. The hybrid model has a larger range
+  then the C-O model. [Figure \ref{fig:nithybrid} and Figure
+  \ref{fig:nitco} cannot support general claims like this because they
+  only show ten of our realizations and it's hard to measure by
+  eye. Figure \ref{fig:cumdist} is much better at demonstrating both
+  of these statements.]}
+Also, on average, the CO model reaches the DDT phase sooner then the
+hybrid model.  Both figures show that production of \Ni{56}
+effectively ceases (the curves flatten out) well before the end of the
+simulations at $4.0$~\second. Also, the figures show that a few
+simulations did not complete. {\color{red} OFFER A WHY?}
 
-The degree of expansion was found using the time at which the first
-detonation point occurred, and the mass at density less then 2e7 g/cc. The
-estimated \Ni{56} Yield is the final estimated mass of the model.
+\blust{The degree of expansion was found using the time at which the first
+detonation point occurred, and the mass at density greater than 2e7 g/cc. The
+estimated \Ni{56} Yield is the final estimated mass of the model.}
 
@@
 characterized by the mass above $2 \times 10^7~\grampercc$ at the
-time of the DDT, with more high-density mass
+time of the first DDT occurrence, with more high-density mass
 indicating less expansion during deflagration. The averages of both
@@
 models is that less expansion during the deflagration phase results in
-greater IGE yields, because less expansion gives more high
-density fuel to be consumed in the detonation.
-being more high density fuel for the detonation to consume.
-As the amount of expansion increases (the less
-mass above $2 \times 10^7 \grampercc$),
+greater IGE yields because less expansion allows the detonation to
+consume more high density fuel.
+As the amount of expansion increases (less
+mass remains above $2 \times 10^7~\grampercc$),
 for a similar amount of expansion, the C-O
@@
 The difference between the two sets of results is more pronounced
-than the difference between hybrid and tradition models
+than the difference between hybrid and traditional C/O models
 found by \citet{willcoxetal2016}. This difference follows from
@@
 fraction of IGE material that is \Ni{56} at the end of the evolution,
-however, is significantly higher. This result differs from
-the results of \citet{willcoxetal2016} as well.
+however, is significantly higher for C/O models than for our hybrid models. 
+{\color{blue}This result differs from the results of
+  \citet{willcoxetal2016} as well and is consistent with the
+  observation that our hybrid models on average expand less during the
+  deflagration stage than our C/O models. By contrast, the hybrid models of
+  \citet{willcoxetal2016} expanded very slightly more
+  than C/O models on average during the deflagration stage.}
 
@@
 compositions of the progenitors. The C-O-Ne hybrid progenitors
-had more more neutron-rich material (a lower $Y_e$) than the
+had more neutron-rich material (a lower $Y_e$) than the
 traditional C-O models. As expected, when this material burns
@@
 
-The difference between these results and those of \citet{willcoxetal2016}
-follows from the hybrid C-O-Ne progenitors having a different
-temperature structure that led to ignition of the explosion at lower
-densities. The C-O models in the \citet{willcoxetal2016} study
+The difference between these results and those of
+\citet{willcoxetal2016} follows from their hybrid C-O-Ne progenitors
+having a different temperature structure that
+led to ignition of the explosion at lower densities.
+The C-O models in the \citet{willcoxetal2016} study
 thus had more material burning at high densities and thus more
 neutronization and a lower relative \Ni{56} yield than the
-hybrid C-O-Ne models. In the case of the comparison here, the
-C-O and hybrid C-O-Ne models {\color{red} the same central
+corresponding hybrid C-O-Ne models. In the case of the comparison here, the
+C-O and hybrid C-O-Ne models {\color{red} have the same central
 temperature and density and very similar temperature and density
 profiles at high densities, so the simulations in both cases
-began with central ignitions. Differences in the explosion outcome
-accordingly follow from differences in the composition.}
+began with central ignitions. Differences in the explosion outcomes
+for our C/O and hybrid C-O-Ne WD models 
+accordingly follow from differences in their composition.}
 

### 2019-03-21 paper/ms.tex
remove whitespace at end of lines
Fix Ni-56 typesetting.

@@
 neutronizing the material, which produces more neutron rich iron-group
-material at the expense of \Ni. Neutronization also shifts the binding
+material at the expense of \Ni{56}. Neutronization also shifts the binding
 energy of the material and the Fermi energy of electrons, respectively

### 2019-03-21 paper/ms.tex
Made use of Flash consistent as \FLASH. Maybe rethink this.

@@
 carbon burning. This MESA model was then mapped to a two-dimensional initial
-condition and an explosion simulated with FLASH. For comparison, a similar
+condition and an explosion simulated with \FLASH. For comparison, a similar
 simulation of an explosion was performed from a traditional C/O progenitor
@@
 In particular, we use the same simulation instrument, a modified version
-of the Flash Code, as \citet{willcoxetal2016} and we refer the reader there
+of the \FLASH\ Code, as \citet{willcoxetal2016} and we refer the reader there
 for a description of modifications for C-O-Ne burning and verification tests
@@
 at the University of Chicago.
-Flash is a parallel, adaptive mesh, multi-physics simulation code
+\FLASH\ is a parallel, adaptive mesh, multi-physics simulation code
 developed first for nuclear astrophysics applications and subsequently
@@
 calder.fryxell.ea:on,flash_pragmatic,flash_evolution}.
-Flash has been applied to a variety of astrophysical problems by a host
+\FLASH\ has been applied to a variety of astrophysical problems by a host
 of researchers, and the version we apply differs from other versions
@@
 these studies is available as a package compatible with the
-current Flash code from \url{http://astronomy.ua.edu/townsley/code.}
+current \FLASH\ code from \url{http://astronomy.ua.edu/townsley/code.}
 Results in this

### 2019-05-08 paper/ms.tex
An example commit for the lecture on version control in PHY504.

@@
 \label{sec:intro}
+
+Yo, hey Bubba!
+
 Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions

### 2019-06-06 paper/ms.tex
Un-did the example change.
Cleanups for title and abstract

@@
 
-\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors}
+\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White
+Dwarf Progenitors That Have Mixed During Cooling}
 
@@
 \begin{abstract}
-The existence of ``hybrid" white dwarfs, made of a C/O
-core within a O/Ne shell is accepted, and studies indicate that these are
+The creation of ``hybrid" white dwarfs, made of a C/O
+core within a O/Ne shell has been proposed, and studies indicate that
+ignition in the C-rich central region makes these
 viable progenitors for thermonuclear (type Ia) supernovae.
@@
 supernovae from a new series of hybrid progenitors that include the
-effects of cooling. The progenitor white dwarf model
+effects of mixing during cooling. The progenitor white dwarf model
 was constructed with the one-dimensional stellar evolution code MESA and
@@
 carbon burning. This MESA model was then mapped to a two-dimensional initial
-condition and an explosion simulated with \FLASH. For comparison, a similar
-simulation of an explosion was performed from a traditional C/O progenitor
-white dwarf. By comparing the yields of the explosions, we found that as
-with earlier studies, these hybrid models are viable supernova progenitors.
-We contrast explosions from these models with explosions
-from previous hybrid models
-{\color{red} without the mixing during the white dwarf cooling}
-and traditional C/O progenitors.
+condition for explosions simulated with \FLASH. For comparison, similar
+simulations were performed for a traditional C/O progenitor
+white dwarf. By comparing the yields of the explosions, we find that, as
+with earlier studies, the lower C abundance in the hybrid progenitor compared
+to the traditional C/O progenitor leads to a lower average yield of $^{56}$Ni.
+Although the unmixed hybrid WD showed a similar decrement also in total iron
+group yield, the mixed case does not.  We attribute this to the higher
+central density required for ignition.
 \end{abstract}
@@
 \label{sec:intro}
-
-Yo, hey Bubba!
 
@@
 $t = 4.0 \second$.
+TODO: add lines from Willcox et al.
 }

### 2019-06-11 plotscripts/collect_ige_ni56_yields.py
Tidy up cumulative yield distribution figure
Switch colors to be more consistent with Don's choice in his 2016 paper.
Use my matplotib so that tex works and style is more formal.
Made a data collection script and included data for figure
(plotscript was previously doing the collection from the individual runs
every time.)
Included the collection script here.

@@ -1,0 +1,47 @@
+
+import numpy as np
+
+#import integral file
+filelistCO = []
+filelistHY = []
+for i in range(11,41):
+    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
+
+for i in range(11,41):
+    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
+
+#CO
+gpermsun = 1.988435e33
+a = []
+b = []
+for fname in filelistCO:
+	data = np.loadtxt(fname)
+	x = data[-1][13]
+	xsolar = x/gpermsun
+	a.append(xsolar)
+	y = data[-1][15]
+	ysolar = y/gpermsun
+	b.append(ysolar)
+
+#HY
+gpermsun = 1.988435e33
+c = []
+d = []
+for fname in filelistHY:
+	data = np.loadtxt(fname)
+	x = data[-1][13]
+	xsolar = x/gpermsun
+	c.append(xsolar)
+	y = data[-1][15]
+	ysolar = y/gpermsun
+	d.append(ysolar)
+
+print "# realization	CO_IGE	CO_Ni56	CONe_IGE	CONe_Ni56"
+for r in range(11,41):
+	i = r-11
+	print "%i\t%16.10e\t%16.10e\t%16.10e\t%16.10e"%(r,a[i],b[i],c[i],d[i])
+
+
+
+
+

### 2019-06-11 plotscripts/plot_cum_dis_ni56.py

@@ -1,5 +1,5 @@
 import matplotlib
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 
@@ -7,13 +7,13 @@ params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
           'font.family':'serif',
           'font.size':10,
-#          'font.serif': 'Times Roman',
+          'font.serif': 'Times Roman',
           'axes.titlesize': 'medium',
           'axes.labelsize': 'medium',
           'legend.fontsize': 8,
           'legend.frameon' : False,
-#          'text.usetex': True,
-#          'figure.dpi': 600,
+          'text.usetex': True,
+          'figure.dpi': 600,
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
@@ -29,44 +29,14 @@ BLUE       = (0.00,0.45,0.70)
 VERMILLION = (0.80,0.40,0.00)
 RED_PURPLE = (0.80,0.60,0.70)
 
-#import integral file
-filelistCO = []
-filelistHY = []
-for i in range(11,41):
-    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
+ax = plt.subplot(111)
 
-for i in range(11,41):
-    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
 
-#plot Ni-56 mass profile
-gpermsun = 1.988435e33 # grams/Msun
-a = []
-for fname in filelistCO:
-    print(fname)
-    data = np.loadtxt(fname)
-    x = data[-1][15]   #final estimated mass
-    xsolar = x/gpermsun        #convert to solar mass
-    a.append(xsolar)           # add to array
-    print(xsolar)
-
-a.sort()                       # sort numbers in order
-print(a)
-totalnumber = len(a)           #find the length of the array: total number
-print(totalnumber)
-index = np.arange(1,totalnumber+1)
-y = index/float(totalnumber)
-plt.plot(a, y, label = 'CO', color = 'b')
+#import data
+data = np.genfromtxt("yields_ige_ni56.dat", names=True)
 
 #Hybrid Models
[…]

### 2019-06-11 paper/ms.tex
Tidy up cumulative yield distribution figure
Switch colors to be more consistent with Don's choice in his 2016 paper.
Use my matplotib so that tex works and style is more formal.
Made a data collection script and included data for figure
(plotscript was previously doing the collection from the individual runs
every time.)
Included the collection script here.
Update and swap color in IGE v dens mass fig
also add results from Don's paper for comparison.

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
+\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
 \caption{\label{fig:cumdist}
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
+\includegraphics[width=\columnwidth]{figures/ige_v_mass_at_high_dens.pdf}
 \caption{\label{fig:masshighdens}
-Final estimated IGE {\color{red}
-TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield
-vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
+Final IGE yield
+vs.\ mass above $2\times 10^7~\grampercc$
 at the time of the first DDT in a simulation.  Individual
 realizations are shown (C-O-Ne
-progenitors in red, C-O in blue) along with rectangles of length
+progenitors in blue, C-O in red) along with rectangles of length
 $\pm 1 \sigma$ along each axis and centered at their average values
-for C-O and C-O-Ne.
+for C-O and C-O-Ne.  Similar rectangles found in W16 for a progenitor without
+mixing during cooling are shown in a lighter shade with dashed borders.
 }

### 2019-06-11 plotscripts/plot_ige_v_mass_at_high_dens.py

@@ -8,17 +8,19 @@ params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
           'font.family':'serif',
           'font.size':10,
-#          'font.serif': 'Times Roman',
+          'font.serif': 'Times Roman',
           'axes.titlesize': 'medium',
           'axes.labelsize': 'medium',
           'legend.fontsize': 8,
           'legend.frameon' : False,
-#         'text.usetex': True,
-#          'figure.dpi': 600,
+          'text.usetex': True,
+          'figure.dpi': 600,
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
-          'path.simplify': False }
+          'path.simplify': False,
+	  # mine below here
+	  'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -32,15 +34,10 @@ RED_PURPLE = (0.80,0.60,0.70)
 
 
 
-#import integral file
-filelistCO = []
-filelistHY = []
-for i in range(11,41):
-    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
+gpermsun = 1.988435e33 # grams/Msun
 
-for i in range(11,41):
-    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
-
+#import data
+data = np.genfromtxt("yields_ige_ni56.dat", names=True)
 
[…]

### 2019-06-12 paper/ms.tex
Update Ni56 vs IGE figure
swapping colors, adding lines from Don's paper, prettying up.

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
+\includegraphics[width=\columnwidth]{figures/ni56_v_ige.pdf}
 \caption{\label{fig:conversion}
 Estimated yield of \Ni{56} as a function of final mass burned to IGE
-for C-O-Ne progenitors (red) and C-O progenitors (blue) at
-$t = 4.0 \second$.
-TODO: add lines from Willcox et al.
+for C-O-Ne progenitors (blue) and C-O progenitors (red) at
+$t = 4.0 \second$.  Lines indicate corresponding relations found in W16 with
+a lower central density and CONe progenitor whose interior is not mixed
+during cooling.
 }

### 2019-06-12 plotscripts/plot_ni56_v_ige.py

@@ -8,17 +8,19 @@ params = {'backend': 'pdf',
  'figure.figsize': [3.38, 3.38],
  'font.family':'serif',
  'font.size':10,
-# 'font.serif': 'Times Roman',
+ 'font.serif': 'Times Roman',
  'axes.titlesize': 'medium' ,
  'axes.labelsize':'medium',
  'legend.fontsize':8,
  'legend.frameon':False,
-# 'text.usetex': True,
-# 'figure.dpi':600,
+ 'text.usetex': True,
+ 'figure.dpi':600,
  'lines.markersize':4,
  'lines.linewidth':1,
  'lines.antialiased':False,
- 'path.simplify':False}
+ 'path.simplify':False,
+ # Townsley below here
+ 'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -30,52 +32,41 @@ BLUE = (0.00, 0.45, 0.70)
 VERMILLION = (0.80, 0.40, 0.00)
 RED_PURPLE = (0.80, 0.60, 0.70)
 
+ax = plt.subplot(111)
 
-#import integral file
-filelistCO = []
-filelistHY = []
-for i in range(11,41):
-    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
 
-for i in range(11,41):
-    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
+#import data
+data = np.genfromtxt("yields_ige_ni56.dat", names=True)
 
 #CO
-gpermsun = 1.988435e33
-a = []
-b = []
-for fname in filelistCO:
-	data = np.loadtxt(fname)
-	x = data[-1][13]
-	xsolar = x/gpermsun
-	a.append(xsolar)
-	y = data[-1][15]
-	ysolar = y/gpermsun
-	b.append(ysolar)
-print(a)
-print(b)
-plt.plot(a, b, "o", label ='CO', color = 'b')
+a = data['CO_IGE']
+b = data['CO_Ni56']
+plt.plot(a, b, "o", label ='CO', color = 'r', marker='s')
 
 #HY
-gpermsun = 1.988435e33
-c = []
-d = []
-for fname in filelistHY:
[…]

### 2019-06-12 plotscripts/plot_cum_dis_ni56.py
Minor adjustment to cum plot
make CO line dashed and make nicer x axis

@@ -17,7 +17,9 @@ params = {'backend': 'pdf',
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
-          'path.simplify': False }
+          'path.simplify': False,
+	  # townsley below here
+	  'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -44,7 +46,7 @@ totalnumber = len(a)           #find the length of the array: total number
 print(totalnumber)
 index = np.arange(1,totalnumber+1)
 y = index/float(totalnumber)
-plt.step(a, y, label = 'Hybrid', color = 'b', where='post')
+plt.step(a, y, label = 'CONe', color = 'b', where='post')
 
 
 #CO
@@ -56,7 +58,7 @@ totalnumber = len(a)           #find the length of the array: total number
 print(totalnumber)
 index = np.arange(1,totalnumber+1)
 y = index/float(totalnumber)
-plt.step(a, y, label = 'CO', color = 'r', linestyle=':', where='post')
+plt.step(a, y, label = 'CO', color = 'r', linestyle='--', where='post')
 
 
 
@@ -74,8 +76,12 @@ plt.legend(loc='best')
 #plt.title('Cumulative distribution of estimated Ni56 Yield')
 plt.xlabel('$^{56}$Ni Yield (M$_\\odot$)')
 plt.ylabel('Cumulative Distribution')
+plt.xlim( [ 0.6, 1.1] )
+
+ax.yaxis.set_minor_locator(matplotlib.ticker.AutoMinorLocator())
+ax.xaxis.set_minor_locator(matplotlib.ticker.AutoMinorLocator())
+
 plt.tight_layout()
-ax.yaxis.set_minor_locator(matplotlib.ticker.MultipleLocator(0.1))
 plt.savefig('cum_dis_Ni56.pdf')
 #plt.show()
              

### 2019-06-12 plotscripts/21_30_plot_CO.py
Update style and colors for all but first figure

@@ -2,7 +2,8 @@ import matplotlib
 import matplotlib.pyplot as plt
 import numpy
 
-# from Rich Townsend for mesa3
+matplotlib.rc_file("ubuntu_matplotlibrc")
+
 params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
           'font.family':'serif',
@@ -17,7 +18,9 @@ params = {'backend': 'pdf',
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
-          'path.simplify': False }
+          'path.simplify': False,
+          # townsley below here
+          'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -29,6 +32,7 @@ BLUE       = (0.00,0.45,0.70)
 VERMILLION = (0.80,0.40,0.00)
 RED_PURPLE = (0.80,0.60,0.70)
 
+ax = plt.subplot(111)
 
 data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_21/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_22/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
@@ -41,22 +45,29 @@ data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_2
 data29 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_29/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data30 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_30/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 
-plt.plot( data21[0], data21[15]/1.99e33, label = '21' )
-plt.plot( data22[0], data22[15]/1.99e33, label = '22' )
-plt.plot( data23[0], data23[15]/1.99e33, label = '23' )
-plt.plot( data24[0], data24[15]/1.99e33, label = '24' )
-plt.plot( data25[0], data25[15]/1.99e33, label = '25' )
-plt.plot( data26[0], data26[15]/1.99e33, label = '26' )
[…]

### 2019-06-12 plotscripts/21_30_plot_Hybrid.py

@@ -2,6 +2,8 @@ import matplotlib
 import matplotlib.pyplot as plt
 import numpy
 
+matplotlib.rc_file("ubuntu_matplotlibrc")
+
 params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
           'font.family':'serif',
@@ -16,7 +18,9 @@ params = {'backend': 'pdf',
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
-          'path.simplify': False }
+          'path.simplify': False,
+          # townsley below here
+          'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -27,6 +31,8 @@ YELLOW     = (0.95,0.90,0.25)
 BLUE       = (0.00,0.45,0.70)
 VERMILLION = (0.80,0.40,0.00)
 RED_PURPLE = (0.80,0.60,0.70)
+
+ax = plt.subplot(111)
 
 data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_21_hybrid2/profile21_flash_h201.dat', unpack=True )
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_22_hybrid2/profile21_flash_h201.dat', unpack=True )
@@ -39,21 +45,29 @@ data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_28_h
 data29 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_29_hybrid2/profile21_flash_h201.dat', unpack=True )
 data30 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_30_hybrid2/profile21_flash_h201.dat', unpack=True )
 
-plt.plot( data21[0], data21[15]/1.99e33, label = '21' )
-plt.plot( data22[0], data22[15]/1.99e33, label = '22' )
-plt.plot( data23[0], data23[15]/1.99e33, label = '23' )
-plt.plot( data24[0], data24[15]/1.99e33, label = '24' )
-plt.plot( data25[0], data25[15]/1.99e33, label = '25' )
-plt.plot( data26[0], data26[15]/1.99e33, label = '26' )
[…]

### 2019-06-12 plotscripts/plot_MBTIGE_v_time.py

@@ -2,6 +2,8 @@ import matplotlib
 import matplotlib.pyplot as plt
 import numpy
 
+matplotlib.rc_file("ubuntu_matplotlibrc")
+
 # from Rich Townsend for mesa3
 params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
@@ -13,7 +15,7 @@ params = {'backend': 'pdf',
           'legend.fontsize': 8,
           'legend.frameon' : False,
 #          'text.usetex': True,
-#          'figure.dpi': 600,
+          'figure.dpi': 600,
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
@@ -29,6 +31,8 @@ BLUE       = (0.00,0.45,0.70)
 VERMILLION = (0.80,0.40,0.00)
 RED_PURPLE = (0.80,0.60,0.70)
 
+ax = plt.subplot(111)
+
 #CO
 
 data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
@@ -38,12 +42,12 @@ data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_2
 data29 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_29/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data30 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_30/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 
-plt.plot( data25[0], data25[13]/1.99e33, color = 'blue')
-plt.plot( data26[0], data26[13]/1.99e33, color = 'blue')
-plt.plot( data27[0], data27[13]/1.99e33, color = 'blue')
-plt.plot( data28[0], data28[13]/1.99e33, color = 'blue')
-plt.plot( data29[0], data29[13]/1.99e33, color = 'blue')
-plt.plot( data30[0], data30[13]/1.99e33, color = 'blue')
+plt.plot( data25[0], data25[13]/1.99e33, color = 'r', label = 'CO')
+plt.plot( data26[0], data26[13]/1.99e33, color = 'r')
[…]

### 2019-06-12 plotscripts/plot_RatioNi56IGE_v_time.py

@@ -2,6 +2,8 @@ import matplotlib
 import matplotlib.pyplot as plt
 import numpy
 
+matplotlib.rc_file("ubuntu_matplotlibrc")
+
 # from Rich Townsend for mesa3
 params = {'backend': 'pdf',
           'figure.figsize': [3.38, 3.38],
@@ -13,11 +15,13 @@ params = {'backend': 'pdf',
           'legend.fontsize': 8,
           'legend.frameon' : False,
 #          'text.usetex': True,
-#          'figure.dpi': 600,
+          'figure.dpi': 600,
           'lines.markersize': 4,
           'lines.linewidth': 1,
           'lines.antialiased': False,
-          'path.simplify': False }
+          'path.simplify': False,
+          # townsley below here
+          'legend.numpoints': 1}
 
 matplotlib.rcParams.update(params)
 
@@ -29,6 +33,7 @@ BLUE       = (0.00,0.45,0.70)
 VERMILLION = (0.80,0.40,0.00)
 RED_PURPLE = (0.80,0.60,0.70)
 
+ax = plt.subplot(111)
 
 data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_21/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_22/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
@@ -99,36 +104,40 @@ IGE29HY = data29HY[13]/1.99e33
 IGE30HY = data30HY[13]/1.99e33
 
 
+plt.plot( data21[0], mass21/IGE21, color = 'r', label = 'CO' )
+plt.plot( data22[0], mass22/IGE22, color = 'r')
+plt.plot( data23[0], mass23/IGE23, color = 'r')
+plt.plot( data24[0], mass24/IGE24, color = 'r')
+plt.plot( data25[0], mass25/IGE25, color = 'r')
+plt.plot( data26[0], mass26/IGE26, color = 'r')
+plt.plot( data27[0], mass27/IGE27, color = 'r')
+plt.plot( data28[0], mass28/IGE28, color = 'r')
[…]

### 2019-06-12 paper/ms.tex
address comments in beginning of results section

@@
 \citet{townetal2009,Meaketal09}.
+This assumption allows the fraction of IGEs in the form of $^{56}$Ni to be estimated from the $Y_e$ tracked by the burning model.
 
@@
 The cumulative distribution of the final \Ni{56} yield for explosions from
-C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
-results are shown in blue. The curve for the hybrid models is shifted
+C-O (red) and hybrid C-O-Ne (blue) models.
+The curve for the hybrid models is shifted
 to the left, indicating that explosions from hybrid progenitors produce
-less \Ni{56} than explosions from traditional C-O models.
+less \Ni{56} than explosions from traditional C-O models with the same central density.
 }
@@
 that the yields of \Ni{56} are consistently lower in explosions
-from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}
+from hybrid progenitors of the same central density.
+This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in W16.
+
+{\color{red} TODO: make table of average yields (like table 1 in W16).}
 
@@
 \includegraphics[width=\columnwidth]{figures/Hybrid_Ni56mass_v_time_plot.pdf}
-\caption{\label{fig:nithybrid}
-Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations.
-Shown are realizations 21-30.
-}
-\end{figure}
-\begin{figure}
 \includegraphics[width=\columnwidth]{figures/CO_Ni56mass_v_time_plot.pdf}
-\caption{\label{fig:nitco}
-Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
+\caption{\label{fig:nithybrid} \label{fig:nitco}
+Evolution of expected \Ni{56} yield in time for ten hybrid C-O-Ne WD (top panel) and ten C-O WD (bottom panel) explosion simulations.
 Shown are realizations 21-30.
@@
 
-The estimated production of \Ni{56} as a function of simulation time
-for 10 simulations of explosions from the hybrid progenitor is shown
-in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
-shown in Figure \ref{fig:nitco}.
-{\color{blue} The figures show that the final estimated \Ni{56} for
-  the C-O model is slightly larger than the hybrid model. Therefore,
-  the C-O produces more \Ni{56}. The hybrid model has a larger range
-  then the C-O model. [Figure \ref{fig:nithybrid} and Figure
-  \ref{fig:nitco} cannot support general claims like this because they
-  only show ten of our realizations and it's hard to measure by
-  eye. Figure \ref{fig:cumdist} is much better at demonstrating both
-  of these statements.]}
-Also, on average, the CO model reaches the DDT phase sooner then the
-hybrid model.  Both figures show that production of \Ni{56}
-effectively ceases (the curves flatten out) well before the end of the
-simulations at $4.0$~\second. Also, the figures show that a few
-simulations did not complete. {\color{red} OFFER A WHY?}
-
-\blust{The degree of expansion was found using the time at which the first
-detonation point occurred, and the mass at density greater than 2e7 g/cc. The
-estimated \Ni{56} Yield is the final estimated mass of the model.}
+The expected final production of \Ni{56} as a function of simulation time
+for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
+On average, the CO model reaches the DDT phase sooner then the
+hybrid model.
+A few simulations ended early, but after reaching their final yields, due to problematic physical conditions in the fluff.
+{\color{red}TODO: confirm.}
 
@@
 C-O-Ne progenitors are in red and C-O progenitors blue.
-{\color{red} SAME AS DON'S FIGURE 19}.
 %SAME AS DON'S FIGURE 19
@@
 %SAME AS DON'S FIGURE 20
-{\color{red} SAME AS DON'S FIGURE 20.}
 }

### 2019-06-14 paper/ms.tex
More work on results
I think I've got the discussion of IGE wrapped up.
Next need to tidy up the discussion of the Ni56/IGE ratio.

@@
 from hybrid progenitors of the same central density.
-This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in W16.
+This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in \cite{willcoxetal2016}.
 
-{\color{red} TODO: make table of average yields (like table 1 in W16).}
+{\color{red} TODO: make table of average yields (like table 1 in \cite{willcoxetal2016}).}
 
@@
 regions with $\pm1\sigma$ widths.
+Lighter shaded regions indicate the averages and standard deviations found by \citet{willcoxetal2016} for hybrid C-O-Ne progenitors that do not mix during cooling.
 
-As expected from previous studies, the trend for both C-O and C-O-Ne
+As expected from previous studies \citep[e.g.][]{townetal2009}, the trend for both C-O and C-O-Ne
 models is that less expansion during the deflagration phase results in
-greater IGE yields because less expansion allows the detonation to
-consume more high density fuel.
-As the amount of expansion increases (less
-mass remains above $2 \times 10^7~\grampercc$),
-for a similar amount of expansion, the C-O
-models tend to yield greater IGE mass. Following
+greater IGE yields.
+This is because less expansion allows the detonation to consume more high density fuel, which is burned more completely \citep{SeitenzahlTownsley2017}.
+At moderate expansion, where the mass at high density is between around 1.0 to 1.1 M$_\odot$, the C-O models tend to yield greater IGE mass.
+Following
 \citet{willcoxetal2016}, we interpret
 the lower IGE yield in C-O-Ne models as resulting
-from the lower \C{12} abundance and the fact that given
+from the lower \C{12} abundance and the fact that, given
 similar fuel density, the \Ne{20}-rich fuel will burn to cooler
@@
 slower burning to IGE and thus a lower IGE yield.
+At lower degrees of expansion, where there is around 1.2~M$_\odot$ of material at high densities, there appears to be little difference between the IGE yields of C-O and C-O-Ne progenetiors.
+This convergence for dense, weakly expanded, cases was not noted in \citet{willcoxetal2016} because they had very few cases with more than 1.1~M$_\odot$.
+It does appear consistent with an extrapolation of their data and the two cases that did yield these higher masses at high density.
+
+This convergence of IGE yield also appears strongly in comparing the averages over the whole set found in this study and that of \citet{willcoxetal2016}.
+As seen from the shaded regions in Figure \ref{fig:masshighdens} (lighter shade is unmixed), the degree of expansion seen for the our mixed progenitors is significantly less than for the unmixed cases.
+This results in more mass at high density in the mixed cases, leading to more similar IGE yields.
+The most likely reason for the weaker expansion is the higher central density necessary to ignite carbon burning with the lower central carbon fraction resulting from mixing during cooling \citep{brooksetal2017}.
+The increase in the IGE yield that results from this higher central density is negligible for the C-O case.
+This is consistent with the results of \citet{Kruegeretal2012}, who found that IGE yield is fairly independent of central density.
+The C-O-Ne case, however, appears to act very differently.
+The steepness of the relation between IGE yield and mass at high density is such that the mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016}.
+This increase closes the gap, making the resulting IGE yields similar.
+
+While the higher central density makes the IGE yields quite similar, the hybrid C-O-Ne WD still produces less $^{56}$Ni than a C-O WD at similar central densitiy.
+In order to understand this we looked more carefully at how the process of electron capture during the explosion proceeds in our simulations.
 
@@
 across the range of masses burned to IGE
-for all C-O and C-O-Ne realizations at the end
-of the simulations ($4.0 \second$),
-at which point the total mass burned to \Ni{56} had become constant.
+for all C-O and C-O-Ne realizations.
 The difference between the two sets of results is more pronounced

### 2019-06-17 paper/ms.tex
Finish cleanup in results section

@@
 \section{Methodology}
+\label{sec:method}
 
@@
 yields were estimated from $Y_e$ and the NSE progress
-variable, by assuming the composition in NSE is \Ni{56} plus equal
-parts \Fe{54} and \Ni{58}, as described in
-\citet{townetal2009,Meaketal09}.
+variable, by assuming the composition upon NSE freeze-out is \Ni{56} plus equal
+parts \Fe{54} and \Ni{58} \citep{townetal2009,Meaketal09}.
 This assumption allows the fraction of IGEs in the form of $^{56}$Ni to be estimated from the $Y_e$ tracked by the burning model.
@@
 
-The expected final production of \Ni{56} as a function of simulation time
+The expected final production of \Ni{56}, after NSE freeze-out, as a function of simulation time
 for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
@@
 time of the first DDT occurrence, with more high-density mass
-indicating less expansion during deflagration. The averages of both
+indicating less expansion during deflagration. The averages and standard deviations, $\sigma$, of both
 the C-O and C-O-Ne suites along both axes are indicated by the shaded
@@
 greater IGE yields.
-This is because less expansion allows the detonation to consume more high density fuel, which is burned more completely \citep{SeitenzahlTownsley2017}.
+This is because less expansion allows the detonation to consume more high density fuel, which is burned more completely \citep[See discussion in][and references therein]{SeitenzahlTownsley2017}.
 At moderate expansion, where the mass at high density is between around 1.0 to 1.1 M$_\odot$, the C-O models tend to yield greater IGE mass.
@@
 This results in more mass at high density in the mixed cases, leading to more similar IGE yields.
-The most likely reason for the weaker expansion is the higher central density necessary to ignite carbon burning with the lower central carbon fraction resulting from mixing during cooling \citep{brooksetal2017}.
+The most likely reason for the weaker expansion is the higher central density necessary to ignite carbon burning with the lower central carbon fraction resulting from mixing during cooling
+(\citealt{brooksetal2017}; Section \ref{sec:method} above).
 The increase in the IGE yield that results from this higher central density is negligible for the C-O case.
@@
 The C-O-Ne case, however, appears to act very differently.
-The steepness of the relation between IGE yield and mass at high density is such that the mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016}.
+The steepness of the relation between IGE yield and mass at high density is such that the mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016},
+shown as lines for comparison.
 This increase closes the gap, making the resulting IGE yields similar.
@@
 In order to understand this we looked more carefully at how the process of electron capture during the explosion proceeds in our simulations.
+While the mixed and unmixed progenitors have similar carbon fractions, the mixed progenitor explodes with a higher central density, as already mentioned.
+Another difference is that the mixed progenitor here does not show the off-center shell ignition that was found previously for the unmixed progenitor.
+Both of these appear to contribute to the difference in the final $^{56}$Ni yield.
 
@@
 than the difference between hybrid and traditional C/O models
-found by \citet{willcoxetal2016}. This difference follows from
-differences in the electron capture rates, which follow from
-{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
-MORE METALLICIY? HELP!}
-%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons.
-%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced.
-Figure 4 shows that CO model has a stronger electron capture then the hybrid model.
-The second is that the central ignition leads to early burning at higher density.
-Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
-%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
-%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
+found by \citet{willcoxetal2016}.
+The results found here, in which the carbon-poor compositions have a lower fractional $^{56}$Ni yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
+This movivates a closer inspection of how the $^{56}$Ni/IGE ratio evolves during the explosion.
 
@@
 \caption{\label{fig:compare_ratio}
-Plot of estimated \Ni{56} mass vs.\ time showing the evolution
-for both suites of simulations. Results from
-C-O-Ne progenitors are in red and C-O progenitors blue.
+Expected ratio of \Ni{56} to total IGE production by mass vs.\ time showing the evolution
+for both suites of simulations. Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
 %SAME AS DON'S FIGURE 19
@@
 for both suites of simulations. Results from C-O-Ne progenitors are
-in red and C-O progenitors blue.
+in blue and C-O progenitors red.
 Note that one of the C/O simulations presented did not complete.
@@
 
-Figure \ref{fig:compare_ratio} shows the fraction by mass of IGE
-material producing \Ni{56} as it evolves in time and Figure
-\ref{fig:compare_burned} shows the concurrent evolution of mass
-burned to IGE for both suites. While there is considerable
-scatter in the results, differences are obvious.
+The fraction, by mass, of IGE material expected to be in the form of $^{56}$Ni after freeze-out is shown in Figure \ref{fig:compare_ratio} as it evolves in time.
+Also shown in Figure~\ref{fig:compare_burned} is the concurrent evolution of mass burned to IGE for both suites.
+The total IGE has a mostly similar evolution, but the ratio demonstrates important differences between C-O and C-O-Ne cases.
 
 During the deflagration phase, the C-O models
-on average burn more material to IGE and also had a significantly higher
+on average burn slightly more material to IGE and also had a significantly higher
 fraction of IGE material that is \Ni{56}, yielding more \Ni{56} than
 the C-O-Ne models. This result is counter to that observed in
-\citet{willcoxetal2016}. During the detonation phase, the differences
-are not as obvious and the final mass of IGEs are comparable. The
-fraction of IGE material that is \Ni{56} at the end of the evolution,
-however, is significantly higher for C/O models than for our hybrid models.
-{\color{blue}This result differs from the results of
-  \citet{willcoxetal2016} as well and is consistent with the
-  observation that our hybrid models on average expand less during the
-  deflagration stage than our C/O models. By contrast, the hybrid models of
-  \citet{willcoxetal2016} expanded very slightly more
-  than C/O models on average during the deflagration stage.}
+\citet{willcoxetal2016}.
+In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of $^{56}$Ni through most of the deflagation phase.
+That difference was then closed during the detonation phase, to obtain similar ratios as seen in the lines above in Figure~\ref{fig:conversion}.
+A similar effect happens here during the detonation phase, but the fraction of material that is $^{56}$Ni stays higher for the C-O progenitors.
 
-We attribute these differences as following from the different
-compositions of the progenitors. The C-O-Ne hybrid progenitors
-had more neutron-rich material (a lower $Y_e$) than the
-traditional C-O models. As expected, when this material burns
-to IGEs, the proportion of neutron-rich material only gets
-higher, as the results demonstrate.
+The differences seen in the deflagration phase in Figure~\ref{fig:compare_ratio} appear to be critical.
+Central ignition at a higher central density leads to much more electron capture during the deflagration phase for the C-O-Ne case.
+Remarkably, up to around 0.5 seconds, no $^{56}$Ni is expected to be produced by the C-O-Ne progenitor.
+The comparison to the results of \citep{willcoxetal2016} indicate that the central ignition, in higher density regions, is important to this ignition.
+Comparing to the C-O progenitor here indicates that the lower energy release may also slow the rise of plumes, allowing more electron capture.
 
-The difference between these results and those of
-\citet{willcoxetal2016} follows from their hybrid C-O-Ne progenitors
-having a different temperature structure that
-led to ignition of the explosion at lower densities.
-The C-O models in the \citet{willcoxetal2016} study
-thus had more material burning at high densities and thus more
-neutronization and a lower relative \Ni{56} yield than the
-corresponding hybrid C-O-Ne models. In the case of the comparison here, the
-C-O and hybrid C-O-Ne models {\color{red} have the same central
-temperature and density and very similar temperature and density
-profiles at high densities, so the simulations in both cases
-began with central ignitions. Differences in the explosion outcomes
-for our C/O and hybrid C-O-Ne WD models
-accordingly follow from differences in their composition.}
+In conclusion, we attribute the following major differences from the progenitor treated here, which is mixed during cooling and centrally ignited, compared to the case in \citet{willcoxetal2016} that did not mix while cooling:
+The higher central density necessitated for ignition by the lower central carbon fraction leads to a higher production of IGE.
+The higher central density also leads to stronger electron capture.
+The off-center ignition used for the C-O-Ne progenitor in \citet{willcoxetal2016} appears to have suppressed electron capture due to the deflagration being more isolated to lower densities.
+Here we find that electron capture is noticably enhanced in the C-O-Ne case compared to C-O at the same density and ignition location.
+
+These features together indicate that explosions from C-O-Ne progenitors should have similar IGE yields to normal C-O progenitors but lower kinetic energies.
+This is due to their being higher central density, and therefore more tightly bound.
+At the same time, C-O-Ne explosions should show lower $^{56}$Ni yield due to enhanced electron capture during the deflagration.
 

### 2019-06-20 paper/ms.tex
Slight amendment to abstract for updated results
Address red text in method section
Note that the central density changed pretty significantly from what
I thought it was.  Will require some updates to other discussion that
are not done yet as of this commit.

@@
 central density required for ignition.
+We also find that the C-O-Ne cases computed here produce a smaller fraction of iron group elements in the form of $^{56}$Ni than found previously,
+a diferrence we attribute to both the central density and the location, center or off-center, of deflagration ignition.
 \end{abstract}
@@
 the effects of physics influencing the transition
-density~\citep{jacketal2010,Krueger2010On-Variations-o,kruegetal12}.
+density~\citep{jacketal2010,Krueger2010On-Variations-o,Kruegeretal2012}.
 
@@
 The simulations performed for this study consisted of a suite of
-{\color{red} 35 CHECK THIS! 40?} two-dimensional simulations of
+30 two-dimensional simulations of
 thermonuclear supernova
@@
 
-{\color{red} THE BELOW NUMBERS NEED SORTING OUT!}
-The C-O and C-O-Ne models has the same central temperature
-and density ????
-The C-O models had a central density and
-temperature of $4.62 \times 10^{9}$ $4.27 \times 10^{9}$ ???
-and $7 \times 10^8$~K, respectively.
-The C-O model had core composition of (\C{12} = 0.4,
-\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition
-of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48).
-The C-O models had a central density and
-temperature of $4.62 \times 10^{9}$
-and $8.07 \times 10^8$~K, respectively.
-The C-O-Ne model had core composition of (\C{12} = 0.X,
-\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition
-of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX).
-The profiles of the two-dimensional models match those of
-the one-dimensional models (shown in \figref{fig:init_conds})
-up to very slight errors from the mapping process. {\color{red}
-OMIT THIS LAST SENTENCE? DONT HAVE A FIGURE}
+The C-O and C-O-Ne models have the same central temperature
+and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
+The C-O model's composition consisted of \C{12}, \O{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
+The C-O-Ne model used in flash had composition consisting of \C{12}, \O{16}, \Ne{20}, and \Ne{22}.
+The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convectiov zone as shown in Figure~\ref{fig:init_conds}.
 
@@
 This resolution and geometry was used in previous studies
-allowing direct comparison to previous results~\citep{kruegetal12}.
+allowing direct comparison to previous results~\citep{Kruegeretal2012}.
 
 The ignition of the deflagration via a match head followed the
-initialization described in~\citet{kruegetal12}, which
+initialization described in~\citet{Kruegeretal2012}, which
 followed the method of~\citet{townetal2009}.
@@
 a different randomly-seeded perturbation was applied to the
-match head for each of the 35 simulations in both suites. {\color{red}
-IS THIS RIGHT- BOTH USED THE SAME REALIZATIONS?}
+match head for each of the 30 simulations in both suites,
 The perturbation to the sphere's surface is a set of
@@
 each set of perturbations is referred to as a ``realization."
+Both suites use the same 30 realizations of the ignition geometry.
 These perturbations have been shown to reproduce
@@
 is parameterized by the fuel density $\rho_{\mathrm{DDT}}$.
-When a rising
-plume reaches the threshold density, in this case
-$\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$,
-a $12$~\km\ region {\color{blue} [radius or diameter?]} of fuel, (\C{12} and \Ne{20}, if present) is
-fully burned $32$~\km\ radially outwards from the flame. This
+When a rising plume reaches the threshold density, in this case $\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$, a $12$~\km\ radius region of fuel, is fully burned $32$~\km\ radially outwards from the flame.
+This
 instantaneous burning in the region of this size provides conditions

### 2019-06-20 paper/ms.tex
Add table of yields and kinetic energies.

@@
 C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
+Average and standard deviations of the sample of yields and kinetic energies are given in Table~\ref{tab:ave_yields}.
 The figure shows that the hybrid models consistently have a higher
@@
 
-{\color{red} TODO: make table of average yields (like table 1 in \cite{willcoxetal2016}).}
+\begin{table}
+\caption{\label{tab:ave_yields}Average Yields and Kinetic Energies}
+\begin{tabular}{lccc}
+\hline
+Progenitor & $^{56}$Ni & IGE & Kinetic Energy \\
+ & ($M_\odot$) & ($M_\odot$) & ($10^{51}$~erg)\\
+\hline
+C--O     & $0.94\pm0.08$ & $1.14\pm0.08$ & $1.35\pm0.06$ \\
+C--O--Ne & $0.89\pm0.10$ & $1.15\pm0.11$ & $1.21\pm0.07$ \\
+\hline
+\end{tabular}
+\end{table}
 

### 2019-06-20 plotscripts/collect_ige_ni56_yields.py

@@ -1,47 +1,0 @@
-
-import numpy as np
-
-#import integral file
-filelistCO = []
-filelistHY = []
-for i in range(11,41):
-    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
-
-for i in range(11,41):
-    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
-
-#CO
-gpermsun = 1.988435e33
-a = []
-b = []
-for fname in filelistCO:
-	data = np.loadtxt(fname)
-	x = data[-1][13]
-	xsolar = x/gpermsun
-	a.append(xsolar)
-	y = data[-1][15]
-	ysolar = y/gpermsun
-	b.append(ysolar)
-
-#HY
-gpermsun = 1.988435e33
-c = []
-d = []
-for fname in filelistHY:
-	data = np.loadtxt(fname)
-	x = data[-1][13]
-	xsolar = x/gpermsun
-	c.append(xsolar)
-	y = data[-1][15]
-	ysolar = y/gpermsun
-	d.append(ysolar)
-
-print "# realization	CO_IGE	CO_Ni56	CONe_IGE	CONe_Ni56"
-for r in range(11,41):
-	i = r-11
-	print "%i\t%16.10e\t%16.10e\t%16.10e\t%16.10e"%(r,a[i],b[i],c[i],d[i])
-
-
-
-
-

### 2019-06-20 plotscripts/collect_ige_ni56_yields_KE.py

@@ -1,0 +1,62 @@
+
+import numpy as np
+
+#import integral file
+filelistCO = []
+filelistHY = []
+for i in range(11,41):
+    filelistCO.append("/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_%s/CO_WD_4km_cfbrooks_flash_2.dat" %i)
+
+for i in range(11,41):
+    filelistHY.append("/dmt/caugustine/Hybrid_Research/flash_runs/snia_%s_hybrid2/profile21_flash_h201.dat" %i)
+
+#CO
+gpermsun = 1.988435e33
+a = []
+b = []
+CO_KE = []
+for fname in filelistCO:
+	data = np.loadtxt(fname)
+	x = data[-1][13]
+	xsolar = x/gpermsun
+	a.append(xsolar)
+	y = data[-1][15]
+	ysolar = y/gpermsun
+	b.append(ysolar)
+	# ener + e_grav
+	CO_KE.append(data[-1][5]+data[-1][8])
+
+#HY
+gpermsun = 1.988435e33
+c = []
+d = []
+CONe_KE = []
+for fname in filelistHY:
+	data = np.loadtxt(fname)
+	x = data[-1][13]
+	xsolar = x/gpermsun
+	c.append(xsolar)
+	y = data[-1][15]
+	ysolar = y/gpermsun
+	d.append(ysolar)
+	# ener + e_grav
+	CONe_KE.append(data[-1][5]+data[-1][8])
+
+print "# realization	CO_IGE	CO_Ni56	CONe_IGE	CONe_Ni56	CO_KE	CONe_KE"
+for r in range(11,41):
+	i = r-11
+	print "%i\t%16.10e\t%16.10e\t%16.10e\t%16.10e\t%16.10e\t%16.10e"%(r,a[i],b[i],c[i],d[i],CO_KE[i],CONe_KE[i])
+
+# print averages and standard dev
+print "# Averages +/- standard deviations, Msun or ergs"
+print "#  CO   IGE : %16.10e +/- %16.10e"%(np.mean(a),np.std(a,ddof=1))
+print "#  CO   Ni56: %16.10e +/- %16.10e"%(np.mean(b),np.std(b,ddof=1))
+print "#  CONe IGE : %16.10e +/- %16.10e"%(np.mean(c),np.std(c,ddof=1))
[…]

### 2019-06-21 plotscripts/plot_cum_dis_ni56.py
Update data file name

@@ -35,7 +35,7 @@ ax = plt.subplot(111)
 
 
 #import data
-data = np.genfromtxt("yields_ige_ni56.dat", names=True)
+data = np.genfromtxt("yields_ige_ni56_KE.dat", names=True)
 
 #Hybrid Models
 a = data['CONe_Ni56']

### 2019-06-21 plotscripts/plot_ige_v_mass_at_high_dens.py

@@ -37,7 +37,7 @@ RED_PURPLE = (0.80,0.60,0.70)
 gpermsun = 1.988435e33 # grams/Msun
 
 #import data
-data = np.genfromtxt("yields_ige_ni56.dat", names=True)
+data = np.genfromtxt("yields_ige_ni56_KE.dat", names=True)
 
 CO_Mass_ddt =[ 2.17181312005e+33, 2.35383629797e+33, 1.64772923719e+33, 2.2114160575e+33, 2.37942340721e+33, 1.83455769713e+33, 2.04200699334e+33, 2.42116213051e+33, 1.95113390103e+33, 2.05317281172e+33, 2.3668519475e+33, 2.07355503262e+33, 1.61643166914e+33, 2.08306944193e+33, 1.84652547594e+33, 2.22696805867e+33, 2.33884296911e+33, 2.33105831045e+33, 2.1501133085e+33, 2.27996712031e+33, 2.27569091886e+33, 2.14242405809e+33, 1.97286525029e+33, 1.77937470081e+33, 2.33282821471e+33, 1.81892363218e+33, 2.3855754721e+33, 2.29943937023e+33, 2.08965708799e+33, 2.03270740927e+33]
 

### 2019-06-21 plotscripts/plot_ni56_v_ige.py

@@ -36,7 +36,7 @@ ax = plt.subplot(111)
 
 
 #import data
-data = np.genfromtxt("yields_ige_ni56.dat", names=True)
+data = np.genfromtxt("yields_ige_ni56_KE.dat", names=True)
 
 #CO
 a = data['CO_IGE']

### 2019-06-21 plotscripts/plot_ige_v_mass_at_high_dens.py
Put in actual numbers from Don for boxes on fig
previously had estimated from figure

@@ -137,15 +137,15 @@ plt.ylabel(r'IGE Yield (M$_\odot$)')
 ax1.add_patch(patches.Rectangle((xC/gpermsun, yC), 2*SDCOmass/gpermsun, 2*SDCOIGE, alpha=0.25,edgecolor='r',facecolor='r'))
 ax1.add_patch(patches.Rectangle((xH/gpermsun, yH), 2* SDHYmass/gpermsun, 2* SDHYIGE ,alpha=0.25,edgecolor='b',facecolor='b'))
 
-w16_cone_x = 0.5*(1.057+0.848)
-w16_cone_dx = 0.5*(1.057-0.848)
-w16_cone_y = 0.5*(1.087+0.865)
-w16_cone_dy = 0.5*(1.087-0.865)
+w16_cone_x = 0.9540876248262445
+w16_cone_dx = 0.10675480927655573
+w16_cone_y = 0.9770366094406242
+w16_cone_dy = 0.10747137261307173
 
-w16_co_x = 0.5*(1.062+0.858)
-w16_co_dx = 0.5*(1.062-0.858)
-w16_co_y = 0.5*(1.185+1.05)
-w16_co_dy = 0.5*(1.185-1.05)
+w16_co_x = 0.967452651967802
+w16_co_dx = 0.10484200298926964
+w16_co_y = 1.1193157785209684
+w16_co_dy = 0.06713166534619701
 
 ax1.add_patch(patches.Rectangle((w16_co_x-w16_co_dx,w16_co_y-w16_co_dy), 2*w16_co_dx, 2*w16_co_dy, alpha=0.1, edgecolor='r',facecolor='r', linestyle='--'))
 ax1.add_patch(patches.Rectangle((w16_cone_x-w16_cone_dx,w16_cone_y-w16_cone_dy), 2*w16_cone_dx, 2*w16_cone_dy, alpha=0.1, edgecolor='b',facecolor='b', linestyle='--'))

### 2019-06-21 paper/ms.tex
Fix up the results section for the central density
When I write the previous pass at the results discussion, I thought the
difference in central density between Don's runs and the current ones
was a lot bigger.

@@
 We also find that the C-O-Ne cases computed here produce a smaller fraction of iron group elements in the form of $^{56}$Ni than found previously,
-a diferrence we attribute to both the central density and the location, center or off-center, of deflagration ignition.
+a difference we attribute to both the central density and the location, center or off-center, of deflagration ignition.
 \end{abstract}
@@
 time of the first DDT occurrence, with more high-density mass
-indicating less expansion during deflagration. The averages and standard deviations, $\sigma$, of both
+indicating less expansion during deflagration \citep{townetal2009}.
+The averages and standard deviations, $\sigma$, of both
 the C-O and C-O-Ne suites along both axes are indicated by the shaded
 regions with $\pm1\sigma$ widths.
-Lighter shaded regions indicate the averages and standard deviations found by \citet{willcoxetal2016} for hybrid C-O-Ne progenitors that do not mix during cooling.
+Lighter shaded regions indicate the averages and standard deviations found by \citet{willcoxetal2016} for hybrid C-O-Ne progenitors that do not mix during cooling and for C--O progenitors with the same central density as them.
 
@@
 This is because less expansion allows the detonation to consume more high density fuel, which is burned more completely \citep[See discussion in][and references therein]{SeitenzahlTownsley2017}.
-At moderate expansion, where the mass at high density is between around 1.0 to 1.1 M$_\odot$, the C-O models tend to yield greater IGE mass.
+At moderate expansion, where the mass at high density is between around 1.0 to 1.1 M$_\odot$, our C-O models tend to yield greater IGE mass.
 Following
 \citet{willcoxetal2016}, we interpret
-the lower IGE yield in C-O-Ne models as resulting
+the lower IGE yield in C-O-Ne models in this range as resulting
 from the lower \C{12} abundance and the fact that, given
@@
 This convergence for dense, weakly expanded, cases was not noted in \citet{willcoxetal2016} because they had very few cases with more than 1.1~M$_\odot$.
-It does appear consistent with an extrapolation of their data and the two cases that did yield these higher masses at high density.
+It does appear consistent with an extrapolation of their data and their two cases that did yield these higher masses at high density.
 
@@
 As seen from the shaded regions in Figure \ref{fig:masshighdens} (lighter shade is unmixed), the degree of expansion seen for the our mixed progenitors is significantly less than for the unmixed cases.
-This results in more mass at high density in the mixed cases, leading to more similar IGE yields.
-The most likely reason for the weaker expansion is the higher central density necessary to ignite carbon burning with the lower central carbon fraction resulting from mixing during cooling
+This results in more mass at high density in the mixed cases, leading the C--O--Ne case to produce a similar amount of IGE, on average, to the C--O case.
+
+There are two major differences between the explosions computed in \citet{willcoxetal2016} and here.
+First, the central density of the progenitor that mixed during cooling is about 60\% higher than that of the unmixed one, $2.2\times10^9$~g~cm$^{-3}$ compared to $1.4\times 10^9$~g~cm$^{-3}$.
+This is due to the higher central density necessary to ignite carbon burning with the lower central carbon fraction resulting from mixing during cooling
 (\citealt{brooksetal2017}; Section \ref{sec:method} above).
+Second, while the case without mixing during cooling led to an off-center ignition of the deflagration, here the mixed case ignited at the center.
+We conclude that each of these contribute in specific ways to the differences between the results of mixed and unmixed progenitors.
+
+Since the mass at high density also increases with increasing central density for the C--O progenitor,
+it appears likely that the difference in central density is important for this increase in the C--O--Ne case as well.
+However, the increase in the mass at high density for the C--O--Ne case is more pronounced.
+This suggests that the central ignition also plays a role.
 The increase in the IGE yield that results from this higher central density is negligible for the C-O case.
@@
 The C-O-Ne case, however, appears to act very differently.
-The steepness of the relation between IGE yield and mass at high density is such that the mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016},
-shown as lines for comparison.
-This increase closes the gap, making the resulting IGE yields similar.
+The mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016}.
+This increase closes the gap, making the averag IGE yields from the C--O and C--O--Ne cases similar.
+The steeper dependence of IGE yield on expansion is partially responsible for this large change, in combination with the larger change in how much expansion happens in the C--O--Ne case.
+This supports both the central density and the location of ignition playing a role in bringing the explosions into a range where C--O and C--O--Ne cases produce similar amounts of IGE.
 
@@
 In order to understand this we looked more carefully at how the process of electron capture during the explosion proceeds in our simulations.
-While the mixed and unmixed progenitors have similar carbon fractions, the mixed progenitor explodes with a higher central density, as already mentioned.
-Another difference is that the mixed progenitor here does not show the off-center shell ignition that was found previously for the unmixed progenitor.
-Both of these appear to contribute to the difference in the final $^{56}$Ni yield.
+Again we find that both the central density of the progenitor and the location of ignition are important.
 
@@
 The difference between the two sets of results is more pronounced
-than the difference between hybrid and traditional C/O models
-found by \citet{willcoxetal2016}.
+than the difference between C--O--Ne and C--O models found by \citet{willcoxetal2016}.
 The results found here, in which the carbon-poor compositions have a lower fractional $^{56}$Ni yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
@@
 In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of $^{56}$Ni through most of the deflagation phase.
-That difference was then closed during the detonation phase, to obtain similar ratios as seen in the lines above in Figure~\ref{fig:conversion}.
+That difference was then closed during the detonation phase, to obtain similar ratios as seen in the lines in Figure~\ref{fig:conversion} above.
 A similar effect happens here during the detonation phase, but the fraction of material that is $^{56}$Ni stays higher for the C-O progenitors.
@@
 Remarkably, up to around 0.5 seconds, no $^{56}$Ni is expected to be produced by the C-O-Ne progenitor.
-The comparison to the results of \citep{willcoxetal2016} indicate that the central ignition, in higher density regions, is important to this ignition.
+The comparison to the results of \citep{willcoxetal2016} indicate that the central ignition, in higher density regions, is important to this outcome.
 Comparing to the C-O progenitor here indicates that the lower energy release may also slow the rise of plumes, allowing more electron capture.
 
-In conclusion, we attribute the following major differences from the progenitor treated here, which is mixed during cooling and centrally ignited, compared to the case in \citet{willcoxetal2016} that did not mix while cooling:
-The higher central density necessitated for ignition by the lower central carbon fraction leads to a higher production of IGE.
-The higher central density also leads to stronger electron capture.
+In conclusion, we attribute the following major differences to the progenitor treated here, which is mixed during cooling and centrally ignited, compared to the case in \citet{willcoxetal2016} that did not mix while cooling:
+The higher central density necessitated for ignition by the lower central carbon fraction leads to a higher production of IGE as well as stronger electron capture.
+Central ignition also enhances the production of IGE.
 The off-center ignition used for the C-O-Ne progenitor in \citet{willcoxetal2016} appears to have suppressed electron capture due to the deflagration being more isolated to lower densities.
@@
 These features together indicate that explosions from C-O-Ne progenitors should have similar IGE yields to normal C-O progenitors but lower kinetic energies.
-This is due to their being higher central density, and therefore more tightly bound.
 At the same time, C-O-Ne explosions should show lower $^{56}$Ni yield due to enhanced electron capture during the deflagration.

### 2019-06-24 paper/ms.tex
Work on the conclusions and a spell check.

@@
 The C-O-Ne model used in flash had composition consisting of \C{12}, \O{16}, \Ne{20}, and \Ne{22}.
-The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convectiov zone as shown in Figure~\ref{fig:init_conds}.
+The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.
 
@@
 slower burning to IGE and thus a lower IGE yield.
-At lower degrees of expansion, where there is around 1.2~M$_\odot$ of material at high densities, there appears to be little difference between the IGE yields of C-O and C-O-Ne progenetiors.
+At lower degrees of expansion, where there is around 1.2~M$_\odot$ of material at high densities, there appears to be little difference between the IGE yields of C-O and C-O-Ne progenitors.
 This convergence for dense, weakly expanded, cases was not noted in \citet{willcoxetal2016} because they had very few cases with more than 1.1~M$_\odot$.
@@
 The mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016}.
-This increase closes the gap, making the averag IGE yields from the C--O and C--O--Ne cases similar.
+This increase closes the gap, making the average IGE yields from the C--O and C--O--Ne cases similar.
 The steeper dependence of IGE yield on expansion is partially responsible for this large change, in combination with the larger change in how much expansion happens in the C--O--Ne case.
@@
 
-While the higher central density makes the IGE yields quite similar, the hybrid C-O-Ne WD still produces less $^{56}$Ni than a C-O WD at similar central densitiy.
+While the higher central density makes the IGE yields quite similar, the hybrid C-O-Ne WD still produces less $^{56}$Ni than a C-O WD at similar central density.
 In order to understand this we looked more carefully at how the process of electron capture during the explosion proceeds in our simulations.
@@
 The results found here, in which the carbon-poor compositions have a lower fractional $^{56}$Ni yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
-This movivates a closer inspection of how the $^{56}$Ni/IGE ratio evolves during the explosion.
+This motivates a closer inspection of how the $^{56}$Ni/IGE ratio evolves during the explosion.
 
@@
 \citet{willcoxetal2016}.
-In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of $^{56}$Ni through most of the deflagation phase.
+In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of $^{56}$Ni through most of the deflagration phase.
 That difference was then closed during the detonation phase, to obtain similar ratios as seen in the lines in Figure~\ref{fig:conversion} above.
@@
 
-In conclusion, we attribute the following major differences to the progenitor treated here, which is mixed during cooling and centrally ignited, compared to the case in \citet{willcoxetal2016} that did not mix while cooling:
+\section{Discussion and Conclusion}
+
+As mentioned above, we describe the results principally in term of the
+yield of the $^{56}$Ni, a proxy for brightness.  Our first conclusion
+is that hybrid progenitors that have experienced mixing during accretion are 
+viable progenitors for type Ia supernovae. $^{56}$Ni yields from simulations
+in DDT explosion paradigm are consistent with yields inferred from
+observations, roughly 0.6 \Msun.  There is of course considerable scatter
+in the results and as with other models in the DDT paradigm,
+these models produce more than 0.6 \Msun, the average being 0.89 \Msun,
+indicating these would correspond to very bright events.
+
+Going beyond the first-order, our simulations of explosions from
+these hybrid progenitors gave a lower \Ni{56} yield than from
+similar traditional C/O progenitors, a result expected from
+the earlier study of explosions from unmixed hybrid 
+progenitors~\citep{willcoxetal2016}. We also attribute this 
+difference to the lower C abundance in the hybrid progenitor than
+in the traditional progenitor.
+
+We were also able to compare the results from these mixed
+hybrid progenitors to those of the earlier unmixed progenitors.
+\citep{willcoxetal2016} reported that compared to the unmixed
+hybrid progenitors, C-O models consistently yielded a greater IGE mass. 
+They interpreted this result as following from 
+the lower \C{12} abundance in the hybrid models and the fact that \Ne{20}-rich fuel burns to cooler 
+temperatures than the fuel in traditional C-O models, which. results in slower burning and thus a lower
+overall IGE yield. Our yields from explosions from the mixed progenitors did not
+show the same diminution in IGE yield. We attribute this difference to the higher
+central density required for ignition of these mixed hybrid models.
+The results of explosions from the mixed hybrid models 
+produced a smaller fraction of IGEs in the form of $^{56}$Ni than the unmixed hybrid case, 
+and we attribute this difference 
+to both the central density and the location, center or off-center, of deflagration ignition,
+which determine the amount of electron capture during burning and hence the relative abundance
+of \Ni{56} to IGEs.
+
+To summarize our conclusions, we attribute the following major differences to the progenitor treated here, 
+which is mixed during cooling and centrally ignited, compared to the case in \citet{willcoxetal2016} 
+that did not mix while cooling:
+
+\begin{itemize}
+
+\item
 The higher central density necessitated for ignition by the lower central carbon fraction leads to a higher production of IGE as well as stronger electron capture.
 Central ignition also enhances the production of IGE.
+
+\item
 The off-center ignition used for the C-O-Ne progenitor in \citet{willcoxetal2016} appears to have suppressed electron capture due to the deflagration being more isolated to lower densities.
-Here we find that electron capture is noticably enhanced in the C-O-Ne case compared to C-O at the same density and ignition location.
-
+
+\item
+In these mixed hybrid models, electron capture is noticeably enhanced in the C-O-Ne case compared to C-O at the same density and ignition location.
+
+\item
 These features together indicate that explosions from C-O-Ne progenitors should have similar IGE yields to normal C-O progenitors but lower kinetic energies.
@@
 
-\section{Discussion and Conclusion}
-
-Below Rough:
-
-The new generation of C-O-Ne hybrid progenitor models explode similarly to
-traditional C-O models. We conclude they are viable progenitors.
-
-The new generation of C-O-Ne hybrid progenitor models yield
-slightly less \Ni{56}, which is actually in keeping with how
-the C-O models compare to observations. Our C-O models tend
-to produce enough \Ni{56} to imply bright events.
-
-More.....
+\end{itemize}
+
+The ``punch line'' of all this is that hybrid progenitors should produce dimmer
+explosions, but not as much difference as found in \citet{willcoxetal2016}. We
+\citep{willcoxetal2016}. We end by noting that the existence of these hybrid
+WDs is a recent state-of-the-art result from stellar evolution, but our understanding 
+and ability to model stellar evolution are far from complete. These results depend
+on the details of the convection and those details depend in turn on the
+presence of the convective Urca process, which is still an outstanding problem 
+subject to ongoing study \citep{calderetal2019,willcoxetal2019}.
 

### 2019-06-24 paper/ms.tex
Made text for C-O etc consistent between sections.

@@
 \begin{abstract}
-The creation of ``hybrid" white dwarfs, made of a C/O
-core within a O/Ne shell has been proposed, and studies indicate that
+The creation of ``hybrid" white dwarfs, made of a C-O
+core within a O-Ne shell has been proposed, and studies indicate that
 ignition in the C-rich central region makes these
 viable progenitors for thermonuclear (type Ia) supernovae.
-Recent work found that the C/O core is mixed with the surrounding O/Ne
+Recent work found that the C-O core is mixed with the surrounding O-Ne
 as the white dwarf cools prior to accretion, which results in lower central
@@
 condition for explosions simulated with \FLASH. For comparison, similar
-simulations were performed for a traditional C/O progenitor
+simulations were performed for a traditional C-O progenitor
 white dwarf. By comparing the yields of the explosions, we find that, as
 with earlier studies, the lower C abundance in the hybrid progenitor compared
-to the traditional C/O progenitor leads to a lower average yield of $^{56}$Ni.
+to the traditional C-O progenitor leads to a lower average yield of $^{56}$Ni.
 Although the unmixed hybrid WD showed a similar decrement also in total iron
@@
 late-time evolution of roughly 8 \Msun~stars indicate that under
-the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne
+the right circumstances, ``hybrid" white dwarfs having a C-O core surrounded by O-Ne
 mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
@@
 
-Hybrid WDs have more mass than traditional C/O WDs, with some studies indicating the
+Hybrid WDs have more mass than traditional C-O WDs, with some studies indicating the
 mass can approach 1.3 \Msun \citep{chenetal2014}. This increased mass
@@
 \Ni{56} yields on average and a trend of lower ejecta kinetic energy
-when compared to explosions from traditional C/O progenitors.
+when compared to explosions from traditional C-O progenitors.
 
@@
 from hybrid progenitors and compared the results to a suite of simulations
-of explosions from traditional C/O progenitor models performed with the
+of explosions from traditional C-O progenitor models performed with the
 same simulation code and from similar initial conditions. The simulations assumed
@@
 The hybrid model was constructed to have conditions as similar a possible
-to a ``classic'' C/O model and the two shared the same central temperature
+to a ``classic'' C-O model and the two shared the same central temperature
 and density.  Figure~\ref{fig:init_conds} shows the density and temperature
@@
 progenitor WD. The central temperature and density were the same as
-the traditional C/O progenitor model.
+the traditional C-O progenitor model.
 The peak temperature of the hybrid model is at the center of the star,
@@
 {\color{blue} We centrally ignite our explosion simulations for both
-  C/O and hybrid models to coincide with the peak temperature at the
+  C-O and hybrid models to coincide with the peak temperature at the
   center of the WDs, unlike the hybrid models
@@
 for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
-On average, the CO model reaches the DDT phase sooner then the
+On average, the C-O model reaches the DDT phase sooner then the
 hybrid model.
@@
 regions with $\pm1\sigma$ widths.
-Lighter shaded regions indicate the averages and standard deviations found by \citet{willcoxetal2016} for hybrid C-O-Ne progenitors that do not mix during cooling and for C--O progenitors with the same central density as them.
+Lighter shaded regions indicate the averages and standard deviations found by \citet{willcoxetal2016} for hybrid C-O-Ne progenitors that do not mix during cooling and for C-O progenitors with the same central density as them.
 
@@
 As seen from the shaded regions in Figure \ref{fig:masshighdens} (lighter shade is unmixed), the degree of expansion seen for the our mixed progenitors is significantly less than for the unmixed cases.
-This results in more mass at high density in the mixed cases, leading the C--O--Ne case to produce a similar amount of IGE, on average, to the C--O case.
+This results in more mass at high density in the mixed cases, leading the C-O-Ne case to produce a similar amount of IGE, on average, to the C-O case.
 
@@
 
-Since the mass at high density also increases with increasing central density for the C--O progenitor,
-it appears likely that the difference in central density is important for this increase in the C--O--Ne case as well.
-However, the increase in the mass at high density for the C--O--Ne case is more pronounced.
+Since the mass at high density also increases with increasing central density for the C-O progenitor,
+it appears likely that the difference in central density is important for this increase in the C-O-Ne case as well.
+However, the increase in the mass at high density for the C-O-Ne case is more pronounced.
 This suggests that the central ignition also plays a role.
@@
 The mean IGE yield found here is more than 0.15~M$_\odot$ larger than that found in \citet{willcoxetal2016}.
-This increase closes the gap, making the average IGE yields from the C--O and C--O--Ne cases similar.
-The steeper dependence of IGE yield on expansion is partially responsible for this large change, in combination with the larger change in how much expansion happens in the C--O--Ne case.
-This supports both the central density and the location of ignition playing a role in bringing the explosions into a range where C--O and C--O--Ne cases produce similar amounts of IGE.
+This increase closes the gap, making the average IGE yields from the C-O and C-O-Ne cases similar.
+The steeper dependence of IGE yield on expansion is partially responsible for this large change, in combination with the larger change in how much expansion happens in the C-O-Ne case.
+This supports both the central density and the location of ignition playing a role in bringing the explosions into a range where C-O and C-O-Ne cases produce similar amounts of IGE.
 
@@
 $t = 4.0 \second$.  Lines indicate corresponding relations found in W16 with
-a lower central density and CONe progenitor whose interior is not mixed
+a lower central density and C-O-Ne progenitor whose interior is not mixed
 during cooling.
@@
 The difference between the two sets of results is more pronounced
-than the difference between C--O--Ne and C--O models found by \citet{willcoxetal2016}.
+than the difference between C-O-Ne and C-O models found by \citet{willcoxetal2016}.
 The results found here, in which the carbon-poor compositions have a lower fractional $^{56}$Ni yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
@@
 in blue and C-O progenitors red.
-Note that one of the C/O simulations presented did not complete.
+Note that one of the C-O simulations presented did not complete.
 %SAME AS DON'S FIGURE 20
@@
 these hybrid progenitors gave a lower \Ni{56} yield than from
-similar traditional C/O progenitors, a result expected from
+similar traditional C-O progenitors, a result expected from
 the earlier study of explosions from unmixed hybrid 

### 2019-06-24 paper/ms.tex
More basic text editing to make things consistent.

@@
 with earlier studies, the lower C abundance in the hybrid progenitor compared
-to the traditional C-O progenitor leads to a lower average yield of $^{56}$Ni.
+to the traditional C-O progenitor leads to a lower average yield of \Ni{56}.
 Although the unmixed hybrid WD showed a similar decrement also in total iron
@@
 central density required for ignition.
-We also find that the C-O-Ne cases computed here produce a smaller fraction of iron group elements in the form of $^{56}$Ni than found previously,
+We also find that the C-O-Ne cases computed here produce a smaller fraction of iron group elements in the form of \Ni{56} than found previously,
 a difference we attribute to both the central density and the location, center or off-center, of deflagration ignition.
@@
 parts \Fe{54} and \Ni{58} \citep{townetal2009,Meaketal09}.
-This assumption allows the fraction of IGEs in the form of $^{56}$Ni to be estimated from the $Y_e$ tracked by the burning model.
+This assumption allows the fraction of IGEs in the form of \Ni{56} to be estimated from the $Y_e$ tracked by the burning model.
 
@@
 \hline
-Progenitor & $^{56}$Ni & IGE & Kinetic Energy \\
+%Progenitor & $^{56}$Ni & IGE & Kinetic Energy \\
+Progenitor & \Ni{56} & IGE & Kinetic Energy \\
  & ($M_\odot$) & ($M_\odot$) & ($10^{51}$~erg)\\
@@
 
-While the higher central density makes the IGE yields quite similar, the hybrid C-O-Ne WD still produces less $^{56}$Ni than a C-O WD at similar central density.
+While the higher central density makes the IGE yields quite similar, the hybrid C-O-Ne WD still produces less \Ni{56} than a C-O WD at similar central density.
 In order to understand this we looked more carefully at how the process of electron capture during the explosion proceeds in our simulations.
@@
 than the difference between C-O-Ne and C-O models found by \citet{willcoxetal2016}.
-The results found here, in which the carbon-poor compositions have a lower fractional $^{56}$Ni yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
-This motivates a closer inspection of how the $^{56}$Ni/IGE ratio evolves during the explosion.
+The results found here, in which the carbon-poor compositions have a lower fractional \Ni{56} yield, are more consistent with the expectation for a lower peak burning temperature with lower C abundance.
+This motivates a closer inspection of how the \Ni{56}/IGE ratio evolves during the explosion.
 
@@
 
-The fraction, by mass, of IGE material expected to be in the form of $^{56}$Ni after freeze-out is shown in Figure \ref{fig:compare_ratio} as it evolves in time.
+The fraction, by mass, of IGE material expected to be in the form of \Ni{56} after freeze-out is shown in Figure \ref{fig:compare_ratio} as it evolves in time.
 Also shown in Figure~\ref{fig:compare_burned} is the concurrent evolution of mass burned to IGE for both suites.
@@
 \citet{willcoxetal2016}.
-In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of $^{56}$Ni through most of the deflagration phase.
+In that work, with a lower density progenitor with a deflagration ignited off-center, the C-O mostly showed a smaller fraction of IGE in the form of \Ni{56} through most of the deflagration phase.
 That difference was then closed during the detonation phase, to obtain similar ratios as seen in the lines in Figure~\ref{fig:conversion} above.
-A similar effect happens here during the detonation phase, but the fraction of material that is $^{56}$Ni stays higher for the C-O progenitors.
+A similar effect happens here during the detonation phase, but the fraction of material that is \Ni{56} stays higher for the C-O progenitors.
 
@@
 Central ignition at a higher central density leads to much more electron capture during the deflagration phase for the C-O-Ne case.
-Remarkably, up to around 0.5 seconds, no $^{56}$Ni is expected to be produced by the C-O-Ne progenitor.
+Remarkably, up to around 0.5 seconds, no \Ni{56} is expected to be produced by the C-O-Ne progenitor.
 The comparison to the results of \citep{willcoxetal2016} indicate that the central ignition, in higher density regions, is important to this outcome.
@@
 As mentioned above, we describe the results principally in term of the
-yield of the $^{56}$Ni, a proxy for brightness.  Our first conclusion
+yield of the \Ni{56}, a proxy for brightness.  Our first conclusion
 is that hybrid progenitors that have experienced mixing during accretion are 
-viable progenitors for type Ia supernovae. $^{56}$Ni yields from simulations
+viable progenitors for type Ia supernovae. \Ni{56} yields from simulations
 in DDT explosion paradigm are consistent with yields inferred from
@@
 The results of explosions from the mixed hybrid models 
-produced a smaller fraction of IGEs in the form of $^{56}$Ni than the unmixed hybrid case, 
+produced a smaller fraction of IGEs in the form of \Ni{56} than the unmixed hybrid case, 
 and we attribute this difference 
@@
 These features together indicate that explosions from C-O-Ne progenitors should have similar IGE yields to normal C-O progenitors but lower kinetic energies.
-At the same time, C-O-Ne explosions should show lower $^{56}$Ni yield due to enhanced electron capture during the deflagration.
+At the same time, C-O-Ne explosions should show lower \Ni{56} yield due to enhanced electron capture during the deflagration.
 

### 2019-06-26 paper/ms.tex
Went though the paper and fixed a good few things. Picked off some of the questions in blue or red text and in so doing added a little text and citations. Updated the references and fixed a few typos.

@@
 perlmutter.aldering.ea:measurements,leibundgut2001}, and these events
-remain the premier distance indicators for cosmological studies {\color{red} REF?}.
+remain critical distance indicators for cosmological studies~\citep{weinbergetal2013}.
 The special property of the light curve is thought to follow
 from the fact that the source of luminosity, the radioactive decay
-of \Ni{56}, synthesized by the thermonuclear burning, is also the
+of \Ni{56} synthesized by the thermonuclear burning, is also the
 principal source of opacity~\citep{Pinto2001The-type-Ia-sup}, giving
@@
 period of accretion combined with either steady burning or a
-series of nova explosions. {\color{blue} During this accretion phase, the WD must} gain at least
+series of nova explosions. During this accretion phase, a traditional
+C-O WD must gain at least
 $\sim 0.4$ \Msun\ as needed for it to approach the
@@
 A particular problem was that most models included a massive He layer on
-the white dwarf. Such a configuration leads to the unobserved result that
+the white dwarf. Such a configuration leads to the result that
 intermediate and heavy elements synthesized in the He detonation appear in
@@
 
-Subsequent work allayed this concern {\color{blue} [we should probably mention how]}
-~\citep{yoonetal2007,lorenaguilaretal2009, Shenetal12, pakmoretal2012b}
+Subsequent work allayed this concern {\color{blue} by demonstrating
+that a low accretion rate from the disrupted secondary, $ < 3 \times 
+10^{-6}$ \Msun per year, did not heat the primary enough for ignition}
+~\citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
+Shenetal12, pakmoretal2012b}
 and active research continues, motivated by the need to explain bright events
@@
 amount of included physics and full three-dimensional simulations
-albeit with less included physics~\citep{caldertownsley2018}.
+albeit with less included physics~\citep[][and references therein]{caldertownsley2018}.
 In the area of stellar evolution, recent investigations revisiting
@@
 results depend on assumptions about convective
-overshoot that have been questioned {\color{blue} [questioned for what reasons?]} \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.
+overshoot that have been questioned~\citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.
 
@@
 
-In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, which will
-make the core-mantle interface subject to convective
-instability \citep{brooksetal2017,schwabgaraud2018}.
-{\color{blue} [can we say a bit more about how this cooling-caused instability works?]}
+In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, 
+which will reduce the stabilizing temperature gradient (the O-Ne layer is hotter 
+than the C-O core) and allow the unstable composition gradient to drive 
+thermocompositional convection~\citep{brooksetal2017,schwabgaraud2019}.
 In the case of the
@@
 heat the core and start C fusion, leading to a period of ``simmering" prior
-to the explosion \citep{PiroBild08}. The upshot is that there is likely to be considerable
-mixing after the hybrid forms that may homogenize the composition
-\citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.
+to the explosion, also mixing the interior \citep{PiroBild08}. The upshot is 
+that there is likely to be considerable mixing after the hybrid forms that will 
+homogenize the composition \citep{denissenkovetal2015,brooksetal2017,schwabgaraud2019}.
 
@@
 the \MESA\ model to a uniform grid of $4$~km resolution.
-{\color{blue}We mass-weighted and averaged quantities in \MESA\ zones with spacing less than $4$~km
-and quadratically interpolated quantities in \MESA\ zones with spacing greater than $4$~km.}
+{\color{blue}To do this, \MESA\ quantities were mass-weighted and averaged in zones with spacing less than $4$~km
+and quadratically interpolated in zones with spacing greater than $4$~km.}
 At this point,
@@
 composition, and the mass below and enclosed by the zone. As
-with \citet{willcoxetal2016} we used the EOS routine from
+with \citet{willcoxetal2016}, we used the EOS routine from
 \CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
@@
   \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
-  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As
- with the models in \citet{willcoxetal2016}, this procedure produced
- a structure that was stable in \FLASH, with fluctuations in central
-density less than $3\%$, for at least $5$ seconds with no energy
-deposition.
+  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} 
+This procedure produced a structure that was stable in \FLASH, with 
+fluctuations in central density less than $3\%$, for at least $5$ 
+seconds with no energy deposition.
 
@@
 the expanding star reaches low densities at which point burning
-effectively ends. The paragraphs in this section provide details
+effectively ends. This section provide details
 of the implementation of this method.
@@
 and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
-The C-O model's composition consisted of \C{12}, \O{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
-The C-O-Ne model used in flash had composition consisting of \C{12}, \O{16}, \Ne{20}, and \Ne{22}.
+The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
+The C-O-Ne model used in flash had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
 The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.
@@
 hybrid model.
-A few simulations ended early, but after reaching their final yields, due to problematic physical conditions in the fluff.
-{\color{red}TODO: confirm.}
+A few simulations ended early, but after reaching their final yields. We attribute
+these occurences as being due to problematic physical conditions in the ``fluff," the
+low-density gas on the grid outside of the star. {\color{red}TODO: confirm if
+possible. If not, leave as is, which is speculative.}
 
@@
 $\pm 1 \sigma$ along each axis and centered at their average values
-for C-O and C-O-Ne.  Similar rectangles found in W16 for a progenitor without
+for C-O and C-O-Ne.  Similar rectangles found in \citet{willcoxetal2016} for a progenitor without
 mixing during cooling are shown in a lighter shade with dashed borders.
@@
 
+Comparing the relative abundances of \Ni{56} to IGE between the
+mixed hybrid progenitors and traditional C-O models indicated
+substantial differences, with the hybrid progenitors producing
+a lower ratio of \Ni{56} to IGEs. This difference was particularly
+pronounced during the deflagration phase of the explosion, and 
+from that we conclude that the evolution of high-density material
+and the amount of neutronization during the burning at high densities
+is critical to the evolution and outcome of the explosion.
+
 We were also able to compare the results from these mixed
 hybrid progenitors to those of the earlier unmixed progenitors.
-\citep{willcoxetal2016} reported that compared to the unmixed
+\citet{willcoxetal2016} reported that compared to the unmixed
 hybrid progenitors, C-O models consistently yielded a greater IGE mass. 

### 2019-07-06 paper/ms.tex
Merged sentences in the abstract to avoid redundancy.

@@
 to the traditional C-O progenitor leads to a lower average yield of \Ni{56}.
-Although the unmixed hybrid WD showed a similar decrement also in total iron
-group yield, the mixed case does not.  We attribute this to the higher
-central density required for ignition.
-We also find that the C-O-Ne cases computed here produce a smaller fraction of iron group elements in the form of \Ni{56} than found previously,
-a difference we attribute to both the central density and the location, center or off-center, of deflagration ignition.
+{\color{blue}Although the unmixed hybrid WD showed a similar decrement also in total iron
+group yield, the mixed case does not and produces a smaller fraction of iron group elements in the form of \Ni{56}.
+We attribute this to the higher central density required for ignition and the location, center or off-center, of deflagration ignition.}
 \end{abstract}

### 2019-07-06 paper/ms.tex
either -> any since cooling will occur after formation of the hybrid WD regardless which SNIa progenitor channel (if any) it is in.

@@
 
-In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, 
+In any case, the hybrid WD will experience a period of cooling,
 which will reduce the stabilizing temperature gradient (the O-Ne layer is hotter 

### 2019-07-06 paper/ms.tex
Add MarginPar command. Comment on verification tests. Willcox+ 2016 did not actually present a comparison of values obtained from the FLASH burning module to values obtained from Torch. We used Torch to guide our modification to the FLASH burning module. So I do not think we can call this a verification test.

@@
 %\usepackage{hyperref}
+
+\setlength{\marginparwidth}{0.5in}
+\newcommand{\MarginPar}[1]{\marginpar{\vskip-\baselineskip\raggedright\tiny\sffamily\hrule\smallskip{\color{red}#1}\par\smallskip\hrule}}
 
@@
 of the \FLASH\ Code, as \citet{willcoxetal2016} and we refer the reader there
-for a description of modifications for C-O-Ne burning and verification tests
-of the burning module.
+for a description of modifications for C-O-Ne burning \blust{and verification tests
+of the burning module}. \MarginPar{See below}
 
@@
 the modifications, details of the modifications to the burning model, and
-verification tests may be found in \citet{willcoxetal2016}.
+\blust{verification tests} may be found in \citet{willcoxetal2016}. \MarginPar{Strictly speaking, that paper did not have quantitative verification tests of the FLASH burning module.}
 

### 2019-07-06 paper/ms.tex
Accept text.

@@
 \end{figure}
-{\color{blue} We centrally ignite our explosion simulations for both
-  C-O and hybrid models to coincide with the peak temperature at the
-  center of the WDs, unlike the hybrid models
-  of~\citet{willcoxetal2016}.}
+We centrally ignite our explosion simulations for both C-O and hybrid
+models to coincide with the peak temperature at the center of the WDs,
+unlike the hybrid models of~\citet{willcoxetal2016}.
 

### 2019-07-06 paper/ms.tex
Reword Fig 1 caption a bit for clarity.

@@
 \caption{\label{fig:init_conds}
-Temperature, density, and  composition profiles of the one-dimensional hybrid
+{\color{blue} Radial} temperature, density, and  composition profiles of the one-dimensional hybrid
 progenitor WD. The central temperature and density were the same as
@@
 The peak temperature of the hybrid model is at the center of the star,
-so both the hybrid and traditional models could share the same
-	central ignition initial conditions.
+so both the hybrid and {\color{blue} C-O}  models could share the same
+	central ignition initial conditions {\color{blue} in our simulations}.
 }

### 2019-07-06 paper/ms.tex
flash->FLASH.
citet->citep

@@
 The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
-The C-O-Ne model used in flash had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
+The C-O-Ne model used in \FLASH\ had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
 The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.
@@
 the scatter in \Ni{56}
-yield from \SNeIa\ \citet{townetal2009}.
+yield from \SNeIa\ \citep{townetal2009}.
 

### 2019-07-15 paper/ms.tex
Update figures with complete time series
There were three runs displayed that had stopped early.
I finished the runs, generally by changing the refinement settings a bit.

@@
 hybrid model.
-A few simulations ended early, but after reaching their final yields. We attribute
-these occurences as being due to problematic physical conditions in the ``fluff," the
-low-density gas on the grid outside of the star. {\color{red}TODO: confirm if
-possible. If not, leave as is, which is speculative.}
 
@@
 Plot of estimated mass burned to IGEs vs.\ time showing the evolution
-for both suites of simulations. Results from C-O-Ne progenitors are
+for both suites of simulations for realizations 25-30. Results from C-O-Ne progenitors are
 in blue and C-O progenitors red.
-Note that one of the C-O simulations presented did not complete.
 %SAME AS DON'S FIGURE 20

### 2019-07-15 plotscripts/21_30_plot_CO.py

@@ -38,7 +38,7 @@ data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_2
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_22/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data23 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_23/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data24 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_24/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
-data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data25 = numpy.genfromtxt( '/dmt/townsley/mixed_hybrid_wd_snia/finish_runs/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data26 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_26/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data27 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_27/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_28/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )

### 2019-07-15 plotscripts/21_30_plot_Hybrid.py

@@ -34,10 +34,10 @@ RED_PURPLE = (0.80,0.60,0.70)
 
 ax = plt.subplot(111)
 
-data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_21_hybrid2/profile21_flash_h201.dat', unpack=True )
+data21 = numpy.genfromtxt( '/dmt/townsley/mixed_hybrid_wd_snia/finish_runs/snia_21_hybrid2/profile21_flash_h201.dat', unpack=True )
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_22_hybrid2/profile21_flash_h201.dat', unpack=True )
 data23 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_23_hybrid2/profile21_flash_h201.dat', unpack=True )
-data24 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_24_hybrid2/profile21_flash_h201.dat', unpack=True )
+data24 = numpy.genfromtxt( '/dmt/townsley/mixed_hybrid_wd_snia/finish_runs/snia_24_hybrid2/profile21_flash_h201.dat', unpack=True )
 data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_25_hybrid2/profile21_flash_h201.dat', unpack=True )
 data26 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_26_hybrid2/profile21_flash_h201.dat', unpack=True )
 data27 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_27_hybrid2/profile21_flash_h201.dat', unpack=True )

### 2019-07-15 plotscripts/plot_MBTIGE_v_time.py

@@ -35,7 +35,7 @@ ax = plt.subplot(111)
 
 #CO
 
-data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data25 = numpy.genfromtxt( '/dmt/townsley/mixed_hybrid_wd_snia/finish_runs/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data26 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_26/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data27 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_27/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_28/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )

### 2019-07-15 plotscripts/plot_RatioNi56IGE_v_time.py

@@ -39,7 +39,7 @@ data21 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_2
 data22 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_22/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data23 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_23/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data24 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_24/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
-data25 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
+data25 = numpy.genfromtxt( '/dmt/townsley/mixed_hybrid_wd_snia/finish_runs/snia_25/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data26 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_26/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data27 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_27/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 data28 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_28/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
@@ -47,10 +47,10 @@ data29 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_2
 data30 = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs_CO/snia_30/CO_WD_4km_cfbrooks_flash_2.dat', unpack=True )
 
 
-data21HY = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_21_hybrid2/profile21_flash_h201.dat', unpack=True )
[…]

### 2019-07-15 paper/ms.tex
Basic tidying pass through the intro.  good now.
Mostly small adjustments and some added references.
Changed the wording so that we are not implying that hybrids can't
appear as double-detonations.  Just don't say anything either way
and stick with mentioning work that is in the literature.

@@
 to the traditional C-O progenitor leads to a lower average yield of \Ni{56}.
-{\color{blue}Although the unmixed hybrid WD showed a similar decrement also in total iron
+Although the unmixed hybrid WD showed a similar decrement also in total iron
 group yield, the mixed case does not and produces a smaller fraction of iron group elements in the form of \Ni{56}.
-We attribute this to the higher central density required for ignition and the location, center or off-center, of deflagration ignition.}
+We attribute this to the higher central density required for ignition and the location, center or off-center, of deflagration ignition.
 \end{abstract}
@@
 the light curves of these events have a special property that allows
-standardization \blust{of their light curves and thus use}
+standardization
 as distance indicators for cosmological studies~\citep{phillips:absolute}.
@@
 We briefly describe these in the subsection that follows.
-Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
+Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,SeitenzahlTownsley2017,roepkesim2018}
 for additional discussion.
@@
 that best reproduce the observed stratified ejecta are those in which
-the burning begins as a subsonic deflagration, {\color{blue} allowing the star
-to expand to lower densities in response, followed} by a
+the burning begins as a subsonic deflagration, allowing the star
+to expand to lower densities in response, followed by a
 supersonic detonation that incinerates the
@@
 moniker ``sub-Chandrasekhar'' \citep{ww94}.
-{\color{blue} Follow-up multidimensional calculations}
+Follow-up multidimensional calculations
 supported the
@@
 further research~\citep{simetal2012,brooksetal2015, shenetal2018,
-glasneretal2018}.
+glasneretal2018,Townsleyetal2019}.
 
@@
 
-Subsequent work allayed this concern {\color{blue} by demonstrating
+Subsequent work allayed this concern by demonstrating
 that a low accretion rate from the disrupted secondary, $ < 3 \times 
-10^{-6}$ \Msun per year, did not heat the primary enough for ignition}
-~\citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
+10^{-6}$ \Msun per year, did not heat the primary enough for ignition
+\citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
 Shenetal12, pakmoretal2012b}
@@
 
-A hybrid WD can become a progenitor of a thermonuclear supernova via two
-of the progenitor scenarios discussed in Section \ref{sec:progenitors}.
-First, the hybrid could be part of a binary system in which the companion star becomes
+A hybrid WD can then become a progenitor of a thermonuclear supernova.
+The hybrid could be part of a binary system in which the companion star becomes
 another white dwarf and the two merge. Recent population synthesis work supports
 this pathway by indicating a substantial contribution to the Ia population rate from
-mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. Second, if the hybrid
+mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. If, on the other hand, the hybrid
 WD is part of a binary with a main sequence or giant companion, it can gain mass and
 approach the Chandrasekhar mass, i.e.\  the single degenerate picture~\citep{willcoxetal2016}.
-{\color{red} COULD NOT FIND ANY EVIDENCE OF HYBRIDS IN THE SUBCHANDRA PATH. SAY
-SOMETHING?}
 
 In any case, the hybrid WD will experience a period of cooling,
-which will reduce the stabilizing temperature gradient (the O-Ne layer is hotter 
+which will reduce the stabilizing temperature gradient (the O-Ne layer is initially hotter 
 than the C-O core) and allow the unstable composition gradient to drive 
-thermocompositional convection~\citep{brooksetal2017,schwabgaraud2019}.
+thermo-compositional convection~\citep{brooksetal2017,schwabgaraud2019}.
 In the case of the
@@
 relatively short delay times. They also suggested that these
-may produce part of the Iax class of events. \citet{Wangetal2014} also with population
-synthesis studied the case
+may produce part of the Iax class of events. \citet{Wangetal2014}, also with population
+synthesis, studied the case
 %received august 28 accepted sept 26
@@
 such as SN 2008ha~\citep{foleyetal2009}.
+Interpretation of these results are made challenging by their use of a progenitor in which no mixing has occurred, not even that expected due to simmering.
 \citet{bravoetal2016} performed one-dimensional simulations of explosions from
@@
 when compared to explosions from traditional C-O progenitors.
+We will compare to the work of \citet{willcoxetal2016} extensively below.
+They did not allow for the mixing of the WD during cooling, before ignition of carbon burning.
+Here we utilize progenitors in which mixing during cooling has been modeled appropriately \citep{brooksetal2017}.
 

### 2019-07-16 paper/ms.tex
Finalizing edits to methodology.
Notably removed use of the word "verification" per Don's request.

@@
 of the \FLASH\ Code, as \citet{willcoxetal2016} and we refer the reader there
-for a description of modifications for C-O-Ne burning \blust{and verification tests
-of the burning module}. \MarginPar{See below}
+for a description of the process and treatment of burning of C--O--Ne fuel and how it differs from C--O fuel.
 
@@
 simultaneously resolve the nuclear flame, so simulations require a model to
-describe the burning on unresovable scales.  The model we apply is a flame
+describe the burning on unresolved scales.  The model we apply is a flame
 capturing scheme and thermally-activated burning module to describe
@@
 balance.
-{\color{blue} Electron capture also influences the evolution in several ways by
+Electron capture also influences the evolution in several ways by
 neutronizing the material, which produces more neutron rich iron-group
@@
 Finally, individual electron capture reactions emit neutrinos that
-escape and remove energy from the system.}
+escape and remove energy from the system.
 Like the input flame speed, the burning model includes tabulated rates for these effects
@@
 we again note that the burning model was adapted for the case of burning in
-hybrid white dwarfs. Direct numerical simulations of burning that guided
-the modifications, details of the modifications to the burning model, and
-\blust{verification tests} may be found in \citet{willcoxetal2016}. \MarginPar{Strictly speaking, that paper did not have quantitative verification tests of the FLASH burning module.}
+hybrid white dwarfs.
+Direct numerical simulations of combustion dynamics and details of how the burning model is used to capture them may be found in \citet{willcoxetal2016}.
 
@@
 included thermohalene mixing during the cooling phase and thus
-had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
+had a lower central C fraction than previous hybrid models~\citep{brooksetal2017}.
 The hybrid model was constructed to have conditions as similar a possible
@@
 \caption{\label{fig:init_conds}
-{\color{blue} Radial} temperature, density, and  composition profiles of the one-dimensional hybrid
+Radial temperature, density, and  composition profiles of the one-dimensional hybrid
 progenitor WD. The central temperature and density were the same as
@@
 The peak temperature of the hybrid model is at the center of the star,
-so both the hybrid and {\color{blue} C-O}  models could share the same
-	central ignition initial conditions {\color{blue} in our simulations}.
+so both the hybrid and C--O models could share the same central ignition initial conditions in our simulations.
+{\color{red} TODO: make figure style consistent with other figures.}
 }
@@
 the \MESA\ model to a uniform grid of $4$~km resolution.
-{\color{blue}To do this, \MESA\ quantities were mass-weighted and averaged in zones with spacing less than $4$~km
-and quadratically interpolated in zones with spacing greater than $4$~km.}
+To do this, \MESA\ quantities were mass-weighted and averaged in zones with spacing less than $4$~km
+and interpolated in zones with spacing greater than $4$~km.
 At this point,
@@
 
-The simulations were performed in two-dimensional $\mathrm{z-r}$
+The simulations were performed in two-dimensional $r$-$z$
 cylindrical coordinates, extending radially from 0 to
@@
 high enough for the detonation to propagate is quickly consumed.
-The simulations were run to 4.0 s, at which time burning
+The simulations were run to 4.0 s, by which time burning
 has effectively ceased.

### 2019-07-16 plotscripts/plot_temp_dens_abund.py
Add plotscript for progenitor profiles
I think this is the form used for the current figure 1.
Will shortly be amended for style consistency with other figures.

@@ -1,0 +1,50 @@
+import matplotlib
+matplotlib.use("TkAgg")
+import matplotlib.pyplot as plt
+import numpy
+
+dc = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_research/wdbuilder/WDBuilder_SNIa-ddt/CO_WD_4km_cfbrooks_flash_pro12.dat',
+	skip_header=2, names=('radius','density','temperature','c12','ne22') )
+
+dh = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_10_hybrid2/400k_flash_21new.dat',
+	skip_header=2, names=('radius','density','temperature','c12','ne20','ne22') )
+
+fig, (axtop, axbot) = plt.subplots(nrows=2)
+
+axtop2 = axtop.twinx()
+
+Rsun = 6.9598e10
+
+axtop.semilogy(dc['radius'],dc['temperature'], color='black', linestyle='-', label='T')
+axtop.semilogy( dh['radius'],dh['temperature'], color='black', linestyle='--', label='hybrid')
+
+axtop2.semilogy(dc['radius'],dc['density'], 'r-', label='dens')
+axtop2.semilogy( dh['radius'],dh['density'], 'r--')
+
+axtop.legend(loc='best')
+axtop2.legend(loc='best')
+
+
+#axbot.semilogy(Rsun*10**dm['logR'],10**dm['log_he4'], color='black', linestyle='-', label='He4')
+#axbot.semilogy( du['radius'],du['he4'], color='black', linestyle='--')
+
+#axbot.semilogy(Rsun*10**dm['logR'],10**dm['log_n14'], 'g-', label='N14')
+#axbot.semilogy( du['radius'],du['n14'], 'g--')
+
+axbot.semilogy(dc['radius'],dc['c12'], 'r-', label='C12')
+axbot.semilogy( dh['radius'],dh['c12'], 'r--')
+
+axbot.semilogy( dc['radius'],1.0-dc['c12']-dc['ne22'], 'c-', label='O16')
+axbot.semilogy( dh['radius'],1.0-dh['c12']-dh['ne20']-dh['ne22'], 'c--')
+
+axbot.semilogy( dc['radius'],0.0*dc['ne22'], 'g-', label='Ne20')
+axbot.semilogy( dh['radius'],dh['ne20'], 'g--')
+
[…]

### 2019-07-16 plotscripts/plot_temp_dens_abund.py
Clean up fig showing initial profiles

@@ -1,28 +1,66 @@
 import matplotlib
-matplotlib.use("TkAgg")
 import matplotlib.pyplot as plt
 import numpy
 
-dc = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_research/wdbuilder/WDBuilder_SNIa-ddt/CO_WD_4km_cfbrooks_flash_pro12.dat',
+fig, (axtop, axmid, axbot) = plt.subplots(3, 1, sharex=True, figsize=(3.38,5.0))
+fig.subplots_adjust(hspace=0)
+
+# From Rich Townsend for mesa3
+
+params = {'backend': 'pdf',
+# 'figure.figsize': [3.38, 3.38],
+ 'font.family':'serif',
+ 'font.size':10,
+ 'font.serif': 'Times Roman',
+ 'axes.titlesize': 'medium' ,
+ 'axes.labelsize':'medium',
+ 'legend.fontsize':8,
+ 'legend.frameon':False,
+ 'text.usetex': True,
+ 'figure.dpi':600,
+ 'lines.markersize':4,
+ 'lines.linewidth':1,
+ 'lines.antialiased':False,
+ 'path.simplify':False,
+ # Townsley below here
+ 'legend.numpoints': 1}
+
+matplotlib.rcParams.update(params)
+
+ORANGE = (0.90, 0.60, 0.00)
+SKY_BLUE = (0.35, 0.70, 0.90)
+BLUE_GREEN = (0.00, 0.60, 0.50)
+YELLOW = (0.95, 0.90, 0.25)
+BLUE = (0.00, 0.45, 0.70)
+VERMILLION = (0.80, 0.40, 0.00)
+RED_PURPLE = (0.80, 0.60, 0.70)
+
+
+# file from /dmt/caugustine/Hybrid_Research/flash_research/wdbuilder/WDBuilder_SNIa-ddt/CO_WD_4km_cfbrooks_flash_pro12.dat
+dc = numpy.genfromtxt( 'CO_WD_4km_cfbrooks_flash_pro12.dat',
 	skip_header=2, names=('radius','density','temperature','c12','ne22') )
 
-dh = numpy.genfromtxt( '/dmt/caugustine/Hybrid_Research/flash_runs/snia_10_hybrid2/400k_flash_21new.dat',
+# file from /dmt/caugustine/Hybrid_Research/flash_runs/snia_10_hybrid2/400k_flash_21new.dat
+dh = numpy.genfromtxt( '400k_flash_21new.dat',
[…]

### 2019-07-16 paper/ms.tex
Clean up fig showing initial profiles
Some minor adjustments to conclusions

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/initial_conds.png}
+\includegraphics[width=\columnwidth]{figures/temp_dens_abund_profile.pdf}
 \caption{\label{fig:init_conds}
@@
 so both the hybrid and C--O models could share the same central ignition initial conditions in our simulations.
-{\color{red} TODO: make figure style consistent with other figures.}
 }
@@
 \item
+Central ignition enhances the production of IGE.
+
+\item
 The higher central density necessitated for ignition by the lower central carbon fraction leads to a higher production of IGE as well as stronger electron capture.
-Central ignition also enhances the production of IGE.
 
@@
 The ``punch line'' of all this is that hybrid progenitors should produce dimmer
-explosions, but not as much difference as found in \citet{willcoxetal2016}. We
-\citep{willcoxetal2016}. We end by noting that the existence of these hybrid
+explosions, but not as much difference as found in \citet{willcoxetal2016}.
+We end by noting that the existence of these hybrid
 WDs is a recent state-of-the-art result from stellar evolution, but our understanding 
@@
 subject to ongoing study \citep{calderetal2019,willcoxetal2019}.
+The choice of central or off-center ignition is tied to how convective Urca affects the convection before the explosion.
+
+\acknowledgements
 

### 2019-08-07 paper/ms.tex
First set of corrections from Josiah's helpful reading.

@@
 its edge and a flame will burn inward, converting the C-O white dwarf into
-an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004}.  Further accretion
+an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004,Shenetal12}. Further accretion
 leads to the collapse of the white dwarf
@@
 \citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
-Shenetal12, pakmoretal2012b}
+pakmoretal2012b}
 and active research continues, motivated by the need to explain bright events
@@
 
-A hybrid WD can then become a progenitor of a thermonuclear supernova.
-The hybrid could be part of a binary system in which the companion star becomes
-another white dwarf and the two merge. Recent population synthesis work supports
-this pathway by indicating a substantial contribution to the Ia population rate from
-mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. If, on the other hand, the hybrid
-WD is part of a binary with a main sequence or giant companion, it can gain mass and
-approach the Chandrasekhar mass, i.e.\  the single degenerate picture~\citep{willcoxetal2016}.
+{\color{blue}
+These hybrid WDs are relevant to the supernova problem because 
+they can become the progenitors thermonuclear supernovae
+if they are part of a binary system. If the companion star becomes
+another WD, the two can merge and produce an explosion.
+If, on the other hand, the hybrid WD has a main sequence 
+or giant companion, it can gain mass and approach the Chandrasekhar mass, i.e.\  
+the single degenerate picture~\citep{willcoxetal2016}.
+}
 
@@
 included thermohalene mixing during the cooling phase and thus
-had a lower central C fraction than previous hybrid models~\citep{brooksetal2017}.
+had a lower central C fraction than previous hybrid 
+models~\citep{brooksetal2017}. We selected the 1.09 \Msun WD model 
+with the 0.4 \Msun C/O core from \citep{brooksetal2017}.
+{\color{blue}
+In order to grow this WD towards the Chandrasekhar mass, it was inserted into 
+a binary with a 1.4 \Msun He star donor in a 3 hour orbital period, similar to 
+the simulations in \citep{brooksetal2016},
+and the system was
+allowed to evolve.  The WD grows, experiences central carbon ignition and 
+simmering, and then is stopped when its central temperature reaches 
+$\log T_{\rm c}(\Kelvin) = 8.9$.}
+
 The hybrid model was constructed to have conditions as similar a possible
@@
 ASC/Alliances Center for Astrophysical Thermonuclear Flashes at the
-University of Chicago.
+University of Chicago. {\color{blue} The authors gratefully thank Josiah 
+Schwab for comments on the manuscript and Jared Brooks for providing
+the hybrid progenitor models used in this study.}
 The source code used for
-these studies is available as a package compatible with the
+this study is available as a package compatible with the
 current \FLASH\ code from \url{http://astronomy.ua.edu/townsley/code.}

### 2019-08-07 paper/ms.tex
fix typo

--- 2019-07-16 paper/ms.tex
@@
 An early concern about this model came from studies finding that
-the as the stars merge, the more massive white dwarf can ignite near
+as the stars merge, the more massive white dwarf can ignite near
 its edge and a flame will burn inward, converting the C-O white dwarf into

### 2019-08-07 paper/ms.tex
More of Josiah's corrections.

--- 2019-08-07 paper/ms.tex
@@
 
-The hybrid model was constructed to have conditions as similar a possible
-to a ``classic'' C-O model and the two shared the same central temperature
-and density.  Figure~\ref{fig:init_conds} shows the density and temperature
-profiles of the two initial one-dimensional models.
+{\color{blue}
+Following the approach of \citet{willcoxetal2016}, we constructed a
+corresponding ``classic'' C-O model to allow comparison of explosion
+results between these hybrid models and those of previous studies
+\citep{Krueger2010On-Variations-o,Kruegeretal2012}. The C-O model was 
+constructed to have conditions as similar a possible to the hybrid
+model (e.g.\  the two shared the same central temperature and density).  
+Figure~\ref{fig:init_conds} shows the density and temperature
+profiles of the two initial one-dimensional models.}
 \begin{figure}
@@
 The peak temperature of the hybrid model is at the center of the star,
-so both the hybrid and C--O models could share the same central ignition initial conditions in our simulations.
+so both the hybrid and C-O models could share the same central ignition initial conditions in our simulations.
 }
@@
 Schwab for comments on the manuscript and Jared Brooks for providing
-the hybrid progenitor models used in this study.}
+the hybrid progenitor models used in this study.} The authors also
+thank Peter Hoeflich for very helpful discussions of this and related work. 
 The source code used for

### 2019-08-07 paper/ms.tex
Updated footnote 5.

@@
 \CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
-Helmholtz EOS table used in \CASTRO\ is in the public BoxLib
+Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
 Microphysics repository at

### 2019-08-07 paper/ms.tex
Took out the blue text

@@
 
-{\color{blue}
 These hybrid WDs are relevant to the supernova problem because 
@@
 the single degenerate picture~\citep{willcoxetal2016}.
-}
 
@@
 with the 0.4 \Msun C/O core from \citep{brooksetal2017}.
-{\color{blue}
 In order to grow this WD towards the Chandrasekhar mass, it was inserted into 
@@
 simmering, and then is stopped when its central temperature reaches 
-$\log T_{\rm c}(\Kelvin) = 8.9$.}
-
-{\color{blue}
+$\log T_{\rm c}(\Kelvin) = 8.9$.
+
 Following the approach of \citet{willcoxetal2016}, we constructed a
@@
 Figure~\ref{fig:init_conds} shows the density and temperature
-profiles of the two initial one-dimensional models.}
+profiles of the two initial one-dimensional models.
 \begin{figure}
@@
 ASC/Alliances Center for Astrophysical Thermonuclear Flashes at the
-University of Chicago. {\color{blue} The authors gratefully thank Josiah 
+University of Chicago. The authors gratefully thank Josiah 
 Schwab for comments on the manuscript and Jared Brooks for providing
-the hybrid progenitor models used in this study.} The authors also
+the hybrid progenitor models used in this study. The authors also
 thank Peter Hoeflich for very helpful discussions of this and related work. 

### 2019-08-07 paper/ms.tex
Updated the manuscript to be in the new format for submission. Also added info like Orcids.

@@
-%\documentclass[12pt,preprint]{aastex}
-\documentclass[iop,apj]{emulateapj}
+\documentclass[preprint2]{aastex63}
 %\usepackage{multirow}
@@
 
+\received{June 1, 2019}
+\revised{January 10, 2019}
+\accepted{\today}
+
+\submitjournal{ApJ}
+
 \bibliographystyle{apj}
@@
 \shorttitle{Hybrid Ia Progenitors}
+\shortauthors{Augustine et al.}
 
@@
 
-\author{
-Carlyn N.\ Augustine\altaffilmark{1},
-Donald E.\ Willcox\altaffilmark{2},
-Dean M.\ Townsley\altaffilmark{1},
-and Alan C.\ Calder\altaffilmark{3,4}
-}
-
-\altaffiltext{1}{
-  Department of Physics and Astronomy,
-  The University of Alabama, Tuscaloosa, AL, 35487-0324, USA
-}
-\altaffiltext{2}{
-  Center for Computational Sciences and Engineering,
-  Lawrence Berkeley National Lab, Berkeley, CA 94720, USA; \\
-  \href{mailto:dewillcox@lbl.gov}{dewillcox@lbl.gov}
-}
-\altaffiltext{3}{
-  Department of Physics and Astronomy,
-  Stony Brook University, Stony Brook, NY, 11794-3800, USA
-}
-\altaffiltext{4}{
-  Institute for Advanced Computational Sciences,
-  Stony Brook University, Stony Brook, NY, 11794-5250, USA
-}
+\correspondingauthor{Alan Calder}
+\email{alan.calder@stonybrook.edu}
+
+\author[0000-0002-9741-5987]{Carlyn N. Augustine}
+\affiliation{
+  Department of Physics and Astronomy \\
+  The University of Alabama \\ 
+  Tuscaloosa, AL, 35487-0324, USA}
+
+\author[0000-0003-2300-5165]{Donald E Willcox}
+\affiliation{
+  Center for Computational Sciences and Engineering \\
+  Lawrence Berkeley National Lab \\
+  Berkeley, CA 94720, USA}
+
+\author[0000-0002-9538-5948]{Dean M. Townsley}
+\affiliation{
+  Department of Physics and Astronomy \\
+  The University of Alabama \\ 
+  Tuscaloosa, AL, 35487-0324, USA}
+
+\author[0000-0001-5525-089X]{Alan C. Calder}
+\affiliation{
+  Department of Physics and Astronomy \\
+  Stony Brook University \\
+  Stony Brook, NY, 11794-3800, USA}
+\affiliation{
+  Institute for Advanced Computational Sciences \\
+  Stony Brook University \\
+  Stony Brook, NY, 11794-5250, USA}
 
@@
 
-\keywords{hydrodynamics --- nuclear reactions, nucleosynthesis, abundances
---- supernovae: general --- white dwarfs}
+\keywords{Hydrodynamics, Nuclear abundances, Nucleosynthesis,
+Type Ia supernovae, White dwarf stars}
 
@@
 In order to grow this WD towards the Chandrasekhar mass, it was inserted into 
-a binary with a 1.4 \Msun He star donor in a 3 hour orbital period, similar to 
-the simulations in \citep{brooksetal2016},
+a binary with a 1.4 \Msun He star donor having a 3 hour orbital period, similar to 
+the simulations in \citet{brooksetal2016},
 and the system was
@@
 \end{figure}
+While the C-O-Ne progenitor is the result of an evolutionary calculation, the C-O progenitor is a parameterized construction, as reflected in the simplified outer thermal structure appearing in Figure~\ref{fig:init_conds}.
 We centrally ignite our explosion simulations for both C-O and hybrid
@@
 
+%ms.bbl file here for non-bibtex submit
+
 \end{document}

### 2019-08-08 paper/ms.tex
Worked in suggestion from Jared. Also strenghtened the acknowledgement as it seems they do not wish to be co-authors.

@@
 into a neutron star, a scenario termed ``accretion-induced collapse''
-\citep{nomotokondo1991}.
+\citep{nomotokondo1991,brooksetalaic2017}.
 
@@
 takes place in a common envelope~\citep{raskinetal2009,pakmoretal2011,kashi:2011,
-pakmoretal2012a,Shenetal12,katzetal2016}.
+pakmoretal2012a,Shenetal12,katzetal2016,brooksetalfast2017}.
 
@@
 MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model 
-included thermohalene mixing during the cooling phase and thus
-had a lower central C fraction than previous hybrid 
-models~\citep{brooksetal2017}. We selected the 1.09 \Msun WD model 
+included larger nuclear reaction networks than previous studies and 
+thus resulted in a electron-to-baryon gradient that became unstable 
+to mixing as the interior cooled, leading to a lower central C 
+fraction than previous hybrid models~\citep{brooksetal2017}. We 
+selected the 1.09 \Msun WD model 
 with the 0.4 \Msun C/O core from \citep{brooksetal2017}.
@@
 University of Chicago. The authors gratefully thank Josiah 
-Schwab for comments on the manuscript and Jared Brooks for providing
-the hybrid progenitor models used in this study. The authors also
+Schwab and Jared Brooks for providing the hybrid progenitor models 
+used in this study and for comments on the manuscript. This study would 
+not have been possible without their kind help. The authors also
 thank Peter Hoeflich for very helpful discussions of this and related work. 

### 2019-08-08 paper/ms.tex
More work in prep for submission. Added Jared as an author.

@@
 
-\received{June 1, 2019}
-\revised{January 10, 2019}
-\accepted{\today}
+%\received{June 1, 2019}
+%\revised{January 10, 2019}
+%\accepted{\today}
 
@@
   Berkeley, CA 94720, USA}
+
+\author{Jared Brooks}
+\affiliation{
+  Department of Physics \\ 
+  University of California \\
+  Santa Barbara, CA 93106, USA}
 
@@
 University of Chicago. The authors gratefully thank Josiah 
-Schwab and Jared Brooks for providing the hybrid progenitor models 
-used in this study and for comments on the manuscript. This study would 
+Schwab for discussion of the study and comments on the manuscript.
 not have been possible without their kind help. The authors also

### 2019-08-30 paper/reply_to_referee.txt
Start on a reply to the referee of the mixed hybrid paper.

----------------------------------------------------------------------
Reviewer's Comments:

> This paper focuses on the outcome of thermonuclear explosions of near
> Chandrasekhar mass white dwarfs coming from the narrow range of IMS that
> produce hybrid C+O+Ne cores. The purpose of the work is to determine
> the differences between the thermonuclear explosion of mixed vs unmixed
> hybrid cores, motivated by the recent finding that the cores undergo a
> phase of convective mixing that destroys the differentiated structure
> made of a C+O nut surrounded by O+Ne layers. The approach consists on
> running the MESA code along the pre-explosive phase, followed by two
> dimensional hydro simulations of the explosion. There are also calculated
> the explosion of pure C+O white dwarfs starting from identical central
> density and temperature as the C+O+Ne mixed white dwarfs. The conclusions
> are that the mixed structures lead to lower yields of 56Ni as compared
> to the pure C+O case as well as to the unmixed hybrid cores.

> The paper is timely and interesting, and it merits publication in ApJ
> after some points are addressed, and the answers be reflected in the
> text. Some of these points are of methodological character, while others
> are more general.

> *Methodology*

> - It is not clear to me if the input deflagration speed (pg 7) has been
> recalibrated to the particular initial composition of the mixed hybrid
> core. Willcox et al (2016) just reports recomputing detonations, but there
> is no mention of deflagrations (at least I have not been able to find it).

> - Why is the MESA calculation stopped and mapped to FLASH just when
> the central temperature reaches log Tc = 8.9? What is the criterion for
> choosing such a temperature? Does it depend on composition?

> - Why was the C+O model constructed with the same central temperature and
> density as the mixed hybrid model? Would it be more appropriate to follow
> a C+O white dwarf with MESA until some runaway condition was accomplished?

> - Related to the last point above: it is not clear how was assigned the
> composition profile to the C+O model. In particular, why is the abundance
> of 22Ne in the C+O model smaller than that in the hybrid mixed model? Does
> it has an impact on the final yield of 56Ni?

> - Why were the models calculated in this paper ignited at the center,
> unlike the models in Willcox et al (2016)? Note that you invoke the
> off-center ignition as one of the causes of the differing results, but you
> do not provide a justification of the different ignition configuration.

> - In the first paragraph of section 3, it is argued that the yield of 56Ni
> was approximated by assuming the composition upon NSE freeze-out is 56Ni
> plus equal parts 54Fe and 58Ni. However, in many models of supernova Ia
> there is a large abundance of 56Ni in the layers that do not go beyond
> QNSE. Have you corrected for this effect somehow?

> *General*

> - Which is the role played by the hybrid progenitors in the global plot of
> supernovae type Ia? Since the lower limit of the 56Ni mass distribution
> is 0.6 solar masses, does it mean that hybrid progenitors lead to
> normal-to-bright supernovae while C+O progenitors represent the brighter
> end of this kind of supernovae? Does it imply a dominant contribution
> of double degenerate channel for the normal supernovae Ia? Most readers
> would thank a brief discussion of these and related issues.

> - Please, provide the values of the carbon abundance at the center and
> the mean of it in the white dwarf, in the initial model as well as in
> the final model of the MESA calculation.

> - Subsections 1.1 and 1.2 are more typical of a review than a regular
> paper, and are not at all necessary to understand what follows. They
> should be shortened to one or two medium length paragraphs. By the way,
> the reference Nomoto et al (1984) does not match the description of the
> flame that precedes it.

> - Figures 3, 6, and 7 are not quite informative, and the same applies
> to the short mention of them in the text. The authors should consider
> removing them.

### 2019-08-30 paper/reply_to_referee.txt
Picked off the first two of the referee's concerns about the mixed hybrids paper.

@@
 
+We thank the referee for reading out manuscript and offering very
+constructive criticism and suggestion. We are in almost complete agreement
+with the referee and have modified the manuscript accordingly. We address
+our changes for each point below. As a result of our revisions, we believe 
+the manuscript is stronger and we hope it is now ready for publication.
+
 > *Methodology*
@@
 
+We regret no explaining the methodology of our deflagration speeds. The 
+answer is that the deflagration speeds for input to the flame model are 
+from tabulated results. Laminar flame speeds are first 
+obtained by interpolation within a
+three-dimensional table of 12C, 22Ne, and log density obtained from
+prior direct numerical simulations. These laminar flame speed are
+then boosted to account for the effects of unresolved buoyancy
+and background turbulence and passed to the flame model. We have
+updated the text of the manuscript to explain the flame speeds.
+
 > - Why is the MESA calculation stopped and mapped to FLASH just when
@@
 > choosing such a temperature? Does it depend on composition?
+
+Again, we did not explain our methodology well. This temperature is
+high enough to ignite the deflagration that leads to the explosion.
+Yes, it is a (somewhat mildly) a funciton of composition, but at
+this temperature these models have very little evolution left before 
+the flame would be born even with differing composition. We have
+udated the text to better explain this issue.
 

### 2019-08-30 paper/ms.tex
Start on a reply to the referee of the mixed hybrid paper.
Picked off the first two of the referee's concerns about the mixed hybrids paper.

@@
 
-\correspondingauthor{Alan Calder}
+\correspondingauthor{Alan C. Calder}
 \email{alan.calder@stonybrook.edu}
@@
 
-\author[0000-0003-2300-5165]{Donald E Willcox}
+\author[0000-0003-2300-5165]{Donald E. Willcox}
 \affiliation{
@@
 tabulated results obtained by direct numerical simulations of
-thermonuclear burning~\citep{timmes92,Chamulak2007The-Laminar-Fla},
-and
-these are boosted to account for speed-up of burning due to unresolved
-buoyancy and background turbulence~\citep{Khok95,
+thermonuclear burning.
+{\color{blue}
+The flame speeds are obtained via linear interpolation within a 
+three-dimensional table that combines the results of \citet{timmes92} 
+and \citet{Chametal08}, and the dimensions of the table are \C{12} 
+mass fraction, \Ne{22} mass fraction and log of density.}
+These laminar flame speeds are boosted to account for the speed-up 
+of burning due to unresolved buoyancy and background turbulence~\citep{Khok95,
 gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
@@
 simmering, and then is stopped when its central temperature reaches 
-$\log T_{\rm c}(\Kelvin) = 8.9$.
+$\log T_{\rm c}(\Kelvin) = 8.9$, {\color{blue} at which point the 
+temperature is high enough to ignite the deflagration that is the first
+stage of the explosion.}
 

### 2019-08-31 paper/reply_to_referee.txt
More work on the new hybrid model manuscript to address the referee's concerns.

@@
 three-dimensional table of 12C, 22Ne, and log density obtained from
-prior direct numerical simulations. These laminar flame speed are
+prior direct numerical simulations. Here 22Ne is uses as a proxy for
+for neutron-rich elements so the interpolated laminar flame speeds capture
+the boost due to neutronization. These laminar flame speed are
 then boosted to account for the effects of unresolved buoyancy
 and background turbulence and passed to the flame model. We have
-updated the text of the manuscript to explain the flame speeds.
+updated the text of the manuscript to explain the flame speeds
+and included a citation to earlier work describing the tabulated
+flame speeds in detail.
+[NOTE: CHECK THIS. The models include 20Ne. Does the above
+description properly account for that? As I recall, nothing new
+was done to the tables for the hybrid Willcox et al. models.]
+
+Also, the detonation tests in Willcox et al. were tests of the
+energy release of the flame model and not flame speed tests. The 
+model identical amounts of energy for both deflagrations and 
+detonations in identical material, so detonation simulations were
+a simple check of the modifications we made to the model to
+include 20Ne in the mix.
 
@@
 Again, we did not explain our methodology well. This temperature is
-high enough to ignite the deflagration that leads to the explosion.
-Yes, it is a (somewhat mildly) a funciton of composition, but at
-this temperature these models have very little evolution left before 
-the flame would be born even with differing composition. We have
-udated the text to better explain this issue.
+very close to that required to ignite the deflagration of the
+first phase of the explosion, so the progenitor is in a ready 
+for ignition state. Yes, it is a (somewhat mildly) a function of 
+composition, but at this temperature these models have very little 
+evolution left before the flame would be born even with differing 
+composition. We have updated the text to better explain this issue.
 
@@
 > it has an impact on the final yield of 56Ni?
+
+The referee raises an interesting point about how one might perform
+these parameter studies. Indeed, a more realistic C/O progenitor as
+would be produced by MESA would be "state of the art." The parameterized
+C/O models we chose are motivated by results from stellar evolution and,
+in particular, have compositions that reflect the effect of ``simmering", 
+that is slow convective burning, in the late stages of evolution as the
+WD approaches the Chandrasekhar limit. This effect is observed as
+the lower C fraction interior to about r =1.2e8 cm (the solid curve
+in the bottom panel of Figure 1). Accordingly, while parameterized, 
+the structure of C/O progenitor does reflect our current understanding 
+of the state just prior to ignition.
+
+For this study we decided to use these parameterized C-O models because
+being able to construct them to match the central density and 
+temperature of the hybrid models allowed us to better control the 
+differences between the hybrid and traditional models. More realistic
+C-O models would not match the conditions of the hybrid models, and
+as we have shown in previous work, differences in density can have
+a substantial effect on the yields.
+
+We have added text to the manuscript and slightly re-arranged the 
+description to better explain the motivation for our choice.
 

### 2019-08-31 paper/ms.tex
More work on the new hybrid model manuscript to address the referee's concerns.

@@
 and \citet{Chametal08}, and the dimensions of the table are \C{12} 
-mass fraction, \Ne{22} mass fraction and log of density.}
+mass fraction, \Ne{22} mass fraction and log of density. While the
+WD contains additional species, we have shown that treating the
+abundance of \Ne{22} as a proxy for neutron-rich elements captures the
+speed-up of laminar flames due to neutronization and thus reasonably 
+produces variations in flame speed due to composition~\cite{jacketal2010}.}
 These laminar flame speeds are boosted to account for the speed-up 
@@
 $\log T_{\rm c}(\Kelvin) = 8.9$, {\color{blue} at which point the 
-temperature is high enough to ignite the deflagration that is the first
-stage of the explosion.}
+temperature is just about high enough to ignite the deflagration that is 
+the first stage of the explosion.}
 
@@
 The simulations performed for this study consisted of a suite of
-30 two-dimensional simulations of
-thermonuclear supernova
-explosions from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
-were compared to a suite of supernova simulations from traditional
-C-O progenitors. In both suites, the simulation
+30 two-dimensional simulations of thermonuclear supernova explosions 
+from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
+were compared to a suite of supernova simulations from traditional C-O 
+progenitors. {\color{blue} The C-O progenitors are parameterized and 
+include the effects of convective ``simmering" in the core as the WD 
+approaches the Chandrasekhar mass~\citep{Chametal08,PiroBild08,jacketal2010}.
+Using parameterized C-O models allowed us to choose conditions, e.g.
+central density, to control differences between the hybrid and traditional 
+models and thus assess the effect of the hybrid structure.
+}
+
+The C-O and C-O-Ne models have the same central temperature
+and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
+The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
+The C-O-Ne model used in \FLASH\ had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
+The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.
+
+In both suites, the simulation
 begins with a progenitor model mapped to the two-dimensional
@@
 of the implementation of this method.
-
-The C-O and C-O-Ne models have the same central temperature
-and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
-The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
-The C-O-Ne model used in \FLASH\ had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
-The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.
 

### 2019-08-31 paper/reply_to_referee.txt
Even more work on the new hybrid paper.

@@
 
+Something else we could have better explained. The hybrid models in Willcox
+et al have a very different structure with the highest temperature, where
+ignition of the deflagration is expected, at a radius of about 300 km. 
+The profiles are illustrated in Figures 2 and 9 of Willcox et al. Yet 
+another thing we have made clear in the revised manuscript.
+
 > - In the first paragraph of section 3, it is argued that the yield of 56Ni

### 2019-08-31 paper/ms.tex
Even more work on the new hybrid paper.

@@
 yield from \SNeIa\ \citep{townetal2009}.
+{\color{blue} We note that the ignition points of the hybrid models of 
+\citet{willcoxetal2016} substantially differed from both the
+(mixed) hybrid and traditional models presented here. Those progenitors
+had the highest temperatures and hence were ignited at a radius of
+about 300 km.}
 
@@
 from hybrid progenitors of the same central density.
-This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in \cite{willcoxetal2016}.
+This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in \citep{willcoxetal2016}.
+{\color{red} CHECK FORMAT OF WILLCOX CITATION}
 

### 2019-09-01 paper/reply_to_referee.txt
More work on the referee's report. Getting there.

@@
 
+[Hmmm. I think this is not right. What to say?] 
+The estimate of 56Ni yield does follow from assuming the NSE mix is
+composed of 56Ni plus equal parts 54Fe and 58Ni, and this approach is
+how all 56Ni in the simulation is calculated. 56Ni in (outer) layers
+that did not go beyond QNSE would have been synthesized by fusion 
+going to the Fe-group and then mixed. As such, the estimate we use 
+should be robust. We have added a sentence with citations and an
+additional citation to previous work verifying this approach in a variety 
+of scenaros to the paragraph.
+
 > *General*
@@
 
+These are the questions that we are exploring with this and related work,
+and we regret not make these clear in the introductory material. We
+have added text addressing exactly these issues.
+
 > - Please, provide the values of the carbon abundance at the center and
@@
 > the final model of the MESA calculation.
+
+TO BE DONE
 
@@
 > removing them.
+
+We appreciate the referee's point. The figures show the evolution of quantites 
+like 56Ni abundance with time and are similar to some of the figures showing 
+abundance evolution in Willcox et al. Because they allow the reader to both 
+visualize the scatter in the yields and also the character of the burning 
+(such as the DDT), we feel they are useful and would like to keep them. Also,
+they are similar to figures in Willcox et al, which allows comparison
+to results from another class of hybrid progenitors. We agree with the referee 
+that the discussion was scant and have improved that.

### 2019-09-01 paper/ms.tex
More work on the referee's report. Getting there.

@@
 
+{\color{blue} 
+Discerning the role played by hybrid progenitors in the global gamut of
+thermonuclear is the goal of the study we present in this paper. We calculate
+the yields of \Ni{56} in simulaitons of thermonuclear supernovae. Because
+the radioactive decay of \Ni{56} powers the light curve of an event, 
+the yield of \Ni{56} serves as a proxy for the event and allows us to
+discern trends in brightness. Our study thus can offer theoretical 
+insight into what events might be explained by explosions from these
+progenitors as well as the overall scatter in the brightness
+of observed events.
+
+Our simulational methododolgy is described in the next section and 
+our results, a comparison of nucleosynthetic explosion yields between these
+new mixed hybrid C-O-Ne progenitors and traditional C-O progenitors
+in the section following the methodology. Our results show systematic
+differences in the yield of \Ni{56} between explosions from the two
+types of progenitors, which we quantify and disuss.
+}
+
 \section{Methodology}
@@
 thermonuclear supernovae and has been presented in a series of
-papers \citep[See][and references therein]{chandlery}. For completeness,
+papers \citep[See][and references therein]{townetal2016,chandlery}. For completeness,
 we briefly review the flame capturing scheme here.
@@
 is equivalent to comparing the brightness of events. The
-yields were estimated from $Y_e$ and the NSE progress
-variable, by assuming the composition upon NSE freeze-out is \Ni{56} plus equal
+yields were estimated from $Y_e$ and the NSE progress variable, by 
+assuming the composition upon NSE freeze-out is \Ni{56} plus equal
 parts \Fe{54} and \Ni{58} \citep{townetal2009,Meaketal09}.
-This assumption allows the fraction of IGEs in the form of \Ni{56} to be estimated from the $Y_e$ tracked by the burning model.
+This assumption allows the fraction of IGEs in the form of \Ni{56} to be 
+estimated from the $Y_e$ tracked by the burning model. 
+{\color{blue}
+This process has been shown to provide estimated \Ni{56} yields consistent with
+the results of detailed network and NSE calculations~\cite{caldertownsley2018}.
+}
 
@@
 from hybrid progenitors of the same central density.
-This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in \citep{willcoxetal2016}.
-{\color{red} CHECK FORMAT OF WILLCOX CITATION}
+This contrast is in a similar direction but not as large as the difference 
+between C-O and C-O-Ne progenitors seen in \citet{willcoxetal2016}.
 
@@
 
-The expected final production of \Ni{56}, after NSE freeze-out, as a function of simulation time
+The production of \Ni{56}, after NSE freeze-out, as a function of simulation time
 for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
-On average, the C-O model reaches the DDT phase sooner then the
-hybrid model.
+{\color{blue} The sharp increase in the yield occuring after approximately 1.0 second indicates
+the transiton to the detonation phase with its significantly faster burning. The curves
+indicate that on average, the C-O models reach the DDT sooner then the hybrid model.}
 
@@
 Expected ratio of \Ni{56} to total IGE production by mass vs.\ time showing the evolution
-for both suites of simulations. Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
+for both suites of simulations. 
+{\color{red} Shown are realizations 21-30.}
+Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
 %SAME AS DON'S FIGURE 19
@@
 
-The fraction, by mass, of IGE material expected to be in the form of \Ni{56} after freeze-out is shown in Figure \ref{fig:compare_ratio} as it evolves in time.
-Also shown in Figure~\ref{fig:compare_burned} is the concurrent evolution of mass burned to IGE for both suites.
+{\color{blue} 
+The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
+freeze-out is shown in Figure \ref{fig:compare_ratio}. 
+Also shown in 
+%Figure~\ref{fig:compare_burned} 
+is the concurrent evolution of mass burned to IGE for both suites.
 The total IGE has a mostly similar evolution, but the ratio demonstrates important differences between C-O and C-O-Ne cases.
+}
 

### 2019-09-01 paper/ms.tex
Even more work on the referee report hybrid.

@@
 
-The single degenerate picture posits a white dwarf gaining mass
-from a main-sequence companion. The process relies on a long
-period of accretion combined with either steady burning or a
-series of nova explosions. During this accretion phase, a traditional
-C-O WD must gain at least
-$\sim 0.4$ \Msun\ as needed for it to approach the
-limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
-the Chandrasekhar limit, conditions in the compressed core are right
-to ignite the thermonuclear burning that will incinerate the star.
-
-Within this progenitor setting, many mechanisms for the explosion have
-been studied with the result being that the outcome is sensitive to
-the ignition conditions and the nature of the thermonuclear burning.
-Studies indicate that neither a pure deflagration (subsonic flame front)
-nor a pure detonation (supersonic burning front) produce ejecta consistent
-with observations \citep{arnett69,roepkeetal07}.  Instead, the models
-that best reproduce the observed stratified ejecta are those in which
-the burning begins as a subsonic deflagration, allowing the star
-to expand to lower densities in response, followed by a
-supersonic detonation that incinerates the
-star~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05}.
-The ``classic'' delayed detonation model is that of
-\citet{Khokhlov1991Delayed-detonat} \citep[See also][]{hoflich.khokhlov.ea:delayed,GameKhokOran05},
-and many variations have been
-explored \citep[and references therein]{hillebrandtetal2013,calderetal2013}.
-The approach we employ for this study is a variation, the
-deflagration-to-detonation transition (DDT), in which the transition
-occurs at the top of a rising Rayleigh-Taylor~\citep{taylor+50,chandra+81}
-unstable plume of hot, burned
-material when it reaches a threshold density.
-We describe this approach and our methodology in detail below.
-
-The double detonation picture is a variation of the single degenerate picture.
-In this case, a white dwarf accretes material from a companion, but rather
-than gaining enough mass to approach the Chandrasekhar limit, a detonation
-occurs in the accreted layer that subsequently triggers another detonation
-in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
-nomoto80,nomoto82b}. Early studies indicated that a detonation in an
-accreted He
-layer could produce an inwardly propagating
-shock that would ignite a detonation in the C-O core and found
-that this scenario could work for a wide range of white dwarf
-masses, not just the near-Chandrasekhar case \citep{livne90}, hence the
-moniker ``sub-Chandrasekhar'' \citep{ww94}.
-Follow-up multidimensional calculations
-supported the
-efficacy of this picture~\citep{livneglasner91, livnearnett95,HoefKhok96,
-hoeflichetal96, wigginsfalle97,wigginsetal98,garciasenzbravowoosley99}.
-These studies indicated that uncertainties in the initial conditions,
-however, were found to play a significant role on the explosion outcome.
-
-A particular problem was that most models included a massive He layer on
-the white dwarf. Such a configuration leads to the result that
-intermediate and heavy elements synthesized in the He detonation appear in
-the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
-hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
-however, found that fairly thin He layers could flash on sub-Chandrasekhar
-mass white dwarfs, partially resolving the issue and encouraging
-further research~\citep{simetal2012,brooksetal2015, shenetal2018,
-glasneretal2018,Townsleyetal2019}.
+There are three widely explored progenitor settings for thermonuclear
+supernovae. These are the white dwarf merger, double detonation, 
+and single degenerate scenarios and we briefly describe each here. 
+We note that all of these could involve hybrid C-O-Ne WDs, but hybrid
+white dwarfs are particularly interesting to the single degenerate
+picture because the greater mass of a hybrid WD might resolve a
+concern.
 
@@
 which may explain some bright events~\citep{scalzo:2010,Yuan:2010}.
-An early concern about this model came from studies finding that
-as the stars merge, the more massive white dwarf can ignite near
-its edge and a flame will burn inward, converting the C-O white dwarf into
-an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004,Shenetal12}. Further accretion
-leads to the collapse of the white dwarf
-into a neutron star, a scenario termed ``accretion-induced collapse''
-\citep{nomotokondo1991,brooksetalaic2017}.
-
+Early modeling efforts found that as the stars merge, the more massive white 
+dwarf can ignite near its edge and fail to produce a 
+supernova~\citep{saionomoto1985,saionomoto2004,Shenetal12}. 
 Subsequent work allayed this concern by demonstrating
@@
 \citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
-pakmoretal2012b}
-and active research continues, motivated by the need to explain bright events
-and the estimated population of WD pairs. Contemporary
+pakmoretal2012b}. Contemporary
 research focuses on variations on the merger idea, including inspiraling pairs,
@@
 
+The double detonation picture posits a white dwarf gaining mass from 
+a companion. The supernova explosion begins with 
+a detonation occuring in an accreted layer of He, and that subsequently triggers 
+another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
+nomoto80,nomoto82b}. Early studies indicated that this scenario could work 
+for a wide range of white dwarf masses, not just the near-Chandrasekhar case 
+\citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
+scenario \citep{ww94}. Of concern in this picture is the mass of the accretted He 
+layer because intermediate and 
+heavy elements synthesized in the He detonation appear will in
+the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
+hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
+however, found that fairly thin He layers could flash on sub-Chandrasekhar
+mass white dwarfs, encouraging
+further research~\citep{simetal2012,brooksetal2015, shenetal2018,
+glasneretal2018,Townsleyetal2019}.
+
+The single degenerate picture also has a white dwarf gaining mass
+from a companion. The process relies on a long
+period of accretion combined with either steady burning or a
+series of nova explosions for a traditional
+C-O WD to gain the $\sim 0.4$ \Msun\ needed for it to approach the
+limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
+the Chandrasekhar limit, conditions in the compressed core are right
+to ignite the thermonuclear burning that will incinerate the star.
+Within this progenitor setting, models that best reproduce observations 
+are those in which the burning begins as a subsonic deflagration
+during which the star expands that is then followed by supersonic 
+detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05,
+hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
+properties assuming this scenario and our describe  methodology in 
+detail below.
+
 \subsection{The Deflagration to Detonation Transition Mechanism Within
@@
 
-Our single-degenerate models are within the DDT explosion paradigm~\citep{1986SvAL,
+The approach we employ for this study is a variation of the delayed
+detonation descibed above, the deflagration-to-detonation transition (DDT)
+explosion paradigm~\citep{1986SvAL,
 Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,fishjump2015}.
@@
 of the WD, it is subject to the Rayleigh-Taylor instability that generates
-turbulence and boosts burning.
+turbulence and boosts burning~\citep{taylor+50,chandra+81}.
 Burning proceeds as a deflagration for about one second, and then
 the flame transitions to a detonation~\citep{hoflich.khokhlov.ea:delayed}.
-
-%Maybe add some of below?
-%and variations include pulsational
-%detonations \cite{ivanovaetal1974,Khokhlov1991Delayed-detonat,
-%arnettlivne94a, arnettlivne94b, bravogarcia-senz2006},
-%gravitationally confined detonation \cite{PlewCaldLamb04,Jordan2008Three-Dimension,
-%jordanetal2012}, and deflagration-to-detonation
-%transitions (DDTs) \cite{1986SvAL,Khokhlov1991Delayed-detonat,NiemWoos97,Niem99,belletal2004,
-%fishjump2015}. We adopt a variation of the latter case, a deflagration-to-detonation transition
-%that occurs at the top of a rising plume of hot, burned material when it
-%reaches a threshold density.
-
-The mechanism by which the deflagration transitions to a detonation
-is incompletely understood, but the development of fluid instabilities
-at the deflagration front, particularly the Rayleigh-Taylor
-instability, is an accepted part of the process.
-Many ideas have been proposed, including the deflagration front
-entering a regime of distributed burning and the net
-rate becoming supersonic \citep{NiemWoos97}, the unstable
-flame reaching a certain fractal dimension~\citep{woosley90},
-and the Zel'dovich mechanism in which conditions are right for
-a pocket of fuel to
-detonate~\citep{zeldovichetal1970,KhokOranWhee97,jacketal2014}.
-We note that regardless of
-the mechanism, the amount of expansion of the star prior to the bulk of burning
-is critical to the composition of material synthesized in the explosion. Also,
-early burning during the deflagration phase is at high enough densities that
-the effects of electron capture are significant and similarly influence the
-composition the material synthesized in the explosion~\citep{hoeflichetal2004,
-hoeflich2006,fesenetal2007,diamondetal2018}.
 Our simulations assume that the transition occurs when the top of a
@@
 density~\citep{townsley.calder.ea:flame}.
-Variations on the choice of this density allowed earlier studies to explore
-the effects of physics influencing the transition
-density~\citep{jacketal2010,Krueger2010On-Variations-o,Kruegeretal2012}.
-
-%
-%
-%Explain the Single Degenerate scenario
-%\citep{Baraffe2004Stability-of-Su,WoosWunsKuhl04,wunschwoosley2004,Kuhletal06,nonakaetal2012}.
-%expansion \citep{Nomo84,WoosWunsKuhl04}, and a flame is born.
-%
-%Explain DDT
-%
-%Go through below and cite some of these as you tell the story
-%
-%d~\citep{arnett.truran.ea:nucleosynthesis}.
-%~\citep{mazzalietal2008}.
-%
-%
-%\citep{khokhlov1993,bychovliberman1995,
-%SNrt,Khok95,NiemHill95,khoketal1997,ZingDurs07,
-%cholazarianvishniac2003,
-%roepkehn2003,roepkehn2004,
-%Zingale2005Three-dimension,Schmetal06a, Schmetal06b,Aspdetal08,
-%Woosetal09,csetal2009,hicksrosner2013,c-ssr2013,
-%jacketal2014,poludnenko2015,hicks2015}.
-%
-%
-%A deflagration alone will not produce a event of normal brightness and
-%expansion velocity~\citep{roepkeetal07}. Instead, the initial
-%deflagration must transition to a detonation after the star has
-%expanded some in order to produce abundances and a stratified ejecta
-%in keeping with
-%observations~\citep{Khokhlov1991Delayed-detonat,hokowh95}.
-%The physics of this ``deflagration-to-detonation transition'' (DDT)
-%are not completely understood, but there has been considerable study
-%based on mechanisms involving flame fronts in highly turbulent
-%conditions~\citep{1986SvAL, woosley90, Khokhlov1991Delayed-detonat,
-%  hokowh95, HoefKhok96, khoketal1997, NiemWoos97, hwt98, Niem99,
-%  GameKhokOran05,roepke07, poletal2011,c-ssr2013,poludnenko2015}.
-%These models generally reproduce the observations under certain
-%assumptions about the ignition~\citep{townetal2009}, but research has
-%shown that the results are very sensitive to the details of the
-%ignition~\citep{PlewCaldLamb04,GameKhokOran05,garciasenz:2005,
-%  roepkeetal07,Jordan2008Three-Dimension}.
+
+In the DDT paradigm, the duration of the deflagration phase sets
+the amount of expansion of the star prior to the bulk of burning
+and is critical to the composition of material synthesized in the 
+explosion. Also, early burning during the deflagration phase is at 
+high enough densities that the effects of electron capture are 
+significant and similarly influence the composition the material 
+synthesized in the explosion~\citep{hoeflichetal2004,
+hoeflich2006,fesenetal2007,diamondetal2018}.
 
@@
 This process has been shown to provide estimated \Ni{56} yields consistent with
-the results of detailed network and NSE calculations~\cite{caldertownsley2018}.
+the results of detailed network and NSE calculations~\citep{townetal2016,caldertownsley2018}.
 }
@@
 the transiton to the detonation phase with its significantly faster burning. The curves
-indicate that on average, the C-O models reach the DDT sooner then the hybrid model.}
+indicate that on average, the C-O-Ne models reach the DDT later then the hybrid model, 
+impling more expansion of the WD and lower density burning in the detonation phase.}
 
@@
 The choice of central or off-center ignition is tied to how convective Urca affects the convection before the explosion.
+
+\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (http://flash.uchicago.edu/), 
+MESA \citep{mesa1,mesa2,mesa3,mesa3e} (http://mesa.sourceforge.net/)
+}
 

### 2019-09-02 paper/reply_to_referee.txt
Even more work on the referee report hybrid.
Ok, finishing up revisions to the hybrid manuscript.

@@
 
-We thank the referee for reading out manuscript and offering very
-constructive criticism and suggestion. We are in almost complete agreement
+We thank the referee for reading our manuscript and offering very
+constructive criticism and suggestions. We are in almost complete agreement
 with the referee and have modified the manuscript accordingly. We address
@@
 
-[Hmmm. I think this is not right. What to say?] 
+[AC: Hmmm. I think this is not right. What to say?]
+
 The estimate of 56Ni yield does follow from assuming the NSE mix is
@@
 
-TO BE DONE
+The central carbon abundance in the MESA model is 0.1419 and the initial
+model for Flash is constructed to have the same central carbon abundance.
+The central carbon abundance in the C-O model is 0.4. We have added these
+numbers to the manuscript. The mean values of C abundances were not
+calculated with the models. We could integrate the models
+to obtain a mass-weighted average, but we are not sure of the utility
+of this quantity as our results show that the yields are a sensitive
+function of the density. We prefer to just state the central C abundances
+and present the profiles as we did in Figure 1 and hope this is acceptable.
 
@@
 > flame that precedes it.
+
+We have substantially shortened the sections, including removing the
+Nomoto (1984) reference.
 
@@
 that the discussion was scant and have improved that.
+
+[AC: CHECK RED TEXT IN THE CAPTION OF FIG. 6 and similar text in the description]
+
+In summar. we have taken the referee's criticism and suggestions and revised 
+the manuscript accordingly. The result is a greatly improved version we trust 
+is ready for publication.

### 2019-09-02 paper/ms.tex
Ok, finishing up revisions to the hybrid manuscript.

@@
 Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,SeitenzahlTownsley2017,roepkesim2018}
-for additional discussion.
-
+for additional discussion. We note that hybrid white dwarfs are particularly 
+interesting to the single degenerate picture because the greater mass of a hybrid WD might resolve a
+concern.
+
+{\color{blue}
 \subsection{Proposed Progenitor Settings}\label{sec:progenitors}
 
-There are three widely explored progenitor settings for thermonuclear
-supernovae. These are the white dwarf merger, double detonation, 
-and single degenerate scenarios and we briefly describe each here. 
-We note that all of these could involve hybrid C-O-Ne WDs, but hybrid
-white dwarfs are particularly interesting to the single degenerate
-picture because the greater mass of a hybrid WD might resolve a
-concern.
-
-The white dwarf merger progenitor picture has two white dwarfs coming
-together and subsequently exploding~\citep{tutukovyungelson76,tutukovyungelson79,
-webbink84,ibentutukov84}. This scenario provides an abundance of degenerate fuel,
-which may explain some bright events~\citep{scalzo:2010,Yuan:2010}.
-Early modeling efforts found that as the stars merge, the more massive white 
-dwarf can ignite near its edge and fail to produce a 
-supernova~\citep{saionomoto1985,saionomoto2004,Shenetal12}. 
-Subsequent work allayed this concern by demonstrating
-that a low accretion rate from the disrupted secondary, $ < 3 \times 
-10^{-6}$ \Msun per year, did not heat the primary enough for ignition
-\citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
-pakmoretal2012b}. Contemporary
-research focuses on variations on the merger idea, including inspiraling pairs,
-collisions, violent mergers, and the ``core-degenerate'' model in which the merger
-takes place in a common envelope~\citep{raskinetal2009,pakmoretal2011,kashi:2011,
-pakmoretal2012a,Shenetal12,katzetal2016,brooksetalfast2017}.
-
-The double detonation picture posits a white dwarf gaining mass from 
-a companion. The supernova explosion begins with 
-a detonation occuring in an accreted layer of He, and that subsequently triggers 
-another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
-nomoto80,nomoto82b}. Early studies indicated that this scenario could work 
-for a wide range of white dwarf masses, not just the near-Chandrasekhar case 
-\citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
-scenario \citep{ww94}. Of concern in this picture is the mass of the accretted He 
-layer because intermediate and 
-heavy elements synthesized in the He detonation appear will in
-the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
-hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
-however, found that fairly thin He layers could flash on sub-Chandrasekhar
-mass white dwarfs, encouraging
-further research~\citep{simetal2012,brooksetal2015, shenetal2018,
-glasneretal2018,Townsleyetal2019}.
-
-The single degenerate picture also has a white dwarf gaining mass
+The single degenerate picture posits a white dwarf gaining mass
 from a companion. The process relies on a long
@@
 during which the star expands that is then followed by supersonic 
-detonation~\citep{Nomo84,Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05,
+detonation~\citep{Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05,
 hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
@@
 detail below.
+
+The double detonation picture also has a white dwarf gaining mass from 
+a companion. The supernova explosion begins with 
+a detonation occuring in an accreted layer of He, and that subsequently triggers 
+another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
+nomoto80,nomoto82b}. Early studies indicated that this scenario could work 
+for a wide range of white dwarf masses, not just the near-Chandrasekhar case 
+\citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
+scenario \citep{ww94}. The mass of the accretted He 
+layer is a concern because intermediate and 
+heavy elements synthesized in the He detonation appear will in
+the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
+hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
+however, found that fairly thin He layers could flash on sub-Chandrasekhar
+mass white dwarfs, encouraging
+further research~\citep{simetal2012,brooksetal2015,shenetal2018,
+glasneretal2018,Townsleyetal2019}.
+
+The white dwarf merger progenitor picture has two white dwarfs coming
+together and subsequently exploding~\citep{tutukovyungelson76,tutukovyungelson79,
+webbink84,ibentutukov84}. This scenario provides an abundance of degenerate fuel,
+which may explain some bright events~\citep{scalzo:2010,Yuan:2010}.
+Early modeling efforts found that as the stars merge, the more massive white 
+dwarf can ignite near its edge and fail to produce a 
+supernova~\citep{saionomoto1985,saionomoto2004,Shenetal12}. 
+Subsequent work allayed this concern by demonstrating
+that a low accretion rate from the disrupted secondary, $ < 3 \times 
+10^{-6}$ \Msun\ per year, did not heat the primary enough for ignition
+\citep{kawai1987,saionomoto2004,yoonetal2007,lorenaguilaretal2009, 
+pakmoretal2012b}. Contemporary
+research focuses on variations on the merger idea, including inspiraling pairs,
+collisions, violent mergers, and the ``core-degenerate'' model in which the merger
+takes place in a common envelope~\citep{raskinetal2009,pakmoretal2011,kashi:2011,
+pakmoretal2012a,Shenetal12,katzetal2016,brooksetalfast2017}.
 
@@
 the deflagration phase begins in the core~\citep{Nomo84,WoosWunsKuhl04}.
+
 This flame is unstable, and as the deflagration propagates toward the surface
@@
 hoeflich2006,fesenetal2007,diamondetal2018}.
+}
 
@@
 Hybrid WDs have more mass than traditional C-O WDs, with some studies indicating the
-mass can approach 1.3 \Msun \citep{chenetal2014}. This increased mass
+mass can approach 1.3 \Msun\ \citep{chenetal2014}. This increased mass
 minimizes one of the problems associated with the single-degenerate picture,
@@
 Discerning the role played by hybrid progenitors in the global gamut of
-thermonuclear is the goal of the study we present in this paper. We calculate
-the yields of \Ni{56} in simulaitons of thermonuclear supernovae. Because
+thermonuclear is the goal of the study we present in this paper. Our simulations
+provide the yields of \Ni{56} in the supernova explosions. Because
 the radioactive decay of \Ni{56} powers the light curve of an event, 
-the yield of \Ni{56} serves as a proxy for the event and allows us to
-discern trends in brightness. Our study thus can offer theoretical 
-insight into what events might be explained by explosions from these
+the yield of \Ni{56} serves as a proxy for brightness of the event so
+our estimates allows us to discern trends in brightness. Our study thus 
+can offer insight into the relative brightness of explosions from these
 progenitors as well as the overall scatter in the brightness
@@
 fraction than previous hybrid models~\citep{brooksetal2017}. We 
-selected the 1.09 \Msun WD model 
-with the 0.4 \Msun C/O core from \citep{brooksetal2017}.
+selected the 1.09 \Msun\ WD model 
+with the 0.4 \Msun\ C/O core from \citep{brooksetal2017}.
 In order to grow this WD towards the Chandrasekhar mass, it was inserted into 
-a binary with a 1.4 \Msun He star donor having a 3 hour orbital period, similar to 
+a binary with a 1.4 \Msun\ He star donor having a 3 hour orbital period, similar to 
 the simulations in \citet{brooksetal2016},
@@
 simmering, and then is stopped when its central temperature reaches 
-$\log T_{\rm c}(\Kelvin) = 8.9$, {\color{blue} at which point the 
+$\log T_{\rm c}(\Kelvin) = 8.9$, 
+{\color{blue} 
+at which point the 
 temperature is just about high enough to ignite the deflagration that is 
-the first stage of the explosion.}
+the first stage of the explosion. The central \C{12} mass fraction 
+of the model is 0.1419.}
 
@@
 model (e.g.\  the two shared the same central temperature and density).  
+{\color{blue} 
+The central \C{12} mass fraction of this model is 0.4.
+}
 Figure~\ref{fig:init_conds} shows the density and temperature
@@
 with \citet{willcoxetal2016}, we used the EOS routine from
-\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
-Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
-Microphysics repository at
-  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
-  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} 
+\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.
 This procedure produced a structure that was stable in \FLASH, with 
@@
 approaches the Chandrasekhar mass~\citep{Chametal08,PiroBild08,jacketal2010}.
-Using parameterized C-O models allowed us to choose conditions, e.g.
+Using parameterized C-O models allowed us to choose conditions, e.g.\
 central density, to control differences between the hybrid and traditional 
@@
 The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
-freeze-out is shown in Figure \ref{fig:compare_ratio}. 
-Also shown in 
-%Figure~\ref{fig:compare_burned} 
-is the concurrent evolution of mass burned to IGE for both suites.
-The total IGE has a mostly similar evolution, but the ratio demonstrates important differences between C-O and C-O-Ne cases.
+freeze-out is shown in Figure \ref{fig:compare_ratio}. The figure presents the results from the
+same realizations as in Figure \ref{fig:nithybrid} The ratios for the yields of 
+explosions from hybrid progenitors are consistenly lower than the ratios of yields from
+traditional progenitors.
+Figure~\ref{fig:compare_burned} shows the 
+concurrent evolution of mass burned to IGE for realizations 25-30 from both suites.
+The total IGE has a mostly similar evolution, and the hybrid results show
+more scatter, but there is not an obvious difference between the results from
+the two progenitors. These plots together show that the 
+ratio is the quantity that demonstrates important differences between 
+C-O and C-O-Ne cases.
 }
@@
 
-\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (http://flash.uchicago.edu/), 
-MESA \citep{mesa1,mesa2,mesa3,mesa3e} (http://mesa.sourceforge.net/)
+\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
+MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
+The
+Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
+Microphysics repository at
+  (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
+  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).
 }

### 2019-09-02 paper/reply_to_referee.txt
Finished the draft revised version of the hybrid paper.

@@
 flame speeds in detail.
-[NOTE: CHECK THIS. The models include 20Ne. Does the above
+
+[AC NOTE: CHECK THE ABOVE. The models include 20Ne. Does the above
 description properly account for that? As I recall, nothing new
@@
 We have substantially shortened the sections, including removing the
-Nomoto (1984) reference.
+Nomoto (1984) reference (good catch!). We modified both sections
+with an emphasis on just the points important to our analysis (e.g. 
+the duration of the deflagration phase and expansion).
 
@@
 
-We appreciate the referee's point. The figures show the evolution of quantites 
+We appreciate the referee's point. The figures show the evolution of quantities 
 like 56Ni abundance with time and are similar to some of the figures showing 
@@
 
-In summar. we have taken the referee's criticism and suggestions and revised 
-the manuscript accordingly. The result is a greatly improved version we trust 
+In summary. we have taken the referee's criticism and suggestions and revised 
+the manuscript accordingly. The result is a significantly improved version we trust 
 is ready for publication.

### 2019-09-02 paper/ms.tex
Finished the draft revised version of the hybrid paper.

@@
 The single degenerate picture posits a white dwarf gaining mass
-from a companion. The process relies on a long
+from a companion, and the process relies on a long
 period of accretion combined with either steady burning or a
@@
 C-O WD to gain the $\sim 0.4$ \Msun\ needed for it to approach the
-limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
+limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As the WD approaches
 the Chandrasekhar limit, conditions in the compressed core are right
@@
 The double detonation picture also has a white dwarf gaining mass from 
-a companion. The supernova explosion begins with 
-a detonation occuring in an accreted layer of He, and that subsequently triggers 
+a companion. The supernova begins with 
+a detonation occurring in an accreted layer of He, and that subsequently triggers 
 another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
@@
 \citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
-scenario \citep{ww94}. The mass of the accretted He 
-layer is a concern because intermediate and 
-heavy elements synthesized in the He detonation appear will in
-the outer parts of the ejecta, which does not match observation~\citep{HoefKhok96,
+scenario \citep{ww94}. The mass of accretted He 
+is a concern because heavier
+elements synthesized in the He detonation will appear in
+the outer ejecta, which does not match observations~\citep{HoefKhok96,
 hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
@@
 The approach we employ for this study is a variation of the delayed
-detonation descibed above, the deflagration-to-detonation transition (DDT)
+detonation described above, the deflagration-to-detonation transition (DDT)
 explosion paradigm~\citep{1986SvAL,
@@
 In the DDT paradigm, the duration of the deflagration phase sets
-the amount of expansion of the star prior to the bulk of burning
-and is critical to the composition of material synthesized in the 
+the amount of expansion of the star prior to the bulk of burning,
+which is critical to the composition of material synthesized in the 
 explosion. Also, early burning during the deflagration phase is at 
@@
 
-Our simulational methododolgy is described in the next section and 
+Our simulational methodology is described in the next section and 
 our results, a comparison of nucleosynthetic explosion yields between these
@@
 differences in the yield of \Ni{56} between explosions from the two
-types of progenitors, which we quantify and disuss.
+types of progenitors, which we quantify and discuss.
 }
@@
 speed-up of laminar flames due to neutronization and thus reasonably 
-produces variations in flame speed due to composition~\cite{jacketal2010}.}
+produces variations in flame speed due to composition~\citep{jacketal2010}.}
 These laminar flame speeds are boosted to account for the speed-up 
@@
 \citet{willcoxetal2016} substantially differed from both the
-(mixed) hybrid and traditional models presented here. Those progenitors
+(mixed) hybrid models presented here and  traditional models. Those progenitors
 had the highest temperatures and hence were ignited at a radius of
@@
 for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
-{\color{blue} The sharp increase in the yield occuring after approximately 1.0 second indicates
-the transiton to the detonation phase with its significantly faster burning. The curves
+{\color{blue} The sharp increase in the yield occurring after approximately 1.0 second indicates
+the transition to the detonation phase with its significantly faster burning. The curves
 indicate that on average, the C-O-Ne models reach the DDT later then the hybrid model, 
-impling more expansion of the WD and lower density burning in the detonation phase.}
+implying more expansion of the WD and lower density burning in the detonation phase.}
 
@@
 same realizations as in Figure \ref{fig:nithybrid} The ratios for the yields of 
-explosions from hybrid progenitors are consistenly lower than the ratios of yields from
+explosions from hybrid progenitors are consistently lower than the ratios of yields from
 traditional progenitors.

### 2019-09-02 paper/ms.tex
Updated the way we do the software command upon receiving advice from the editor.

@@
 
+%\software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
+%MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
+%The Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
+%Microphysics repository at
+%  (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
+%  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$),
+%  Matplotlib (\url{http://dx.doi.org/10.5281/zenodo.44579}).
+%}
+
 \software{Flash \citep{Fryxetal00,calder.curtis.ea:high-performance,calder.fryxell.ea:on,flash_pragmatic,flash_evolution} (\url{http://flash.uchicago.edu/}), 
 MESA \citep{mesa1,mesa2,mesa3,mesa3e} (\url{http://mesa.sourceforge.net/}),
-The
-Helmholtz EOS table used in \CASTRO\ is available in the public BoxLib
+The Helmholtz EOS table used in \CASTRO\ \citep{timmes.swesty:accuracy}, Available in the public BoxLib
 Microphysics repository at
   (\url{https://github.com/BoxLib-Codes/Microphysics.git}, commit
-  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).
+  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$),
+  Matplotlib (\url{http://dx.doi.org/10.5281/zenodo.44579}).
 }

### 2019-09-23 paper/reply_to_referee.txt
Updated one of the questions based on a conversation with Don.

@@
 
+[rephrasing the question- does 20Ne count as fuel for both
+the energy release and the flame speed from the table? Don seems 
+to recall that we had the energy release of burning 20Ne in the 
+detonation tests, which says it was included for the energy 
+release. But do we just consider 12C + 12C buring for the
+flame speed?]
+
 Also, the detonation tests in Willcox et al. were tests of the
 energy release of the flame model and not flame speed tests. The 
-model identical amounts of energy for both deflagrations and 
+model releases identical amounts of energy for both deflagrations and 
 detonations in identical material, so detonation simulations were

### 2019-10-03 paper/ms.tex
fix typo.

@@
 hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
-properties assuming this scenario and our describe  methodology in 
+properties assuming this scenario and describe our methodology in
 detail below.
@@
 \citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
-scenario \citep{ww94}. The mass of accretted He 
+scenario \citep{ww94}. The mass of accreted He
 is a concern because heavier

### 2019-10-03 paper/ms.tex
add word

@@
 high enough densities that the effects of electron capture are 
-significant and similarly influence the composition the material 
+significant and similarly influence the composition of the material
 synthesized in the explosion~\citep{hoeflichetal2004,

### 2019-10-03 paper/ms.tex
word

@@
 These hybrid WDs are relevant to the supernova problem because 
-they can become the progenitors thermonuclear supernovae
+they can become the progenitors of thermonuclear supernovae
 if they are part of a binary system. If the companion star becomes

### 2019-10-03 paper/ms.tex
word

@@
 Discerning the role played by hybrid progenitors in the global gamut of
-thermonuclear is the goal of the study we present in this paper. Our simulations
+thermonuclear supernovae is the goal of the study we present in this paper. Our simulations
 provide the yields of \Ni{56} in the supernova explosions. Because

### 2019-10-03 paper/ms.tex
clarify sentence

@@
 
-Our simulational methodology is described in the next section and 
-our results, a comparison of nucleosynthetic explosion yields between these
+Our simulation methodology is described in the next section and
+our results include a comparison of nucleosynthetic explosion yields between these
 new mixed hybrid C-O-Ne progenitors and traditional C-O progenitors

### 2019-10-03 paper/ms.tex
Code->code

@@
 In particular, we use the same simulation instrument, a modified version
-of the \FLASH\ Code, as \citet{willcoxetal2016} and we refer the reader there
+of the \FLASH\ code, as \citet{willcoxetal2016} and we refer the reader there
 for a description of the process and treatment of burning of C--O--Ne fuel and how it differs from C--O fuel.

### 2019-10-03 paper/ms.tex
Reword sentence about C-O-Ne burning in Willcox+ 2016 to be more specific about what we did.

@@
 hybrid white dwarfs.
-Direct numerical simulations of combustion dynamics and details of how the burning model is used to capture them may be found in \citet{willcoxetal2016}.
+{\color{blue} Parameter studies of detonations in C-O-Ne material and details of how the burning model is used to capture C-O-Ne burning may be found in \citet{willcoxetal2016}.}
 

### 2019-10-03 paper/ms.tex
Give a few details for how we constructed the C-O WD model.

@@
 \end{figure}
-While the C-O-Ne progenitor is the result of an evolutionary calculation, the C-O progenitor is a parameterized construction, as reflected in the simplified outer thermal structure appearing in Figure~\ref{fig:init_conds}.
+{\color{blue} While the C-O-Ne progenitor is the result of an evolutionary calculation,
+the C-O progenitor is constructed by integrating the equation of hydrostatic equilibrium
+using the Helmholtz stellar equation of state of \citet{timmes.swesty:accuracy} starting
+from the central density and temperature of the C-O-Ne WD model.
+This parameterized construction is reflected in the simplified
+outer thermal structure for the C-O WD model appearing in Figure~\ref{fig:init_conds}.}
 We centrally ignite our explosion simulations for both C-O and hybrid

### 2019-10-18 paper/reply_to_referee.txt
Worked in the first of Dean's suggestions.

@@
 
-We regret no explaining the methodology of our deflagration speeds. The 
+We regret not explaining the methodology of our deflagration speeds. The 
 answer is that the deflagration speeds for input to the flame model are 
@@
 and background turbulence and passed to the flame model. We have
-updated the text of the manuscript to explain the flame speeds
+updated the text of section 2.1 to explain the flame speeds
 and included a citation to earlier work describing the tabulated
@@
 detonation tests, which says it was included for the energy 
-release. But do we just consider 12C + 12C buring for the
+release. But do we just consider 12C + 12C burning for the
 flame speed?]
@@
 evolution left before the flame would be born even with differing 
-composition. We have updated the text to better explain this issue.
+composition. We have updated the text (Section 2.2) to better explain 
+this issue.
 
@@
 
-We have added text to the manuscript and slightly re-arranged the 
-description to better explain the motivation for our choice.
+We have added text to sections 2.2 and 2.4 of the manuscript and 
+slightly re-arranged the description to better explain the motivation 
+for our choice.
 
@@
 The profiles are illustrated in Figures 2 and 9 of Willcox et al. Yet 
-another thing we have made clear in the revised manuscript.
+another thing we have made clear in the revised manuscript. In this
+case, we added text to section 2.4.
 
@@
 going to the Fe-group and then mixed. As such, the estimate we use 
-should be robust. We have added a sentence with citations and an
-additional citation to previous work verifying this approach in a variety 
-of scenaros to the paragraph.
+should be robust. We have added a sentence to this paragraph of 
+section 3 with citations and an additional citation to previous 
+work verifying this approach in a variety of scenarios to the 
+paragraph.
 
@@
 and we regret not make these clear in the introductory material. We
-have added text addressing exactly these issues.
+have added text at the end of section 1.3 addressing exactly these issues.
 

### 2019-10-18 paper/ms.tex
Worked in the first of Dean's suggestions.

@@
 produces variations in flame speed due to composition~\citep{jacketal2010}.}
+{\color{green} Using these tables, which were made for mixtures without $^{20}$Ne,
+effectively assumes that the substitution of $^{20}$Ne for $^{16}$O will not
+change the flame speeds significantly.  We consider this a reasonable
+approximation given that, in the interior of our star, $^{16}$O is still much
+more abundant than $^{20}$Ne, and that the flame propagation is largely
+dominated by turbulent effects.}
 These laminar flame speeds are boosted to account for the speed-up 

### 2019-10-18 paper/ms.tex
Added a sentence on the history of the progenitors at the suggestion of Dean.

@@
 central density, to control differences between the hybrid and traditional 
-models and thus assess the effect of the hybrid structure.
+models and thus assess the effect of the hybrid structure.}
+{\color{green}
+The central density at ignition depends on both the carbon abundance 
+and the binary history, mainly cooling time before accretion 
+\citep{Kruegeretal2012}, and so this comparison does not correspond 
+to a comparable binary scenario, but is intended as a more 
+straightforward comparison.
 }

### 2019-10-21 paper/ms.tex
Add period.

@@
 freeze-out is shown in Figure \ref{fig:compare_ratio}. The figure presents the results from the
-same realizations as in Figure \ref{fig:nithybrid} The ratios for the yields of 
+same realizations as in Figure \ref{fig:nithybrid}. The ratios for the yields of 
 explosions from hybrid progenitors are consistently lower than the ratios of yields from

### 2019-10-21 paper/reply_to_referee.txt
Added a sentence making it clear that we used the same flame speed tables as Willcox et al.
A few changes for the submission version.

@@
 
-We thank the referee for reading our manuscript and offering very
-constructive criticism and suggestions. We are in almost complete agreement
-with the referee and have modified the manuscript accordingly. We address
-our changes for each point below. As a result of our revisions, we believe 
-the manuscript is stronger and we hope it is now ready for publication.
+We thank the referee for reading our manuscript and offering
+very constructive criticism and suggestions. We are in almost
+complete agreement with the referee and have modified the manuscript
+accordingly. We address our changes for each point below, and the changes
+we made to the manuscript are in blue in the revised version. As a result
+of our revisions, we believe the manuscript is stronger and we hope it
+is now ready for publication.
 
@@
 We regret not explaining the methodology of our deflagration speeds. The
-answer is that the deflagration speeds for input to the flame model are 
-from tabulated results. Laminar flame speeds are first 
-obtained by interpolation within a
-three-dimensional table of 12C, 22Ne, and log density obtained from
-prior direct numerical simulations. Here 22Ne is uses as a proxy for
-for neutron-rich elements so the interpolated laminar flame speeds capture
-the boost due to neutronization. These laminar flame speed are
-then boosted to account for the effects of unresolved buoyancy
-and background turbulence and passed to the flame model. We have
-updated the text of section 2.1 to explain the flame speeds
-and included a citation to earlier work describing the tabulated
-flame speeds in detail.
+answer is that the deflagration speeds for input to the flame model
+are from tabulated results. Laminar flame speeds are first obtained by
+interpolation within a three-dimensional table of 12C, 22Ne, and log
+density obtained from prior direct numerical simulations. Here 22Ne is
+uses as a proxy for for neutron-rich elements so the interpolated laminar
+flame speeds capture the boost due to neutronization. We use the same
+tables that were used in Willcox et al. and previous work. These laminar
+flame speed are then boosted to account for the effects of unresolved
+buoyancy and background turbulence and passed to the flame model. We have
+updated the text of section 2.1 to explain the flame speeds and included a
+citation to earlier work describing the tabulated flame speeds in detail.
 
-[AC NOTE: CHECK THE ABOVE. The models include 20Ne. Does the above
-description properly account for that? As I recall, nothing new
-was done to the tables for the hybrid Willcox et al. models.]
-
-[rephrasing the question- does 20Ne count as fuel for both
-the energy release and the flame speed from the table? Don seems 
-to recall that we had the energy release of burning 20Ne in the 
-detonation tests, which says it was included for the energy 
-release. But do we just consider 12C + 12C burning for the
-flame speed?]
-
-Also, the detonation tests in Willcox et al. were tests of the
-energy release of the flame model and not flame speed tests. The 
-model releases identical amounts of energy for both deflagrations and 
-detonations in identical material, so detonation simulations were
-a simple check of the modifications we made to the model to
-include 20Ne in the mix.
+Also, the detonation tests in Willcox et al. were tests of the energy
+release of the flame model and not flame speed tests. The model releases
+identical amounts of energy for both deflagrations and detonations in
+identical material, so detonation simulations were a simple check of
+the modifications we made to the model to include 20Ne in the mix.
 
@@
 Again, we did not explain our methodology well. This temperature is
-very close to that required to ignite the deflagration of the
-first phase of the explosion, so the progenitor is in a ready 
-for ignition state. Yes, it is a (somewhat mildly) a function of 
-composition, but at this temperature these models have very little 
-evolution left before the flame would be born even with differing 
-composition. We have updated the text (Section 2.2) to better explain 
-this issue.
+very close to that required to ignite the deflagration of the first
+phase of the explosion, so the progenitor is in a ready for ignition
+state. Yes, it is a (somewhat mildly) a function of composition, but
+at this temperature these models have very little evolution left before
+the flame would be born even with differing composition. We have updated
+the text (Section 2.2) to better explain this issue.
 
@@
 The referee raises an interesting point about how one might perform
-these parameter studies. Indeed, a more realistic C/O progenitor as
-would be produced by MESA would be "state of the art." The parameterized
-C/O models we chose are motivated by results from stellar evolution and,
-in particular, have compositions that reflect the effect of ``simmering", 
-that is slow convective burning, in the late stages of evolution as the
-WD approaches the Chandrasekhar limit. This effect is observed as
+these parameter studies. Indeed, a more realistic C/O progenitor as would
+be produced by MESA would be "state of the art." The parameterized C/O
+models we chose are motivated by results from stellar evolution and, in
+particular, have compositions that reflect the effect of ``simmering",
+that is slow convective burning, in the late stages of evolution as
+the WD approaches the Chandrasekhar limit. This effect is observed as
 the lower C fraction interior to about r =1.2e8 cm (the solid curve
@@
 For this study we decided to use these parameterized C-O models because
-being able to construct them to match the central density and 
-temperature of the hybrid models allowed us to better control the 
-differences between the hybrid and traditional models. More realistic
-C-O models would not match the conditions of the hybrid models, and
-as we have shown in previous work, differences in density can have
-a substantial effect on the yields.
+being able to construct them to match the central density and temperature
+of the hybrid models allowed us to better control the differences
+between the hybrid and traditional models. More realistic C-O models
+would not match the conditions of the hybrid models, and as we have
+shown in previous work, differences in density can have a substantial
+effect on the yields.
 
@@
 
-Something else we could have better explained. The hybrid models in Willcox
-et al have a very different structure with the highest temperature, where
-ignition of the deflagration is expected, at a radius of about 300 km. 
-The profiles are illustrated in Figures 2 and 9 of Willcox et al. Yet 
-another thing we have made clear in the revised manuscript. In this
-case, we added text to section 2.4.
+Something else we could have better explained. The hybrid models
+in Willcox et al have a very different structure with the highest
+temperature, where ignition of the deflagration is expected, at a radius
+of about 300 km.  The profiles are illustrated in Figures 2 and 9 of
+Willcox et al. Yet another thing we have made clear in the revised
+manuscript. In this case, we added text to section 2.4.
 
@@
 
-[AC: Hmmm. I think this is not right. What to say?]
-
 The estimate of 56Ni yield does follow from assuming the NSE mix is
@@
 how all 56Ni in the simulation is calculated. 56Ni in (outer) layers
-that did not go beyond QNSE would have been synthesized by fusion 
-going to the Fe-group and then mixed. As such, the estimate we use 
-should be robust. We have added a sentence to this paragraph of 
-section 3 with citations and an additional citation to previous 
-work verifying this approach in a variety of scenarios to the 
-paragraph.
+that did not go beyond QNSE would have been synthesized by fusion going
+to the Fe-group and then mixed. As such, the estimate we use should be
+robust. We have added a sentence to this paragraph of section 3 with
+citations and an additional citation to previous work verifying this
+approach in a variety of scenarios to the paragraph.
 
@@
 These are the questions that we are exploring with this and related work,
-and we regret not make these clear in the introductory material. We
-have added text at the end of section 1.3 addressing exactly these issues.
+and we regret not make these clear in the introductory material. We have
+added text at the end of section 1.3 addressing exactly these issues.
 
@@
 model for Flash is constructed to have the same central carbon abundance.
-The central carbon abundance in the C-O model is 0.4. We have added these
-numbers to the manuscript. The mean values of C abundances were not
-calculated with the models. We could integrate the models
-to obtain a mass-weighted average, but we are not sure of the utility
-of this quantity as our results show that the yields are a sensitive
-function of the density. We prefer to just state the central C abundances
-and present the profiles as we did in Figure 1 and hope this is acceptable.
+The central carbon abundance in the C-O model is 0.4. We have added
+these numbers to the manuscript. The mean values of C abundances were
+not calculated with the models. We could integrate the models to obtain
+a mass-weighted average, but we are not sure of the utility of this
+quantity as our results show that the yields are a sensitive function
+of the density. We prefer to just state the central C abundances and
+present the profiles as we did in Figure 1 and hope this is acceptable.
 
@@
 We have substantially shortened the sections, including removing the
-Nomoto (1984) reference (good catch!). We modified both sections
-with an emphasis on just the points important to our analysis (e.g. 
-the duration of the deflagration phase and expansion).
+Nomoto (1984) reference (good catch!). We modified both sections with an
+emphasis on just the points important to our analysis (e.g.  the duration
+of the deflagration phase and expansion).
 
@@
 
-We appreciate the referee's point. The figures show the evolution of quantities 
-like 56Ni abundance with time and are similar to some of the figures showing 
-abundance evolution in Willcox et al. Because they allow the reader to both 
-visualize the scatter in the yields and also the character of the burning 
-(such as the DDT), we feel they are useful and would like to keep them. Also,
-they are similar to figures in Willcox et al, which allows comparison
-to results from another class of hybrid progenitors. We agree with the referee 
-that the discussion was scant and have improved that.
+We appreciate the referee's point. The figures show the evolution of
+quantities like 56Ni abundance with time and are similar to some of
+the figures showing abundance evolution in Willcox et al. Because they
+allow the reader to both visualize the scatter in the yields and also the
+character of the burning (such as the DDT), we feel they are useful and
+would like to keep them. Also, they are similar to figures in Willcox
+et al, which allows comparison to results from another class of hybrid
+progenitors. We agree with the referee that the discussion was scant
+and have improved that.
 
-[AC: CHECK RED TEXT IN THE CAPTION OF FIG. 6 and similar text in the description]
-
-In summary. we have taken the referee's criticism and suggestions and revised 
-the manuscript accordingly. The result is a significantly improved version we trust 
-is ready for publication.
+In summary. we have taken the referee's criticism and suggestions and
+revised the manuscript accordingly. The result is a significantly improved
+version we trust is ready for publication.

### 2019-10-21 paper/ms.tex
A few changes for the submission version.

--- 2019-10-18 paper/ms.tex
@@
 produces variations in flame speed due to composition~\citep{jacketal2010}.}
-{\color{green} Using these tables, which were made for mixtures without $^{20}$Ne,
+{\color{blue} Using these tables, which were made for mixtures without $^{20}$Ne,
 effectively assumes that the substitution of $^{20}$Ne for $^{16}$O will not
@@
 models and thus assess the effect of the hybrid structure.
+The central density at ignition depends on both the carbon abundance 
+and the binary history, mainly cooling time before accretion 
+\citep{Kruegeretal2012}, and so this comparison does not correspond 
+to a comparable binary scenario, but is intended as a more 
+straightforward comparison.
 }
@@
 for both suites of simulations. 
-{\color{red} Shown are realizations 21-30.}
+{\color{blue} Shown are realizations 21-30.}
 Results from C-O-Ne progenitors are in blue and C-O progenitors in red.

### 2019-10-24 paper/reply_to_referee.txt
Updated the sentence that describes the detonation tests of Willcox et al in the reply to the referee.

@@
 
-Also, the detonation tests in Willcox et al. were tests of the energy
-release of the flame model and not flame speed tests. The model releases
-identical amounts of energy for both deflagrations and detonations in
-identical material, so detonation simulations were a simple check of
-the modifications we made to the model to include 20Ne in the mix.
+Also, the detonation tests in Willcox et al. were tests that the
+addition of 20Ne did not alter the four-stage structure assumed by
+the flame model. The ZND detonations indicated that the burning still
+proceeds through four main stages of burning distinguished by "steps"
+in the density/pressure profiles behind the ZND shock corresponding to
+mass fraction crossing times for fuel->ash, ash->NSQE, NSQE->NSE. This
+justified the minimal modification to the burning in FLASH where
+we included 20Ne in the initial composition and included its energy
+generation assuming 20Ne burns to 24Mg.
 

### 2019-10-25 paper/ms.tex
Quick update to fix W16

--- 2019-10-21 paper/ms.tex
@@
 hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
-properties assuming this scenario and describe our methodology in
+properties assuming this scenario and our describe  methodology in 
 detail below.
@@
 \citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
-scenario \citep{ww94}. The mass of accreted He
+scenario \citep{ww94}. The mass of accretted He 
 is a concern because heavier
@@
 high enough densities that the effects of electron capture are 
-significant and similarly influence the composition of the material
+significant and similarly influence the composition the material 
 synthesized in the explosion~\citep{hoeflichetal2004,
@@
 These hybrid WDs are relevant to the supernova problem because 
-they can become the progenitors of thermonuclear supernovae
+they can become the progenitors thermonuclear supernovae
 if they are part of a binary system. If the companion star becomes
@@
 Discerning the role played by hybrid progenitors in the global gamut of
-thermonuclear supernovae is the goal of the study we present in this paper. Our simulations
+thermonuclear is the goal of the study we present in this paper. Our simulations
 provide the yields of \Ni{56} in the supernova explosions. Because
@@
 
-Our simulation methodology is described in the next section and
-our results include a comparison of nucleosynthetic explosion yields between these
+Our simulational methodology is described in the next section and 
+our results, a comparison of nucleosynthetic explosion yields between these
 new mixed hybrid C-O-Ne progenitors and traditional C-O progenitors
@@
 In particular, we use the same simulation instrument, a modified version
-of the \FLASH\ code, as \citet{willcoxetal2016} and we refer the reader there
+of the \FLASH\ Code, as \citet{willcoxetal2016} and we refer the reader there
 for a description of the process and treatment of burning of C--O--Ne fuel and how it differs from C--O fuel.
@@
 produces variations in flame speed due to composition~\citep{jacketal2010}.}
-{\color{blue} Using these tables, which were made for mixtures without $^{20}$Ne,
-effectively assumes that the substitution of $^{20}$Ne for $^{16}$O will not
-change the flame speeds significantly.  We consider this a reasonable
-approximation given that, in the interior of our star, $^{16}$O is still much
-more abundant than $^{20}$Ne, and that the flame propagation is largely
-dominated by turbulent effects.}
 These laminar flame speeds are boosted to account for the speed-up 
@@
 hybrid white dwarfs.
-{\color{blue} Parameter studies of detonations in C-O-Ne material and details of how the burning model is used to capture C-O-Ne burning may be found in \citet{willcoxetal2016}.}
+Direct numerical simulations of combustion dynamics and details of how the burning model is used to capture them may be found in \citet{willcoxetal2016}.
 
@@
 \end{figure}
-{\color{blue} While the C-O-Ne progenitor is the result of an evolutionary calculation,
-the C-O progenitor is constructed by integrating the equation of hydrostatic equilibrium
-using the Helmholtz stellar equation of state of \citet{timmes.swesty:accuracy} starting
-from the central density and temperature of the C-O-Ne WD model.
-This parameterized construction is reflected in the simplified
-outer thermal structure for the C-O WD model appearing in Figure~\ref{fig:init_conds}.}
+While the C-O-Ne progenitor is the result of an evolutionary calculation, the C-O progenitor is a parameterized construction, as reflected in the simplified outer thermal structure appearing in Figure~\ref{fig:init_conds}.
 We centrally ignite our explosion simulations for both C-O and hybrid
@@
 models and thus assess the effect of the hybrid structure.
-The central density at ignition depends on both the carbon abundance 
-and the binary history, mainly cooling time before accretion 
-\citep{Kruegeretal2012}, and so this comparison does not correspond 
-to a comparable binary scenario, but is intended as a more 
-straightforward comparison.
 }
@@
 for C-O-Ne progenitors (blue) and C-O progenitors (red) at
-$t = 4.0 \second$.  Lines indicate corresponding relations found in W16 with
+$t = 4.0 \second$.  Lines indicate corresponding relations found in 
+\cite{willcoxetal2016} with
 a lower central density and C-O-Ne progenitor whose interior is not mixed
@@
 for both suites of simulations. 
-{\color{blue} Shown are realizations 21-30.}
+{\color{red} Shown are realizations 21-30.}
 Results from C-O-Ne progenitors are in blue and C-O progenitors in red.

### 2019-10-27 paper/ms.tex
Tiny formating issue- removed a space.
Took at the blue

@@
 
-{\color{blue}
 \subsection{Proposed Progenitor Settings}\label{sec:progenitors}
@@
 hoeflich2006,fesenetal2007,diamondetal2018}.
-}
 
@@
 
-{\color{blue} 
 Discerning the role played by hybrid progenitors in the global gamut of
@@
 types of progenitors, which we quantify and discuss.
-}
 
@@
 thermonuclear burning.
-{\color{blue}
 The flame speeds are obtained via linear interpolation within a 
@@
 speed-up of laminar flames due to neutronization and thus reasonably 
-produces variations in flame speed due to composition~\citep{jacketal2010}.}
-{\color{blue} Using these tables, which were made for mixtures without $^{20}$Ne,
+produces variations in flame speed due to composition~\citep{jacketal2010}.
+Using these tables, which were made for mixtures without $^{20}$Ne,
 effectively assumes that the substitution of $^{20}$Ne for $^{16}$O will not
@@
 more abundant than $^{20}$Ne, and that the flame propagation is largely
-dominated by turbulent effects.}
+dominated by turbulent effects.
 These laminar flame speeds are boosted to account for the speed-up 
@@
 hybrid white dwarfs.
-{\color{blue} Parameter studies of detonations in C-O-Ne material and details of how the burning model is used to capture C-O-Ne burning may be found in \citet{willcoxetal2016}.}
+Parameter studies of detonations in C-O-Ne material and details of how the burning model 
+is used to capture C-O-Ne burning may be found in \citet{willcoxetal2016}.
 
@@
 $\log T_{\rm c}(\Kelvin) = 8.9$, 
-{\color{blue} 
 at which point the 
@@
 the first stage of the explosion. The central \C{12} mass fraction 
-of the model is 0.1419.}
+of the model is 0.1419.
 
@@
 model (e.g.\  the two shared the same central temperature and density).  
-{\color{blue} 
 The central \C{12} mass fraction of this model is 0.4.
-}
 Figure~\ref{fig:init_conds} shows the density and temperature
@@
 \end{figure}
-{\color{blue} While the C-O-Ne progenitor is the result of an evolutionary calculation,
+While the C-O-Ne progenitor is the result of an evolutionary calculation,
 the C-O progenitor is constructed by integrating the equation of hydrostatic equilibrium
@@
 This parameterized construction is reflected in the simplified
-outer thermal structure for the C-O WD model appearing in Figure~\ref{fig:init_conds}.}
+outer thermal structure for the C-O WD model appearing in Figure~\ref{fig:init_conds}.
 We centrally ignite our explosion simulations for both C-O and hybrid
@@
 were compared to a suite of supernova simulations from traditional C-O 
-progenitors. {\color{blue} The C-O progenitors are parameterized and 
+progenitors. The C-O progenitors are parameterized and 
 include the effects of convective ``simmering" in the core as the WD 
@@
 straightforward comparison.
-}
 
@@
 yield from \SNeIa\ \citep{townetal2009}.
-{\color{blue} We note that the ignition points of the hybrid models of 
+We note that the ignition points of the hybrid models of 
 \citet{willcoxetal2016} substantially differed from both the
@@
 had the highest temperatures and hence were ignited at a radius of
-about 300 km.}
+about 300 km.
 
@@
 estimated from the $Y_e$ tracked by the burning model. 
-{\color{blue}
 This process has been shown to provide estimated \Ni{56} yields consistent with
 the results of detailed network and NSE calculations~\citep{townetal2016,caldertownsley2018}.
-}
 
@@
 for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
-{\color{blue} The sharp increase in the yield occurring after approximately 1.0 second indicates
+The sharp increase in the yield occurring after approximately 1.0 second indicates
 the transition to the detonation phase with its significantly faster burning. The curves
 indicate that on average, the C-O-Ne models reach the DDT later then the hybrid model, 
-implying more expansion of the WD and lower density burning in the detonation phase.}
+implying more expansion of the WD and lower density burning in the detonation phase.
 
@@
 for both suites of simulations. 
-{\color{blue} Shown are realizations 21-30.}
+Shown are realizations 21-30.}
 Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
 %SAME AS DON'S FIGURE 19
-}
 \end{figure}
@@
 
-{\color{blue} 
 The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
@@
 C-O and C-O-Ne cases.
-}
 

### 2019-12-01 paper/ms.tex
Fixed a redundant citation caught by the ApJ.

@@
 by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
-wheelerharkness1990conf,Fili97}, with the type Ia designation following from
+wheelerharkness1990conf,filippenko:optical}, with the type Ia designation following from
 the absence of H in the spectrum and the presence of a specific Si

### 2019-12-02 paper/ms.tex
Updated the manuscript a tad to reflect the things the editors caught. Probably not needed, but it might be helpful.

@@
 explosion mechanism.
-Some of their models are similar to those of \citep{denissenkovetal2015} and
+Some of their models are similar to those of \citet{denissenkovetal2015} and
 they report that many models produce less synthesized
@@
 the yield of \Ni{56} serves as a proxy for brightness of the event so
-our estimates allows us to discern trends in brightness. Our study thus 
+our estimates allow us to discern trends in brightness. Our study thus 
 can offer insight into the relative brightness of explosions from these
@@
 Electron capture also influences the evolution in several ways by
-neutronizing the material, which produces more neutron rich iron-group
+neutronizing the material, which produces more neutron-rich iron-group
 material at the expense of \Ni{56}. Neutronization also shifts the binding
@@
 selected the 1.09 \Msun\ WD model 
-with the 0.4 \Msun\ C/O core from \citep{brooksetal2017}.
+with the 0.4 \Msun\ C/O core from \citet{brooksetal2017}.
 In order to grow this WD towards the Chandrasekhar mass, it was inserted into 
@@
 the expanding star reaches low densities at which point burning
-effectively ends. This section provide details
+effectively ends. This section provides details
 of the implementation of this method.
@@
 a different randomly-seeded perturbation was applied to the
-match head for each of the 30 simulations in both suites,
+match head for each of the 30 simulations in both suites.
 The perturbation to the sphere's surface is a set of
@@
 is parameterized by the fuel density $\rho_{\mathrm{DDT}}$.
-When a rising plume reaches the threshold density, in this case $\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$, a $12$~\km\ radius region of fuel, is fully burned $32$~\km\ radially outwards from the flame.
+When a rising plume reaches the threshold density, in this case $\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$, a $12$~\km\ radius region of fuel is fully burned $32$~\km\ radially outwards from the flame.
 This
@@
 greater IGE yields.
-This is because less expansion allows the detonation to consume more high density fuel, which is burned more completely \citep[See discussion in][and references therein]{SeitenzahlTownsley2017}.
+This is because less expansion allows the detonation to consume more high-density fuel, which is burned more completely \citep[See discussion in][and references therein]{SeitenzahlTownsley2017}.
 At moderate expansion, where the mass at high density is between around 1.0 to 1.1 M$_\odot$, our C-O models tend to yield greater IGE mass.
@@
 
-As mentioned above, we describe the results principally in term of the
+As mentioned above, we describe the results principally in terms of the
 yield of the \Ni{56}, a proxy for brightness.  Our first conclusion
@@
 the lower \C{12} abundance in the hybrid models and the fact that \Ne{20}-rich fuel burns to cooler 
-temperatures than the fuel in traditional C-O models, which. results in slower burning and thus a lower
+temperatures than the fuel in traditional C-O models, which results in slower burning and thus a lower
 overall IGE yield. Our yields from explosions from the mixed progenitors did not
